### 2020-08-08 Analysis/Code/Paper.Rmd
Initial commit.

---
 title: |
   | Consumer Reviews and Product Discounts:
   | Evidence From Video Games

 author: "Dmitry Sorokin"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
 output:
  pdf_document:
    keep_tex: true
    fig_height: 2.5
    fig_width: 6
    number_sections: true
    citation_package: natbib
    extra_dependencies:
       footmisc: ["bottom"] # footnote management
       setspace: ["doublespacing"] # spacing of the paper
       caption: ["tableposition=top"]
       dsfont: null # indicator function 1
       booktabs: null
       makecell: null
    includes:
       in_header: extra_header.tex

 bibliography: reviewsBib.bib
 fontsize: 12pt
 geometry: margin=1in
 link-citations: true
 linkcolor: mypink
 filecolor: myblue
 citecolor: mypink
 urlcolor: mypink
---

```{r cache = F}
source(here("Analysis", "Code", "StructuralFunctions.R"))
load(here("Analysis", "Input", "info.Rda"))
load(here("Analysis", "Input", "panel.Rda"))
```

# Introduction

# Literature Review

This paper contributes to several closely related literatures in economics and marketing. The oldest of these is the literature investigating the impact of online consumer reviews on sales. An extensive review of the studies focusing on this topic and their meta-analysis is provided, for example, by @Floyd14. 
<!-- Researchers have analyzed multiple online platforms, selling different products and employing different review systems, and produced, overall, conflicting evidence on whether reviews improve sales, and if so, through which channels. The major identification challenge stems from the fact that better reviews might simply be manifestations of consumer preferences for certain products, or reflect higher quality of the underlying products. As preferences and quality are unobserved and, in general, fluid, researchers have struggled to come up with convincing identification strategies. -->
In a seminal contribution in this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales. A similar approach applied to the same market was recently used by @ReimersWaldfogel20, who reaffirm the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews. @ZhuZhang10 exploit differences between two different video games consoles rather than websites, and find that review ratings matter only for less popular games.

For identification, the difference-in-differences approach relies on the existence of several comparable platforms, and assumes that the unobserved platform-specific tastes
for those platforms are fixed. Another approach to identification exploits the rounding of the review data that platforms use to produce simple visual review labels. For example, Yelp.com, a popular restaurant comparison service, assigns 4 stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but 4.5 stars to restaurants with an average score between 4.25 and 4.74.  @AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue. @SorokinStevens20 applies a similar approach to the video games market and also finds that better review labels increase sales, albeit raising some concerns about the validity of the approach. In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from the video games' usage data. The present paper supplements the panel methods in @SorokinStevens20 by offering a structural way to estimate the effect of reviews on sales in the absence of direct sales data.

With benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits. There are several ways firms can affect their online reviews. One is review fraud. @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves. @LucaZervas16 provide similar evidence for restaurants on Yelp. A more honest way for a firm to influence reviews is by assuming an active approach to review management, and to publicly respond to reviews published online. @GuYe14 provide evidence that consumers who had left a negative review about their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management. @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future. This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes. In somewhat contradictory findings, @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to, while @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity, because consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.

Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews. Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle. Another strand of literature is studying whether different kinds of promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a Groupon price promotion. They present evidence that customers attracted by the promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher, which can explain the reasons behind their dissatisfaction. Thus, the paper cautions against running price promotions in an attempt to poach new customers and improve the online reputation. @Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews. In an experimental study on Ebay, @CabralLi15 also find that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and they provide evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.

The present study contributes to this literature by providing novel evidence from a new market. I show that customers buying computer games are significantly more likely to leave positive reviews during discounts. More importantly, I go beyond the descriptive nature of the other papers in the literature, and show that firms leverage this fact to improve their reviews by giving discounts, thus providing evidence of a novel reputation management behavior. A study similar in spirit to mine is that of @Zegners17, who argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap". However, this study also finds that books are more likely to solicit negative feedback when sold for free, which somewhat undermines the strategy. Similar to @ByersEtAl12, @Zegners17 argues that purchasers of free books differ from the purchasers of regular books in their observable characteristics, and explains the negativity of the reviews by the selection effect.

# Institutional Setting and Data

## Steam Marketplace

Steam is arguably the largest online marketplace for selling computer games in the world. Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it has earned around US\$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames]. Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion 
in 2018, about the size of the U.S. film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD], Steam is a major player in an increasingly more important industry. Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to be studied in its own right.

Any user who has a copy of a game on Steam can leave a review for that game. Starting from late 2016, by default, Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer). This distinguishes Steam from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews). This gives me confidence in the authenticity of most reviews. This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors. With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave scrupulously.

A review consists of a binary grade, "thumbs up" or "thumbs down", and review's text. A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews. Based on the score, Steam assigns *review labels*, or bins, to each game. These labels\footnote{There are labels worse than "Negative", but they are rare, so I bin all of them into "Negative"} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}. For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.

```{r}
tab <- data.table(`Review Bin` = c("No Score", "Negative", "Mixed", "Mostly Positive", 
                                   "Positive", "Very Positive", "Overwhelmingly Positive"),
                  `N. of Reviews` = c("[0, 10)", "Any", "Any", "Any", "[0, 50)", 
                                          "More than 50", "More than 500"),
                  `Score` = c("-", "[0, 40)", "[40, 70)", "[70, 80)", "[80, 100)",
                              "[80, 100)", "[95, 100]"))
kable(tab, "latex",
      label = "ReviewBinsTable",
      caption = "The mapping between the review score and review bins on Steam",
      align = c('l', "c", "c"),
      valign = 't',
      linesep = "",
      booktabs = T)
```

Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc. [@steamVisibility]. A customer could either click on the games already presented to her, or browse one of the categories that Steam offers. Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support). Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}. From that list the user can get some basic information about each game, such as its name, price, and if the game is currently on a discount. Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has. I use this feature of the Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main independent review variables, rather than, say, the review score or the review texts. Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place. Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales. Crucially, according to Steam's documentation, all review labels better than “Negative“ have a very similar contribution to visibility on the platform, which means, for example, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2]. Therefore, any effect of the review labels on, say sales, should come through the perceived quality differences between different bins, rather than some mechanical visibility differences. As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.

 ```{r fig.cap='\\label{steamStore}Example Browsing Session on Steam', out.width="75%", fig.align="center"}
 knitr::include_graphics(here("Analysis", "Output", "Paper_files", "figure-latex", "steamStore.pdf"))
 ```

## Data

Valve Corporation, the owner of Steam, is notoriously secretive about its data and algorithms. Given the importance of the information on the performance of different games for game developers and publishers, the community has responded to this secrecy by establishing projects that monitor Steam in real time and extract  information that could be relevant for parties interested in Steam. The majority of data used in this project comes from one such project called “Steam Database”, or “SteamDB”.

Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB. More importantly, Steam Database offers a daily time series of prices and player activity for each game on Steam. In principle, the pricing information could be obtained by a repeated scraping of the store. However, the player activity information is not trivial to obtain, as Steam does not directly reveal such data, let alone the data on sales of different titles. The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community most certainly implies that they are doing the best they can. The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent player for each game on a daily basis. In other words, if on a particular day 10 people play the game every hour, except noon, when 13 people play the game simultaneously, then the recorded player count for this game on that day will be 13. The price and the player count time series are the major “dynamic” variables used in the analysis. The last dynamic variable, namely the evolution of the review score for each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the path of the review score.

```{r example-game, fig.cap='\\label{exampleGame} An Example Game in the Sample: Player Count, Price, and Review Score Histories.', fig.height = 5}
plotGame(589530)
```

Steam is home to more than 25,000 games that differ in their genres, prices, sales, release dates, frequency of updates, and other characteristics. Inevitably, an appropriate sample should be selected for the analysis. @SorokinStevens20 studies the causal effect of reviews on sales on Steam, and I mirror closely the sample selection procedure used in that paper. First, Steam has made some significant changes to its review system in late 2016, and one of the effects was the removal of the a big number of reviews from the review score calculation. While it could be an intervention that is worthy of an independent study, in practice combining the data from before and after the intervention led to unsound results, so I focus on the two year period from January 2017 to January 2019, keeping the review system as stable as possible. In particular, only games that were released in this time period make it to the sample.

Second, online multiplayer games and games that update frequently are dropped from the sample, as these are products whose quality is changing a lot over time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience. Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}. Unobserved quality would present a big obstacle to the identification of the effect of reviews on pricing decisions or sales, because, say, a game that has just issued a major update might both upgrade to a better review label (because of the positive reception of the new content) and give a big discount to rekindle the interest of the players, but the discounting decision would not be influenced by the review transition. For the same reasons, I also drop free games and games that are released in a beta-version (the so called “Early Access” program), as these products are likely to be adding new content, and the update history is not a perfect way to monitor the updating activity. Finally, I drop few games with a player count of less than four on their median day, as these games are simply very small, and the quality of their player count data is questionable.

## Sample Description

The final sample includes `r info[, .N]` games which I observe for `r panel[, max(age), by = ID][, round(mean(V1))]` days each, on average. The main variables in the analysis are the aforementioned dynamic variables: player count, price, and review score history. An example observation from the sample is given in Figure \ref{exampleGame}. For the majority of the games in the sample, the player count is the highest around the release date, and then it quickly fades away and oscillates around a smaller level. The player count also jumps when a discount is given, reflecting the influx of new players. Games differ a lot in their sizes, as is evident from Figure \ref{sampleSizeHist}.

```{r sample-size-hist, fig.cap='\\label{sampleSizeHist} Distributions of the Player Count on, and the Number of Reviews Accumulated by, the Age of 180 Days.'}
p1 <- ggplot(data = panel[age==180, .(x = log(number))]) +
  geom_histogram(mapping = aes(x = x, y = ..density..), 
                 color = "black", 
                 position = "identity", 
                 alpha = 0.9,
                 binwidth = 0.5,
                 boundary = 0,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x), 
                 color = "black", 
                 position = "identity", 
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Log Players",
                     breaks = seq(0, 8),
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL, 
                     minor_breaks = NULL) +
  my.theme()

p2 <- ggplot(data = panel[age==180, .(x = log(reviews))]) +
  geom_histogram(mapping = aes(x = x, y = ..density..), 
                 color = "black", 
                 position = "identity", 
                 alpha = 0.9,
                 binwidth = 0.5,
                 boundary = 0,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x), 
                 color = "black", 
                 position = "identity", 
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Log Reviews",
                     breaks = seq(0, 8),
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL, 
                     minor_breaks = NULL) +
  my.theme()

ggarrange(p1, p2, ncol = 2, nrow = 1, align = "h")
```

```{r sample-size-hist-vert, include=FALSE}
# for beamer
ggarrange(p1, p2, ncol = 1, nrow = 2, align = "h")
```

As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is important. A representative game in the sample never changes its price, but instead occasionally goes on discounts, slowly increasing their magnitude as the game ages. There are
`r panel[discount==F, diff(price), by = ID][V1>0, .N]` incidents of price change in the data, compared to 
`r panel[discNew==T, .N]` discounts. Steam has a number of rules that regulate price promotions on its platform. A game can have a launch discount, but, otherwise, it has to wait for two months since the release before changing its price or giving a discount. A game can not go on discounts too frequently, and has to wait between four to six weeks
after a price promotion to be able to run a new one. The duration of a custom discount is restricted to be at least one full day, and at most two weeks. Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on a discount. As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”. Curated promotions are featured prominently on Steam's main page, and, arguably, lead to more visibility and sales for the participating titles than custom discounts, which also contribute to visibility, but typically do not get the front-page promotional slots. An important type of curated discounts are the so-called “Seasonal Sales”--big platform-wide events that take place about four times a year around major holidays. Figure \ref{seasonalSales} shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving). Around `r  round(panel[discSeason==T & discNew == T, .N]/panel[discNew==T, .N]*100)`% of discounts in the sample go live during a Seasonal Sale. Thus, firms have significant agency when it comes to running price promotions, but platform regulations and platform-wide discounts are important determinants of firms' decision to discount.

```{r seasonal-sales, fig.cap='\\label{seasonalSales} Fraction of Games in the Sample Running a Promotion.'}
months1 <- c(-1, 30, 58, 89, 119, 150, 180, 211, 242, 272, 303, 333) + 1
months2 <- c(333 + 32 + months1, 699 + 31)
ggplot(data = panel[, .(y=sum(discount > 0)/(.N)), by = t]) +
  # ggtitle() +
  geom_line(aes(x = t, y = y),
            color = my.colors[1],
            size = 1) +
  scale_x_continuous(name = NULL,
                     breaks = c(months1, months2)[seq(1,25,3)], 
                     labels = months(getDate(c(months1, months2))[seq(1,25,3)], 
                                     abbreviate=T),
                     minor_breaks = NULL) +
  scale_y_continuous(name = "Fraction of Games",
                     minor_breaks = NULL)  +
  my.theme(leg.x = 0.25, leg.y = 0.9)
rm(months1, months2)
```

The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly. Recall that the review score is just the fraction of the positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in. Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release. On average across games, the standard deviation of the review score (out of one hundred) is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`, with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that. The score is only assigned once the game reaches 10 reviews, and once can see that 10 reviews is enough on average keep the score stable. The distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, is, then, representative of the situation at other ages.

```{r review-descriptive-plots, fig.width = 6.5, fig.cap='\\label{reviewDescriptivePlots} Distribution of Games by Review Bins and the CDF\'s of Review Arrival Times by Quintiles at 180 Days.'}
# Histogram of the bin distribution at the age of 180 days
labls <- c("No Score", "Negative", "Mixed", "M. Positive", "Positive", "V. Positive", "Ov. Positive")
short.labls <- c("N/S", "Neg", "Mix", "M.Pos", "Pos", "V.Pos", "Ov.Pos")
nGroups <- 3
p1 <- ggplot(data = panel[age==180, 
                    .(`Review Bin` = factor(labls[1*noScore + 2*negative + 3*mixed + 4*mPositive + 
                                                  5*realPositive + 6*vPositive + 7*ovPositive],
                      levels = labls, labels = short.labls)
                      )]) +
  geom_bar(mapping = aes(x = `Review Bin`, 
                         y = ..prop.., group=1), 
                 color = "black", 
                 alpha = 0.9,
                 fill = my.colors[1]) +
  scale_y_continuous(name = "Frequency") +
  my.theme()

# Arrival of reviews relative to the number accumulated at 180 days, by quintiles
# Assign a number to each game that measures the number of full months it has
# spent in the sample
panel[, ageGroup:=age%/%30][, ageGroup:=rep(max(ageGroup), .N), by = ID]
M <- panel[, max(ageGroup)]
# Create an auxilary table that for every age (in months) takes games that have
# been present for that many months, and then splits those games into 10 groups,
# based on the amount of reviews they had at that age.
f <- data.table(age=integer(), sizeGroup=integer(), ID=integer())
for(m in 1:M){
  f<-rbindlist(list(f,
                    panel[ageGroup>=m&age==30*m, 
                          .(age, sizeGroup=ecdf(reviews)(reviews), ID)
                          ][, sizeGroup:=cut(sizeGroup,nGroups,labels=seq(1:nGroups))]),
               use.names=TRUE)
}
setkey(f, age, sizeGroup, ID)

# Create a table that has data on averaged arrivals of reviews.
# arrival[month==M & size==G, .(age, fracRev)]
# returns a data table of length (30M+1) (all months have 30 days except the first one),
# where fracRev shows the fraction of total reviews an average game has accumulated by that day.
arrival <- data.table(month=integer(), size=integer(), age=integer(), fracRev=double())
for(a in f[, unique(age)]){
  for(size in 1:nGroups){
    ids <- f[age==a & sizeGroup==size, ID]
    arrival<-rbindlist(list(arrival,
             panel[ID%in%ids & age<=a, .(month=a%/%30,size=size,age,
                                         freq=reviews/max(reviews)),
             by=ID][, .(fracRev=mean(freq,na.rm=T)), by=c("month","size","age")]),
             use.names=TRUE)
  }
}
rm(a,ids,size,M,f)

p2 <- ggplot(data=arrival[month==6, ]) +
  geom_line(aes(x=age, y=fracRev, color=factor(size)),
            size=1) +
  scale_x_continuous(name = "Age (Days)",
                     breaks = seq(0,180,30),
                     minor_breaks = NULL) +
  scale_y_continuous(name = "% Of Reviews") +
  scale_color_manual(values = my.colors,
                     name = "Tercile: ") +
  my.theme(leg.x = 0.8, leg.y = 0.4) +
   theme(legend.direction = "vertical")
rm(arrival)

ggarrange(p1, p2, ncol = 2, nrow = 1, align = "h")
```

```{r}
transitions <- panel[, .(t, neg=c(NA, diff(negative)),
                    mix=c(NA, diff(mixed)),
                    mpos=c(NA, diff(mPositive)),
                    pos=c(NA, diff(realPositive)),
                    vPos=c(NA, diff(vPositive)),
                    ovPos=c(NA, diff(ovPositive)),
                    negative, mixed, mPositive, realPositive,
                    vPositive, ovPositive), by=ID]
transitions <- transitions[neg ==-1 | mix ==-1 | 
                           mpos == -1 | pos == -1 | 
                           vPos == -1 | ovPos == -1, ]
transitions[neg==-1, origin := "Negative"]
transitions[mix==-1, origin := "Mixed"]
transitions[mpos==-1, origin := "M. Positive"]
transitions[pos==-1, origin := "Positive"]
transitions[vPos==-1, origin := "V. Positive"]
transitions[ovPos==-1, origin := "Ov. Positive"]
transitions[, origin := factor(origin, 
                               levels = labls[-1],
                               labels = labls[-1],
                               ordered = T)]
setkey(transitions, ID, t)
transitions[, trID := (1:length(t)), by = ID]
setkey(transitions, ID, t, trID)
# separate good transitions from bad transitions
transitions[, goodTr := F]
transitions[neg==-1 | (mix==-1 & neg!=1) | (mpos == -1 & mix != 1 & neg!= 1) |
            (pos==-1 & (vPos==1 | ovPos==1)) | (vPos==-1 & ovPos == 1), goodTr := T]

transitions[, dur := shift(t,-1) - t, by = ID]
```

Despite the relative rigidity of the review score, there is enough transitions between the review bins to make the analysis of pricing decisions by firms around such transitions possible. Table \ref{tab:transitionMatrix} describes the transitions between review bins in the sample. The number of unique games that have changed review labels in the data is `r transitions[, unique(ID)] %>% length`, and the number of transitions is `r transitions[, .N]`. Sometimes games switch their bins briefly, and go back soon after. The number of transitions that led to the game spending at least 7 days in the new bin is `r transitions[(is.na(dur) | dur >= 7), .N]`. Table \ref{mDiscountTable} describes the state of the games in the two weeks before their transitions. Discounting  does take place before the transitions, games transition at very different ages, but tend to have only a limited number of reviews by the time their review bin changes.

```{r}
kable(
   cbind(
      transitions[, .(
         Neg = round(100*mean(negative)),
         Mix = round(100*mean(mixed)), 
         `M. Pos` = round(100*mean(mPositive)), 
         Pos = round(100*mean(realPositive)),
         `V. Pos` = round(100*mean(vPositive)),
         `Ov. Pos` = round(100*mean(ovPositive))),
         keyby=origin][,` `:=origin][,-c("origin")],
      transitions[, .(
         Neg = sum(negative),
         Mix = sum(mixed),
         `M. Pos` = sum(mPositive),
         Pos = sum(realPositive),
         `V. Pos` = sum(vPositive),
         `Ov. Pos` = sum(ovPositive)),
         keyby=origin][,-c("origin")]),
      format = "latex",
      label = "transitionMatrix",
      caption = "Transition Probability And Count Matrices",
      align = c('c', "c", "c", "c", "c", "c", "c"),
      valign = 't',
      linesep = "",
      booktabs = T) %>%
add_header_above(c("Probabilities" = 6, " ","Counts" = 6)) %>%
kable_styling(latex_options = c("scale_down"))
```

```{r results='asis'}
transPanel <- transitions[(is.na(dur) | dur >= 7), 
                          .(time = t + seq(-14,14),
                            tToTransit = seq(-14,14),
                            trID, goodTr),
                 by = c("ID","t")] %>% unique()
transPanel[, t := NULL]
setnames(transPanel, old = "time", new = "t")
transPanel <- merge(transPanel, panel[,.(ID, t, age, discount, discNew, tWODisc, reviews, score, noScore, negative, mPositive, positive, realPositive, vPositive, ovPositive, day, week)], by = c("ID","t"))
setkey(transPanel, "ID", "t", "trID")

transPanel[, discount := discount*100]
transPanel[, tToTransitNeg := tToTransit * (tToTransit < 0)]
transPanel[, tToTransitPos := tToTransit * (tToTransit >= 0)]

stargazer(
   transPanel[tToTransit<0, .(
      `Mean Discount (%)` = mean(discount),
      `Age` = round(mean(age)),
      `Reviews` = round(mean(reviews))), 
      by = c("ID", "trID")][, -c("ID", "trID")],
         title = "Average Discount, Age, and Review Count Two Weeks Before A Transition",
         label = "mDiscountTable",
         omit.summary.stat = c("min", "max"),
         header = F,
         digits = 0)
```

```{r transition-discount-plot, fig.cap='\\label{discountsTransitions} Discounting By Games Around The Transition.'}
ggplot(data=transPanel[, .(x=tToTransit, y=100*(discount>0),
                           g=factor(goodTr))],
       aes(x=x, y=y)) +
   geom_vline(xintercept = 0, linetype = "longdash", size = 0.2) +
   aes(color=g) + 
   stat_summary(fun.data = mean_se,
               #color = my.colors[1:2],
               size=0.4) +
   geom_smooth(#color=my.colors[3],
              size=0.6, se = F) +
   scale_x_continuous(name = "Days After Transition",
                     breaks = seq(-14, 14, 2),
                     minor_breaks = NULL) +
   scale_y_continuous(name = "% Of Games Discounting", ) +
   scale_color_manual(labels = c("Bad", "Good"),
                      name = "Transition",
                      values = my.colors) +
   my.theme(leg.x = 0.78, leg.y = 0.82)
```

```{r, include=F}
reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos + 
              + noScore + negative + mPositive + realPositive + vPositive + ovPositive +
              log(reviews) + age + poly(tWODisc, degree = 2) + day + week, data = transPanel)
cov<-vcovHC(reg1)
se1 <- sqrt(diag(cov))

star.out.transitions <- stargazer(reg1,
          label = "transitionReg",
          table.placement = "hp",
          header = FALSE,
          title = "Discounts In The Days Around Transition",
          se=list(se1),
          #column.labels=c(),
          dep.var.labels = c("Discount Probability"),
          covariate.labels = c("Days to Transition", "Days After Transition", "No Score", 
                               "Negative", "Mostly Positive", "Positive", "Very Positive",
                               "Ov. Positive", "Log Reviews", "Age", "Const"),
          model.numbers = F,
          omit = c("day", "week", "tWODisc"),
          omit.stat=c("f","adj.rsq","ser"),
          no.space=T)
```

# Descriptive Evidence

In this section I present evidence that firms use discounting to manage their online reputation, in particular, by running price promotions when they are close to improving their review label. For now, let us resort to a very simplistic story of why a firm would be interested in doing that. Assume that discounts increase the inflow customers, and that more customers means more reviews. Also, take for granted, for now, that better review labels improve sales. Then, if a firm is one positive review away from upgrading its review label, it might be tempted to speed things up by giving a discount. Similarly, a product that is close to sliding into a worse review bin, could be tempted to run a price promotion, in order to avoid a slump in its reviews. I will address this story in more detail in the discussion part of this section, but for now I turn attention to simply establishing that this sort of behavior indeed takes place in the sample.

The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels are very often preceded by discounts. The graph shows that two weeks prior to a transition only 15% of games were on a discount, a number close to the sample average, but that this number more than doubles to around 35% one day before the label change. Regression analysis controlling for review label, number of reviews, age, day of the week and week time effects, as well as time since the previous discount, confirms that the association depicted in Figure \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in the Appendix). A game is approximately `r round(reg1$coefficients[2]*14*100)` pp more likely to be on a discount on the day of the transition than it is two weeks prior to it, and it is `r round(-reg1$coefficients[3]*14*100)` pp less likely to be on a discount two weeks following the transition. Given that the probability for a game to be on a discount on a random day is `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% in the sample, these effects amount to `r round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% and `r round(100*(-reg1$coefficients[3]/panel[, mean((discount > 0), na.rm=T)]))`% changes in the daily probability of a discount, which is quite sizable.

Of course, this finding simply shows a correlation between firms' discounting behavior and review transitions. The same pattern could emerge if the causality between the two variables is reversed, i.e. the discounts cause transitions, and not the other way around. Imagine a hypothetical world in which games are only bought on discounts. In this world any action in the data would be preceded (and, to some extent, caused) by a discount. In other words, firms could be giving discounts for reasons unrelated to reviews, but transitions sometimes would follow as a result. As a matter of fact, suppose that the story I am after is true, and that firms try to achieve transitions  via price promotions. In that case, discounts *have* to be able to aid transitioning, making the reverse causality inherent in this setting. The analysis behind Figure \ref{discountsTransitions} remains imperfect for yet another reason. A discount given when a firm is close to a positive transition is not guaranteed to lead to a transition. Similarly, a firm trying to avoid a negative transition by giving a discount might succeed. In both cases, the behavior that we are interested in goes undetected if one only studies transitions that took place in the data.

The solution to both problems that I suggest is to study *potential* transitional situations instead of the realized ones. First, it solves the reverse causality problem. A discount given today can cause a transition tomorrow, but a decision to give a discount can not cause the proximity to a transition that chronologically precedes it. Second, it clearly solves the selection issue explained above, when the analysis considers solely the firms that transitioned.

With the focus now on potential transitions, the crucial question is how to define proximity to a transition. One approach would be to use the raw review count, and to say that a game is close to upgrading its review label when it needs five (ten, twenty ...) more positive reviews to transition. However, given the heterogeneity in the popularity of different games (see Figure \ref{sampleSizeHist}), five extra reviews could be nothing for a very popular game, and hard to acquire for a small game. For this reason I use a different approach, that measures proximity by the expected number of days that a game has to wait to accumulate the reviews necessary for a transition. In particular, for every game-date pair I first measure how many positive reviews that game needs at the moment to upgrade its review bin, and how many negative reviews that game needs to degrade its review bin. In the next step, for each game I calculate the average speed of review arrivals, by simply dividing the number of positive (negative) reviews as of the last day in the sample by the age of the game on that day. Knowing the speed of positive and negative review arrivals, and the  number of reviews necessary for a transition, I then define the proximity to a positive (negative) transition to be the expected number of days needed for the game to accumulate the necessary number of positive (negative) reviews, assuming that it does not receive any negative (positive) reviews during that time.

To illustrate this definition, consider an example game with 19 positive reviews and 6 negative reviews at some moment in time. This game has a review score of 76\%, and the “Mostly Positive” review label. It needs 5 additional positive reviews to secure a score of 80\%, the threshold that would earn it the “Positive” label.  Similarly, 3 new negative reviews would be sufficient for the game to slide into the “Mixed” review category, as the score would become $19/(25 + 3) \times 100\%= 67\%$, which is less than the $70\%$ required for the “Mostly Positive” bin. If this game ends up having 80 positive and 20 negative reviews at the age of 200 days, its last day in the sample, then, on average, it was receiving 0.4 positive and 0.1 negative reviews per day. Thus, for a positive transition it requires $5/0.4 = 12.5$ days of only good reviews arriving at this rate. Similarly, for a negative transition it requires $3 / 0.1 = 30$ days of only bad reviews arriving at this rate. So, for this game I set its proximity to a potential positive transition to be 12.5 days, and its proximity to a potential negative transition to be 30 days.

```{r include = F,}
band <- 7

panel[, pRevRate := max(pReviews,na.rm = T)/max(age, na.rm = T), by = ID]
panel[, nRevRate := max(nReviews,na.rm = T)/max(age, na.rm = T), by = ID]

R.low <- 0.4
R.high <- 0.7
panel[score < R.high*100 & score >= R.low*100,
      needPos := ceiling((R.high*reviews-pReviews)/(1-R.high))]
panel[score < R.high*100 & score >= R.low*100,
      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
# corrects for the rounding error caused by machine precision division of, say, 4/10 != 0.4. If you are supposed to be brought exactly to the cutoff, your needNeg is one review more than that
panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]

R.low <- 0.7
R.high <- 0.8
panel[score < R.high*100 & score >= R.low*100,
      needPos := ceiling((R.high*reviews-pReviews)/(1-R.high))]
panel[score < R.high*100 & score >= R.low*100,
      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]

panel[pRevRate > 0, needPosDays:=needPos/pRevRate]
panel[nRevRate > 0, needNegDays:=needNeg/nRevRate]
panel[, pos.treatment := (needPos <= 2*band)]
panel[, neg.treatment := (needNeg <= 2*band)]

reg3 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
               mPositive + age + young + day + week,
                 data=panel[],
            model="within")
cov<-vcovHC(reg3, method="white1")
se3 <- sqrt(diag(cov))

R.low <- 0.7
R.high <- 0.8
panel[score >= R.high*100 & reviews < 50,
      needPos := 50 - reviews]
panel[score >= R.high*100 & reviews < 50,
      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]

R.high <- 0.95
panel[vPositive == T & score >= R.high*100 & reviews < 500,
      needPos := 500 - reviews]
panel[vPositive == T & score >= R.high*100 & reviews < 500,
      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]

panel[score < R.high*100 & vPositive == T,
      needPos := pmax(ceiling((R.high*reviews-pReviews)/(1-R.high)), 500-reviews)]
panel[score < R.high*100 & vPositive == T,
      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]

panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]

panel[, needPosDays:=needPos/pRevRate]
panel[nRevRate > 0, needNegDays:=needNeg/nRevRate]
panel[, pos.treatment := (needPos <= 2*band)]
panel[, neg.treatment := (needNeg <= 2*band)]

reg1 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
               mPositive + realPositive + vPositive + age + young + day + week,
                 data=panel[],
            model="within")
cov<-vcovHC(reg1, method="white1")
se1 <- sqrt(diag(cov))

panel[, pos.treatment := (needPos <= band)]
panel[, neg.treatment := (needNeg <= band)]

reg2 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
               mPositive + realPositive + vPositive + age + young + day + week,
                 data=panel[],
            model="within")
cov<-vcovHC(reg2, method="white1")
se2 <- sqrt(diag(cov))

star.out <- stargazer(reg1, reg2, reg3,
             label = "potentialTransitionsResults",
             table.placement = "hp",
             header = FALSE,
             title = "Discounts Close to Potential Transitions",
             se=list(se1, se2, se3),
             dep.var.labels = c("Discount Probability"),
             column.labels = c("Full", "1 W. to Tr.", "Simple Tr."),
             covariate.labels = c("Close to Pos. Transition", "Close to Neg. Transition",
                                  "Log Days to Pos. Tr.", "Log Days to Neg Tr.",
                                  "Log Reviews", "Mostly Positive", "Positive",
                                  "Very Positive", "Age", "Age $\\le 14$"),
             model.numbers = F,
             omit = c("day", "week", "tWODisc"),
             omit.stat=c("f","adj.rsq","ser"),
             no.space=T)

```

As the example above shows, it is impossible to consider proximity to a positive transition without taking into account the proximity to a negative transition, at least for moderately sized games. If firms' strategies for these types of transitions are different, then studying such transitions separately could attenuate the effect of the proximity to, say, a positive transition, on the discount probability: a firm that is close to upgrading its review bin might not give a discount not because it is a bad way to accomplish that transition, but because that firm is at the same time close to downgrading its review bin, and might prefer to exercise prudence. For this reason, I define two “treatment” variables of interest. Game $i$ at date $t$ is said to be close to a positive transition, $T_{it}^+ = 1$, if its proximity to a positive transition is less than or equal to `r 2*band` days. Similarly, game $i$ at date $t$ is said to be close to a negative transition, $T_{it}^- = 1$, if its proximity to a positive transition is less than or equal to `r 2*band` days. The `r 2*band` cutoff is inspired by the maximum duration of custom discounts on Steam, and the patterns of discounting around successful transitions, depicted in Figure \ref{discountsTransitions}. To estimate the effect of being close to a review transition on the discounting behavior, I then estimate the following model:
\begin{equation}\label{potTransitionsReg}
disc_{it} = \beta^+ T_{it}^+ + \beta^- T_{it}^- + X_{it}\beta + f_i + \tau_t + \varepsilon_{it},
\end{equation}

\noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, review bin dummies, and age; $f_i$ is a set of game-level fixed effects, and $\tau_t$ is a set of day of the week effects and sample week time effects. These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSales}. We expect $\beta^+$ to be positive, but, when it comes to $\beta^-$, any sign could be rationalized. A positive sign on  $\beta^-$ would serve as evidence that firms use discounting in order to escape from slumps in their reviews bins, while a negative sign would indicate that, on the contrary, firms on the verge of a bad transition become more prudent with their discounts, trying to not instigate extra purchasing/reviewing activity.

```{r results = 'asis'}
cat(star_insert_row(star.out,
                    c("Time Effects: Weekdays, Week &  $\\checkmark$ &  $\\checkmark$ & $\\checkmark$ \\\\",
                      "Game Effects & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\",
                      "Poly($t$ W/O Discount, $d=2$) & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\"),
                    insert.after = c(33,33,33)))
```

Notice that the inclusion of both the distance to a potential positive, and a potential negative, transition in the regression drops all observations from the lowest ("Negative") and the highest ("Overwhelmingly Positive") review bins, as for games in those bins only one way of review transition is possible. However, given that the proportion of such observations in the sample is quite small, this is not a big concern. The analysis also excludes the observations with a “No Review Score” label, as I do not want to take a stance on what constitutes an improvement or a deterioration of the review score for such games. The results of estimating Equation \ref{potTransitionsReg} are presented in Table \ref{potentialTransitionsResults}. The first column is the full specification that uses all observations in the sample (except the omissions just mentioned). The second column uses a more stringent definition of proximity to a transition, requiring a game to be `r band`, rather than `r 2*band`, days away from a potential transition to be counted as being “close to a transition”. The third column uses only transitions between “Mixed”, “Mostly Positive”, and “Positive” labels, as these are the transitions that rely on the review score only, while “Very Positive” and “Overwhelmingly Positive” require both a certain review score, and a certain number of reviews.\footnote{Technically, a game improving its review score from 79\% to 80\% can transition to both “Positive” and “Very Positive”, so the results in the third column bundle together these types of transitions.}. @SorokinStevens20 exclusively uses these simple review bins in their regression discontinuity analysis, precisely in order to avoid the complications that arise from double thresholds required for “Very Positive” and “Overwhelmingly Positive”.

The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion. Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg1$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount. The uncertainty about the sign and the significance of the proximity to a potential negative transition is resolved in favor of the prudent approach on the firms' side: the results suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg3$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`-`r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is only present in two out of three specifications.

## Discussion

It is not unreasonable to say that model \ref{potTransitionsReg} is able to identify the causal effect of the proximity to a review transition on discounting behavior. As the sample was selected to include only products with the most stable quality and the lowest number of game updates, the path of the review score is relatively exogenous for the firms. Taking its current review score as given, a firm can decide whether to run a price promotion or not, which makes the main independent variables in my analysis exogenous. On top of that, model \ref{potTransitionsReg} includes a rich set of controls and fixed effects. Some threats to identification still remain, of course. One is unobserved marketing interventions preceding discounts. If advertisements improves the review score, then, by definition, advertisement would be correlated with the treatment variable, moving games a bit closer to transitions. If a discount then follows, as a part of the general marketing plan, rather than to leverage the new proximity to a transition, the positive association between discounting and positive transitions would be spurious. Note, however, that it would be more natural to expect firms to roll out all marketing interventions at the same time (i.e., running a price promotion while the game is advertised). In that case, the threat to identification vanishes.

I would now like to step back and look at the story behind the behavior that I am documenting. Several gaps are not filled yet. First, I have not presented evidence that discounting meaningfully increases sales and leads to more reviews. Neither have I presented evidence that better review bins increase sales. Perhaps, more importantly, I have not discussed why firms should expect customers buying during a discount to leave better reviews than customers paying the regular price. If there is no difference between the two groups, then giving a discount when the game is close to a transition is, at best, a gamble. In fact, there is some empirical evidence that customers who choose to go to a restaurant because of a promotion tend to leave worse reviews [@ByersEtAl12; @Li16], even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19]. Theoretically, this effect is ambiguous. Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews. At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews. See, for example, @AcemogluEtAl19.

The results I presented in this section, therefore, lead to the following hypotheses. I show that firms give discounts to avoid bad transitions and to facilitate the good ones; thus, it has to be the case that the reviews left on a discount tend to be more positive than the ones left off a discount. Second, if that is indeed the case, then the firms that get especially positive reviews during price promotions should be more likely to try to use discounting to manipulate their reviews. Heterogeneity between the firms is crucial for the second hypothesis. In order to test these hypotheses, and to provide evidence on the effect of discounting on sales and reviewing activity, as well as the effect of reviews on sales, I now turn to formulation and estimation of a structural model demand, reviewing and gaming activity on Steam.

# Empirical Model

## Setup

Consider game \(i\) that is observed on a daily basis. On day \(t\)
the game sells one copy to each of the \(B_{it}\) short-lived buyers that arrive on
that day, a number that is unobserved by the econometrician. Define
*active players* of this game, \(A_{it}\), to be the customers who have
already purchased the game and are still playing it, either because they have
not yet completed it or are not bored with it yet. This number  has an empirical counterpart in
the face of the player count variable, observable to the econometrician. The game loses \(E_{it}\) players on day \(t\), which is also not observed.
I assume that, once a player stops playing the game, she never returns to it again. It is easy to see then that \(A_{it}\) follows the following process:
\begin{equation}\label{activeProccess}
  A_{it} = A_{it-1} + B_{it} - E_{it}
\end{equation}

Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about
them in order to make progress.

\begin{assumption}\label{arrivalAssumptions}
$B_{it}$ is Poisson with arrival rate $\lambda_{it} = \lambda_i(1+x'_{it}\beta)$, where $x_{it}$ is a vector of observable characteristics of the game, and $\lambda_i$ and $\beta$ are parameters. $E_{it}$ follows a binomial distribution $B(A_{it-1}, 1-\psi_i)$, where $\psi_i$ is a parameter.
\end{assumption}

The rationale behind assumption (\ref{arrivalAssumptions}) is simple.
Consumers arrive every day according to the game specific arrival rate
\(\lambda_i\), but that rate can go up or down depending on the values
of observable characteristics \(x_{it}\) of the game that affect demand:
price, reviews, age of the game, or seasonal factors. The mapping between these variables and the number of copies sold is, of course, nothing else but the demand curve for game $i$. A change of $0.01$ in the index $x_{it}'\beta$ means that quantity demanded of game $i$ goes up by one percent. This multiplicative structure is necessary, because it will allow me to estimate the price sensitivity and the effect of reviews on sales in relative terms\footnote{See the Identification section for more details}. Buyers of the game become active players, and are subject to a fixed daily risk of $1-\psi_i$ of abandoning the game. Given that the number of active players “flipping” this coin at the end of day $t-1$ is $A_{it-1}$, this process gives rise to the binomial distribution for the number of exiters.

Every buyer of game $i$ is a potential reviewer. I assume that a buyer who buys the game at $t-k$ leaves a positive (negative) review for the game on day $t$ with probability \(r_{it}^+\)	 (\(r_{it}^-\)), and no review otherwise. For the reasons I will explain later, I will refer to  $r_{it}^+$ as the *like rate*, and to $r_{it}^-$ as the *dislike rate*.  The focus of the analysis is on the difference between the reviews left on and off a discount. To that end, I parametrize the like and dislike rates to depend on the discounting behavior of the firm as follows.

\begin{assumption}\label{likeDiscountAss}
The like rate is a linear function of discounts:
$r_{it}^+ = \rho_{0i}^+ + \rho_{1i}^+ disc_{it-k}$.  The dislike rate is a linear function of discounts: $r_{it}^- = \rho_{0i}^- + \rho_{1i}^- disc_{it-k}$.
\end{assumption}

\noindent Notice, that a price change affects the reviewing behavior in two ways. First, a lower prices increases the inflow of buyers through a higher $\lambda_{it}$. This leads to more reviews being left. My parametrization allows to further study if the reviewers who bought the game on a discount are more or less likely to leave positive and negative reviews. I use a dummy variable $disc_{it-k}$ to measure discounting because this will allow me to derive a closed-form estimator for the  parameters of interest.

## Identification

### Demand Parameters
The prediction of \(A_{it}\) that follows from (\ref{activeProccess}) takes the form of
\begin{equation}
\mathbb{E}\left[A_{it}\,|\,A_{it-1}, x_{it} \right] = A_{it-1} + \lambda_i(1+x'_{it}\beta) - (1-\psi_i)A_{it-1} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta),
\end{equation} so the model implies the following regression equation
\begin{equation}\label{arrivalReg}
 A_{it} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
\end{equation}
with
\(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\). This model is
non-linear in parameters, because \(\lambda_i\) is not known and enters
the model multiplying \(\beta\), the parameters common to all games. If
not for this commonality in $\beta$, estimation of (\ref{arrivalReg}) would be
straightforwardly achieved by opening the parentheses and estimating
\begin{equation}\label{arrivalRegInd}
A_{it} = \lambda_i + \psi_i A_{it-1} + x'_{it}\beta_i + u_{it}
\end{equation}
using OLS on a game-by-game basis. This commonality is
essential, however, because one game in the sample typically does not exhibit enough variation in review labels to be able to identify the effect of upgrading the review tier on sales.

The fact that $x'_{it}\beta$ multiplies the game fixed effect $\lambda_i$ allows me to estimate the dependence of quantity sold on price and reviews in relative terms, i.e., to obtain the elasticities. Normally, a log transformation is used to achieve that. Indeed, @SorokinStevens20 is able to estimate these elasticities with a within-estimator, using the following model
\begin{equation}\label{logReg}
\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}.
\end{equation}
This specification “controls” for the (log) number of continuing players in order to overcome the non-availability of direct sales data; however, it is the numbers of active players and buyers that are additive, not their logs. Thus, the structural model I formulate confronts the estimation problem in a more “heads-up” way, and in that regard offers an improvement over @SorokinStevens20. I will contrast the results obtained by the two approaches in the results section, comparing a more detailed structural approach with a less precise, but a more easily implementable, log regression approach.

Another important reason for insisting on estimating the relative effects stems from the limitations of my data. Recall that the player count variable measures only the *maximum concurrent* number of active players every day. This implies that the estimated values of $\lambda_{it}$ would take into account only those new buyers who contribute to gaming activity during the “rush hour”. An implicit assumption in my analysis is that new buyers of the game all choose their gaming time following the same game-specific distribution. I use this assumption to say that, if the number of new active players during rush hour goes up by 1%, then sales go up by 1% across all types of players,  not only among the "rush hour ones".

Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model \ref{arrivalReg}, and guarantees identification of all parameters, as long as there is sufficient variation in the data. Of course, this is only true as long as equation \ref{arrivalReg} is the right model of the data generating process. A threat to identification would come from unobserved demand shifters $\tilde x_{it}$ that are correlated with the observed factors $x_{it}$ (omitted variable bias). For instance, an advertising intervention that is coupled with a price promotion would increase demand, but the entire effect would be attributed to the observed change in price. My approach is vulnerable to such events, as long as one is interested in getting the causal estimate of the discount elasticity of demand.

However, I argue that (\ref{arrivalReg}) is an adequate specification, if the goal is to estimate the causal effect of reviews on sales, or to get a predictive model of demand. First and foremost, the reviews are not a choice variable of a firm, and rather serve as a state variable that a firm takes as given every day. Of course, there are various things that a firm can do, that can, in a non-guaranteed fashion, affect this variable. But, as long as the major tools that a firm has access to are controlled for in the regression, the exogenous variation in the review variables is sufficient to identify the causal effect of reviews on sales.

One important way in which I control for various tools that firms have at their disposal is through sample selection. Sample selection rules out the possibility of an omitted variable bias stemming from a number of variables that could collectively be referred to as “changing quality”. The games in the sample are single player games, and thus are not subject to time-varying network externalities or frequent quality updates, that could be correlated with reviews, depths of discounts, and the player count. Second, game specific effect $\lambda_i$ controls for all time-invariant characteristics of game $i$ that determine average sales: initial marketing budget, extraneous popularity of the game's plot or setting, etc. Similarly, time effects control for important within-week seasonality in gaming patterns and for the extensive platform-wide sales. Third, note that Equation (\ref{arrivalReg}) allows each game to have its own continuation probability $\psi_i$, which could prove crucial in eliciting sales from the player count data. Two games could have the same observed median daily player count---say, ten people---but very different sales levels, if game one offers a lot of replayability and is played by the same ten people over and over again, and game two is played by new ten people every day. Intuitively, $\psi_i$ is identified by the rate of decay of the player count when it is far from its (slowly-changing) trend or average. Game release and discounts offer such events, when the player count spikes briefly due to all the new players who just bought the game; see example game in Figure \ref{exampleGame}.

### Price Elasticity of Demand
To close off the discussion of identification of the demand parameters in Equation (\ref{arrivalReg}), I would like to elaborate on the identification of the price elasticity parameter. As I mentioned before, at the very least, including the price in the regression controls for unobserved marketing interventions that are coupled with discounts. Estimating the true price elasticity of demand is not important for the questions addressed in this paper, as I am not trying to prescribe the sizes of the discounts that firms should be giving to have a meaningful chance of affecting their review labels when they are close to a review transition. Arguably, a 100% discount is a powerful enough option to make this strategy viable, at least in principle. However, should the price coefficient be of primary interest, I would like to list some further factors that have an impact on the identification of thereof.

First, I believe that standard concerns about the endogeneity of prices are not directly applicable in my context. The reason is the high frequency nature of the data and the stickiness of posted prices. Using the classic notation, imagine that a discount is given on date $t$, and we observe a quantity-price pair $(Q_t, P_t)$, both of which are different from their yesterday's counterparts $(Q_{t-1}, P_{t-1})$. The standard endogeneity concern is that firm's demand is subject to shocks, and that the firm would change its price precisely when those shocks occur. The two points then, roughly speaking, would belong to different demand curves, and one can not identify the slope of the demand curve\footnote{Assuming, as is usually done, that demand shifters lead to parallel shifts in demand}. In my setting, however, this would require the firms to systematically give discounts *exactly on the days* of the demand shocks, which requires possessing a level of insight into one's demand condition that is unrealistic, especially for small independent studios. While a discount for a racing game on the day of a major F-1 race is not implausible, should the demand for the game go up with a lag of as little as one day, then both $(Q_t, P_t)$ and $(Q_{t-1}, P_{t-1})$ would belong to the same demand curve, and, therefore, identification would not be threatened.

My second point is that, even though unobserved marketing interventions that are coupled with price promotions, would,  undoubtedly, be an issue, this problem could be addressed with some extra data collection. One way to proceed would be to study if such coupled promotions in fact do take place. In particular, one could collect data on YouTube queries mentioning the games in the sample, and use spikes in such queries as a proxy for unobserved marketing campaigns.

A deeper problem for identifying the price elasticity of demand lies in defining precisely the elasticity of interest. A video game is a durable good, and some consumers could be purchasing it strategically, thinking about the probability and depth of discounts that they could get in the near future. A discount that is announced a week in advance will appear to have a strong effect on sales, but only because consumers would abstain from purchasing the game throughout that week. For studying counterfactual price policies one would need to specify a more complicated model of forward-looking consumers, and estimate the fundamentals of their behavior. A related problem is the importance of salience in a marketplace that has many thousands of products. Any price elasticity estimated relies on Steam keeping its algorithms unchanged. A game can give a 99% discount, but the quantity demanded will not change much if that promotion happens to not be reflected in Steam's system. This has implications, for instance, for picking good instruments for prices. Curated discounts created and managed by Steam are suggested to firms, and not chosen by them. In principle, such price changes could be exogenous to daily demand conditions. However, they could hardly be used as instruments for the price, because they also bring an immense boost in visibility, by the virtue of occupying the prime store main page space.

### Review Parameters

The part of the model describing the reviewing behavior of the buyers is more starightforward. Intuitively, the propensity to leave a review on and off a discount (the like and dislike rates $r_{it}^+$, $r_{it}^-$) are identified by the differences in reviews left on and off a discount. In fact, this intuition becomes a rigorous proof, as wil be shown shortly.

Following assumption \ref{arrivalAssumptions}, the arrival of buyers for game $i$ on day $t$ follows a Poisson distribution with arrival rate $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$. I also assumed that, $k$ days later, each consumer leaves a  positive review with probability $r_{it}^+$, a negative review with probability $r_{it}^-$, and no review otherwise. Then, the following proposition is true:
\begin{proposition}\label{poissonReviews}
The number of good reviews $G_{it}$ for game $i$ on day $t$ is distributed Poisson with rate $r_{it}^+\lambda_{it-k}$. The number of bad reviews $B_{it}$ for game $i$ on day $t$ is distributed Poisson with rate $r_{it}^-\lambda_{it-k}$. Moreover, $G_{it}$ and $B_{it}$ are independent.
\end{proposition}

Proposition \ref{poissonReviews} allows one to easily write down the likelihood for positive and negative reviews separately. I will use the positive reviews as the leading example here, but all the findings automatically translate to the negative reviews case as well. For every game I observe the history of the review arrivals $\{(g_{it}, b_{it})\}_{t=1}^{T_i}$. Since $\PP{G_{it} = g_{it}} = \frac{ (r_{it}^+\lambda_{it-k} )^{g_{it}} }{g_{it}!} e^{ -r_{it-k}^+\lambda_{it-k} }$, the log-likelihood of the history of likes is given by
\begin{equation}\label{reviewsLikelihood}
\ell(g_i; r_{it}^+, \lambda_{it-k}) = \sum_{t\ge k} g_{it} \log r_{it}^+\lambda_{it-k} - r_{it}^+\lambda_{it-k} - \log g_{it}!
\end{equation}

I treat $\lambda_{it}$ as known, because parameters $\lambda_{i}$ and $\beta$ that determine it can be estimated consistently for the majority of games in the sample, given the long time dimension of the panel. For now I also take the lag $k$ between the time when the user buys the game and leaves a review for the game to be known. The parameters of interest are $(\rho_{0i}^+, \rho_{1i}^+)$, which parametrize the like rate as $r_{it}^+ = \rho_{0i}^+ + \rho_{1i}^+ disc_{it-k}$. The likelihood is concave in the parameters, so the parameters are identified as the maximizer of the likelihood. Restricting attention to a binary discount variable $disc_{it}$ allows me to derive a closed-form estimator for $(\rho_{0i}^+, \rho_{1i}^+)$. During a discount the like rate of game $i$ is $\rho_{0i}^+ + \rho_{1i}^+$, which is consistently estimated as 
\begin{equation}\label{rhohat1}
\hat \rho_{0i}^+ + \hat\rho_{1i}^+ = \frac{\sum_{t \ge k} disc_{it-k}g_{it}}{\sum_{t\ge k} disc_{it-k}\lambda_{it-k}},
\end{equation}
As we can see, the ML-estimator of the like rate during a price promotion is just the ratio of the number of good reviews left on a discount over the expected arrival on that day. Similarly, the like rate off a discount can be estimated by
\begin{equation}\label{rhohat2}
\hat \rho_{0i}^+ = \frac{\sum_{t\ge k} (1-disc_{it-k})g_{it}}{\sum_{t\ge k} (1-disc_{it-k})\lambda_{it-k}},
\end{equation}
with the interpretation that the like rate in the absence of a discount is just a ratio of the reviews left outside of a discount and the expected number of customers outside a discount.

Note that one can use these estimators to estimate the *average review score* on and off a discount, i.e., whether users are relatively more or less likely to leave a good review during a discount. For example, without a price promotion, one obtains
\begin{equation}\label{avReviewScore}
\frac{\sum_{t\ge k} (1-disc_{it-k})g_{it}}{\sum_{t\ge k} (1-disc_{it-k})g_{it} + \sum_{t\ge k} (1-disc_{it-k})b_{it}}
=
\frac{\hat \rho_{0i}^+}{\hat \rho_{0i}^+  + \hat \rho_{0i}^- }
\end{equation}
It is intuitively clear that the relative propensity to leave a good, rather than a bad, review should be easily estimable by comparing the ratios of good to bad reviews, without any knowledge of the quantity of games sold. This intuition is fully reflected in Equation (\ref{avReviewScore}), where the arrival rates $\lambda_{it-k}$ have disappeared entirely.

The analysis above is complicated by two facts. First, for each game I observe the exact review count, but my demand estimates only apply to rush hours. If, say, every player leaves a review, and every day there are two new players who play in the morning, and three new players who play in the evening, my data would register 3 players leaving 5 reviews on a daily basis. This is the reason why I refer to the values of $(r_{it}^+, r_{it}^-)$ as rates, rather than probabilities (which they are in the model). Propositon \ref{poissonReviews}, stating that the number of good reviews on day $t$ for game $i$ is a Poisson random variable with rate $r_{it}^+\lambda_{it-k}$, could be treated as an assumption, rather than a result. In that case, nothing constrains the $r_{it}^+$ parameter to be less than 1, and the identification argument goes through in the exactly the same way.

Another problem stems from the fact that the purchase date behind a review is not available to the researcher. For that reason, the model features an additional parameter $k$, the lag between purchasing the game and leaving a review, that I assumed to be known. To estimate that parameter I leverage the fact that spikes in player activity on the first day of a sale represent new users, and study the review response during the following week in order to uncover the modal lag for leaving a review (see Table \ref{reviewLag} in the Appendix). This number turns out to be one day. Even though time to posting a review has a non-degenerate distribution, modelling it in a more nuanced way would significantly contribute to complexity: the likelihood of receiving a poisitive review on day 100 would depend on the entire history of buyer arrivals prior to that date. Therefore, I proceed using $\hat k = 1$.

## Estimation and Results

### Demand Parameters

```{r cache = F}
reg.results <- fread(here("Analysis", "Temp", "juliaResults.csv")) %>% as.data.frame()
beta.hat <- reg.results[seq(1, nrow(reg.results), 3), 4] %>% round(., 3)
reg.results.stats <- fread(here("Analysis", "Temp", "juliaResults2.csv")) %>% as.data.frame()
effects<-fread(here("Analysis", "Temp", "juliaResults3.csv"))
effects <- merge(effects, info[, .(id, ID)], by = c("id"), all.x = T)
panel <- merge(panel, effects[, .(ID, t, lambda = lambda * z)], by = c("ID", "t"))
effects <- effects[, .(psi=psi[1], lambda=lambda[1], mz = mean(z)), by = ID]
info <- merge(info, effects, by = c("ID"))
rm(effects)
```

### Review Parameters

\newpage
\appendix

# Additional Tables and Figures
## Discounts Around Transitions
```{r results = 'asis'}
cat(star_insert_row(star.out.transitions, c("Time Effects & Weekdays, Week \\\\",
                                "Game Effects & $\\times$ \\\\",
                                "Polynomial($t$ W/O Discount) & $d = 2$ \\\\"), insert.after = c(34,34,34)))
```
\newpage
## Review Lag
Table \ref{reviewLag} presents the results of estimating
$$NewReviews_{it} =\sum_{l = 0}^{7} \mathds{1}(\text{Disc. } l \text{ days ago})
+ reviewBin_{it} + age_{it} + young_{it} +  f_i + \tau_t + u_{it}$$
```{r include=F}
# Calculate the daily new review count and the lags of the dummy for new discount. 
panel[, new.reviews := c(reviews[1], diff(reviews)), by = ID]
panel[, discNewLag2 := shift(discNewLag), by = ID][is.na(discNewLag2), discNewLag2 := F]
panel[, discNewLag3 := shift(discNewLag2), by = ID][is.na(discNewLag3), discNewLag3 := F]
panel[, discNewLag4 := shift(discNewLag3), by = ID][is.na(discNewLag4), discNewLag4 := F]
panel[, discNewLag5 := shift(discNewLag4), by = ID][is.na(discNewLag5), discNewLag5 := F]
panel[, discNewLag6 := shift(discNewLag5), by = ID][is.na(discNewLag6), discNewLag6 := F]
panel[, discNewLag7 := shift(discNewLag6), by = ID][is.na(discNewLag7), discNewLag7 := F]

# normally, a lag(discNew, 0:7) could be used in the regression formula, but R returns an
# error that I can not debug
reg1 <- plm(new.reviews ~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
                          discNewLag5 + discNewLag6 + discNewLag7 + 
                          negative + mPositive + positive + age + young + day + week,
                          data = panel, model = "within")
cov<-vcovHC(reg1, method="white1")
se1 <- sqrt(diag(cov))

star.out <- stargazer(reg1,
             label = "reviewLag",
             table.placement = "hp",
             header = FALSE,
             title = "Spikes in Reviews After a Discount",
             se=list(se1),
             dep.var.labels = c("New Reviews"),
             covariate.labels = c("Discount 0 Days Ago", "Discount 1 Day Ago",
                                  "Discount 2 Days Ago", "Discount 3 Days Ago",
                                  "Discount 4 Days Ago", "Discount 5 Days Ago", 
                                  "Discount 6 Days Ago", "Discount 7 Days Ago"),
             model.numbers = F,
             omit = c("day","week","negative","mPositive","positive","age", "young"),
             omit.stat=c("f","adj.rsq","ser"),
             no.space=T)
panel[, discNewLag2:=NULL][, discNewLag3:=NULL][, discNewLag4:=NULL][, discNewLag5:=NULL]
panel[, discNewLag6:=NULL][, discNewLag7:=NULL][, new.reviews:=NULL]
```

```{r results = 'asis'}
cat(star_insert_row(star.out, c("Time Effects & Weekdays, Week \\\\",
                                "Game Effects & $\\checkmark$ \\\\"), insert.after = c(28,28)))
```

\newpage
# Mathematical Appendix

## Proofs

\textbf{Proposition} \ref{poissonReviews}. Let the total number of reviewers during a day, $R$, be distributed Poisson with rate $\lambda$,  $R\sim P(\cdot; \lambda)$. A reviewer leaves a good review with probability $\pi$, and a bad review with probability $1-\pi$. Then, the numbers of good and bad reviews, $G$ and $B$, are independent Poisson random variables with rates $\pi\lambda$ and $(1-\pi)\lambda$.

In the main text I have a Poisson arrival of customers, and only a fraction of them become reviewers, but the same proof goes through with that modification as well. The independence between the numbers of good and bad reviews is the surprising part of the proposition, and it is better highlighted in the form presented here.

\vspace{1em}\noindent *Proof*: We start by showing that $G$ is Poisson.
$$
\PP{G=g} = \sum_{n=g}^{\infty}\CP{G = g}{R=n}\PP{R = n} 
=
\sum_{n = g}^{\infty}
\frac{n!}{g!(n-g)!}
\pi^g (1-\pi)^{n-g}
\frac{\lambda^n}{n!} e^{-\lambda}
$$

\noindent We leave only the parts that depend on $n$ within the sum:
$$
e^{-\lambda}\frac{\pi^g}{g!}\sum_{n = g}^{\infty}
\frac{(1-\pi)^{n-g} \lambda^n}{(n-g)!}
=
e^{-\lambda}\frac{\pi^g\lambda^g}{g!}\sum_{n = g}^{\infty}
\frac{(1-\pi)^{n-g} \lambda^{n-g} }{(n-g)!}
=
e^{-\pi\lambda}\frac{\pi^g\lambda^g}{g!}\sum_{k=0}^{\infty}
\frac{[(1-\pi)\lambda]^{k} }{k!}e^{-(1-\pi)\lambda}
$$

\noindent The sum we have is just $\sum_{k=0}^{\infty} P(k; \lambda) = 1$, so the answer is
$$
\PP{G=g} = \frac{[\pi\lambda]^g}{g!}e^{-\pi\lambda} = P(g; \pi\lambda)
$$

Now the independence part. We are interested in $\PP{G=g, B=b}$, which could be written as
$$\PP{G=g, B=b} = \CP{G=g, B=b}{R=g+b}\PP{R=g+b} = 
\frac{(g+b)!}{g!b!}
\pi^g (1-\pi)^b
\frac{\lambda^{g+b}}{(g+b)!} e^{-\lambda}
$$
Simply write $e^{-\lambda} = e^{-\pi\lambda}e^{-(1-\pi)\lambda}$, and collect the terms with $g$ and with $b$ to get
$$
\PP{G=g, B=b} = 
\frac{\pi^g \lambda^g}{g!}e^{-\pi\lambda}
\frac{(1-\pi)^b\lambda^b}{b!}e^{-(1-\pi)\lambda}
=
P(g; \pi \lambda) P(b; (1-\pi)\lambda)$$
\begin{flushright}
$\triangleleft$
\end{flushright}

\newpage
## NLLS estimator of $\beta$

In this appendix I  develop the estimator for the parameters of the model
\begin{equation}\label{nonLinearLS}
 y_{it} = \psi_i y_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
\end{equation}
This model has \(2n\) \(i\)-specific parameters \((\lambda_i, \psi_i)\) and \(\dim(\beta)\) parameters that are shared by all entities in the panel. Estimation is via Non-linear Least Squares. The F.O.C. of the problem could
be reduced so as to concentrate out all \((\lambda_i,\psi_i)\) parameters. Thus, estimation of \(2n + \dim(\beta)\) parameters reduces to solving a system of non-linear equations for \(\dim(\beta)\) parameters (or solving a NLLS problem of that dimension).

The estimator is defined as the minimizer of the sum of squared errors:
\begin{equation}\label{sse}
 \hat \theta := \underset{\lambda_i, \psi_i, \beta}{\mathrm{argmin}}\;
 \sum_{i=1}^n \sum_{t=2}^{T_i} (y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))^2
\end{equation}
The F.O.C. are
\begin{alignat}{3}
\label{regFOC1} \psi_i:\; & \sum_{t=2}^{T_i} (y_{it} - \psi_iy_{it-1} - \lambda_i(1+x_{it}'\beta))y_{it-1} &\;=\;& 0\\
\label{regFOC2} \lambda_i:\; &\sum_{t=2}^{T_i} (y_{it} - \psi_iy_{it-1} - \lambda_i(1+x_{it}'\beta))(1+x_{it}'\beta) &\;=\;& 0 \\
  \beta:\; & \sum_{i=1}^n \sum_{t=2}^{T_i} (y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))\lambda_ix_{it} &\;=\;& 0
\end{alignat}
Conditional on \(\beta\), the F.O.C. for \((\psi_i, \lambda_i)\) are F.O.C.'s of an OLS problem of the form
\[\min_{\psi_i, \lambda_i}\sum_{t=2}^{T_i} (y_{it} - \psi_i y_{it-1} - \lambda_iz_{it})^2,\]
where \(z_{it} = (1+x_{it}'\beta)\). Defining, in the standard way, \(\tilde{\mathbf Z}_i (\beta)\) to be the matrix with row \(t\) given by \([z_{it+1}, y_{it}]\), and \(y_i\) to be the vector of \(y_{it}\)
observations, we get that the values of \(\hat \lambda_i,\hat \psi_i\) that solve (\ref{regFOC1})-(\ref{regFOC2}) are given by
\begin{equation}\label{psilambda}
\begin{bmatrix}
\hat \lambda_i \\
\hat \psi_i
\end{bmatrix}(\beta)
=
(\tilde{\mathbf Z}_i' (\beta)\tilde{\mathbf Z}_i (\beta))^{-1}\tilde{\mathbf Z}_i' (\beta)y_i
\end{equation}

\noindent The estimator \(\hat \beta\) of \(\beta\) is now obtained
as a solution to
\begin{equation}\label{concFOC}
\sum_{i=1}^n \sum_{t=2}^{T_i} (y_{it} - \psi_i(\beta) y_{it-1} - \lambda_i(\beta)(1+x'_{it}\beta))\lambda_i(\beta)x_{it} = 0
\end{equation}
In practice I solve the concentrated minimization problem using (\ref{concFOC}) as the gradient.

Supplying an analytic expression for the Hessian matrix has proven to significantly expedite and improve convergence. The concentrated out sum of squared errors is $SSE(\beta) = SSE(\beta, \lambda(\beta), \psi(\beta))$, and while the expression for the gradient simplifies to $\partial SSE/\partial \beta$ due to the envelope theorem, the expression for the Hessian is more complex:
\begin{equation}\label{hessianEq}
\frac{d SSE}{d^2\beta} = \frac{\partial SSE}{\partial^2 \beta} + 
\sum_i \frac{\partial SSE}{\partial\lambda_i \partial \beta} \left(\frac{d \lambda_i}{d \beta}\right)' + 
\sum_i \frac{\partial SSE}{\partial\psi_i \partial \beta} \left(\frac{d \psi_i}{d \beta}\right)'
\end{equation}

\noindent The expressions for $\frac{d \lambda_i}{d \beta}$ and $\frac{d \psi_i}{d \beta}$ are obtained by applying the inverse function theorem to (\ref{psilambda}), and the remaining derivatives could be obtained directly.

The asymptotic covariance matrix for \(\hat \theta\) in a nonlinear
LS problem \(\sum_i (y_i - m(x_i, \theta))^2\) is estimated using the sample analog of
\begin{equation}
\mathbf V_\theta = \left(\mathbb{E}\left[m_{\theta i}m_{\theta i}'\right]\right)^{-1}
                \mathbb{E}\left[m_{\theta i}m_{\theta i}'e_i^2\right]
                \left(\mathbb{E}\left[m_{\theta i}'m_{\theta i}\right]\right)^{-1},
\end{equation}
where
\(m_{\theta i} = \frac{\partial}{\partial \theta} m(x_i, \theta_0)\),
\(e_i = y_i - m(x_i, \theta_0)\) [@Hansen20, p.751]. More details could be found in the code.

\newpage

### 2020-08-08 Analysis/Output/Paper.tex
Initial commit.

--- 2020-08-08 Analysis/Code/Paper.Rmd
@@
----
- title: |
-   | Consumer Reviews and Product Discounts:
-   | Evidence From Video Games
-
- author: "Dmitry Sorokin"
- date: "`r format(Sys.time(), '%B %d, %Y')`"
- classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
- output:
-  pdf_document:
-    keep_tex: true
-    fig_height: 2.5
-    fig_width: 6
-    number_sections: true
-    citation_package: natbib
-    extra_dependencies:
-       footmisc: ["bottom"] # footnote management
-       setspace: ["doublespacing"] # spacing of the paper
-       caption: ["tableposition=top"]
-       dsfont: null # indicator function 1
-       booktabs: null
-       makecell: null
-    includes:
-       in_header: extra_header.tex
-
- bibliography: reviewsBib.bib
- fontsize: 12pt
- geometry: margin=1in
- link-citations: true
- linkcolor: mypink
- filecolor: myblue
- citecolor: mypink
- urlcolor: mypink
----
-
-```{r cache = F}
-source(here("Analysis", "Code", "StructuralFunctions.R"))
-load(here("Analysis", "Input", "info.Rda"))
-load(here("Analysis", "Input", "panel.Rda"))
-```
-
-# Introduction
-
-# Literature Review
-
-This paper contributes to several closely related literatures in economics and marketing.
-The oldest of these is the literature investigating the impact of online consumer reviews on sales.
-An extensive review of the studies focusing on this topic and their meta-analysis is provided, for example, by @Floyd14.
-<!-- Researchers have analyzed multiple online platforms, selling different products and employing different review systems, and produced, overall, conflicting evidence on whether reviews improve sales, and if so, through which channels.
-The major identification challenge stems from the fact that better reviews might simply be manifestations of consumer preferences for certain products, or reflect higher quality of the underlying products.
-As preferences and quality are unobserved and, in general, fluid, researchers have struggled to come up with convincing identification strategies.
--->
-In a seminal contribution in this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales.
-A similar approach applied to the same market was recently used by @ReimersWaldfogel20, who reaffirm the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews.
-@ZhuZhang10 exploit differences between two different video games consoles rather than websites, and find that review ratings matter only for less popular games.
-
-For identification, the difference-in-differences approach relies on the existence of several comparable platforms, and assumes that the unobserved platform-specific tastes
-for those platforms are fixed.
-Another approach to identification exploits the rounding of the review data that platforms use to produce simple visual review labels.
-For example, Yelp.com, a popular restaurant comparison service, assigns 4 stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but 4.5 stars to restaurants with an average score between 4.25 and 4.74.
-@AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue.
-@SorokinStevens20 applies a similar approach to the video games market and also finds that better review labels increase sales, albeit raising some concerns about the validity of the approach.
-In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from the video games' usage data.
-The present paper supplements the panel methods in @SorokinStevens20 by offering a structural way to estimate the effect of reviews on sales in the absence of direct sales data.
-
-With benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits.
-There are several ways firms can affect their online reviews.
-One is review fraud.
-@Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves.
-@LucaZervas16 provide similar evidence for restaurants on Yelp.
-A more honest way for a firm to influence reviews is by assuming an active approach to review management, and to publicly respond to reviews published online.
-@GuYe14 provide evidence that consumers who had left a negative review about their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management.
-@XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future.
-This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes.
-In somewhat contradictory findings, @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to, while @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity, because consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.
-
-Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews.
-Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle.
-Another strand of literature is studying whether different kinds of promotions have an effect on firms' online reputation.
-In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a Groupon price promotion.
-They present evidence that customers attracted by the promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher, which can explain the reasons behind their dissatisfaction.
-Thus, the paper cautions against running price promotions in an attempt to poach new customers and improve the online reputation.
-@Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion.
-@ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews.
-In an experimental study on Ebay, @CabralLi15 also find that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and they provide evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.
-
-The present study contributes to this literature by providing novel evidence from a new market.
-I show that customers buying computer games are significantly more likely to leave positive reviews during discounts.
-More importantly, I go beyond the descriptive nature of the other papers in the literature, and show that firms leverage this fact to improve their reviews by giving discounts, thus providing evidence of a novel reputation management behavior.
-A study similar in spirit to mine is that of @Zegners17, who argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap".
-However, this study also finds that books are more likely to solicit negative feedback when sold for free, which somewhat undermines the strategy.
-Similar to @ByersEtAl12, @Zegners17 argues that purchasers of free books differ from the purchasers of regular books in their observable characteristics, and explains the negativity of the reviews by the selection effect.
-
-# Institutional Setting and Data
-
-## Steam Marketplace
-
-Steam is arguably the largest online marketplace for selling computer games in the world.
-Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it has earned around US\$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames].
-Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion
-in 2018, about the size of the U.S.
-film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD], Steam is a major player in an increasingly more important industry.
-Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to be studied in its own right.
-
-Any user who has a copy of a game on Steam can leave a review for that game.
-Starting from late 2016, by default, Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer).
-This distinguishes Steam from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews).
-This gives me confidence in the authenticity of most reviews.
-This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors.
-With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave scrupulously.
-
-A review consists of a binary grade, "thumbs up" or "thumbs down", and review's text.
-A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews.
-Based on the score, Steam assigns *review labels*, or bins, to each game.
-These labels\footnote{There are labels worse than "Negative", but they are rare, so I bin all of them into "Negative"} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}.
-For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.
-
-```{r}
-tab <- data.table(`Review Bin` = c("No Score", "Negative", "Mixed", "Mostly Positive", 
-                                   "Positive", "Very Positive", "Overwhelmingly Positive"),
-                  `N. of Reviews` = c("[0, 10)", "Any", "Any", "Any", "[0, 50)", 
-                                          "More than 50", "More than 500"),
-                  `Score` = c("-", "[0, 40)", "[40, 70)", "[70, 80)", "[80, 100)",
-                              "[80, 100)", "[95, 100]"))
-kable(tab, "latex",
-      label = "ReviewBinsTable",
-      caption = "The mapping between the review score and review bins on Steam",
-      align = c('l', "c", "c"),
-      valign = 't',
-      linesep = "",
-      booktabs = T)
-```
-
-Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc.
-[@steamVisibility].
-A customer could either click on the games already presented to her, or browse one of the categories that Steam offers.
-Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support).
-Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}.
-From that list the user can get some basic information about each game, such as its name, price, and if the game is currently on a discount.
-Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has.
-I use this feature of the Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main independent review variables, rather than, say, the review score or the review texts.
-Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place.
-Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales.
-Crucially, according to Steam's documentation, all review labels better than “Negative“ have a very similar contribution to visibility on the platform, which means, for example, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2].
-Therefore, any effect of the review labels on, say sales, should come through the perceived quality differences between different bins, rather than some mechanical visibility differences.
-As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.
-
- ```{r fig.cap='\\label{steamStore}Example Browsing Session on Steam', out.width="75%", fig.align="center"}
- knitr::include_graphics(here("Analysis", "Output", "Paper_files", "figure-latex", "steamStore.pdf"))
- ```
-
-## Data
-
-Valve Corporation, the owner of Steam, is notoriously secretive about its data and algorithms.
-Given the importance of the information on the performance of different games for game developers and publishers, the community has responded to this secrecy by establishing projects that monitor Steam in real time and extract  information that could be relevant for parties interested in Steam.
-The majority of data used in this project comes from one such project called “Steam Database”, or “SteamDB”.
-
-Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB.
-More importantly, Steam Database offers a daily time series of prices and player activity for each game on Steam.
-In principle, the pricing information could be obtained by a repeated scraping of the store.
-However, the player activity information is not trivial to obtain, as Steam does not directly reveal such data, let alone the data on sales of different titles.
-The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community most certainly implies that they are doing the best they can.
-The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent player for each game on a daily basis.
-In other words, if on a particular day 10 people play the game every hour, except noon, when 13 people play the game simultaneously, then the recorded player count for this game on that day will be 13.
-The price and the player count time series are the major “dynamic” variables used in the analysis.
-The last dynamic variable, namely the evolution of the review score for each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the path of the review score.
-
-```{r example-game, fig.cap='\\label{exampleGame} An Example Game in the Sample: Player Count, Price, and Review Score Histories.', fig.height = 5}
-plotGame(589530)
-```
-
-Steam is home to more than 25,000 games that differ in their genres, prices, sales, release dates, frequency of updates, and other characteristics.
-Inevitably, an appropriate sample should be selected for the analysis.
-@SorokinStevens20 studies the causal effect of reviews on sales on Steam, and I mirror closely the sample selection procedure used in that paper.
-First, Steam has made some significant changes to its review system in late 2016, and one of the effects was the removal of the a big number of reviews from the review score calculation.
-While it could be an intervention that is worthy of an independent study, in practice combining the data from before and after the intervention led to unsound results, so I focus on the two year period from January 2017 to January 2019, keeping the review system as stable as possible.
-In particular, only games that were released in this time period make it to the sample.
-
-Second, online multiplayer games and games that update frequently are dropped from the sample, as these are products whose quality is changing a lot over time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience.
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+%
+\documentclass[
+  12pt,
+  pagebackref]{article}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdfauthor={Dmitry Sorokin},
+  colorlinks=true,
+  linkcolor=mypink,
+  filecolor=myblue,
+  citecolor=mypink,
+  urlcolor=mypink,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{5}
+\renewcommand{\ttdefault}{cmr} % change the font of inline R results to normal
+\renewcommand*{\backref}[1]{}
+\renewcommand*{\backrefalt}[4]{%
+    \ifcase #1 (Not cited.)%
+    \or        [Cited on page~#2.]%
+    \else      [Cited on pages~#2.]%
+    \fi}
+\setlength{\parindent}{25pt}
+\setlength{\parskip}{0pt}
+\setlength{\skip\footins}{0.25cm} % margin before footnotes
+\definecolor{myblue}{RGB}{31, 61, 122}
+\definecolor{mypink}{RGB}{204, 0, 82}
+\newtheorem{assumption}{Assumption}[section]
+\newtheorem{proposition}{Proposition}[section]
+\newcommand{\EE}[1]{\mathbb{E}\left[#1\right]}
+\newcommand{\PP}[1]{\mathbb{P}\left(#1\right)}
+\newcommand{\CP}[2]{\mathbb{P}\left(#1 \,| \, #2 \right)}
+\newcommand{\CE}[2]{\mathbb{E}\left[#1\,|\,#2 \right]}
+\usepackage[bottom]{footmisc}
+\usepackage[doublespacing]{setspace}
+\usepackage[tableposition=top]{caption}
+\usepackage{dsfont}
+\usepackage{booktabs}
+\usepackage{makecell}
+\usepackage[]{natbib}
+\bibliographystyle{plainnat}
+
+\title{Consumer Reviews and Product Discounts:\\
+Evidence From Video Games}
+\author{Dmitry Sorokin}
+\date{August 08, 2020}
+
+\begin{document}
+\maketitle
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+\hypertarget{literature-review}{%
+\section{Literature Review}\label{literature-review}}
+
+This paper contributes to several closely related literatures in
+economics and marketing. The oldest of these is the literature
+investigating the impact of online consumer reviews on sales. An
+extensive review of the studies focusing on this topic and their
+meta-analysis is provided, for example, by \citet{Floyd14}. In a seminal
+contribution in this literature, \citet{ChevalierMayzlin06} uses a
+difference-in-differences approach, exploiting the differences in
+reviews for the same books across Amazon.com and Barnesandnoble.com, to
+argue that better reviews causally improve sales. A similar approach
+applied to the same market was recently used by
+\citet{ReimersWaldfogel20}, who reaffirm the importance of reviews for
+sales of books and quantify the welfare implications of the
+informational content of consumer reviews. \citet{ZhuZhang10} exploit
+differences between two different video games consoles rather than
+websites, and find that review ratings matter only for less popular
+games.
+
+For identification, the difference-in-differences approach relies on the
+existence of several comparable platforms, and assumes that the
+unobserved platform-specific tastes for those platforms are fixed.
+Another approach to identification exploits the rounding of the review
+data that platforms use to produce simple visual review labels. For
+example, Yelp.com, a popular restaurant comparison service, assigns 4
+stars to restaurants that have an average review score between 4 and
+4.24 (out of 5), but 4.5 stars to restaurants with an average score
+between 4.25 and 4.74. \citet{AndersonMagruder12} and \citet{Luca16}
+develop a regression discontinuity approach exploiting this rounding to
+show that an additional half-star on Yelp.com increases restaurants'
+traffic and revenue. \citet{SorokinStevens20} applies a similar approach
+to the video games market and also finds that better review labels
+increase sales, albeit raising some concerns about the validity of the
+approach. In the absence of direct sales data, \citet{SorokinStevens20}
+uses a particular regression specification that extracts the information
+on sales from the video games' usage data. The present paper supplements
+the panel methods in \citet{SorokinStevens20} by offering a structural
+way to estimate the effect of reviews on sales in the absence of direct
+sales data.
+
+With benefits of having good reviews come the incentives to influence
+the reviews in order to reap those benefits. There are several ways
+firms can affect their online reviews. One is review fraud.
+\citet{Mayzlin14} provides evidence that small hotel owners leave
+negative reviews for their competitors, and good reviews for themselves.
+\citet{LucaZervas16} provide similar evidence for restaurants on Yelp. A
+more honest way for a firm to influence reviews is by assuming an active
+approach to review management, and to publicly respond to reviews
+published online. \citet{GuYe14} provide evidence that consumers who had
+left a negative review about their hotel experience in the past were
+more likely to leave a positive review of the same hotel after a future
+stay if their previous review was responded to by the management.
+\citet{XieEtAl17} shows that lengthy in-depth managerial responses to
+negative reviews are associated with better financial performance in the
+future. This literature has also been concerned with how consumers
+change their reviewing behavior when managers start responding to
+reviews, essentially moving from studying individual responses to
+describing equilibrium outcomes. In somewhat contradictory findings,
+\citet{ProserpioZervas17} argues that hotels responding to bad reviews
+experience an increase in both the valence and the volume of their
+reviews, attributing it to consumers' reluctance to leave short
+indefensible reviews in a situation when they can be responded to, while
+\citet{ChevalierEtAl18} finds the opposite effect in the same market,
+arguing that managerial responses encourage negative review activity,
+because consumers get a signal that the firm is ``listening'' to them,
+and are then stimulated to leave negative reviews that they deem more
+influential.
+
+Direct ways of managing online reputation discussed above, however, are
+not the only avenues through which businesses can affect their reviews.
+Reviews are left by customers, and the happier they are, the better
+reviews they should leave, at least in principle. Another strand of
+literature is studying whether different kinds of promotions have an
+effect on firms' online reputation. In a seminal study,
+\citet{ByersEtAl12} documents that restaurants receive substantially
+worse reviews after running a Groupon price promotion. They present
+evidence that customers attracted by the promotion are different from
+regular customers, and that they are more likely to be trying out a new
+restaurant or cuisine while using the Groupon voucher, which can explain
+the reasons behind their dissatisfaction. Thus, the paper cautions
+against running price promotions in an attempt to poach new customers
+and improve the online reputation. \citet{Li16} confirms the finding in
+the same setting, but finds that restaurants with fewer and worse
+reviews can actually benefit from participating in a Groupon promotion.
+\citet{ZhuEtAl19} shows that customers who received a discount leave
+more positive, albeit less informative, reviews. In an experimental
+study on Ebay, \citet{CabralLi15} also find that offering a rebate for
+leaving (any) review significantly decreased the likelihood of negative
+feedback, and they provide evidence that this is due to reciprocity on
+the side of the clients, rather than the differences between customers
+buying with a rebate and without it.
+
+The present study contributes to this literature by providing novel
+evidence from a new market. I show that customers buying computer games
+are significantly more likely to leave positive reviews during
+discounts. More importantly, I go beyond the descriptive nature of the
+other papers in the literature, and show that firms leverage this fact
+to improve their reviews by giving discounts, thus providing evidence of
+a novel reputation management behavior. A study similar in spirit to
+mine is that of \citet{Zegners17}, who argues that less-known authors of
+eBooks on a crowded online marketplace are more likely to give their
+books out for free in order to build reputation and escape the ``zero
+reviews trap''. However, this study also finds that books are more
+likely to solicit negative feedback when sold for free, which somewhat
+undermines the strategy. Similar to \citet{ByersEtAl12},
+\citet{Zegners17} argues that purchasers of free books differ from the
+purchasers of regular books in their observable characteristics, and
+explains the negativity of the reviews by the selection effect.
+
+\hypertarget{institutional-setting-and-data}{%
+\section{Institutional Setting and
+Data}\label{institutional-setting-and-data}}
+
+\hypertarget{steam-marketplace}{%
+\subsection{Steam Marketplace}\label{steam-marketplace}}
+
+Steam is arguably the largest online marketplace for selling computer
+games in the world. Founded in 2003, in 2013 it was responsible for
+about 75\% of PC games sold online globally \citep{steamBloomberg}, and
+in 2017 it has earned around US\$4.3 billion, with an estimated market
+share of 18\% in the entire market for PC games \citep{psgames}. Given
+an ongoing unprecedented growth in the size of the video games' market
+\citep[\$43.4 billion in 2018, about the size of the U.S. film
+industry,][]{videoGamesMarket} and the increasing share of online sales
+in this market \citep[83\% in 2018, compared to 20\% in
+2009,][]{steamNPD}, Steam is a major player in an increasingly more
+important industry. Thus, this marketplace is not merely a laboratory
+for studies hoping to extrapolate the findings to other more well-known
+platforms, but is an important digital market to be studied in its own
+right.
+
+Any user who has a copy of a game on Steam can leave a review for that
+game. Starting from late 2016, by default, Steam only uses reviews left
+by customers who have \emph{purchased} the game in its review score
+calculation, excluding reviews left by customers who had obtained a key
+to activate the game through other channels (directly from the
+developer, or by purchasing the code from a different retailer). This
+distinguishes Steam from some other platforms studied in the literature,
+notably Yelp and TripAdvisor, where any user can leave a review (and, to
+a certain extent, Amazon, where non-verified users can also leave
+reviews). This gives me confidence in the authenticity of most reviews.
+This confidence is further backed by the importance of Steam to game
+developers and publishers, and Steam's history of monitoring the
+platform for fraudulent activity and excluding unscrupulous actors. With
+such high stakes, and a non-negligible risk of being caught, there are
+good reasons to expect the developers to behave scrupulously.
+
+A review consists of a binary grade, ``thumbs up'' or ``thumbs down'',
+and review's text. A \emph{review score} is defined as the fraction of
+positive reviews among all reviews a game has, provided it has at least
+10 reviews. Based on the score, Steam assigns \emph{review labels}, or
+bins, to each game. These
+labels\footnote{There are labels worse than "Negative", but they are rare, so I bin all of them into "Negative"}
+and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}.
+For example, a game with 7 positive and 2 negative reviews would have
+neither a review score, nor a label, but an extra positive review would
+promote it to the ``Positive'' bin.
+
+\begin{table}[t]
+
+\caption{\label{tab:ReviewBinsTable}The mapping between the review score and review bins on Steam}
+\centering
+\begin{tabular}{lcc}
+\toprule
+Review Bin & N. of Reviews & Score\\
+\midrule
+No Score & [0, 10) & -\\
+Negative & Any & [0, 40)\\
+Mixed & Any & [40, 70)\\
+Mostly Positive & Any & [70, 80)\\
+Positive & [0, 50) & [80, 100)\\
+Very Positive & More than 50 & [80, 100)\\
+Overwhelmingly Positive & More than 500 & [95, 100]\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Steam's homepage welcomes customers with a selection of featured games,
+that could include new games, popular games that are currently on a
+discount, games that have recently released a major update, etc.
+\citep{steamVisibility}. A customer could either click on the games
+already presented to her, or browse one of the categories that Steam
+offers. Available categories are based on games' characteristics such as
+performance (e.g., ``Top Sellers'', ``New Releases''), genre (e.g,
+``Racing'', ``Anime'', ``Simulation''), or technical characteristics (VR
+or controller support). Games within a category are organized into a
+list, with an example session presented in Figure \ref{steamStore}. From
+that list the user can get some basic information about each game, such
+as its name, price, and if the game is currently on a discount.
+Importantly, if the user hovers her cursor over a game, she could
+further see the review label of the game and the number of reviews the
+game has. I use this feature of the Steam's store to rationalize why
+later in the analysis I choose to focus on the review labels as my main
+independent review variables, rather than, say, the review score or the
+review texts. Granted, informative review texts could be important for
+purchase decisions \citep{ChevalierMayzlin06}, but on Steam, in order to
+gain access to such information, a customer should be willing to click
+on the game in the first place. Thus, I conjecture that games with
+better review labels will, other things equal, attract more customers,
+and lead to more sales. Crucially, according to Steam's documentation,
+all review labels better than ``Negative`` have a very similar
+contribution to visibility on the platform, which means, for example,
+that games are not ordered by their review labels when the customer is
+browsing different categories \citeyearpar{steamVisibility2}. Therefore,
+any effect of the review labels on, say sales, should come through the
+perceived quality differences between different bins, rather than some
+mechanical visibility differences. As an illustration, note that the
+first game in the list depicted in Figure \ref{steamStore} has ``Mixed''
+reviews.
+
+\begin{figure}[h]
+
+ {\centering \includegraphics[width=0.75\linewidth,]{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/steamStore}
+
+ }
+
+ \caption{\label{steamStore}Example Browsing Session on Steam}\label{fig:unnamed-chunk-3}
+ \end{figure}
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
+
+Valve Corporation, the owner of Steam, is notoriously secretive about
+its data and algorithms. Given the importance of the information on the
+performance of different games for game developers and publishers, the
+community has responded to this secrecy by establishing projects that
+monitor Steam in real time and extract information that could be
+relevant for parties interested in Steam. The majority of data used in
+this project comes from one such project called ``Steam Database'', or
+``SteamDB''.
+
+Descriptive information on any game, that I will refer to as ``static'',
+such as its title, developer, release date, etc., are readily available
+from Steam, and this information is also present on SteamDB. More
+importantly, Steam Database offers a daily time series of prices and
+player activity for each game on Steam. In principle, the pricing
+information could be obtained by a repeated scraping of the store.
+However, the player activity information is not trivial to obtain, as
+Steam does not directly reveal such data, let alone the data on sales of
+different titles. The creators of SteamDB have declined to explain their
+collection method, but their reputation in the gaming community most
+certainly implies that they are doing the best they can. The resulting
+variable that SteamDB offers, that I will refer to as the \emph{player
+count}, measures the maximum number of concurrent player for each game
+on a daily basis. In other words, if on a particular day 10 people play
+the game every hour, except noon, when 13 people play the game
+simultaneously, then the recorded player count for this game on that day
+will be 13. The price and the player count time series are the major
+``dynamic'' variables used in the analysis. The last dynamic variable,
+namely the evolution of the review score for each game, is obtained by
+scraping the reviews directly from Steam, and reverse engineering the
+path of the review score.
+
+\begin{figure}[h]
+
+{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/example-game-1}
+
+}
+
+\caption{\label{exampleGame} An Example Game in the Sample: Player Count, Price, and Review Score Histories.}\label{fig:example-game}
+\end{figure}
+
+Steam is home to more than 25,000 games that differ in their genres,
+prices, sales, release dates, frequency of updates, and other
+characteristics. Inevitably, an appropriate sample should be selected
+for the analysis. \citet{SorokinStevens20} studies the causal effect of
+reviews on sales on Steam, and I mirror closely the sample selection
+procedure used in that paper. First, Steam has made some significant
+changes to its review system in late 2016, and one of the effects was
+the removal of the a big number of reviews from the review score
+calculation. While it could be an intervention that is worthy of an
+independent study, in practice combining the data from before and after
+the intervention led to unsound results, so I focus on the two year
+period from January 2017 to January 2019, keeping the review system as
+stable as possible. In particular, only games that were released in this
+time period make it to the sample.
+
+Second, online multiplayer games and games that update frequently are
+dropped from the sample, as these are products whose quality is changing
+a lot over
+time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience.
 Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}.
-Unobserved quality would present a big obstacle to the identification of the effect of reviews on pricing decisions or sales, because, say, a game that has just issued a major update might both upgrade to a better review label (because of the positive reception of the new content) and give a big discount to rekindle the interest of the players, but the discounting decision would not be influenced by the review transition.
-For the same reasons, I also drop free games and games that are released in a beta-version (the so called “Early Access” program), as these products are likely to be adding new content, and the update history is not a perfect way to monitor the updating activity.
-Finally, I drop few games with a player count of less than four on their median day, as these games are simply very small, and the quality of their player count data is questionable.
-
-## Sample Description
-
-The final sample includes `r info[, .N]` games which I observe for `r panel[, max(age), by = ID][, round(mean(V1))]` days each, on average.
-The main variables in the analysis are the aforementioned dynamic variables: player count, price, and review score history.
-An example observation from the sample is given in Figure \ref{exampleGame}.
-For the majority of the games in the sample, the player count is the highest around the release date, and then it quickly fades away and oscillates around a smaller level.
-The player count also jumps when a discount is given, reflecting the influx of new players.
-Games differ a lot in their sizes, as is evident from Figure \ref{sampleSizeHist}.
-
-```{r sample-size-hist, fig.cap='\\label{sampleSizeHist} Distributions of the Player Count on, and the Number of Reviews Accumulated by, the Age of 180 Days.'}
-p1 <- ggplot(data = panel[age==180, .(x = log(number))]) +
-  geom_histogram(mapping = aes(x = x, y = ..density..), 
-                 color = "black", 
-                 position = "identity", 
-                 alpha = 0.9,
-                 binwidth = 0.5,
-                 boundary = 0,
-                 fill = my.colors[1]) +
-  geom_density(mapping = aes(x = x), 
-                 color = "black", 
-                 position = "identity", 
-                 alpha = 0.4,
-                 fill = my.colors[1]) +
-  scale_x_continuous(name = "Log Players",
-                     breaks = seq(0, 8),
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = NULL, 
-                     minor_breaks = NULL) +
-  my.theme()
-
-p2 <- ggplot(data = panel[age==180, .(x = log(reviews))]) +
-  geom_histogram(mapping = aes(x = x, y = ..density..), 
-                 color = "black", 
-                 position = "identity", 
-                 alpha = 0.9,
-                 binwidth = 0.5,
-                 boundary = 0,
-                 fill = my.colors[1]) +
-  geom_density(mapping = aes(x = x), 
-                 color = "black", 
-                 position = "identity", 
-                 alpha = 0.4,
-                 fill = my.colors[1]) +
-  scale_x_continuous(name = "Log Reviews",
-                     breaks = seq(0, 8),
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = NULL, 
-                     minor_breaks = NULL) +
-  my.theme()
-
-ggarrange(p1, p2, ncol = 2, nrow = 1, align = "h")
-```
-
-```{r sample-size-hist-vert, include=FALSE}
-# for beamer
-ggarrange(p1, p2, ncol = 1, nrow = 2, align = "h")
-```
-
-As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is important.
-A representative game in the sample never changes its price, but instead occasionally goes on discounts, slowly increasing their magnitude as the game ages.
-There are
-`r panel[discount==F, diff(price), by = ID][V1>0, .N]` incidents of price change in the data, compared to 
-`r panel[discNew==T, .N]` discounts.
-Steam has a number of rules that regulate price promotions on its platform.
-A game can have a launch discount, but, otherwise, it has to wait for two months since the release before changing its price or giving a discount.
-A game can not go on discounts too frequently, and has to wait between four to six weeks
-after a price promotion to be able to run a new one.
-The duration of a custom discount is restricted to be at least one full day, and at most two weeks.
-Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on a discount.
-As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”.
-Curated promotions are featured prominently on Steam's main page, and, arguably, lead to more visibility and sales for the participating titles than custom discounts, which also contribute to visibility, but typically do not get the front-page promotional slots.
-An important type of curated discounts are the so-called “Seasonal Sales”--big platform-wide events that take place about four times a year around major holidays.
-Figure \ref{seasonalSales} shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving).
-Around `r  round(panel[discSeason==T & discNew == T, .N]/panel[discNew==T, .N]*100)`% of discounts in the sample go live during a Seasonal Sale.
-Thus, firms have significant agency when it comes to running price promotions, but platform regulations and platform-wide discounts are important determinants of firms' decision to discount.
-
-```{r seasonal-sales, fig.cap='\\label{seasonalSales} Fraction of Games in the Sample Running a Promotion.'}
-months1 <- c(-1, 30, 58, 89, 119, 150, 180, 211, 242, 272, 303, 333) + 1
-months2 <- c(333 + 32 + months1, 699 + 31)
-ggplot(data = panel[, .(y=sum(discount > 0)/(.N)), by = t]) +
-  # ggtitle() +
-  geom_line(aes(x = t, y = y),
-            color = my.colors[1],
-            size = 1) +
-  scale_x_continuous(name = NULL,
-                     breaks = c(months1, months2)[seq(1,25,3)], 
-                     labels = months(getDate(c(months1, months2))[seq(1,25,3)], 
-                                     abbreviate=T),
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = "Fraction of Games",
-                     minor_breaks = NULL)  +
-  my.theme(leg.x = 0.25, leg.y = 0.9)
-rm(months1, months2)
-```
-
-The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly.
-Recall that the review score is just the fraction of the positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in.
-Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release.
-On average across games, the standard deviation of the review score (out of one hundred) is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`, with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that.
-The score is only assigned once the game reaches 10 reviews, and once can see that 10 reviews is enough on average keep the score stable.
-The distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, is, then, representative of the situation at other ages.
-
-```{r review-descriptive-plots, fig.width = 6.5, fig.cap='\\label{reviewDescriptivePlots} Distribution of Games by Review Bins and the CDF\'s of Review Arrival Times by Quintiles at 180 Days.'}
-# Histogram of the bin distribution at the age of 180 days
-labls <- c("No Score", "Negative", "Mixed", "M. Positive", "Positive", "V. Positive", "Ov. Positive")
-short.labls <- c("N/S", "Neg", "Mix", "M.Pos", "Pos", "V.Pos", "Ov.Pos")
-nGroups <- 3
-p1 <- ggplot(data = panel[age==180, 
-                    .(`Review Bin` = factor(labls[1*noScore + 2*negative + 3*mixed + 4*mPositive + 
-                                                  5*realPositive + 6*vPositive + 7*ovPositive],
-                      levels = labls, labels = short.labls)
-                      )]) +
-  geom_bar(mapping = aes(x = `Review Bin`, 
-                         y = ..prop.., group=1), 
-                 color = "black", 
-                 alpha = 0.9,
-                 fill = my.colors[1]) +
-  scale_y_continuous(name = "Frequency") +
-  my.theme()
-
-# Arrival of reviews relative to the number accumulated at 180 days, by quintiles
-# Assign a number to each game that measures the number of full months it has
-# spent in the sample
-panel[, ageGroup:=age%/%30][, ageGroup:=rep(max(ageGroup), .N), by = ID]
-M <- panel[, max(ageGroup)]
-# Create an auxilary table that for every age (in months) takes games that have
-# been present for that many months, and then splits those games into 10 groups,
-# based on the amount of reviews they had at that age.
-f <- data.table(age=integer(), sizeGroup=integer(), ID=integer())
-for(m in 1:M){
-  f<-rbindlist(list(f,
-                    panel[ageGroup>=m&age==30*m, 
-                          .(age, sizeGroup=ecdf(reviews)(reviews), ID)
-                          ][, sizeGroup:=cut(sizeGroup,nGroups,labels=seq(1:nGroups))]),
-               use.names=TRUE)
+Unobserved quality would present a big obstacle to the identification of
+the effect of reviews on pricing decisions or sales, because, say, a
+game that has just issued a major update might both upgrade to a better
+review label (because of the positive reception of the new content) and
+give a big discount to rekindle the interest of the players, but the
+discounting decision would not be influenced by the review transition.
+For the same reasons, I also drop free games and games that are released
+in a beta-version (the so called ``Early Access'' program), as these
+products are likely to be adding new content, and the update history is
+not a perfect way to monitor the updating activity. Finally, I drop few
+games with a player count of less than four on their median day, as
+these games are simply very small, and the quality of their player count
+data is questionable.
+
+\hypertarget{sample-description}{%
+\subsection{Sample Description}\label{sample-description}}
+
+The final sample includes 906 games which I observe for 393 days each,
+on average. The main variables in the analysis are the aforementioned
+dynamic variables: player count, price, and review score history. An
+example observation from the sample is given in Figure
+\ref{exampleGame}. For the majority of the games in the sample, the
+player count is the highest around the release date, and then it quickly
+fades away and oscillates around a smaller level. The player count also
+jumps when a discount is given, reflecting the influx of new players.
+Games differ a lot in their sizes, as is evident from Figure
+\ref{sampleSizeHist}.
+
+\begin{figure}[h]
+
+{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/sample-size-hist-1}
+
 }
-setkey(f, age, sizeGroup, ID)
-
-# Create a table that has data on averaged arrivals of reviews.
-# arrival[month==M & size==G, .(age, fracRev)]
-# returns a data table of length (30M+1) (all months have 30 days except the first one),
-# where fracRev shows the fraction of total reviews an average game has accumulated by that day.
-arrival <- data.table(month=integer(), size=integer(), age=integer(), fracRev=double())
-for(a in f[, unique(age)]){
-  for(size in 1:nGroups){
-    ids <- f[age==a & sizeGroup==size, ID]
-    arrival<-rbindlist(list(arrival,
-             panel[ID%in%ids & age<=a, .(month=a%/%30,size=size,age,
-                                         freq=reviews/max(reviews)),
-             by=ID][, .(fracRev=mean(freq,na.rm=T)), by=c("month","size","age")]),
-             use.names=TRUE)
+
+\caption{\label{sampleSizeHist} Distributions of the Player Count on, and the Number of Reviews Accumulated by, the Age of 180 Days.}\label{fig:sample-size-hist}
+\end{figure}
+
+As the goal of the paper is to understand if firms use pricing tools in
+order to improve their online reputation, a detailed overview of pricing
+and review variables is important. A representative game in the sample
+never changes its price, but instead occasionally goes on discounts,
+slowly increasing their magnitude as the game ages. There are 43
+incidents of price change in the data, compared to 6331 discounts. Steam
+has a number of rules that regulate price promotions on its platform. A
+game can have a launch discount, but, otherwise, it has to wait for two
+months since the release before changing its price or giving a discount.
+A game can not go on discounts too frequently, and has to wait between
+four to six weeks after a price promotion to be able to run a new one.
+The duration of a custom discount is restricted to be at least one full
+day, and at most two weeks. Besides these custom discounts, that are
+fully managed by the firms, Steam has a series of curated discounts,
+when the platform invites selected titles to go on a discount. As
+\citet{steamDiscounting} explains it, ``while there aren't strict rules,
+as a base guideline we tend to focus on the top 10-20\% selling games on
+Steam that are positively reviewed and have otherwise proven to be
+successful''. Curated promotions are featured prominently on Steam's
+main page, and, arguably, lead to more visibility and sales for the
+participating titles than custom discounts, which also contribute to
+visibility, but typically do not get the front-page promotional slots.
+An important type of curated discounts are the so-called ``Seasonal
+Sales''--big platform-wide events that take place about four times a
+year around major holidays. Figure \ref{seasonalSales} shows that the
+biggest sales take place in Winter (Christmas and New Year) and Summer
+(July 4), but there are also significant discounts in the Fall
+(Halloween and Thanksgiving). Around 64\% of discounts in the sample go
+live during a Seasonal Sale. Thus, firms have significant agency when it
+comes to running price promotions, but platform regulations and
+platform-wide discounts are important determinants of firms' decision to
+discount.
+
+\begin{figure}[h]
+
+{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/seasonal-sales-1}
+
 }
+
+\caption{\label{seasonalSales} Fraction of Games in the Sample Running a Promotion.}\label{fig:seasonal-sales}
+\end{figure}
+
+The path of the review score of a typical game is quite different from
+its price history, in that the review score tends to settle quickly.
+Recall that the review score is just the fraction of the positive
+reviews among all reviews, so the law of large number implies that this
+ratio crystallizes as more reviews flow in. Second plot in Figure
+\ref{reviewDescriptivePlots} shows that games tend to receive half of
+the reviews they have at the age of 180 days in their first month after
+the release. On average across games, the standard deviation of the
+review score (out of one hundred) is just 2.2, with a split of 1.83 in
+the first thirty days and 1.83 after that. The score is only assigned
+once the game reaches 10 reviews, and once can see that 10 reviews is
+enough on average keep the score stable. The distribution of games by
+bins at the age of 180 days, depicted in Figure
+\ref{reviewDescriptivePlots}, is, then, representative of the situation
+at other ages.
+
+\begin{figure}[h]
+
+{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/review-descriptive-plots-1}
+
 }
-rm(a,ids,size,M,f)
-
-p2 <- ggplot(data=arrival[month==6, ]) +
-  geom_line(aes(x=age, y=fracRev, color=factor(size)),
-            size=1) +
-  scale_x_continuous(name = "Age (Days)",
-                     breaks = seq(0,180,30),
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = "% Of Reviews") +
-  scale_color_manual(values = my.colors,
-                     name = "Tercile: ") +
-  my.theme(leg.x = 0.8, leg.y = 0.4) +
-   theme(legend.direction = "vertical")
-rm(arrival)
-
-ggarrange(p1, p2, ncol = 2, nrow = 1, align = "h")
-```
-
-```{r}
-transitions <- panel[, .(t, neg=c(NA, diff(negative)),
-                    mix=c(NA, diff(mixed)),
-                    mpos=c(NA, diff(mPositive)),
-                    pos=c(NA, diff(realPositive)),
-                    vPos=c(NA, diff(vPositive)),
-                    ovPos=c(NA, diff(ovPositive)),
-                    negative, mixed, mPositive, realPositive,
-                    vPositive, ovPositive), by=ID]
-transitions <- transitions[neg ==-1 | mix ==-1 | 
-                           mpos == -1 | pos == -1 | 
-                           vPos == -1 | ovPos == -1, ]
-transitions[neg==-1, origin := "Negative"]
-transitions[mix==-1, origin := "Mixed"]
-transitions[mpos==-1, origin := "M. Positive"]
-transitions[pos==-1, origin := "Positive"]
-transitions[vPos==-1, origin := "V. Positive"]
-transitions[ovPos==-1, origin := "Ov. Positive"]
-transitions[, origin := factor(origin, 
-                               levels = labls[-1],
-                               labels = labls[-1],
-                               ordered = T)]
-setkey(transitions, ID, t)
-transitions[, trID := (1:length(t)), by = ID]
-setkey(transitions, ID, t, trID)
-# separate good transitions from bad transitions
-transitions[, goodTr := F]
-transitions[neg==-1 | (mix==-1 & neg!=1) | (mpos == -1 & mix != 1 & neg!= 1) |
-            (pos==-1 & (vPos==1 | ovPos==1)) | (vPos==-1 & ovPos == 1), goodTr := T]
-
-transitions[, dur := shift(t,-1) - t, by = ID]
-```
-
-Despite the relative rigidity of the review score, there is enough transitions between the review bins to make the analysis of pricing decisions by firms around such transitions possible.
-Table \ref{tab:transitionMatrix} describes the transitions between review bins in the sample.
-The number of unique games that have changed review labels in the data is `r transitions[, unique(ID)] %>% length`, and the number of transitions is `r transitions[, .N]`.
-Sometimes games switch their bins briefly, and go back soon after.
-The number of transitions that led to the game spending at least 7 days in the new bin is `r transitions[(is.na(dur) | dur >= 7), .N]`.
-Table \ref{mDiscountTable} describes the state of the games in the two weeks before their transitions.
-Discounting  does take place before the transitions, games transition at very different ages, but tend to have only a limited number of reviews by the time their review bin changes.
-
-```{r}
-kable(
-   cbind(
-      transitions[, .(
-         Neg = round(100*mean(negative)),
-         Mix = round(100*mean(mixed)), 
-         `M. Pos` = round(100*mean(mPositive)), 
-         Pos = round(100*mean(realPositive)),
-         `V. Pos` = round(100*mean(vPositive)),
-         `Ov. Pos` = round(100*mean(ovPositive))),
-         keyby=origin][,` `:=origin][,-c("origin")],
-      transitions[, .(
-         Neg = sum(negative),
-         Mix = sum(mixed),
-         `M. Pos` = sum(mPositive),
-         Pos = sum(realPositive),
-         `V. Pos` = sum(vPositive),
-         `Ov. Pos` = sum(ovPositive)),
-         keyby=origin][,-c("origin")]),
-      format = "latex",
-      label = "transitionMatrix",
-      caption = "Transition Probability And Count Matrices",
-      align = c('c', "c", "c", "c", "c", "c", "c"),
-      valign = 't',
-      linesep = "",
-      booktabs = T) %>%
-add_header_above(c("Probabilities" = 6, " ","Counts" = 6)) %>%
-kable_styling(latex_options = c("scale_down"))
-```
-
-```{r results='asis'}
-transPanel <- transitions[(is.na(dur) | dur >= 7), 
-                          .(time = t + seq(-14,14),
-                            tToTransit = seq(-14,14),
-                            trID, goodTr),
-                 by = c("ID","t")] %>% unique()
-transPanel[, t := NULL]
-setnames(transPanel, old = "time", new = "t")
-transPanel <- merge(transPanel, panel[,.(ID, t, age, discount, discNew, tWODisc, reviews, score, noScore, negative, mPositive, positive, realPositive, vPositive, ovPositive, day, week)], by = c("ID","t"))
-setkey(transPanel, "ID", "t", "trID")
-
-transPanel[, discount := discount*100]
-transPanel[, tToTransitNeg := tToTransit * (tToTransit < 0)]
-transPanel[, tToTransitPos := tToTransit * (tToTransit >= 0)]
-
-stargazer(
-   transPanel[tToTransit<0, .(
-      `Mean Discount (%)` = mean(discount),
-      `Age` = round(mean(age)),
-      `Reviews` = round(mean(reviews))), 
-      by = c("ID", "trID")][, -c("ID", "trID")],
-         title = "Average Discount, Age, and Review Count Two Weeks Before A Transition",
-         label = "mDiscountTable",
-         omit.summary.stat = c("min", "max"),
-         header = F,
-         digits = 0)
-```
-
-```{r transition-discount-plot, fig.cap='\\label{discountsTransitions} Discounting By Games Around The Transition.'}
-ggplot(data=transPanel[, .(x=tToTransit, y=100*(discount>0),
-                           g=factor(goodTr))],
-       aes(x=x, y=y)) +
-   geom_vline(xintercept = 0, linetype = "longdash", size = 0.2) +
-   aes(color=g) + 
-   stat_summary(fun.data = mean_se,
-               #color = my.colors[1:2],
-               size=0.4) +
-   geom_smooth(#color=my.colors[3],
-              size=0.6, se = F) +
-   scale_x_continuous(name = "Days After Transition",
-                     breaks = seq(-14, 14, 2),
-                     minor_breaks = NULL) +
-   scale_y_continuous(name = "% Of Games Discounting", ) +
-   scale_color_manual(labels = c("Bad", "Good"),
-                      name = "Transition",
-                      values = my.colors) +
-   my.theme(leg.x = 0.78, leg.y = 0.82)
-```
-
-```{r, include=F}
-reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos + 
-              + noScore + negative + mPositive + realPositive + vPositive + ovPositive +
-              log(reviews) + age + poly(tWODisc, degree = 2) + day + week, data = transPanel)
-cov<-vcovHC(reg1)
-se1 <- sqrt(diag(cov))
-
-star.out.transitions <- stargazer(reg1,
-          label = "transitionReg",
-          table.placement = "hp",
-          header = FALSE,
-          title = "Discounts In The Days Around Transition",
-          se=list(se1),
-          #column.labels=c(),
-          dep.var.labels = c("Discount Probability"),
-          covariate.labels = c("Days to Transition", "Days After Transition", "No Score", 
-                               "Negative", "Mostly Positive", "Positive", "Very Positive",
-                               "Ov. Positive", "Log Reviews", "Age", "Const"),
-          model.numbers = F,
-          omit = c("day", "week", "tWODisc"),
-          omit.stat=c("f","adj.rsq","ser"),
-          no.space=T)
-```
-
-# Descriptive Evidence
-
-In this section I present evidence that firms use discounting to manage their online reputation, in particular, by running price promotions when they are close to improving their review label.
-For now, let us resort to a very simplistic story of why a firm would be interested in doing that.
-Assume that discounts increase the inflow customers, and that more customers means more reviews.
-Also, take for granted, for now, that better review labels improve sales.
-Then, if a firm is one positive review away from upgrading its review label, it might be tempted to speed things up by giving a discount.
-Similarly, a product that is close to sliding into a worse review bin, could be tempted to run a price promotion, in order to avoid a slump in its reviews.
-I will address this story in more detail in the discussion part of this section, but for now I turn attention to simply establishing that this sort of behavior indeed takes place in the sample.
-
-The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels are very often preceded by discounts.
-The graph shows that two weeks prior to a transition only 15% of games were on a discount, a number close to the sample average, but that this number more than doubles to around 35% one day before the label change.
-Regression analysis controlling for review label, number of reviews, age, day of the week and week time effects, as well as time since the previous discount, confirms that the association depicted in Figure \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in the Appendix).
-A game is approximately `r round(reg1$coefficients[2]*14*100)` pp more likely to be on a discount on the day of the transition than it is two weeks prior to it, and it is `r round(-reg1$coefficients[3]*14*100)` pp less likely to be on a discount two weeks following the transition.
-Given that the probability for a game to be on a discount on a random day is `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% in the sample, these effects amount to `r round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% and `r round(100*(-reg1$coefficients[3]/panel[, mean((discount > 0), na.rm=T)]))`% changes in the daily probability of a discount, which is quite sizable.
-
-Of course, this finding simply shows a correlation between firms' discounting behavior and review transitions.
-The same pattern could emerge if the causality between the two variables is reversed, i.e.
-the discounts cause transitions, and not the other way around.
-Imagine a hypothetical world in which games are only bought on discounts.
-In this world any action in the data would be preceded (and, to some extent, caused) by a discount.
-In other words, firms could be giving discounts for reasons unrelated to reviews, but transitions sometimes would follow as a result.
-As a matter of fact, suppose that the story I am after is true, and that firms try to achieve transitions  via price promotions.
-In that case, discounts *have* to be able to aid transitioning, making the reverse causality inherent in this setting.
-The analysis behind Figure \ref{discountsTransitions} remains imperfect for yet another reason.
-A discount given when a firm is close to a positive transition is not guaranteed to lead to a transition.
-Similarly, a firm trying to avoid a negative transition by giving a discount might succeed.
-In both cases, the behavior that we are interested in goes undetected if one only studies transitions that took place in the data.
-
-The solution to both problems that I suggest is to study *potential* transitional situations instead of the realized ones.
-First, it solves the reverse causality problem.
-A discount given today can cause a transition tomorrow, but a decision to give a discount can not cause the proximity to a transition that chronologically precedes it.
-Second, it clearly solves the selection issue explained above, when the analysis considers solely the firms that transitioned.
-
-With the focus now on potential transitions, the crucial question is how to define proximity to a transition.
-One approach would be to use the raw review count, and to say that a game is close to upgrading its review label when it needs five (ten, twenty ...) more positive reviews to transition.
-However, given the heterogeneity in the popularity of different games (see Figure \ref{sampleSizeHist}), five extra reviews could be nothing for a very popular game, and hard to acquire for a small game.
-For this reason I use a different approach, that measures proximity by the expected number of days that a game has to wait to accumulate the reviews necessary for a transition.
-In particular, for every game-date pair I first measure how many positive reviews that game needs at the moment to upgrade its review bin, and how many negative reviews that game needs to degrade its review bin.
-In the next step, for each game I calculate the average speed of review arrivals, by simply dividing the number of positive (negative) reviews as of the last day in the sample by the age of the game on that day.
-Knowing the speed of positive and negative review arrivals, and the  number of reviews necessary for a transition, I then define the proximity to a positive (negative) transition to be the expected number of days needed for the game to accumulate the necessary number of positive (negative) reviews, assuming that it does not receive any negative (positive) reviews during that time.
-
-To illustrate this definition, consider an example game with 19 positive reviews and 6 negative reviews at some moment in time.
-This game has a review score of 76\%, and the “Mostly Positive” review label.
-It needs 5 additional positive reviews to secure a score of 80\%, the threshold that would earn it the “Positive” label.
-Similarly, 3 new negative reviews would be sufficient for the game to slide into the “Mixed” review category, as the score would become $19/(25 + 3) \times 100\%= 67\%$, which is less than the $70\%$ required for the “Mostly Positive” bin.
-If this game ends up having 80 positive and 20 negative reviews at the age of 200 days, its last day in the sample, then, on average, it was receiving 0.4 positive and 0.1 negative reviews per day.
-Thus, for a positive transition it requires $5/0.4 = 12.5$ days of only good reviews arriving at this rate.
-Similarly, for a negative transition it requires $3 / 0.1 = 30$ days of only bad reviews arriving at this rate.
-So, for this game I set its proximity to a potential positive transition to be 12.5 days, and its proximity to a potential negative transition to be 30 days.
-
-```{r include = F,}
-band <- 7
-
-panel[, pRevRate := max(pReviews,na.rm = T)/max(age, na.rm = T), by = ID]
-panel[, nRevRate := max(nReviews,na.rm = T)/max(age, na.rm = T), by = ID]
-
-R.low <- 0.4
-R.high <- 0.7
-panel[score < R.high*100 & score >= R.low*100,
-      needPos := ceiling((R.high*reviews-pReviews)/(1-R.high))]
-panel[score < R.high*100 & score >= R.low*100,
-      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
-# corrects for the rounding error caused by machine precision division of, say, 4/10 != 0.4. If you are supposed to be brought exactly to the cutoff, your needNeg is one review more than that
-panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
-
-R.low <- 0.7
-R.high <- 0.8
-panel[score < R.high*100 & score >= R.low*100,
-      needPos := ceiling((R.high*reviews-pReviews)/(1-R.high))]
-panel[score < R.high*100 & score >= R.low*100,
-      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
-panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
-
-panel[pRevRate > 0, needPosDays:=needPos/pRevRate]
-panel[nRevRate > 0, needNegDays:=needNeg/nRevRate]
-panel[, pos.treatment := (needPos <= 2*band)]
-panel[, neg.treatment := (needNeg <= 2*band)]
-
-reg3 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
-               mPositive + age + young + day + week,
-                 data=panel[],
-            model="within")
-cov<-vcovHC(reg3, method="white1")
-se3 <- sqrt(diag(cov))
-
-R.low <- 0.7
-R.high <- 0.8
-panel[score >= R.high*100 & reviews < 50,
-      needPos := 50 - reviews]
-panel[score >= R.high*100 & reviews < 50,
-      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
-panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
-
-R.high <- 0.95
-panel[vPositive == T & score >= R.high*100 & reviews < 500,
-      needPos := 500 - reviews]
-panel[vPositive == T & score >= R.high*100 & reviews < 500,
-      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
-
-panel[score < R.high*100 & vPositive == T,
-      needPos := pmax(ceiling((R.high*reviews-pReviews)/(1-R.high)), 500-reviews)]
-panel[score < R.high*100 & vPositive == T,
-      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
-
-panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
-
-panel[, needPosDays:=needPos/pRevRate]
-panel[nRevRate > 0, needNegDays:=needNeg/nRevRate]
-panel[, pos.treatment := (needPos <= 2*band)]
-panel[, neg.treatment := (needNeg <= 2*band)]
-
-reg1 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
-               mPositive + realPositive + vPositive + age + young + day + week,
-                 data=panel[],
-            model="within")
-cov<-vcovHC(reg1, method="white1")
-se1 <- sqrt(diag(cov))
-
-panel[, pos.treatment := (needPos <= band)]
-panel[, neg.treatment := (needNeg <= band)]
-
-reg2 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
-               mPositive + realPositive + vPositive + age + young + day + week,
-                 data=panel[],
-            model="within")
-cov<-vcovHC(reg2, method="white1")
-se2 <- sqrt(diag(cov))
-
-star.out <- stargazer(reg1, reg2, reg3,
-             label = "potentialTransitionsResults",
-             table.placement = "hp",
-             header = FALSE,
-             title = "Discounts Close to Potential Transitions",
-             se=list(se1, se2, se3),
-             dep.var.labels = c("Discount Probability"),
-             column.labels = c("Full", "1 W. to Tr.", "Simple Tr."),
-             covariate.labels = c("Close to Pos. Transition", "Close to Neg. Transition",
-                                  "Log Days to Pos. Tr.", "Log Days to Neg Tr.",
-                                  "Log Reviews", "Mostly Positive", "Positive",
-                                  "Very Positive", "Age", "Age $\\le 14$"),
-             model.numbers = F,
-             omit = c("day", "week", "tWODisc"),
-             omit.stat=c("f","adj.rsq","ser"),
-             no.space=T)
-
-```
-
-As the example above shows, it is impossible to consider proximity to a positive transition without taking into account the proximity to a negative transition, at least for moderately sized games.
-If firms' strategies for these types of transitions are different, then studying such transitions separately could attenuate the effect of the proximity to, say, a positive transition, on the discount probability: a firm that is close to upgrading its review bin might not give a discount not because it is a bad way to accomplish that transition, but because that firm is at the same time close to downgrading its review bin, and might prefer to exercise prudence.
-For this reason, I define two “treatment” variables of interest.
-Game $i$ at date $t$ is said to be close to a positive transition, $T_{it}^+ = 1$, if its proximity to a positive transition is less than or equal to `r 2*band` days.
-Similarly, game $i$ at date $t$ is said to be close to a negative transition, $T_{it}^- = 1$, if its proximity to a positive transition is less than or equal to `r 2*band` days.
-The `r 2*band` cutoff is inspired by the maximum duration of custom discounts on Steam, and the patterns of discounting around successful transitions, depicted in Figure \ref{discountsTransitions}.
-To estimate the effect of being close to a review transition on the discounting behavior, I then estimate the following model:
+
+\caption{\label{reviewDescriptivePlots} Distribution of Games by Review Bins and the CDF's of Review Arrival Times by Quintiles at 180 Days.}\label{fig:review-descriptive-plots}
+\end{figure}
+
+Despite the relative rigidity of the review score, there is enough
+transitions between the review bins to make the analysis of pricing
+decisions by firms around such transitions possible. Table
+\ref{tab:transitionMatrix} describes the transitions between review bins
+in the sample. The number of unique games that have changed review
+labels in the data is 596, and the number of transitions is 1688.
+Sometimes games switch their bins briefly, and go back soon after. The
+number of transitions that led to the game spending at least 7 days in
+the new bin is 1225. Table \ref{mDiscountTable} describes the state of
+the games in the two weeks before their transitions. Discounting does
+take place before the transitions, games transition at very different
+ages, but tend to have only a limited number of reviews by the time
+their review bin changes.
+
+\begin{table}[t]
+
+\caption{\label{tab:transitionMatrix}Transition Probability And Count Matrices}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}{ccccccccccccc}
+\toprule
+\multicolumn{6}{c}{Probabilities} & \multicolumn{1}{c}{ } & \multicolumn{6}{c}{Counts} \\
+\cmidrule(l{3pt}r{3pt}){1-6} \cmidrule(l{3pt}r{3pt}){8-13}
+Neg & Mix & M. Pos & Pos & V. Pos & Ov. Pos &   & Neg & Mix & M. Pos & Pos & V. Pos & Ov. Pos\\
+\midrule
+0 & 100 & 0 & 0 & 0 & 0 & Negative & 0 & 58 & 0 & 0 & 0 & 0\\
+24 & 0 & 76 & 0 & 0 & 0 & Mixed & 60 & 0 & 189 & 0 & 0 & 0\\
+0 & 43 & 0 & 25 & 33 & 0 & M. Positive & 0 & 245 & 0 & 141 & 188 & 0\\
+0 & 0 & 40 & 0 & 60 & 0 & Positive & 0 & 2 & 207 & 0 & 310 & 0\\
+0 & 0 & 84 & 0 & 0 & 16 & V. Positive & 0 & 0 & 220 & 0 & 0 & 43\\
+0 & 0 & 0 & 0 & 100 & 0 & Ov. Positive & 0 & 0 & 0 & 0 & 25 & 0\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{Average Discount, Age, and Review Count Two Weeks Before A Transition} 
+  \label{mDiscountTable} 
+\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} \\ 
+\hline \\[-1.8ex] 
+Mean Discount (\%) & 1,225 & 10 & 14 & 0 & 15.9 \\ 
+Age & 1,225 & 142 & 157 & 8 & 226 \\ 
+Reviews & 1,225 & 130 & 343 & 26 & 81 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+\begin{figure}[h]
+
+{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/transition-discount-plot-1}
+
+}
+
+\caption{\label{discountsTransitions} Discounting By Games Around The Transition.}\label{fig:transition-discount-plot}
+\end{figure}
+
+\hypertarget{descriptive-evidence}{%
+\section{Descriptive Evidence}\label{descriptive-evidence}}
+
+In this section I present evidence that firms use discounting to manage
+their online reputation, in particular, by running price promotions when
+they are close to improving their review label. For now, let us resort
+to a very simplistic story of why a firm would be interested in doing
+that. Assume that discounts increase the inflow customers, and that more
+customers means more reviews. Also, take for granted, for now, that
+better review labels improve sales. Then, if a firm is one positive
+review away from upgrading its review label, it might be tempted to
+speed things up by giving a discount. Similarly, a product that is close
+to sliding into a worse review bin, could be tempted to run a price
+promotion, in order to avoid a slump in its reviews. I will address this
+story in more detail in the discussion part of this section, but for now
+I turn attention to simply establishing that this sort of behavior
+indeed takes place in the sample.
+
+The departing point of the analysis is Figure
+\ref{discountsTransitions}, which shows that transitions between review
+labels are very often preceded by discounts. The graph shows that two
+weeks prior to a transition only 15\% of games were on a discount, a
+number close to the sample average, but that this number more than
+doubles to around 35\% one day before the label change. Regression
+analysis controlling for review label, number of reviews, age, day of
+the week and week time effects, as well as time since the previous
+discount, confirms that the association depicted in Figure
+\ref{discountsTransitions} is robust (see Table \ref{transitionReg} in
+the Appendix). A game is approximately 8 pp more likely to be on a
+discount on the day of the transition than it is two weeks prior to it,
+and it is 16 pp less likely to be on a discount two weeks following the
+transition. Given that the probability for a game to be on a discount on
+a random day is 16\% in the sample, these effects amount to 3\% and 7\%
+changes in the daily probability of a discount, which is quite sizable.
+
+Of course, this finding simply shows a correlation between firms'
+discounting behavior and review transitions. The same pattern could
+emerge if the causality between the two variables is reversed, i.e.~the
+discounts cause transitions, and not the other way around. Imagine a
+hypothetical world in which games are only bought on discounts. In this
+world any action in the data would be preceded (and, to some extent,
+caused) by a discount. In other words, firms could be giving discounts
+for reasons unrelated to reviews, but transitions sometimes would follow
+as a result. As a matter of fact, suppose that the story I am after is
+true, and that firms try to achieve transitions via price promotions. In
+that case, discounts \emph{have} to be able to aid transitioning, making
+the reverse causality inherent in this setting. The analysis behind
+Figure \ref{discountsTransitions} remains imperfect for yet another
+reason. A discount given when a firm is close to a positive transition
+is not guaranteed to lead to a transition. Similarly, a firm trying to
+avoid a negative transition by giving a discount might succeed. In both
+cases, the behavior that we are interested in goes undetected if one
+only studies transitions that took place in the data.
+
+The solution to both problems that I suggest is to study
+\emph{potential} transitional situations instead of the realized ones.
+First, it solves the reverse causality problem. A discount given today
+can cause a transition tomorrow, but a decision to give a discount can
+not cause the proximity to a transition that chronologically precedes
+it. Second, it clearly solves the selection issue explained above, when
+the analysis considers solely the firms that transitioned.
+
+With the focus now on potential transitions, the crucial question is how
+to define proximity to a transition. One approach would be to use the
+raw review count, and to say that a game is close to upgrading its
+review label when it needs five (ten, twenty \ldots) more positive
+reviews to transition. However, given the heterogeneity in the
+popularity of different games (see Figure \ref{sampleSizeHist}), five
+extra reviews could be nothing for a very popular game, and hard to
+acquire for a small game. For this reason I use a different approach,
+that measures proximity by the expected number of days that a game has
+to wait to accumulate the reviews necessary for a transition. In
+particular, for every game-date pair I first measure how many positive
+reviews that game needs at the moment to upgrade its review bin, and how
+many negative reviews that game needs to degrade its review bin. In the
+next step, for each game I calculate the average speed of review
+arrivals, by simply dividing the number of positive (negative) reviews
+as of the last day in the sample by the age of the game on that day.
+Knowing the speed of positive and negative review arrivals, and the
+number of reviews necessary for a transition, I then define the
+proximity to a positive (negative) transition to be the expected number
+of days needed for the game to accumulate the necessary number of
+positive (negative) reviews, assuming that it does not receive any
+negative (positive) reviews during that time.
+
+To illustrate this definition, consider an example game with 19 positive
+reviews and 6 negative reviews at some moment in time. This game has a
+review score of 76\%, and the ``Mostly Positive'' review label. It needs
+5 additional positive reviews to secure a score of 80\%, the threshold
+that would earn it the ``Positive'' label. Similarly, 3 new negative
+reviews would be sufficient for the game to slide into the ``Mixed''
+review category, as the score would become
+\(19/(25 + 3) \times 100\%= 67\%\), which is less than the \(70\%\)
+required for the ``Mostly Positive'' bin. If this game ends up having 80
+positive and 20 negative reviews at the age of 200 days, its last day in
+the sample, then, on average, it was receiving 0.4 positive and 0.1
+negative reviews per day. Thus, for a positive transition it requires
+\(5/0.4 = 12.5\) days of only good reviews arriving at this rate.
+Similarly, for a negative transition it requires \(3 / 0.1 = 30\) days
+of only bad reviews arriving at this rate. So, for this game I set its
+proximity to a potential positive transition to be 12.5 days, and its
+proximity to a potential negative transition to be 30 days.
+
+As the example above shows, it is impossible to consider proximity to a
+positive transition without taking into account the proximity to a
+negative transition, at least for moderately sized games. If firms'
+strategies for these types of transitions are different, then studying
+such transitions separately could attenuate the effect of the proximity
+to, say, a positive transition, on the discount probability: a firm that
+is close to upgrading its review bin might not give a discount not
+because it is a bad way to accomplish that transition, but because that
+firm is at the same time close to downgrading its review bin, and might
+prefer to exercise prudence. For this reason, I define two ``treatment''
+variables of interest. Game \(i\) at date \(t\) is said to be close to a
+positive transition, \(T_{it}^+ = 1\), if its proximity to a positive
+transition is less than or equal to 14 days. Similarly, game \(i\) at
+date \(t\) is said to be close to a negative transition,
+\(T_{it}^- = 1\), if its proximity to a positive transition is less than
+or equal to 14 days. The 14 cutoff is inspired by the maximum duration
+of custom discounts on Steam, and the patterns of discounting around
+successful transitions, depicted in Figure \ref{discountsTransitions}.
+To estimate the effect of being close to a review transition on the
+discounting behavior, I then estimate the following model:
 \begin{equation}\label{potTransitionsReg}
@@
 
-\noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, review bin dummies, and age; $f_i$ is a set of game-level fixed effects, and $\tau_t$ is a set of day of the week effects and sample week time effects.
-These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSales}.
-We expect $\beta^+$ to be positive, but, when it comes to $\beta^-$, any sign could be rationalized.
-A positive sign on  $\beta^-$ would serve as evidence that firms use discounting in order to escape from slumps in their reviews bins, while a negative sign would indicate that, on the contrary, firms on the verge of a bad transition become more prudent with their discounts, trying to not instigate extra purchasing/reviewing activity.
-
-```{r results = 'asis'}
-cat(star_insert_row(star.out,
-                    c("Time Effects: Weekdays, Week &  $\\checkmark$ &  $\\checkmark$ & $\\checkmark$ \\\\",
-                      "Game Effects & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\",
-                      "Poly($t$ W/O Discount, $d=2$) & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\"),
-                    insert.after = c(33,33,33)))
-```
-
-Notice that the inclusion of both the distance to a potential positive, and a potential negative, transition in the regression drops all observations from the lowest ("Negative") and the highest ("Overwhelmingly Positive") review bins, as for games in those bins only one way of review transition is possible.
-However, given that the proportion of such observations in the sample is quite small, this is not a big concern.
-The analysis also excludes the observations with a “No Review Score” label, as I do not want to take a stance on what constitutes an improvement or a deterioration of the review score for such games.
-The results of estimating Equation \ref{potTransitionsReg} are presented in Table \ref{potentialTransitionsResults}.
-The first column is the full specification that uses all observations in the sample (except the omissions just mentioned).
-The second column uses a more stringent definition of proximity to a transition, requiring a game to be `r band`, rather than `r 2*band`, days away from a potential transition to be counted as being “close to a transition”.
-The third column uses only transitions between “Mixed”, “Mostly Positive”, and “Positive” labels, as these are the transitions that rely on the review score only, while “Very Positive” and “Overwhelmingly Positive” require both a certain review score, and a certain number of reviews.\footnote{Technically, a game improving its review score from 79\% to 80\% can transition to both “Positive” and “Very Positive”, so the results in the third column bundle together these types of transitions.}.
-@SorokinStevens20 exclusively uses these simple review bins in their regression discontinuity analysis, precisely in order to avoid the complications that arise from double thresholds required for “Very Positive” and “Overwhelmingly Positive”.
-
-The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion.
-Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg1$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
-The uncertainty about the sign and the significance of the proximity to a potential negative transition is resolved in favor of the prudent approach on the firms' side: the results suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg3$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`-`r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is only present in two out of three specifications.
-
-## Discussion
-
-It is not unreasonable to say that model \ref{potTransitionsReg} is able to identify the causal effect of the proximity to a review transition on discounting behavior.
-As the sample was selected to include only products with the most stable quality and the lowest number of game updates, the path of the review score is relatively exogenous for the firms.
-Taking its current review score as given, a firm can decide whether to run a price promotion or not, which makes the main independent variables in my analysis exogenous.
-On top of that, model \ref{potTransitionsReg} includes a rich set of controls and fixed effects.
-Some threats to identification still remain, of course.
-One is unobserved marketing interventions preceding discounts.
-If advertisements improves the review score, then, by definition, advertisement would be correlated with the treatment variable, moving games a bit closer to transitions.
-If a discount then follows, as a part of the general marketing plan, rather than to leverage the new proximity to a transition, the positive association between discounting and positive transitions would be spurious.
-Note, however, that it would be more natural to expect firms to roll out all marketing interventions at the same time (i.e., running a price promotion while the game is advertised).
-In that case, the threat to identification vanishes.
-
-I would now like to step back and look at the story behind the behavior that I am documenting.
-Several gaps are not filled yet.
-First, I have not presented evidence that discounting meaningfully increases sales and leads to more reviews.
-Neither have I presented evidence that better review bins increase sales.
-Perhaps, more importantly, I have not discussed why firms should expect customers buying during a discount to leave better reviews than customers paying the regular price.
-If there is no difference between the two groups, then giving a discount when the game is close to a transition is, at best, a gamble.
-In fact, there is some empirical evidence that customers who choose to go to a restaurant because of a promotion tend to leave worse reviews [@ByersEtAl12; @Li16], even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19].
-Theoretically, this effect is ambiguous.
-Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews.
-At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews.
-See, for example, @AcemogluEtAl19.
-
-The results I presented in this section, therefore, lead to the following hypotheses.
-I show that firms give discounts to avoid bad transitions and to facilitate the good ones; thus, it has to be the case that the reviews left on a discount tend to be more positive than the ones left off a discount.
-Second, if that is indeed the case, then the firms that get especially positive reviews during price promotions should be more likely to try to use discounting to manipulate their reviews.
-Heterogeneity between the firms is crucial for the second hypothesis.
-In order to test these hypotheses, and to provide evidence on the effect of discounting on sales and reviewing activity, as well as the effect of reviews on sales, I now turn to formulation and estimation of a structural model demand, reviewing and gaming activity on Steam.
-
-# Empirical Model
-
-## Setup
-
-Consider game \(i\) that is observed on a daily basis. On day \(t\)
-the game sells one copy to each of the \(B_{it}\) short-lived buyers that arrive on
-that day, a number that is unobserved by the econometrician. Define
-*active players* of this game, \(A_{it}\), to be the customers who have
-already purchased the game and are still playing it, either because they have
-not yet completed it or are not bored with it yet. This number  has an empirical counterpart in
-the face of the player count variable, observable to the econometrician. The game loses \(E_{it}\) players on day \(t\), which is also not observed.
-I assume that, once a player stops playing the game, she never returns to it again. It is easy to see then that \(A_{it}\) follows the following process:
-\begin{equation}\label{activeProccess}
+\noindent \(disc_{it} = \mathds{1}\{Discount_{it} > 0\}\) is a dummy
+measuring if the game is on a discount or not, \(X_{it}\) is a set of
+control variables that includes log proximities to positive and negative
+transitions, log review count, review bin dummies, and age; \(f_i\) is a
+set of game-level fixed effects, and \(\tau_t\) is a set of day of the
+week effects and sample week time effects. These time effects are
+especially important to include in the regressions with discounting
+variables on the left hand side, because Steam's curated discounts all
+start on predetermined days of the week, and seasonal sales affect a big
+number of games at the same time, as depicted in Figure
+\ref{seasonalSales}. We expect \(\beta^+\) to be positive, but, when it
+comes to \(\beta^-\), any sign could be rationalized. A positive sign on
+\(\beta^-\) would serve as evidence that firms use discounting in order
+to escape from slumps in their reviews bins, while a negative sign would
+indicate that, on the contrary, firms on the verge of a bad transition
+become more prudent with their discounts, trying to not instigate extra
+purchasing/reviewing activity.
+
+\begin{table}[hp] \centering    \caption{Discounts Close to Potential Transitions}    \label{potentialTransitionsResults}  \begin{tabular}{@{\extracolsep{5pt}}lccc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{3}{c}{\textit{Dependent variable:}} \\  \cline{2-4}  \\[-1.8ex] & \multicolumn{3}{c}{Discount Probability} \\   & Full & 1 W.
+to Tr.
+& Simple Tr.
+\\  \hline \\[-1.8ex]   Close to Pos.
+Transition & 0.010$^{***}$ & 0.009$^{***}$ & 0.007$^{***}$ \\    & (0.002) & (0.002) & (0.003) \\    Close to Neg.
+Transition & $-$0.008$^{***}$ & $-$0.002 & $-$0.007$^{***}$ \\    & (0.002) & (0.002) & (0.003) \\    Log Days to Pos.
+Tr.
+& 0.005$^{***}$ & 0.004$^{***}$ & 0.007$^{***}$ \\    & (0.001) & (0.001) & (0.001) \\    Log Days to Neg Tr.
+& $-$0.003$^{***}$ & $-$0.002$^{***}$ & $-$0.001 \\    & (0.001) & (0.001) & (0.001) \\    Log Reviews & $-$0.003$^{***}$ & $-$0.002$^{***}$ & $-$0.003$^{***}$ \\    & (0.001) & (0.001) & (0.001) \\    Mostly Positive & $-$0.008$^{***}$ & $-$0.009$^{***}$ & $-$0.007$^{***}$ \\    & (0.002) & (0.002) & (0.002) \\    Positive & $-$0.012$^{***}$ & $-$0.013$^{***}$ &  \\    & (0.002) & (0.002) &  \\    Very Positive & $-$0.008$^{***}$ & $-$0.007$^{***}$ &  \\    & (0.002) & (0.002) &  \\    Age & 0.0001$^{***}$ & 0.0001$^{***}$ & 0.0001$^{***}$ \\    & (0.00000) & (0.00000) & (0.00001) \\    Age $\le 14$ & 0.050$^{***}$ & 0.049$^{***}$ & 0.018$^{*}$ \\    & (0.005) & (0.005) & (0.009) \\   \hline \\[-1.8ex]  Time Effects: Weekdays, Week &  $\checkmark$ &  $\checkmark$ & $\checkmark$ \\ Game Effects & $\checkmark$ & $\checkmark$ & $\checkmark$ \\ Poly($t$ W/O Discount, $d=2$) & $\checkmark$ & $\checkmark$ & $\checkmark$ \\ Observations & 295,228 & 295,228 & 113,901 \\  R$^{2}$ & 0.172 & 0.172 & 0.173 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  \end{table}
+
+Notice that the inclusion of both the distance to a potential positive,
+and a potential negative, transition in the regression drops all
+observations from the lowest (``Negative'') and the highest
+(``Overwhelmingly Positive'') review bins, as for games in those bins
+only one way of review transition is possible. However, given that the
+proportion of such observations in the sample is quite small, this is
+not a big concern. The analysis also excludes the observations with a
+``No Review Score'' label, as I do not want to take a stance on what
+constitutes an improvement or a deterioration of the review score for
+such games. The results of estimating Equation \ref{potTransitionsReg}
+are presented in Table \ref{potentialTransitionsResults}. The first
+column is the full specification that uses all observations in the
+sample (except the omissions just mentioned). The second column uses a
+more stringent definition of proximity to a transition, requiring a game
+to be 7, rather than 14, days away from a potential transition to be
+counted as being ``close to a transition''. The third column uses only
+transitions between ``Mixed'', ``Mostly Positive'', and ``Positive''
+labels, as these are the transitions that rely on the review score only,
+while ``Very Positive'' and ``Overwhelmingly Positive'' require both a
+certain review score, and a certain number of
+reviews.\footnote{Technically, a game improving its review score from 79\% to 80\% can transition to both “Positive” and “Very Positive”, so the results in the third column bundle together these types of transitions.}.
+\citet{SorokinStevens20} exclusively uses these simple review bins in
+their regression discontinuity analysis, precisely in order to avoid the
+complications that arise from double thresholds required for ``Very
+Positive'' and ``Overwhelmingly Positive''.
+
+The results in Table \ref{potentialTransitionsResults} unequivocally
+support the hypothesis that proximity to a review bin upgrade increases
+firms' willingness to run a price promotion. Measured against the 16\%
+probability for a random game-day pair from the sample to have a
+discount\footnote{The corresponding number for the games in the treatment group is 17.},
+the effects constitute a 4-6\% increase in the daily probability of a
+discount. The uncertainty about the sign and the significance of the
+proximity to a potential negative transition is resolved in favor of the
+prudent approach on the firms' side: the results suggest that firms
+under a risk of deteriorating their review label are 4-5\% less likely
+to go on a discount, albeit the effect is only present in two out of
+three specifications.
+
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
+
+It is not unreasonable to say that model \ref{potTransitionsReg} is able
+to identify the causal effect of the proximity to a review transition on
+discounting behavior. As the sample was selected to include only
+products with the most stable quality and the lowest number of game
+updates, the path of the review score is relatively exogenous for the
+firms. Taking its current review score as given, a firm can decide
+whether to run a price promotion or not, which makes the main
+independent variables in my analysis exogenous. On top of that, model
+\ref{potTransitionsReg} includes a rich set of controls and fixed
+effects. Some threats to identification still remain, of course. One is
+unobserved marketing interventions preceding discounts. If
+advertisements improves the review score, then, by definition,
+advertisement would be correlated with the treatment variable, moving
+games a bit closer to transitions. If a discount then follows, as a part
+of the general marketing plan, rather than to leverage the new proximity
+to a transition, the positive association between discounting and
+positive transitions would be spurious. Note, however, that it would be
+more natural to expect firms to roll out all marketing interventions at
+the same time (i.e., running a price promotion while the game is
+advertised). In that case, the threat to identification vanishes.
+
+I would now like to step back and look at the story behind the behavior
+that I am documenting. Several gaps are not filled yet. First, I have
+not presented evidence that discounting meaningfully increases sales and
+leads to more reviews. Neither have I presented evidence that better
+review bins increase sales. Perhaps, more importantly, I have not
+discussed why firms should expect customers buying during a discount to
+leave better reviews than customers paying the regular price. If there
+is no difference between the two groups, then giving a discount when the
+game is close to a transition is, at best, a gamble. In fact, there is
+some empirical evidence that customers who choose to go to a restaurant
+because of a promotion tend to leave worse reviews
+\citep{ByersEtAl12, Li16}, even though the effect could be positive in
+certain cases \citep{Li16, ZhuEtAl19}. Theoretically, this effect is
+ambiguous. Consumers who buy when the price is low could be a worse
+match for the product and, thus, leave worse reviews. At the same time,
+such customers get a higher utility from paying less, which, together
+with a desire to reciprocate, can lead them to leave better reviews.
+See, for example, \citet{AcemogluEtAl19}.
+
+The results I presented in this section, therefore, lead to the
+following hypotheses. I show that firms give discounts to avoid bad
+transitions and to facilitate the good ones; thus, it has to be the case
+that the reviews left on a discount tend to be more positive than the
+ones left off a discount. Second, if that is indeed the case, then the
+firms that get especially positive reviews during price promotions
+should be more likely to try to use discounting to manipulate their
+reviews. Heterogeneity between the firms is crucial for the second
+hypothesis. In order to test these hypotheses, and to provide evidence
+on the effect of discounting on sales and reviewing activity, as well as
+the effect of reviews on sales, I now turn to formulation and estimation
+of a structural model demand, reviewing and gaming activity on Steam.
+
+\hypertarget{empirical-model}{%
+\section{Empirical Model}\label{empirical-model}}
+
+\hypertarget{setup}{%
+\subsection{Setup}\label{setup}}
+
+Consider game \(i\) that is observed on a daily basis. On day \(t\) the
+game sells one copy to each of the \(B_{it}\) short-lived buyers that
+arrive on that day, a number that is unobserved by the econometrician.
+Define \emph{active players} of this game, \(A_{it}\), to be the
+customers who have already purchased the game and are still playing it,
+either because they have not yet completed it or are not bored with it
+yet. This number has an empirical counterpart in the face of the player
+count variable, observable to the econometrician. The game loses
+\(E_{it}\) players on day \(t\), which is also not observed. I assume
+that, once a player stops playing the game, she never returns to it
+again. It is easy to see then that \(A_{it}\) follows the following
+process: \begin{equation}\label{activeProccess}
   A_{it} = A_{it-1} + B_{it} - E_{it}
@@
 
-Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about
-them in order to make progress.
+Both the arrival of buyers and the exit of players are not observed, so
+some assumptions need to be made about them in order to make progress.
 
@@
 of observable characteristics \(x_{it}\) of the game that affect demand:
-price, reviews, age of the game, or seasonal factors.
-The mapping between these variables and the number of copies sold is, of course, nothing else but the demand curve for game $i$.
-A change of $0.01$ in the index $x_{it}'\beta$ means that quantity demanded of game $i$ goes up by one percent.
-This multiplicative structure is necessary, because it will allow me to estimate the price sensitivity and the effect of reviews on sales in relative terms\footnote{See the Identification section for more details}.
-Buyers of the game become active players, and are subject to a fixed daily risk of $1-\psi_i$ of abandoning the game.
-Given that the number of active players “flipping” this coin at the end of day $t-1$ is $A_{it-1}$, this process gives rise to the binomial distribution for the number of exiters.
-
-Every buyer of game $i$ is a potential reviewer.
-I assume that a buyer who buys the game at $t-k$ leaves a positive (negative) review for the game on day $t$ with probability \(r_{it}^+\)	 (\(r_{it}^-\)), and no review otherwise.
-For the reasons I will explain later, I will refer to  $r_{it}^+$ as the *like rate*, and to $r_{it}^-$ as the *dislike rate*.
-The focus of the analysis is on the difference between the reviews left on and off a discount.
-To that end, I parametrize the like and dislike rates to depend on the discounting behavior of the firm as follows.
+price, reviews, age of the game, or seasonal factors. The mapping
+between these variables and the number of copies sold is, of course,
+nothing else but the demand curve for game \(i\). A change of \(0.01\)
+in the index \(x_{it}'\beta\) means that quantity demanded of game \(i\)
+goes up by one percent. This multiplicative structure is necessary,
+because it will allow me to estimate the price sensitivity and the
+effect of reviews on sales in relative
+terms\footnote{See the Identification section for more details}. Buyers
+of the game become active players, and are subject to a fixed daily risk
+of \(1-\psi_i\) of abandoning the game. Given that the number of active
+players ``flipping'' this coin at the end of day \(t-1\) is
+\(A_{it-1}\), this process gives rise to the binomial distribution for
+the number of exiters.
+
+Every buyer of game \(i\) is a potential reviewer. I assume that a buyer
+who buys the game at \(t-k\) leaves a positive (negative) review for the
+game on day \(t\) with probability \(r_{it}^+\) (\(r_{it}^-\)), and no
+review otherwise. For the reasons I will explain later, I will refer to
+\(r_{it}^+\) as the \emph{like rate}, and to \(r_{it}^-\) as the
+\emph{dislike rate}. The focus of the analysis is on the difference
+between the reviews left on and off a discount. To that end, I
+parametrize the like and dislike rates to depend on the discounting
+behavior of the firm as follows.
 
@@
 
-\noindent Notice, that a price change affects the reviewing behavior in two ways.
-First, a lower prices increases the inflow of buyers through a higher $\lambda_{it}$.
-This leads to more reviews being left.
-My parametrization allows to further study if the reviewers who bought the game on a discount are more or less likely to leave positive and negative reviews.
-I use a dummy variable $disc_{it-k}$ to measure discounting because this will allow me to derive a closed-form estimator for the  parameters of interest.
-
-## Identification
-
-### Demand Parameters
-The prediction of \(A_{it}\) that follows from (\ref{activeProccess}) takes the form of
-\begin{equation}
+\noindent Notice, that a price change affects the reviewing behavior in
+two ways. First, a lower prices increases the inflow of buyers through a
+higher \(\lambda_{it}\). This leads to more reviews being left. My
+parametrization allows to further study if the reviewers who bought the
+game on a discount are more or less likely to leave positive and
+negative reviews. I use a dummy variable \(disc_{it-k}\) to measure
+discounting because this will allow me to derive a closed-form estimator
+for the parameters of interest.
+
+\hypertarget{identification}{%
+\subsection{Identification}\label{identification}}
+
+\hypertarget{demand-parameters}{%
+\subsubsection{Demand Parameters}\label{demand-parameters}}
+
+The prediction of \(A_{it}\) that follows from (\ref{activeProccess})
+takes the form of \begin{equation}
 \mathbb{E}\left[A_{it}\,|\,A_{it-1}, x_{it} \right] = A_{it-1} + \lambda_i(1+x'_{it}\beta) - (1-\psi_i)A_{it-1} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta),
@@
  A_{it} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
-\end{equation}
-with
+\end{equation} with
 \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\). This model is
@@
 the model multiplying \(\beta\), the parameters common to all games. If
-not for this commonality in $\beta$, estimation of (\ref{arrivalReg}) would be
-straightforwardly achieved by opening the parentheses and estimating
-\begin{equation}\label{arrivalRegInd}
+not for this commonality in \(\beta\), estimation of (\ref{arrivalReg})
+would be straightforwardly achieved by opening the parentheses and
+estimating \begin{equation}\label{arrivalRegInd}
 A_{it} = \lambda_i + \psi_i A_{it-1} + x'_{it}\beta_i + u_{it}
-\end{equation}
-using OLS on a game-by-game basis. This commonality is
-essential, however, because one game in the sample typically does not exhibit enough variation in review labels to be able to identify the effect of upgrading the review tier on sales.
-
-The fact that $x'_{it}\beta$ multiplies the game fixed effect $\lambda_i$ allows me to estimate the dependence of quantity sold on price and reviews in relative terms, i.e., to obtain the elasticities.
-Normally, a log transformation is used to achieve that.
-Indeed, @SorokinStevens20 is able to estimate these elasticities with a within-estimator, using the following model
+\end{equation} using OLS on a game-by-game basis. This commonality is
+essential, however, because one game in the sample typically does not
+exhibit enough variation in review labels to be able to identify the
+effect of upgrading the review tier on sales.
+
+The fact that \(x'_{it}\beta\) multiplies the game fixed effect
+\(\lambda_i\) allows me to estimate the dependence of quantity sold on
+price and reviews in relative terms, i.e., to obtain the elasticities.
+Normally, a log transformation is used to achieve that. Indeed,
+\citet{SorokinStevens20} is able to estimate these elasticities with a
+within-estimator, using the following model
 \begin{equation}\label{logReg}
 \log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}.
-\end{equation}
-This specification “controls” for the (log) number of continuing players in order to overcome the non-availability of direct sales data; however, it is the numbers of active players and buyers that are additive, not their logs.
-Thus, the structural model I formulate confronts the estimation problem in a more “heads-up” way, and in that regard offers an improvement over @SorokinStevens20.
-I will contrast the results obtained by the two approaches in the results section, comparing a more detailed structural approach with a less precise, but a more easily implementable, log regression approach.
-
-Another important reason for insisting on estimating the relative effects stems from the limitations of my data.
-Recall that the player count variable measures only the *maximum concurrent* number of active players every day.
-This implies that the estimated values of $\lambda_{it}$ would take into account only those new buyers who contribute to gaming activity during the “rush hour”.
-An implicit assumption in my analysis is that new buyers of the game all choose their gaming time following the same game-specific distribution.
-I use this assumption to say that, if the number of new active players during rush hour goes up by 1%, then sales go up by 1% across all types of players,  not only among the "rush hour ones".
-
-Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model \ref{arrivalReg}, and guarantees identification of all parameters, as long as there is sufficient variation in the data.
-Of course, this is only true as long as equation \ref{arrivalReg} is the right model of the data generating process.
-A threat to identification would come from unobserved demand shifters $\tilde x_{it}$ that are correlated with the observed factors $x_{it}$ (omitted variable bias).
-For instance, an advertising intervention that is coupled with a price promotion would increase demand, but the entire effect would be attributed to the observed change in price.
-My approach is vulnerable to such events, as long as one is interested in getting the causal estimate of the discount elasticity of demand.
-
-However, I argue that (\ref{arrivalReg}) is an adequate specification, if the goal is to estimate the causal effect of reviews on sales, or to get a predictive model of demand.
-First and foremost, the reviews are not a choice variable of a firm, and rather serve as a state variable that a firm takes as given every day.
-Of course, there are various things that a firm can do, that can, in a non-guaranteed fashion, affect this variable.
-But, as long as the major tools that a firm has access to are controlled for in the regression, the exogenous variation in the review variables is sufficient to identify the causal effect of reviews on sales.
-
-One important way in which I control for various tools that firms have at their disposal is through sample selection.
-Sample selection rules out the possibility of an omitted variable bias stemming from a number of variables that could collectively be referred to as “changing quality”.
-The games in the sample are single player games, and thus are not subject to time-varying network externalities or frequent quality updates, that could be correlated with reviews, depths of discounts, and the player count.
-Second, game specific effect $\lambda_i$ controls for all time-invariant characteristics of game $i$ that determine average sales: initial marketing budget, extraneous popularity of the game's plot or setting, etc.
-Similarly, time effects control for important within-week seasonality in gaming patterns and for the extensive platform-wide sales.
-Third, note that Equation (\ref{arrivalReg}) allows each game to have its own continuation probability $\psi_i$, which could prove crucial in eliciting sales from the player count data.
-Two games could have the same observed median daily player count---say, ten people---but very different sales levels, if game one offers a lot of replayability and is played by the same ten people over and over again, and game two is played by new ten people every day.
-Intuitively, $\psi_i$ is identified by the rate of decay of the player count when it is far from its (slowly-changing) trend or average.
-Game release and discounts offer such events, when the player count spikes briefly due to all the new players who just bought the game; see example game in Figure \ref{exampleGame}.
-
-### Price Elasticity of Demand
-To close off the discussion of identification of the demand parameters in Equation (\ref{arrivalReg}), I would like to elaborate on the identification of the price elasticity parameter.
-As I mentioned before, at the very least, including the price in the regression controls for unobserved marketing interventions that are coupled with discounts.
-Estimating the true price elasticity of demand is not important for the questions addressed in this paper, as I am not trying to prescribe the sizes of the discounts that firms should be giving to have a meaningful chance of affecting their review labels when they are close to a review transition.
-Arguably, a 100% discount is a powerful enough option to make this strategy viable, at least in principle.
-However, should the price coefficient be of primary interest, I would like to list some further factors that have an impact on the identification of thereof.
-
-First, I believe that standard concerns about the endogeneity of prices are not directly applicable in my context.
-The reason is the high frequency nature of the data and the stickiness of posted prices.
-Using the classic notation, imagine that a discount is given on date $t$, and we observe a quantity-price pair $(Q_t, P_t)$, both of which are different from their yesterday's counterparts $(Q_{t-1}, P_{t-1})$.
-The standard endogeneity concern is that firm's demand is subject to shocks, and that the firm would change its price precisely when those shocks occur.
-The two points then, roughly speaking, would belong to different demand curves, and one can not identify the slope of the demand curve\footnote{Assuming, as is usually done, that demand shifters lead to parallel shifts in demand}.
-In my setting, however, this would require the firms to systematically give discounts *exactly on the days* of the demand shocks, which requires possessing a level of insight into one's demand condition that is unrealistic, especially for small independent studios.
-While a discount for a racing game on the day of a major F-1 race is not implausible, should the demand for the game go up with a lag of as little as one day, then both $(Q_t, P_t)$ and $(Q_{t-1}, P_{t-1})$ would belong to the same demand curve, and, therefore, identification would not be threatened.
-
-My second point is that, even though unobserved marketing interventions that are coupled with price promotions, would,  undoubtedly, be an issue, this problem could be addressed with some extra data collection.
-One way to proceed would be to study if such coupled promotions in fact do take place.
-In particular, one could collect data on YouTube queries mentioning the games in the sample, and use spikes in such queries as a proxy for unobserved marketing campaigns.
-
-A deeper problem for identifying the price elasticity of demand lies in defining precisely the elasticity of interest.
-A video game is a durable good, and some consumers could be purchasing it strategically, thinking about the probability and depth of discounts that they could get in the near future.
-A discount that is announced a week in advance will appear to have a strong effect on sales, but only because consumers would abstain from purchasing the game throughout that week.
-For studying counterfactual price policies one would need to specify a more complicated model of forward-looking consumers, and estimate the fundamentals of their behavior.
-A related problem is the importance of salience in a marketplace that has many thousands of products.
-Any price elasticity estimated relies on Steam keeping its algorithms unchanged.
-A game can give a 99% discount, but the quantity demanded will not change much if that promotion happens to not be reflected in Steam's system.
-This has implications, for instance, for picking good instruments for prices.
-Curated discounts created and managed by Steam are suggested to firms, and not chosen by them.
-In principle, such price changes could be exogenous to daily demand conditions.
-However, they could hardly be used as instruments for the price, because they also bring an immense boost in visibility, by the virtue of occupying the prime store main page space.
-
-### Review Parameters
-
-The part of the model describing the reviewing behavior of the buyers is more starightforward.
-Intuitively, the propensity to leave a review on and off a discount (the like and dislike rates $r_{it}^+$, $r_{it}^-$) are identified by the differences in reviews left on and off a discount.
-In fact, this intuition becomes a rigorous proof, as wil be shown shortly.
-
-Following assumption \ref{arrivalAssumptions}, the arrival of buyers for game $i$ on day $t$ follows a Poisson distribution with arrival rate $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$.
-I also assumed that, $k$ days later, each consumer leaves a  positive review with probability $r_{it}^+$, a negative review with probability $r_{it}^-$, and no review otherwise.
-Then, the following proposition is true:
+\end{equation} This specification ``controls'' for the (log) number of
+continuing players in order to overcome the non-availability of direct
+sales data; however, it is the numbers of active players and buyers that
+are additive, not their logs. Thus, the structural model I formulate
+confronts the estimation problem in a more ``heads-up'' way, and in that
+regard offers an improvement over \citet{SorokinStevens20}. I will
+contrast the results obtained by the two approaches in the results
+section, comparing a more detailed structural approach with a less
+precise, but a more easily implementable, log regression approach.
+
+Another important reason for insisting on estimating the relative
+effects stems from the limitations of my data. Recall that the player
+count variable measures only the \emph{maximum concurrent} number of
+active players every day. This implies that the estimated values of
+\(\lambda_{it}\) would take into account only those new buyers who
+contribute to gaming activity during the ``rush hour''. An implicit
+assumption in my analysis is that new buyers of the game all choose
+their gaming time following the same game-specific distribution. I use
+this assumption to say that, if the number of new active players during
+rush hour goes up by 1\%, then sales go up by 1\% across all types of
+players, not only among the ``rush hour ones''.
+
+Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\)
+holds by definition for Model \ref{arrivalReg}, and guarantees
+identification of all parameters, as long as there is sufficient
+variation in the data. Of course, this is only true as long as equation
+\ref{arrivalReg} is the right model of the data generating process. A
+threat to identification would come from unobserved demand shifters
+\(\tilde x_{it}\) that are correlated with the observed factors
+\(x_{it}\) (omitted variable bias). For instance, an advertising
+intervention that is coupled with a price promotion would increase
+demand, but the entire effect would be attributed to the observed change
+in price. My approach is vulnerable to such events, as long as one is
+interested in getting the causal estimate of the discount elasticity of
+demand.
+
+However, I argue that (\ref{arrivalReg}) is an adequate specification,
+if the goal is to estimate the causal effect of reviews on sales, or to
+get a predictive model of demand. First and foremost, the reviews are
+not a choice variable of a firm, and rather serve as a state variable
+that a firm takes as given every day. Of course, there are various
+things that a firm can do, that can, in a non-guaranteed fashion, affect
+this variable. But, as long as the major tools that a firm has access to
+are controlled for in the regression, the exogenous variation in the
+review variables is sufficient to identify the causal effect of reviews
+on sales.
+
+One important way in which I control for various tools that firms have
+at their disposal is through sample selection. Sample selection rules
+out the possibility of an omitted variable bias stemming from a number
+of variables that could collectively be referred to as ``changing
+quality''. The games in the sample are single player games, and thus are
+not subject to time-varying network externalities or frequent quality
+updates, that could be correlated with reviews, depths of discounts, and
+the player count. Second, game specific effect \(\lambda_i\) controls
+for all time-invariant characteristics of game \(i\) that determine
+average sales: initial marketing budget, extraneous popularity of the
+game's plot or setting, etc. Similarly, time effects control for
+important within-week seasonality in gaming patterns and for the
+extensive platform-wide sales. Third, note that Equation
+(\ref{arrivalReg}) allows each game to have its own continuation
+probability \(\psi_i\), which could prove crucial in eliciting sales
+from the player count data. Two games could have the same observed
+median daily player count---say, ten people---but very different sales
+levels, if game one offers a lot of replayability and is played by the
+same ten people over and over again, and game two is played by new ten
+people every day. Intuitively, \(\psi_i\) is identified by the rate of
+decay of the player count when it is far from its (slowly-changing)
+trend or average. Game release and discounts offer such events, when the
+player count spikes briefly due to all the new players who just bought
+the game; see example game in Figure \ref{exampleGame}.
+
+\hypertarget{price-elasticity-of-demand}{%
+\subsubsection{Price Elasticity of
+Demand}\label{price-elasticity-of-demand}}
+
+To close off the discussion of identification of the demand parameters
+in Equation (\ref{arrivalReg}), I would like to elaborate on the
+identification of the price elasticity parameter. As I mentioned before,
+at the very least, including the price in the regression controls for
+unobserved marketing interventions that are coupled with discounts.
+Estimating the true price elasticity of demand is not important for the
+questions addressed in this paper, as I am not trying to prescribe the
+sizes of the discounts that firms should be giving to have a meaningful
+chance of affecting their review labels when they are close to a review
+transition. Arguably, a 100\% discount is a powerful enough option to
+make this strategy viable, at least in principle. However, should the
+price coefficient be of primary interest, I would like to list some
+further factors that have an impact on the identification of thereof.
+
+First, I believe that standard concerns about the endogeneity of prices
+are not directly applicable in my context. The reason is the high
+frequency nature of the data and the stickiness of posted prices. Using
+the classic notation, imagine that a discount is given on date \(t\),
+and we observe a quantity-price pair \((Q_t, P_t)\), both of which are
+different from their yesterday's counterparts \((Q_{t-1}, P_{t-1})\).
+The standard endogeneity concern is that firm's demand is subject to
+shocks, and that the firm would change its price precisely when those
+shocks occur. The two points then, roughly speaking, would belong to
+different demand curves, and one can not identify the slope of the
+demand
+curve\footnote{Assuming, as is usually done, that demand shifters lead to parallel shifts in demand}.
+In my setting, however, this would require the firms to systematically
+give discounts \emph{exactly on the days} of the demand shocks, which
+requires possessing a level of insight into one's demand condition that
+is unrealistic, especially for small independent studios. While a
+discount for a racing game on the day of a major F-1 race is not
+implausible, should the demand for the game go up with a lag of as
+little as one day, then both \((Q_t, P_t)\) and \((Q_{t-1}, P_{t-1})\)
+would belong to the same demand curve, and, therefore, identification
+would not be threatened.
+
+My second point is that, even though unobserved marketing interventions
+that are coupled with price promotions, would, undoubtedly, be an issue,
+this problem could be addressed with some extra data collection. One way
+to proceed would be to study if such coupled promotions in fact do take
+place. In particular, one could collect data on YouTube queries
+mentioning the games in the sample, and use spikes in such queries as a
+proxy for unobserved marketing campaigns.
+
+A deeper problem for identifying the price elasticity of demand lies in
+defining precisely the elasticity of interest. A video game is a durable
+good, and some consumers could be purchasing it strategically, thinking
+about the probability and depth of discounts that they could get in the
+near future. A discount that is announced a week in advance will appear
+to have a strong effect on sales, but only because consumers would
+abstain from purchasing the game throughout that week. For studying
+counterfactual price policies one would need to specify a more
+complicated model of forward-looking consumers, and estimate the
+fundamentals of their behavior. A related problem is the importance of
+salience in a marketplace that has many thousands of products. Any price
+elasticity estimated relies on Steam keeping its algorithms unchanged. A
+game can give a 99\% discount, but the quantity demanded will not change
+much if that promotion happens to not be reflected in Steam's system.
+This has implications, for instance, for picking good instruments for
+prices. Curated discounts created and managed by Steam are suggested to
+firms, and not chosen by them. In principle, such price changes could be
+exogenous to daily demand conditions. However, they could hardly be used
+as instruments for the price, because they also bring an immense boost
+in visibility, by the virtue of occupying the prime store main page
+space.
+
+\hypertarget{review-parameters}{%
+\subsubsection{Review Parameters}\label{review-parameters}}
+
+The part of the model describing the reviewing behavior of the buyers is
+more starightforward. Intuitively, the propensity to leave a review on
+and off a discount (the like and dislike rates \(r_{it}^+\),
+\(r_{it}^-\)) are identified by the differences in reviews left on and
+off a discount. In fact, this intuition becomes a rigorous proof, as wil
+be shown shortly.
+
+Following assumption \ref{arrivalAssumptions}, the arrival of buyers for
+game \(i\) on day \(t\) follows a Poisson distribution with arrival rate
+\(\lambda_{it} = \lambda_i (1 + x_{it}'\beta)\). I also assumed that,
+\(k\) days later, each consumer leaves a positive review with
+probability \(r_{it}^+\), a negative review with probability
+\(r_{it}^-\), and no review otherwise. Then, the following proposition
+is true:
+
 \begin{proposition}\label{poissonReviews}
@@
 
-Proposition \ref{poissonReviews} allows one to easily write down the likelihood for positive and negative reviews separately.
-I will use the positive reviews as the leading example here, but all the findings automatically translate to the negative reviews case as well.
-For every game I observe the history of the review arrivals $\{(g_{it}, b_{it})\}_{t=1}^{T_i}$.
-Since $\PP{G_{it} = g_{it}} = \frac{ (r_{it}^+\lambda_{it-k} )^{g_{it}} }{g_{it}!} e^{ -r_{it-k}^+\lambda_{it-k} }$, the log-likelihood of the history of likes is given by
+Proposition \ref{poissonReviews} allows one to easily write down the
+likelihood for positive and negative reviews separately. I will use the
+positive reviews as the leading example here, but all the findings
+automatically translate to the negative reviews case as well. For every
+game I observe the history of the review arrivals
+\(\{(g_{it}, b_{it})\}_{t=1}^{T_i}\). Since
+\(\PP{G_{it} = g_{it}} = \frac{ (r_{it}^+\lambda_{it-k} )^{g_{it}} }{g_{it}!} e^{ -r_{it-k}^+\lambda_{it-k} }\),
+the log-likelihood of the history of likes is given by
 \begin{equation}\label{reviewsLikelihood}
@@
 
-I treat $\lambda_{it}$ as known, because parameters $\lambda_{i}$ and $\beta$ that determine it can be estimated consistently for the majority of games in the sample, given the long time dimension of the panel.
-For now I also take the lag $k$ between the time when the user buys the game and leaves a review for the game to be known.
-The parameters of interest are $(\rho_{0i}^+, \rho_{1i}^+)$, which parametrize the like rate as $r_{it}^+ = \rho_{0i}^+ + \rho_{1i}^+ disc_{it-k}$.
-The likelihood is concave in the parameters, so the parameters are identified as the maximizer of the likelihood.
-Restricting attention to a binary discount variable $disc_{it}$ allows me to derive a closed-form estimator for $(\rho_{0i}^+, \rho_{1i}^+)$.
-During a discount the like rate of game $i$ is $\rho_{0i}^+ + \rho_{1i}^+$, which is consistently estimated as
-\begin{equation}\label{rhohat1}
+I treat \(\lambda_{it}\) as known, because parameters \(\lambda_{i}\)
+and \(\beta\) that determine it can be estimated consistently for the
+majority of games in the sample, given the long time dimension of the
+panel. For now I also take the lag \(k\) between the time when the user
+buys the game and leaves a review for the game to be known. The
+parameters of interest are \((\rho_{0i}^+, \rho_{1i}^+)\), which
+parametrize the like rate as
+\(r_{it}^+ = \rho_{0i}^+ + \rho_{1i}^+ disc_{it-k}\). The likelihood is
+concave in the parameters, so the parameters are identified as the
+maximizer of the likelihood. Restricting attention to a binary discount
+variable \(disc_{it}\) allows me to derive a closed-form estimator for
+\((\rho_{0i}^+, \rho_{1i}^+)\). During a discount the like rate of game
+\(i\) is \(\rho_{0i}^+ + \rho_{1i}^+\), which is consistently estimated
+as \begin{equation}\label{rhohat1}
 \hat \rho_{0i}^+ + \hat\rho_{1i}^+ = \frac{\sum_{t \ge k} disc_{it-k}g_{it}}{\sum_{t\ge k} disc_{it-k}\lambda_{it-k}},
-\end{equation}
-As we can see, the ML-estimator of the like rate during a price promotion is just the ratio of the number of good reviews left on a discount over the expected arrival on that day.
-Similarly, the like rate off a discount can be estimated by
-\begin{equation}\label{rhohat2}
+\end{equation} As we can see, the ML-estimator of the like rate during a
+price promotion is just the ratio of the number of good reviews left on
+a discount over the expected arrival on that day. Similarly, the like
+rate off a discount can be estimated by \begin{equation}\label{rhohat2}
 \hat \rho_{0i}^+ = \frac{\sum_{t\ge k} (1-disc_{it-k})g_{it}}{\sum_{t\ge k} (1-disc_{it-k})\lambda_{it-k}},
-\end{equation}
-with the interpretation that the like rate in the absence of a discount is just a ratio of the reviews left outside of a discount and the expected number of customers outside a discount.
-
-Note that one can use these estimators to estimate the *average review score* on and off a discount, i.e., whether users are relatively more or less likely to leave a good review during a discount.
-For example, without a price promotion, one obtains
+\end{equation} with the interpretation that the like rate in the absence
+of a discount is just a ratio of the reviews left outside of a discount
+and the expected number of customers outside a discount.
+
+Note that one can use these estimators to estimate the \emph{average
+review score} on and off a discount, i.e., whether users are relatively
+more or less likely to leave a good review during a discount. For
+example, without a price promotion, one obtains
 \begin{equation}\label{avReviewScore}
@@
 \frac{\hat \rho_{0i}^+}{\hat \rho_{0i}^+  + \hat \rho_{0i}^- }
-\end{equation}
-It is intuitively clear that the relative propensity to leave a good, rather than a bad, review should be easily estimable by comparing the ratios of good to bad reviews, without any knowledge of the quantity of games sold.
-This intuition is fully reflected in Equation (\ref{avReviewScore}), where the arrival rates $\lambda_{it-k}$ have disappeared entirely.
-
-The analysis above is complicated by two facts.
-First, for each game I observe the exact review count, but my demand estimates only apply to rush hours.
-If, say, every player leaves a review, and every day there are two new players who play in the morning, and three new players who play in the evening, my data would register 3 players leaving 5 reviews on a daily basis.
-This is the reason why I refer to the values of $(r_{it}^+, r_{it}^-)$ as rates, rather than probabilities (which they are in the model).
-Propositon \ref{poissonReviews}, stating that the number of good reviews on day $t$ for game $i$ is a Poisson random variable with rate $r_{it}^+\lambda_{it-k}$, could be treated as an assumption, rather than a result.
-In that case, nothing constrains the $r_{it}^+$ parameter to be less than 1, and the identification argument goes through in the exactly the same way.
-
-Another problem stems from the fact that the purchase date behind a review is not available to the researcher.
-For that reason, the model features an additional parameter $k$, the lag between purchasing the game and leaving a review, that I assumed to be known.
-To estimate that parameter I leverage the fact that spikes in player activity on the first day of a sale represent new users, and study the review response during the following week in order to uncover the modal lag for leaving a review (see Table \ref{reviewLag} in the Appendix).
-This number turns out to be one day.
-Even though time to posting a review has a non-degenerate distribution, modelling it in a more nuanced way would significantly contribute to complexity: the likelihood of receiving a poisitive review on day 100 would depend on the entire history of buyer arrivals prior to that date.
-Therefore, I proceed using $\hat k = 1$.
-
-## Estimation and Results
-
-### Demand Parameters
-
-```{r cache = F}
-reg.results <- fread(here("Analysis", "Temp", "juliaResults.csv")) %>% as.data.frame()
-beta.hat <- reg.results[seq(1, nrow(reg.results), 3), 4] %>% round(., 3)
-reg.results.stats <- fread(here("Analysis", "Temp", "juliaResults2.csv")) %>% as.data.frame()
-effects<-fread(here("Analysis", "Temp", "juliaResults3.csv"))
-effects <- merge(effects, info[, .(id, ID)], by = c("id"), all.x = T)
-panel <- merge(panel, effects[, .(ID, t, lambda = lambda * z)], by = c("ID", "t"))
-effects <- effects[, .(psi=psi[1], lambda=lambda[1], mz = mean(z)), by = ID]
-info <- merge(info, effects, by = c("ID"))
-rm(effects)
-```
-
-### Review Parameters
+\end{equation} It is intuitively clear that the relative propensity to
+leave a good, rather than a bad, review should be easily estimable by
+comparing the ratios of good to bad reviews, without any knowledge of
+the quantity of games sold. This intuition is fully reflected in
+Equation (\ref{avReviewScore}), where the arrival rates
+\(\lambda_{it-k}\) have disappeared entirely.
+
+The analysis above is complicated by two facts. First, for each game I
+observe the exact review count, but my demand estimates only apply to
+rush hours. If, say, every player leaves a review, and every day there
+are two new players who play in the morning, and three new players who
+play in the evening, my data would register 3 players leaving 5 reviews
+on a daily basis. This is the reason why I refer to the values of
+\((r_{it}^+, r_{it}^-)\) as rates, rather than probabilities (which they
+are in the model). Propositon \ref{poissonReviews}, stating that the
+number of good reviews on day \(t\) for game \(i\) is a Poisson random
+variable with rate \(r_{it}^+\lambda_{it-k}\), could be treated as an
+assumption, rather than a result. In that case, nothing constrains the
+\(r_{it}^+\) parameter to be less than 1, and the identification
+argument goes through in the exactly the same way.
+
+Another problem stems from the fact that the purchase date behind a
+review is not available to the researcher. For that reason, the model
+features an additional parameter \(k\), the lag between purchasing the
+game and leaving a review, that I assumed to be known. To estimate that
+parameter I leverage the fact that spikes in player activity on the
+first day of a sale represent new users, and study the review response
+during the following week in order to uncover the modal lag for leaving
+a review (see Table \ref{reviewLag} in the Appendix). This number turns
+out to be one day. Even though time to posting a review has a
+non-degenerate distribution, modelling it in a more nuanced way would
+significantly contribute to complexity: the likelihood of receiving a
+poisitive review on day 100 would depend on the entire history of buyer
+arrivals prior to that date. Therefore, I proceed using \(\hat k = 1\).
+
+\hypertarget{estimation-and-results}{%
+\subsection{Estimation and Results}\label{estimation-and-results}}
+
+\hypertarget{demand-parameters-1}{%
+\subsubsection{Demand Parameters}\label{demand-parameters-1}}
+
+\hypertarget{review-parameters-1}{%
+\subsubsection{Review Parameters}\label{review-parameters-1}}
 
@@
 
-# Additional Tables and Figures
-## Discounts Around Transitions
-```{r results = 'asis'}
-cat(star_insert_row(star.out.transitions, c("Time Effects & Weekdays, Week \\\\",
-                                "Game Effects & $\\times$ \\\\",
-                                "Polynomial($t$ W/O Discount) & $d = 2$ \\\\"), insert.after = c(34,34,34)))
-```
+\hypertarget{additional-tables-and-figures}{%
+\section{Additional Tables and
+Figures}\label{additional-tables-and-figures}}
+
+\hypertarget{discounts-around-transitions}{%
+\subsection{Discounts Around
+Transitions}\label{discounts-around-transitions}}
+
+\begin{table}[hp] \centering    \caption{Discounts In The Days Around Transition}    \label{transitionReg}  \begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Discount Probability \\  \hline \\[-1.8ex]   Days to Transition & 0.006$^{***}$ \\    & (0.0005) \\    Days After Transition & $-$0.011$^{***}$ \\    & (0.0005) \\    No Score & 0.181$^{***}$ \\    & (0.026) \\    Negative & 0.004 \\    & (0.010) \\    Mostly Positive & $-$0.001 \\    & (0.005) \\    Positive & 0.032$^{***}$ \\    & (0.007) \\    Very Positive & 0.001 \\    & (0.006) \\    Ov.
+Positive & 0.004 \\    & (0.013) \\    Log Reviews & $-$0.011$^{***}$ \\    & (0.002) \\    Age & 0.0003$^{***}$ \\    & (0.00001) \\    Const & 0.872$^{***}$ \\    & (0.014) \\   \hline \\[-1.8ex]  Time Effects & Weekdays, Week \\ Game Effects & $\times$ \\ Polynomial($t$ W/O Discount) & $d = 2$ \\ Observations & 32,412 \\  R$^{2}$ & 0.397 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  \end{table}
 \newpage
-## Review Lag
+
+\hypertarget{review-lag}{%
+\subsection{Review Lag}\label{review-lag}}
+
 Table \ref{reviewLag} presents the results of estimating
-$$NewReviews_{it} =\sum_{l = 0}^{7} \mathds{1}(\text{Disc. } l \text{ days ago})
-+ reviewBin_{it} + age_{it} + young_{it} +  f_i + \tau_t + u_{it}$$
-```{r include=F}
-# Calculate the daily new review count and the lags of the dummy for new discount. 
-panel[, new.reviews := c(reviews[1], diff(reviews)), by = ID]
-panel[, discNewLag2 := shift(discNewLag), by = ID][is.na(discNewLag2), discNewLag2 := F]
-panel[, discNewLag3 := shift(discNewLag2), by = ID][is.na(discNewLag3), discNewLag3 := F]
-panel[, discNewLag4 := shift(discNewLag3), by = ID][is.na(discNewLag4), discNewLag4 := F]
-panel[, discNewLag5 := shift(discNewLag4), by = ID][is.na(discNewLag5), discNewLag5 := F]
-panel[, discNewLag6 := shift(discNewLag5), by = ID][is.na(discNewLag6), discNewLag6 := F]
-panel[, discNewLag7 := shift(discNewLag6), by = ID][is.na(discNewLag7), discNewLag7 := F]
-
-# normally, a lag(discNew, 0:7) could be used in the regression formula, but R returns an
-# error that I can not debug
-reg1 <- plm(new.reviews ~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
-                          discNewLag5 + discNewLag6 + discNewLag7 + 
-                          negative + mPositive + positive + age + young + day + week,
-                          data = panel, model = "within")
-cov<-vcovHC(reg1, method="white1")
-se1 <- sqrt(diag(cov))
-
-star.out <- stargazer(reg1,
-             label = "reviewLag",
-             table.placement = "hp",
-             header = FALSE,
-             title = "Spikes in Reviews After a Discount",
-             se=list(se1),
-             dep.var.labels = c("New Reviews"),
-             covariate.labels = c("Discount 0 Days Ago", "Discount 1 Day Ago",
-                                  "Discount 2 Days Ago", "Discount 3 Days Ago",
-                                  "Discount 4 Days Ago", "Discount 5 Days Ago", 
-                                  "Discount 6 Days Ago", "Discount 7 Days Ago"),
-             model.numbers = F,
-             omit = c("day","week","negative","mPositive","positive","age", "young"),
-             omit.stat=c("f","adj.rsq","ser"),
-             no.space=T)
-panel[, discNewLag2:=NULL][, discNewLag3:=NULL][, discNewLag4:=NULL][, discNewLag5:=NULL]
-panel[, discNewLag6:=NULL][, discNewLag7:=NULL][, new.reviews:=NULL]
-```
-
-```{r results = 'asis'}
-cat(star_insert_row(star.out, c("Time Effects & Weekdays, Week \\\\",
-                                "Game Effects & $\\checkmark$ \\\\"), insert.after = c(28,28)))
-```
+\[NewReviews_{it} =\sum_{l = 0}^{7} \mathds{1}(\text{Disc. } l \text{ days ago})
++ reviewBin_{it} + age_{it} + young_{it} +  f_i + \tau_t + u_{it}\]
+
+\begin{table}[hp] \centering    \caption{Spikes in Reviews After a Discount}    \label{reviewLag}  \begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & New Reviews \\  \hline \\[-1.8ex]   Discount 0 Days Ago & 1.107$^{***}$ \\    & (0.123) \\    Discount 1 Day Ago & 3.308$^{***}$ \\    & (0.277) \\    Discount 2 Days Ago & 1.397$^{***}$ \\    & (0.139) \\    Discount 3 Days Ago & 0.748$^{***}$ \\    & (0.110) \\    Discount 4 Days Ago & 0.612$^{***}$ \\    & (0.096) \\    Discount 5 Days Ago & 0.397$^{***}$ \\    & (0.104) \\    Discount 6 Days Ago & 0.036 \\    & (0.086) \\    Discount 7 Days Ago & $-$0.160$^{**}$ \\    & (0.073) \\   \hline \\[-1.8ex]  Time Effects & Weekdays, Week \\ Game Effects & $\checkmark$ \\ Observations & 355,983 \\  R$^{2}$ & 0.054 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  \end{table}
 
 \newpage
-# Mathematical Appendix
-
-## Proofs
-
-\textbf{Proposition} \ref{poissonReviews}.
-Let the total number of reviewers during a day, $R$, be distributed Poisson with rate $\lambda$,  $R\sim P(\cdot; \lambda)$.
-A reviewer leaves a good review with probability $\pi$, and a bad review with probability $1-\pi$.
-Then, the numbers of good and bad reviews, $G$ and $B$, are independent Poisson random variables with rates $\pi\lambda$ and $(1-\pi)\lambda$.
-
-In the main text I have a Poisson arrival of customers, and only a fraction of them become reviewers, but the same proof goes through with that modification as well.
-The independence between the numbers of good and bad reviews is the surprising part of the proposition, and it is better highlighted in the form presented here.
-
-\vspace{1em}\noindent *Proof*: We start by showing that $G$ is Poisson.
-$$
+
+\hypertarget{mathematical-appendix}{%
+\section{Mathematical Appendix}\label{mathematical-appendix}}
+
+\hypertarget{proofs}{%
+\subsection{Proofs}\label{proofs}}
+
+\textbf{Proposition} \ref{poissonReviews}. Let the total number of
+reviewers during a day, \(R\), be distributed Poisson with rate
+\(\lambda\), \(R\sim P(\cdot; \lambda)\). A reviewer leaves a good
+review with probability \(\pi\), and a bad review with probability
+\(1-\pi\). Then, the numbers of good and bad reviews, \(G\) and \(B\),
+are independent Poisson random variables with rates \(\pi\lambda\) and
+\((1-\pi)\lambda\).
+
+In the main text I have a Poisson arrival of customers, and only a
+fraction of them become reviewers, but the same proof goes through with
+that modification as well. The independence between the numbers of good
+and bad reviews is the surprising part of the proposition, and it is
+better highlighted in the form presented here.
+
+\vspace{1em}
+
+\noindent *Proof*: We start by showing that \(G\) is Poisson. \[
 \PP{G=g} = \sum_{n=g}^{\infty}\CP{G = g}{R=n}\PP{R = n} 
@@
 \frac{\lambda^n}{n!} e^{-\lambda}
-$$
-
-\noindent We leave only the parts that depend on $n$ within the sum:
-$$
+\]
+
+\noindent We leave only the parts that depend on \(n\) within the sum:
+\[
 e^{-\lambda}\frac{\pi^g}{g!}\sum_{n = g}^{\infty}
@@
 \frac{[(1-\pi)\lambda]^{k} }{k!}e^{-(1-\pi)\lambda}
-$$
-
-\noindent The sum we have is just $\sum_{k=0}^{\infty} P(k; \lambda) = 1$, so the answer is
-$$
+\]
+
+\noindent The sum we have is just
+\(\sum_{k=0}^{\infty} P(k; \lambda) = 1\), so the answer is \[
 \PP{G=g} = \frac{[\pi\lambda]^g}{g!}e^{-\pi\lambda} = P(g; \pi\lambda)
-$$
-
-Now the independence part. We are interested in $\PP{G=g, B=b}$, which could be written as
-$$\PP{G=g, B=b} = \CP{G=g, B=b}{R=g+b}\PP{R=g+b} = 
+\]
+
+Now the independence part. We are interested in \(\PP{G=g, B=b}\), which
+could be written as \[\PP{G=g, B=b} = \CP{G=g, B=b}{R=g+b}\PP{R=g+b} = 
 \frac{(g+b)!}{g!b!}
@@
 \frac{\lambda^{g+b}}{(g+b)!} e^{-\lambda}
-$$
-Simply write $e^{-\lambda} = e^{-\pi\lambda}e^{-(1-\pi)\lambda}$, and collect the terms with $g$ and with $b$ to get
-$$
+\] Simply write \(e^{-\lambda} = e^{-\pi\lambda}e^{-(1-\pi)\lambda}\),
+and collect the terms with \(g\) and with \(b\) to get \[
 \PP{G=g, B=b} = 
@@
 =
-P(g; \pi \lambda) P(b; (1-\pi)\lambda)$$
+P(g; \pi \lambda) P(b; (1-\pi)\lambda)\]
+
 \begin{flushright}
@@
 \newpage
-## NLLS estimator of $\beta$
+
+\hypertarget{nlls-estimator-of-beta}{%
+\subsection{\texorpdfstring{NLLS estimator of
+\(\beta\)}{NLLS estimator of \textbackslash beta}}\label{nlls-estimator-of-beta}}
 
@@
  y_{it} = \psi_i y_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
-\end{equation}
-This model has \(2n\) \(i\)-specific parameters \((\lambda_i, \psi_i)\) and \(\dim(\beta)\) parameters that are shared by all entities in the panel.
-Estimation is via Non-linear Least Squares.
-The F.O.C.
-of the problem could
-be reduced so as to concentrate out all \((\lambda_i,\psi_i)\) parameters.
-Thus, estimation of \(2n + \dim(\beta)\) parameters reduces to solving a system of non-linear equations for \(\dim(\beta)\) parameters (or solving a NLLS problem of that dimension).
+\end{equation} This model has \(2n\) \(i\)-specific parameters
+\((\lambda_i, \psi_i)\) and \(\dim(\beta)\) parameters that are shared
+by all entities in the panel. Estimation is via Non-linear Least
+Squares. The F.O.C. of the problem could be reduced so as to concentrate
+out all \((\lambda_i,\psi_i)\) parameters. Thus, estimation of
+\(2n + \dim(\beta)\) parameters reduces to solving a system of
+non-linear equations for \(\dim(\beta)\) parameters (or solving a NLLS
+problem of that dimension).
 
@@
  \sum_{i=1}^n \sum_{t=2}^{T_i} (y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))^2
-\end{equation}
-The F.O.C. are
-\begin{alignat}{3}
+\end{equation} The F.O.C. are \begin{alignat}{3}
 \label{regFOC1} \psi_i:\; & \sum_{t=2}^{T_i} (y_{it} - \psi_iy_{it-1} - \lambda_i(1+x_{it}'\beta))y_{it-1} &\;=\;& 0\\
@@
   \beta:\; & \sum_{i=1}^n \sum_{t=2}^{T_i} (y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))\lambda_ix_{it} &\;=\;& 0
-\end{alignat}
-Conditional on \(\beta\), the F.O.C. for \((\psi_i, \lambda_i)\) are F.O.C.'s of an OLS problem of the form
+\end{alignat} Conditional on \(\beta\), the F.O.C. for
+\((\psi_i, \lambda_i)\) are F.O.C.'s of an OLS problem of the form
 \[\min_{\psi_i, \lambda_i}\sum_{t=2}^{T_i} (y_{it} - \psi_i y_{it-1} - \lambda_iz_{it})^2,\]
-where \(z_{it} = (1+x_{it}'\beta)\).
-Defining, in the standard way, \(\tilde{\mathbf Z}_i (\beta)\) to be the matrix with row \(t\) given by \([z_{it+1}, y_{it}]\), and \(y_i\) to be the vector of \(y_{it}\)
-observations, we get that the values of \(\hat \lambda_i,\hat \psi_i\) that solve (\ref{regFOC1})-(\ref{regFOC2}) are given by
+where \(z_{it} = (1+x_{it}'\beta)\). Defining, in the standard way,
+\(\tilde{\mathbf Z}_i (\beta)\) to be the matrix with row \(t\) given by
+\([z_{it+1}, y_{it}]\), and \(y_i\) to be the vector of \(y_{it}\)
+observations, we get that the values of \(\hat \lambda_i,\hat \psi_i\)
+that solve (\ref{regFOC1})-(\ref{regFOC2}) are given by
 \begin{equation}\label{psilambda}
@@
 
-\noindent The estimator \(\hat \beta\) of \(\beta\) is now obtained
-as a solution to
-\begin{equation}\label{concFOC}
+\noindent The estimator \(\hat \beta\) of \(\beta\) is now obtained as a
+solution to \begin{equation}\label{concFOC}
 \sum_{i=1}^n \sum_{t=2}^{T_i} (y_{it} - \psi_i(\beta) y_{it-1} - \lambda_i(\beta)(1+x'_{it}\beta))\lambda_i(\beta)x_{it} = 0
-\end{equation}
-In practice I solve the concentrated minimization problem using (\ref{concFOC}) as the gradient.
-
-Supplying an analytic expression for the Hessian matrix has proven to significantly expedite and improve convergence.
-The concentrated out sum of squared errors is $SSE(\beta) = SSE(\beta, \lambda(\beta), \psi(\beta))$, and while the expression for the gradient simplifies to $\partial SSE/\partial \beta$ due to the envelope theorem, the expression for the Hessian is more complex:
+\end{equation} In practice I solve the concentrated minimization problem
+using (\ref{concFOC}) as the gradient.
+
+Supplying an analytic expression for the Hessian matrix has proven to
+significantly expedite and improve convergence. The concentrated out sum
+of squared errors is
+\(SSE(\beta) = SSE(\beta, \lambda(\beta), \psi(\beta))\), and while the
+expression for the gradient simplifies to
+\(\partial SSE/\partial \beta\) due to the envelope theorem, the
+expression for the Hessian is more complex:
 \begin{equation}\label{hessianEq}
@@
 
-\noindent The expressions for $\frac{d \lambda_i}{d \beta}$ and $\frac{d \psi_i}{d \beta}$ are obtained by applying the inverse function theorem to (\ref{psilambda}), and the remaining derivatives could be obtained directly.
-
-The asymptotic covariance matrix for \(\hat \theta\) in a nonlinear
-LS problem \(\sum_i (y_i - m(x_i, \theta))^2\) is estimated using the sample analog of
-\begin{equation}
+\noindent The expressions for \(\frac{d \lambda_i}{d \beta}\) and
+\(\frac{d \psi_i}{d \beta}\) are obtained by applying the inverse
+function theorem to (\ref{psilambda}), and the remaining derivatives
+could be obtained directly.
+
+The asymptotic covariance matrix for \(\hat \theta\) in a nonlinear LS
+problem \(\sum_i (y_i - m(x_i, \theta))^2\) is estimated using the
+sample analog of \begin{equation}
 \mathbf V_\theta = \left(\mathbb{E}\left[m_{\theta i}m_{\theta i}'\right]\right)^{-1}
@@
                 \left(\mathbb{E}\left[m_{\theta i}'m_{\theta i}\right]\right)^{-1},
-\end{equation}
-where
+\end{equation} where
 \(m_{\theta i} = \frac{\partial}{\partial \theta} m(x_i, \theta_0)\),
-\(e_i = y_i - m(x_i, \theta_0)\) [@Hansen20, p.751]. More details could be found in the code.
+\(e_i = y_i - m(x_i, \theta_0)\) \citep[p.751]{Hansen20}. More details
+could be found in the code.
 
 \newpage
+
+  \bibliography{reviewsBib.bib}
+
+\end{document}

### 2020-08-08 Analysis/Code/StructuralFunctions.R

@@ -1,0 +1,233 @@
+# Define some variables
+one.year <- anydate("2016-01-01") - anydate("2015-01-01")
+one.day<- anydate("2014-01-02") - anydate("2014-01-01")
+sampleStartDate <- "2017-01-01"
+sampleFinalDate <- anydate("2019-01-01")
+
+# The color scheme
+my.colors <- c("#1b85b8",  "#cc3399", "#007f66",  "#f27d0c", "#cc2a36")
+
+# The style function has two arguments that specify the location of the legend
+# in graphs that need one. The defaults are specified, but feel free to change
+# the location if the graph looks better that way
+my.theme <- function(leg.x = 0.75, leg.y = 0.1){
+  theme_bw() +
+    theme(panel.background = element_rect(
+      #fill = wes_palette("Moonrise1")[3]
+    ),
+    text = element_text(family="Times",size=11),
+    plot.title = element_text(size=10, family="Times", face="bold",
+                              #hjust=0.5,
+                              lineheight=2),
+    axis.title.x = element_text(family="Times",size=11),  
+    axis.title.y = element_text(family="Times",size=11),  
+    legend.text  = element_text(family="Times",size=10),
+    legend.title = element_text(size=10,family="Times",
+                                face="bold"),
+    legend.position = c(leg.x, leg.y),
+    legend.direction = "horizontal",
+    legend.background = element_rect(
+      fill = "white",
+      size = 0.25,
+      linetype="solid",
+      colour = "black"))
+}
+
+splitPriceDuration <- function(x){
+  # Break the duration of the price into 7-day periods, and return the vector with
+  # the number of days (x7) that needs to be added to the date to make sure each
+  # week has a date that we can use to duplicate the price.
+  # Example: price duration is 22 days. Return a vector (7, 14, 21) (days), that
+  # could then be added to the date of the price change. This way every week
+  # will have price information.
+
+  # Add n.weeks rows
+  n.weeks <- x[, p.dur] %>% as.integer(.) %/% 7
+  switch(as.integer(x[, p.dur]) %% 7 == 0, n.weeks <- n.weeks - 1)
+  
+  # 7 day step
+  step <- anydate("1992-01-08") - anydate("1992-01-01")
+  
[…]

### 2020-08-08 Build/Code/BrushUpCleanData.R

@@ -1,0 +1,306 @@
+# Load functions
+source(here("Build", "Code", "BuildFunctions.R"))
+
+# Load cleaned dataset 
+load(here("Build", "Input", "allSteamReviews.Rda"))
+
+# Drop games based on specific date 
+#  For earlier run, we used date of second policy change : 03-09-2017
+#  We now include all dates before May 1, 2019
+dateThreshold=as.Date('05-01-2019','%m-%d-%Y')
+allSteamReviews[,min_date:=min(posted_date),by=c('game_id')]
+sample_data=allSteamReviews[min_date<=dateThreshold,]
+sample_data[,min_date:=NULL]
+rm(list=c("allSteamReviews"))
+# Create review counts by day + game + activation type
+aggSteamReviews = create_ts_reviews(sample_data)
+
+# Create dummy for whether game had early access
+setDT(sample_data)
+early_access_data=sample_data[,list(yes_early_access=sum(early_access_review!='')>0),
+                              by=c('game_id')]
+early_access_dates=sample_data[early_access_review=='Early Access Review',
+                               list(early_access_start=min(posted_date),
+                                    early_access_end=max(posted_date)),by=c('game_id')]
+early_access_data=merge(early_access_data,
+                        early_access_dates,
+                        all.x=T,
+                        on='game_id')
+early_access_data[,early_access_daysInEA:=as.integer(early_access_end-early_access_start)]
+save(early_access_data,file=here("Build","Temp","earlyAccess.dta"))
+rm(list=c("sample_data"))
+# Create columns that are the visible reviews 
+setDT(aggSteamReviews)
+
+
+# Create columns that are cumulative sums of postive/negative review counts
+aggSteamReviews[,positive_review_total:=cumsum(positive_review_by_day)
+                ,by=list(game_id,steam_key_activation,posted_date)]
+aggSteamReviews[,negative_review_total:=cumsum(negative_review_by_day)
+                ,by=list(game_id,steam_key_activation,posted_date)]
+aggSteamReviews[,total_review_total:=cumsum(total_review_by_day)
+                ,by=list(game_id,steam_key_activation,posted_date)]
+
+
+# ~~ Create columns for reviews left by users who bought their game on steam and 
+# all other users ~~
+#
+# onSteam  -> reviewers bought game on steam
+# offSteam -> reviewers received game another way (either off steam or with a 
[…]

### 2020-08-08 Build/Code/BuildFunctions.R

@@ -1,0 +1,236 @@
+interpolateInterval <- function(tVec, yVec, toleratedDif = 1){
+  # Interpolates between (t0, y0) and (t1, y1). tVec=(t0, t1) and yVec=(y0, y1)
+  # If the difference between the points is too big, don't interpolate.
+  # By default, the tolerance is 1, which means that all points would be interpolated
+  nPoints <- tVec[2] - tVec[1] + 1
+  
+  if(abs(yVec[2]-yVec[1])/max(yVec[1], yVec[2]) < toleratedDif){
+    seq(yVec[1], yVec[2], length.out = nPoints)[2:(nPoints-1)] %>%
+      as.integer()
+  }
+  else{
+    seq(0, 0, length.out = nPoints)[2:(nPoints-1)] %>%
+      as.integer()
+  }
+}
+
+interpolateVariable <- function(v, toleratedDif = 1){
+  # Take a vector of number and replace zeroes with interpolation of the closest
+  # non-zero elements. Example: 
+  # > interpolateVariable(c(NA, NA, 0, 1, 4, 0, 0, 1)) 
+  # > NA NA  0  1  4  3  2  1
+  
+  # temporarily replace NA with 0
+  naInd <- is.na(v)
+  v[naInd] <- 0
+  
+  # indentify the positions of non-zero elements
+  nonZerov <- v != 0
+  lenV <- length(v)
+  nonZeroInd <- (1:lenV)[nonZerov]
+  n <- length(nonZeroInd)
+  if (n <= 1){
+    v[naInd] <- NA
+    return(v)
+  }
+  first <- nonZeroInd[1]
+  last <- nonZeroInd[n]
+
+  # eliminate all the non-zero elements that follow each other and which, 
+  # for that reason, are not needed in interpolation
+  shiftNonZero <- c(nonZeroInd[-1], last + 1)
+  indVec <- (1:n)[(shiftNonZero - nonZeroInd - 1) != 0]
+  
+  # pairs of indicies (t0,t1) to interpolate between
+  tVecs <- lapply(indVec, function(x) nonZeroInd[c(x, x+1)])
+  # pairs of values (y0,y1) to interpolate
+  yVecs <- lapply(tVecs, function(x) v[c(x[1], x[2])])
+  
+  if (length(tVecs) == 0){
+    v[naInd] <- NA
+    return(v)
+  }
+  
[…]

### 2020-08-08 Build/Code/CreateSample.R

@@ -1,0 +1,249 @@
+# This organizes processed raw data and has some basic filters
+source(here("Build", "Code", "BrushUpCleanData.R"))
+# Load functions
+source(here("Build", "Code", "BuildFunctions.R"))
+
+# ~ SAMPLE DESCRIPTION ~
+# keep single player games launched when prices were available, not EA, and with 
+# at least medPlayersCutoff players playing on a median day. Releasedate should be 
+# after sampleStartDate. Data was already prefiltered in 
+# BrushUpCleanData.R, but some more filtering will be necessary
+
+# Define some variables
+medPlayersCutoff <- 4
+# min age
+min.age <- 7
+one.year <- anydate("2016-01-01") - anydate("2015-01-01")
+one.day<- anydate("2014-01-02") - anydate("2014-01-01")
+sampleStartDate <- "2017-01-01"
+sampleFinalDate <- anydate("2019-01-01")
+
+# ~FINAL SAMPLE SELECTION ~ 
+load(here("Build", "Temp", "infoSample.Rda"))
+info<-info[mult==F&multOnline ==F&crossplatform==F&mmo==F&ea==F&
+           start>=sampleStartDate&medPlayers2Years>=medPlayersCutoff][,
+          mult:=NULL][,multOnline:=NULL][,mmo:=NULL][,crossplatform:=F]
+info[,ea:=NULL][,eaExit:=NULL]
+
+# Drop the largest outlier game
+info <- info[ID != 437060, ]
+
+load(here("Build", "Temp", "pricesSample.Rda"))
+prices[, discNew := discount > 0]
+prices[, date := anydate(date)]
+
+# some manual corrections of scraping mistakes. These mistakes seem to steamDB's,
+# not mine
+prices <- rbind(prices, list(626640, anydate("2017-10-26"), 6.99, 0.00, F))
+setkey(prices, ID, "date")
+prices <- rbind(prices, list(366870, anydate("2018-02-20"), 19.99, 0.00, F))
+prices <- rbind(prices, list(583760, anydate("2017-08-22"), 0.99, 0.00, F))
+prices <- rbind(prices, list(586090, anydate("2017-12-15"), 0.99, 0.00, F))
+prices <- rbind(prices, list(595440, anydate("2018-02-19"), 0.99, 0.00, F))
+prices <- rbind(prices, list(595440, anydate("2018-04-16"), 0.49, 0.51, T))
+prices <- rbind(prices, list(601530, anydate("2017-10-02"), 5.99, 0.00, F))
[…]

### 2020-08-08 MakePaper.R

@@ -1,0 +1,38 @@
+# Load libraries 
+library(here)
+library(devtools) # for installing packages through GitHub, needed for starpolishr
+library(data.table)
+library(stringr)
+library(stringi) # that is wasteful, but it happened
+library(anytime)
+library(dplyr)
+library(magrittr)
+library(fastDummies)
+library(kableExtra)
+library(ggplot2)
+library(wesanderson)
+library(ggthemes)
+library(ggridges)
+library(ggpubr)
+library(sandwich)
+library(lmtest)
+library(plm)
+library(stargazer)
+library(starpolishr)
+library(texreg)
+library(R.utils)
+library(rmarkdown)
+
+knitr::opts_chunk$set(echo=F,eval=T,message=F,warning=F,comment=NA,cache=T)
+knitr::opts_chunk$set(fig.pos = "h", out.extra = "", fig.align = "center")
+
+# If you have obtained raw data from me, you can uncomment this in order to 
+# create the sample yourself.
+
+# source(here("Build", "Code", "CreateSample.R")) 
+
+# Output of Build is Input for Analysis, creating a symbolic link 
+createLink(here("Analysis", "Input"), here("Build", "Output"), skip = T)
+
+# Create the Paper
+render(here("Analysis","Code", "Paper.Rmd"), output_dir = here("Analysis", "Output"))

### 2020-08-08 Analysis/Output/Paper.tex
Packrat snapshot

@@
 \author{Dmitry Sorokin}
-\date{August 08, 2020}
+\date{\texttt{r\ format(Sys.time(),\ \textquotesingle{}\%B\ \%d,\ \%Y\textquotesingle{})}}
 
@@
 
-\begin{table}[t]
+\begin{table}
 
@@
 \centering
-\begin{tabular}{lcc}
+\begin{tabular}[t]{lcc}
 \toprule
@@
 
- {\centering \includegraphics[width=0.75\linewidth,]{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/steamStore}
+ {\centering \includegraphics[width=0.75\linewidth,]{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/steamStore}
 
@@
 
-{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/example-game-1}
+{\centering \includegraphics{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/example-game-1}
 
@@
 
-The final sample includes 906 games which I observe for 393 days each,
-on average. The main variables in the analysis are the aforementioned
-dynamic variables: player count, price, and review score history. An
-example observation from the sample is given in Figure
+The final sample includes \texttt{r\ info{[},\ .N{]}} games which I
+observe for
+\texttt{r\ panel{[},\ max(age),\ by\ =\ ID{]}{[},\ round(mean(V1)){]}}
+days each, on average. The main variables in the analysis are the
+aforementioned dynamic variables: player count, price, and review score
+history. An example observation from the sample is given in Figure
 \ref{exampleGame}. For the majority of the games in the sample, the
@@
 
-{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/sample-size-hist-1}
+{\centering \includegraphics{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/sample-size-hist-1}
 
@@
 never changes its price, but instead occasionally goes on discounts,
-slowly increasing their magnitude as the game ages. There are 43
-incidents of price change in the data, compared to 6331 discounts. Steam
-has a number of rules that regulate price promotions on its platform. A
-game can have a launch discount, but, otherwise, it has to wait for two
-months since the release before changing its price or giving a discount.
-A game can not go on discounts too frequently, and has to wait between
-four to six weeks after a price promotion to be able to run a new one.
-The duration of a custom discount is restricted to be at least one full
-day, and at most two weeks. Besides these custom discounts, that are
-fully managed by the firms, Steam has a series of curated discounts,
-when the platform invites selected titles to go on a discount. As
-\citet{steamDiscounting} explains it, ``while there aren't strict rules,
-as a base guideline we tend to focus on the top 10-20\% selling games on
-Steam that are positively reviewed and have otherwise proven to be
-successful''. Curated promotions are featured prominently on Steam's
-main page, and, arguably, lead to more visibility and sales for the
-participating titles than custom discounts, which also contribute to
-visibility, but typically do not get the front-page promotional slots.
-An important type of curated discounts are the so-called ``Seasonal
-Sales''--big platform-wide events that take place about four times a
-year around major holidays. Figure \ref{seasonalSales} shows that the
-biggest sales take place in Winter (Christmas and New Year) and Summer
-(July 4), but there are also significant discounts in the Fall
-(Halloween and Thanksgiving). Around 64\% of discounts in the sample go
-live during a Seasonal Sale. Thus, firms have significant agency when it
-comes to running price promotions, but platform regulations and
-platform-wide discounts are important determinants of firms' decision to
-discount.
+slowly increasing their magnitude as the game ages. There are
+\texttt{r\ panel{[}discount==F,\ diff(price),\ by\ =\ ID{]}{[}V1\textgreater{}0,\ .N{]}}
+incidents of price change in the data, compared to
+\texttt{r\ panel{[}discNew==T,\ .N{]}} discounts. Steam has a number of
+rules that regulate price promotions on its platform. A game can have a
+launch discount, but, otherwise, it has to wait for two months since the
+release before changing its price or giving a discount. A game can not
+go on discounts too frequently, and has to wait between four to six
+weeks after a price promotion to be able to run a new one. The duration
+of a custom discount is restricted to be at least one full day, and at
+most two weeks. Besides these custom discounts, that are fully managed
+by the firms, Steam has a series of curated discounts, when the platform
+invites selected titles to go on a discount. As \citet{steamDiscounting}
+explains it, ``while there aren't strict rules, as a base guideline we
+tend to focus on the top 10-20\% selling games on Steam that are
+positively reviewed and have otherwise proven to be successful''.
+Curated promotions are featured prominently on Steam's main page, and,
+arguably, lead to more visibility and sales for the participating titles
+than custom discounts, which also contribute to visibility, but
+typically do not get the front-page promotional slots. An important type
+of curated discounts are the so-called ``Seasonal Sales''--big
+platform-wide events that take place about four times a year around
+major holidays. Figure \ref{seasonalSales} shows that the biggest sales
+take place in Winter (Christmas and New Year) and Summer (July 4), but
+there are also significant discounts in the Fall (Halloween and
+Thanksgiving). Around
+\texttt{r\ \ round(panel{[}discSeason==T\ \&\ discNew\ ==\ T,\ .N{]}/panel{[}discNew==T,\ .N{]}*100)}\%
+of discounts in the sample go live during a Seasonal Sale. Thus, firms
+have significant agency when it comes to running price promotions, but
+platform regulations and platform-wide discounts are important
+determinants of firms' decision to discount.
 
@@
 
-{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/seasonal-sales-1}
+{\centering \includegraphics{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/seasonal-sales-1}
 
@@
 the release. On average across games, the standard deviation of the
-review score (out of one hundred) is just 2.2, with a split of 1.83 in
-the first thirty days and 1.83 after that. The score is only assigned
-once the game reaches 10 reviews, and once can see that 10 reviews is
-enough on average keep the score stable. The distribution of games by
-bins at the age of 180 days, depicted in Figure
-\ref{reviewDescriptivePlots}, is, then, representative of the situation
-at other ages.
+review score (out of one hundred) is just
+\texttt{r\ round(panel{[},\ sd(score,\ na.rm=T),\ by\ =\ ID{]}{[},\ mean(V1,\ na.rm\ =\ T){]},\ 2)},
+with a split of
+\texttt{r\ round(panel{[}age\ \textless{}=\ 30,\ sd(score,\ na.rm=T),\ by\ =\ ID{]}{[},\ mean(V1,\ na.rm\ =\ T){]},\ 2)}
+in the first thirty days and
+\texttt{r\ round(panel{[}age\ \textgreater{}\ 30,\ sd(score,\ na.rm=T),\ by\ =\ ID{]}{[},\ mean(V1,\ na.rm\ =\ T){]},\ 2)}
+after that. The score is only assigned once the game reaches 10 reviews,
+and once can see that 10 reviews is enough on average keep the score
+stable. The distribution of games by bins at the age of 180 days,
+depicted in Figure \ref{reviewDescriptivePlots}, is, then,
+representative of the situation at other ages.
 
@@
 
-{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/review-descriptive-plots-1}
+{\centering \includegraphics{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/review-descriptive-plots-1}
 
@@
 in the sample. The number of unique games that have changed review
-labels in the data is 596, and the number of transitions is 1688.
+labels in the data is
+\texttt{r\ transitions{[},\ unique(ID){]}\ \%\textgreater{}\%\ length},
+and the number of transitions is \texttt{r\ transitions{[},\ .N{]}}.
 Sometimes games switch their bins briefly, and go back soon after. The
 number of transitions that led to the game spending at least 7 days in
-the new bin is 1225. Table \ref{mDiscountTable} describes the state of
-the games in the two weeks before their transitions. Discounting does
-take place before the transitions, games transition at very different
-ages, but tend to have only a limited number of reviews by the time
-their review bin changes.
-
-\begin{table}[t]
+the new bin is
+\texttt{r\ transitions{[}(is.na(dur)\ \textbar{}\ dur\ \textgreater{}=\ 7),\ .N{]}}.
+Table \ref{mDiscountTable} describes the state of the games in the two
+weeks before their transitions. Discounting does take place before the
+transitions, games transition at very different ages, but tend to have
+only a limited number of reviews by the time their review bin changes.
+
+\begin{table}
 
@@
 \resizebox{\linewidth}{!}{
-\begin{tabular}{ccccccccccccc}
+\begin{tabular}[t]{ccccccccccccc}
 \toprule
@@
 
-{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/transition-discount-plot-1}
+{\centering \includegraphics{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/transition-discount-plot-1}
 
@@
 \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in
-the Appendix). A game is approximately 8 pp more likely to be on a
-discount on the day of the transition than it is two weeks prior to it,
-and it is 16 pp less likely to be on a discount two weeks following the
-transition. Given that the probability for a game to be on a discount on
-a random day is 16\% in the sample, these effects amount to 3\% and 7\%
+the Appendix). A game is approximately
+\texttt{r\ round(reg1\$coefficients{[}2{]}*14*100)} pp more likely to be
+on a discount on the day of the transition than it is two weeks prior to
+it, and it is \texttt{r\ round(-reg1\$coefficients{[}3{]}*14*100)} pp
+less likely to be on a discount two weeks following the transition.
+Given that the probability for a game to be on a discount on a random
+day is
+\texttt{r\ round(panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}*100)}\%
+in the sample, these effects amount to
+\texttt{r\ round(100*(reg1\$coefficients{[}2{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}\%
+and
+\texttt{r\ round(100*(-reg1\$coefficients{[}3{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}\%
 changes in the daily probability of a discount, which is quite sizable.
@@
 positive transition, \(T_{it}^+ = 1\), if its proximity to a positive
-transition is less than or equal to 14 days. Similarly, game \(i\) at
-date \(t\) is said to be close to a negative transition,
+transition is less than or equal to \texttt{r\ 2*band} days. Similarly,
+game \(i\) at date \(t\) is said to be close to a negative transition,
 \(T_{it}^- = 1\), if its proximity to a positive transition is less than
-or equal to 14 days. The 14 cutoff is inspired by the maximum duration
-of custom discounts on Steam, and the patterns of discounting around
-successful transitions, depicted in Figure \ref{discountsTransitions}.
-To estimate the effect of being close to a review transition on the
-discounting behavior, I then estimate the following model:
-\begin{equation}\label{potTransitionsReg}
+or equal to \texttt{r\ 2*band} days. The \texttt{r\ 2*band} cutoff is
+inspired by the maximum duration of custom discounts on Steam, and the
+patterns of discounting around successful transitions, depicted in
+Figure \ref{discountsTransitions}. To estimate the effect of being close
+to a review transition on the discounting behavior, I then estimate the
+following model: \begin{equation}\label{potTransitionsReg}
 disc_{it} = \beta^+ T_{it}^+ + \beta^- T_{it}^- + X_{it}\beta + f_i + \tau_t + \varepsilon_{it},
@@
 more stringent definition of proximity to a transition, requiring a game
-to be 7, rather than 14, days away from a potential transition to be
-counted as being ``close to a transition''. The third column uses only
-transitions between ``Mixed'', ``Mostly Positive'', and ``Positive''
-labels, as these are the transitions that rely on the review score only,
-while ``Very Positive'' and ``Overwhelmingly Positive'' require both a
-certain review score, and a certain number of
+to be \texttt{r\ band}, rather than \texttt{r\ 2*band}, days away from a
+potential transition to be counted as being ``close to a transition''.
+The third column uses only transitions between ``Mixed'', ``Mostly
+Positive'', and ``Positive'' labels, as these are the transitions that
+rely on the review score only, while ``Very Positive'' and
+``Overwhelmingly Positive'' require both a certain review score, and a
+certain number of
 reviews.\footnote{Technically, a game improving its review score from 79\% to 80\% can transition to both “Positive” and “Very Positive”, so the results in the third column bundle together these types of transitions.}.
@@
 support the hypothesis that proximity to a review bin upgrade increases
-firms' willingness to run a price promotion. Measured against the 16\%
+firms' willingness to run a price promotion. Measured against the
+\texttt{r\ round(panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}*100)}\%
 probability for a random game-day pair from the sample to have a
-discount\footnote{The corresponding number for the games in the treatment group is 17.},
-the effects constitute a 4-6\% increase in the daily probability of a
-discount. The uncertainty about the sign and the significance of the
-proximity to a potential negative transition is resolved in favor of the
-prudent approach on the firms' side: the results suggest that firms
-under a risk of deteriorating their review label are 4-5\% less likely
-to go on a discount, albeit the effect is only present in two out of
-three specifications.
+discount\textbackslash footnote\{The corresponding number for the games
+in the treatment group is
+\texttt{r\ round(100*panel{[}ID\ \%in\%\ panel{[}pos.treatment\ ==\ 1,\ unique(ID){]},\ mean((discount\ \textgreater{}\ 0),\ na.rm\ =\ T){]})}.\},
+the effects constitute a
+\texttt{r\ round(100*(reg3\$coefficients{[}1{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}-\texttt{r\ round(100*(reg1\$coefficients{[}1{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}\%
+increase in the daily probability of a discount. The uncertainty about
+the sign and the significance of the proximity to a potential negative
+transition is resolved in favor of the prudent approach on the firms'
+side: the results suggest that firms under a risk of deteriorating their
+review label are
+\texttt{r\ -round(100*(reg3\$coefficients{[}2{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}-\texttt{r\ -round(100*(reg1\$coefficients{[}2{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}\%
+less likely to go on a discount, albeit the effect is only present in
+two out of three specifications.
 

### 2020-08-08 Analysis/Code/Paper.Rmd
Added the ability to render as HTML

@@
        in_header: extra_header.tex
+  html_document:
+    fig_height: 2.5
+    fig_width: 6
+    number_sections: true
 

### 2020-08-08 MakePaper.R

@@ -35,4 +35,6 @@ knitr::opts_chunk$set(fig.pos = "h", out.extra = "", fig.align = "center")
 createLink(here("Analysis", "Input"), here("Build", "Output"), skip = T)
 
 # Create the Paper
-render(here("Analysis","Code", "Paper.Rmd"), output_dir = here("Analysis", "Output"))
+render(here("Analysis","Code", "Paper.Rmd"), 
+       output_dir = here("Analysis", "Output"),
+       output_format = "pdf_document")

### 2020-08-09 Analysis/Code/Paper.Rmd
Added an option to create a hyperlink to the bibliography

--- 2020-08-08 Analysis/Code/Paper.Rmd
@@
  output:
-  pdf_document:
-    keep_tex: true
+  latex_document:
+    #keep_tex: true
     fig_height: 2.5
@@
 ```{r cache = F}
+knitr::opts_chunk$set(echo=F,eval=T,message=F,warning=F,comment=NA,cache=T)
+knitr::opts_chunk$set(fig.pos = "h", out.extra = "", fig.align = "center")
+
 source(here("Analysis", "Code", "StructuralFunctions.R"))
@@
 
-```{r include = F,}
+```{r include = F, cache=F}
 band <- 7

### 2020-08-09 Analysis/Output/Paper.tex
Added an option to create a hyperlink to the bibliography

--- 2020-08-08 Analysis/Output/Paper.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
 \PassOptionsToPackage{hyphens}{url}
@@
 %
-\documentclass[
-  12pt,
-  pagebackref]{article}
+\documentclass[12pt,pagebackref]{article}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
+  \usepackage{textcomp} % provides euro and other symbols
+\else % if luatex or xelatex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
-% Use upquote if available, for straight quotes in verbatim environments
+% use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
+% use microtype if available
+\IfFileExists{microtype.sty}{%
 \usepackage[]{microtype}
@@
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
 \IfFileExists{parskip.sty}{%
@@
 \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{hyperref}
 \hypersetup{
@@
             urlcolor=mypink,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
 \usepackage[margin=1in]{geometry}
-\usepackage{graphicx}
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 \setcounter{secnumdepth}{5}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
 \renewcommand{\ttdefault}{cmr} % change the font of inline R results to normal
@@
 \author{Dmitry Sorokin}
-\date{August 08, 2020}
+\date{August 09, 2020}
 
@@
 
- {\centering \includegraphics[width=0.75\linewidth,]{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/steamStore}
+ {\centering \includegraphics[width=0.75\linewidth,]{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/steamStore}
 
@@
 
-{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/example-game-1}
+{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/example-game-1}
 
@@
 
-{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/sample-size-hist-1}
+{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/sample-size-hist-1}
 
@@
 
-{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/seasonal-sales-1}
+{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/seasonal-sales-1}
 
@@
 
-{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/review-descriptive-plots-1}
+{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/review-descriptive-plots-1}
 
@@
 
-{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/transition-discount-plot-1}
+{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/transition-discount-plot-1}
 
@@
 raw review count, and to say that a game is close to upgrading its
-review label when it needs five (ten, twenty \ldots) more positive
+review label when it needs five (ten, twenty \ldots{}) more positive
 reviews to transition. However, given the heterogeneity in the
@@
 \subsection{\texorpdfstring{NLLS estimator of
-\(\beta\)}{NLLS estimator of \textbackslash beta}}\label{nlls-estimator-of-beta}}
+\(\beta\)}{NLLS estimator of \textbackslash{}beta}}\label{nlls-estimator-of-beta}}
 

### 2020-08-09 Analysis/Code/NLLS.jl

@@ -1,0 +1,336 @@
+using Distributions
+using DataFrames
+using LinearAlgebra
+using StatsBase
+using NLSolversBase
+using Optim
+using CSVFiles
+
+include("estimation_funcs.jl");
+
+# test on simulated data
+# X = simdata(700, 700)
+# regressors = [:age, :discnew, :discount, :logreviews, :noreviews,
+#               :negative, :mixed, :positive]
+#
+#
+# solution = @time Optim.optimize(Optim.only_fg!((F, G, x) -> ssr_concentrated!(F, G, nothing, x, X)),
+#                           β, LBFGS(), Optim.Options(allow_f_increases = true))
+#
+# solution = @time Optim.optimize(Optim.only_fgh!((F, G, H, x) -> ssr_concentrated!(F, G, H, x, X; hessian = true)),
+#                         β, Newton(), Optim.Options(allow_f_increases = true))
+#
+# β̂ = solution.minimizer
+# # create a value of z from β and map estimate_ψλ through the data
+# varβ̂ = varβ(β̂; data = X)
+# print_tests(testβ(β̂ , varβ̂))
+
+
+
+panel = "/Users/Dmitry/Steam/Build/Output/AnalysisData/juliaData.csv" |>
+        load |> DataFrame
+#panel = panel[Not(in.(panel.id, Ref([508, 678, 1270, 1297]))), :]
+
+# convert the Bools
+panel.discNew = (x -> ifelse(x=="TRUE", true, false)).(panel.discNew)
+panel.discNewLag = (x -> ifelse(x=="TRUE", true, false)).(panel.discNewLag)
+#panel.exogDiscNew = (x -> ifelse(x=="TRUE", true, false)).(panel.exogDiscNew)
+#panel.exogDiscNewLag = (x -> ifelse(x=="TRUE", true, false)).(panel.exogDiscNewLag)
+panel.noScore = (x -> ifelse(x=="TRUE", true, false)).(panel.noScore)
+panel.negative = (x -> ifelse(x=="TRUE", true, false)).(panel.negative)
+panel.mPositive = (x -> ifelse(x=="TRUE", true, false)).(panel.mPositive)
+panel.positive = (x -> ifelse(x=="TRUE", true, false)).(panel.positive)
+panel.young = (x -> ifelse(x=="TRUE", true, false)).(panel.young)
+panel.discSeason = (x -> ifelse(x=="TRUE", true, false)).(panel.discSeason)
+
+# initialize entries of the data frame that will be used later
[…]

### 2020-08-09 Analysis/Code/estimation_funcs.jl

@@ -1,0 +1,451 @@
+function simgame(id::Int64, t0::Int64, T::Int64, num0::Int64, β,
+                 λ::Int64, ψ::Float64, q::Float64)
+
+    # review parameters
+    r = 0.05 # probability to be a reviewer
+    rT = 7 # maximum number of days to leave a review
+    reviewtime = 1:rT
+    dateprobs = [0.6, 0.3, 0.02, 0.02, 0.02, 0.02, 0.02]
+
+    # Initialize the arrays: allow extra space for convenience, to store reviewers
+    # that won't realize in time
+    posrevs = 1
+    negrevs = 0
+    posarrivals = zeros(Int64, T+rT)
+    negarrivals = zeros(Int64, T+rT)
+
+    # All the x regressors go in this data frame
+    X = DataFrame(id=id, t=t0:(t0+T-1), number = zeros(Int64,T),
+                  numberLag = zeros(Int64,T), age = 1:T, discnew = zeros(Bool,T),
+                  discount = zeros(Float64,T), logreviews = zeros(Float64, T),
+                  noreviews = zeros(Bool,T), negative = zeros(Bool,T),
+                  mixed = zeros(Bool,T), positive = zeros(Bool,T))
+
+    X[1, :number] = num0
+    regressors = [:age, :discnew, :discount, :logreviews, :noreviews,
+                  :negative, :mixed, :positive]
+    # Discounts progressively get bigger, prob = 1/40, meaning 1 discount every
+    # 40 days, on average
+    disc_counter = 1
+    disc_prob = 0.025
+    disc_sizes = [0.1, 0.15, 0.25, 0.33, 0.5, 0.66, 0.75]
+    disc_durations = [1, 4, 7, 14]
+
+
+    function randomdiscount!(t::Int64)
+    # Checks if there is a discount at t. If not, tosses a coin and fills
+    # the entry of X
+      if X[t, :discount] > 0
+          return
+      end
+      if rand(Bernoulli(disc_prob)) == true
+          X[t, :discnew] = true
+          disc_counter == 6 ? nothing : disc_counter += rand([0,1])
+          dur = rand(disc_durations)
+          t_end = min(T, t+dur-1)
[…]

### 2020-08-09 MakePaper.R

@@ -23,9 +23,6 @@ library(texreg)
 library(R.utils)
 library(rmarkdown)
 
-knitr::opts_chunk$set(echo=F,eval=T,message=F,warning=F,comment=NA,cache=T)
-knitr::opts_chunk$set(fig.pos = "h", out.extra = "", fig.align = "center")
-
 # If you have obtained raw data from me, you can uncomment this in order to 
 # create the sample yourself.
 
@@ -34,7 +31,16 @@ knitr::opts_chunk$set(fig.pos = "h", out.extra = "", fig.align = "center")
 # Output of Build is Input for Analysis, creating a symbolic link 
 createLink(here("Analysis", "Input"), here("Build", "Output"), skip = T)
 
+# uncomment the line below if pdf_document compilation fails, but
+# you would like to compile the latex file yourself. It will create
+# a symlink to the bibliography in the folder of Paper.tex
+createLink(here("Analysis", "Output", "reviewsBib.bib"), 
+           here("Analysis", "Code", "reviewsBib.bib"), skip = T)
+
 # Create the Paper
 render(here("Analysis","Code", "Paper.Rmd"), 
        output_dir = here("Analysis", "Output"),
-       output_format = "pdf_document")
+       output_format = "latex_document"
+       )
+
+

### 2020-08-12 Analysis/Code/Paper.Rmd
Merged the NLLS results with LS.

@@
 
-## Estimation and Results
+## Results
+
+In this section I present the estimates of the model parameters.
+I start with the demand parameters $(\lambda_i, \psi_i, \beta)$ in (\ref{arrivalReg}), and contrast these estimates with the ones delivered by running a regression (\ref{logReg}).
+Then I proceed to the parameters of the review process, where the focus will be on the contributions $(\rho_{1i}^+, \rho_{1i}^-)$ of discounts to the like and dislike rates.
 
 ### Demand Parameters
+
+An ideal set of covariates $x_{it}$ that I would like to use in estimating (\ref{arrivalReg}), given by
+$$
+A_{it} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
+$$
+\noindent would be price, the review label, log reviews, age (plus a dummy for being at most 14 days old), and a set of day of the week and sample week time effects.
+However, this proved to be computationally infeasible.
+Even though I manage to concentrate out $2n=$`r 2*info[, .N]` game-specific parameters $(\lambda_i, \psi_i)$ from the numerical optimization routine, estimation of $\beta$ still relies on minimizing the sum of squared residuals in a $\dim(\beta)$-dimensional space.
+The routine would fail to converge to a solution within reasonable boundaries, so I had to eliminate some regressors.
 
@@
 
+```{r results='asis'}
+reg1 <- plm(log(number) ~ log(numberLag) + log(price) + noScore +
+              negative + mPositive + positive + log(reviews+1) + 
+              age + young + discSeason + day,
+                 data=panel[price!=0,],
+            model="within")
+
+reg2 <- plm(log(number) ~ log(numberLag) + log(price) + noScore + 
+              negative + mPositive + realPositive + vPositive + 
+              ovPositive + log(reviews+1) + age + young + 
+              day + week,
+                data=panel[price!=0,],
+            model="within")
+
+res <- plmJuliaToTex(reg1, reg2, reg.results[, c(1,4)],
+                     reg.results.stats[, c(1,4)])
+rm(reg.results, reg.results.stats)
+
+table <- texreg(res,
+                stars = c(0.01, 0.05, 0.1),
+                digits = 3,
+                custom.model.names = c("NLLS", "Reg", "Full Reg"),
+                reorder.coef = c(1, 9, 2, 3, 8, 10, 
+                                 4, 5, 6, 7, 11, 12),
+                caption = "Estimates of the Demand Parameters",
+                caption.above = T,
+                label = "demandEstimates")
+
+season.location <- str_locate(table, c("Weekdays"))[1]
+table.bottom <- str_sub(table, season.location, str_length(table))
+table.top <- str_sub(table, 1, season.location - 1)
+table.bottom <- str_replace_all(table.bottom, "0.000", "\\\\times")
+table.bottom <- str_replace_all(table.bottom, "1.000", "\\\\checkmark")
+table.bottom <- str_replace_all(table.bottom, ".000", "")
+table <- paste(table.top, table.bottom, sep = "")
+class(table) <- c("character", "texregTable")
+table
+```
+
+The week effects contribute the most to the dimensionality of the problem, as there are `r panel[, length(unique(week))]` weeks in the sample.
+The reason to include these week effects is to account for platform-wide shocks.
+The biggest shocks shared by games on Steam are Seasonal Sales.
+These sales take place around major holidays, and, thus, blend together the increased platform-wide demand with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSales}).
+To capture these periods in a parsimonious way, I calculated the average daily discount in the sample, and labeled the days when the average discount exceeded 20\%.
+Figure \ref{seasonalSalesPeriods} in the Appendix shows that my definition tracks closely the spikes in the aggregate discounting behavior.
+I also tried using the raw value of the average discount in the sample, but the results remained the same.
+
+Another exclusion I have to make is that of the “Very Positive” and “Overwhelmingly Positive” review lables.
+While the latter is not very prevalent in the sample, as is depicted in Figure \ref{reviewDescriptivePlots}, the former is by far the most common review label.
+In order to avoid dropping out these observations, I pool the “Very Positive” and “Overwhelmingly Positive” labels together with the “Positive” label.
+Recall that the only difference between “Positive” and “Very Positive” is whether the game has less or more than 50 reviews, so this pooling averages between two similar and adjacent review labels.
+
+Thus, the final set of covariates that I use in estimating (\ref{arrivalReg}) are: price, review label, log reviews, two age variables, and a set of day of the week time effects, and a Seasonal Sale dummy.
+I mentioned in the Identification section that a more simplistic, yet more tractable, alternative to estimating the non-linear model (\ref{arrivalReg}) is given by equation (\ref{logReg})
+$$
+\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}
+$$
+\noindent To check whether the omitted covariates could be playing a crucial role, I will report the results of estimaing (\ref{logReg}) both with the ideal set of covariates, and with the covariates used to estimate (\ref{arrivalReg}).
+The results are presented in Table \ref{demandEstimates}.
+
 ### Review Parameters
@@
 ## Discounts Around Transitions
+
 ```{r results = 'asis'}
@@
 ```
+
 \newpage
@@
                                 "Game Effects & $\\checkmark$ \\\\"), insert.after = c(28,28)))
+```
+
+\newpage
+## Definition of Seasonal Sales
+```{r seasonal-sales-periods, fig.cap='\\label{seasonalSalesPeriods} Seasonal Sales and Discounting Activity.
+Shaded regions are my definition of Seasonal Sales periods.
+The first spike on the graph is excluded because the sample starts with just one game, and I exclude the first 2 weeks from the calculations.'}
+months1 <- c(-1, 30, 58, 89, 119, 150, 180, 211, 242, 272, 303, 333) + 1
+months2 <- c(333 + 32 + months1, 699 + 31)
+
+f<-panel[, .(disc = discSeason[1]), keyby = t][, .(t, z=c(NA, diff(disc)))]
+
+discPeriods <- data.frame(xstart = f[z==1, t], xend = c(f[z==-1, t], panel[, max(t)]))
+
+ggplot(data = panel[, .(y=sum(discount > 0)/(.N), z=avDisc[1]), by = t]) +
+  geom_rect(data = discPeriods, aes(xmin = xstart, xmax = xend, ymin = -Inf, ymax = Inf), fill = my.colors[2], alpha = 0.25) + 
+  # ggtitle() +
+  geom_line(aes(x = t, y = y),
+            color = my.colors[1],
+            size = 1) +
+  scale_x_continuous(name = NULL,
+                     breaks = c(months1, months2)[seq(1,25,3)], 
+                     labels = months(getDate(c(months1, months2))[seq(1,25,3)], 
+                                     abbreviate=T),
+                     minor_breaks = NULL) +
+  scale_y_continuous(name = "Fraction of Games",
+                     minor_breaks = NULL)  +
+  my.theme(leg.x = 0.25, leg.y = 0.9)
+
+rm(months1, months2, f, discPeriods)
 ```

### 2020-08-12 Analysis/Output/Paper.tex
Merged the NLLS results with LS.

@@
 \author{Dmitry Sorokin}
-\date{August 09, 2020}
+\date{August 12, 2020}
 
@@
 
- \caption{\label{steamStore}Example Browsing Session on Steam}\label{fig:unnamed-chunk-3}
+ \caption{\label{steamStore}Example Browsing Session on Steam}\label{fig:unnamed-chunk-5}
  \end{figure}
@@
 
-\hypertarget{estimation-and-results}{%
-\subsection{Estimation and Results}\label{estimation-and-results}}
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
+In this section I present the estimates of the model parameters. I start
+with the demand parameters \((\lambda_i, \psi_i, \beta)\) in
+(\ref{arrivalReg}), and contrast these estimates with the ones delivered
+by running a regression (\ref{logReg}). Then I proceed to the parameters
+of the review process, where the focus will be on the contributions
+\((\rho_{1i}^+, \rho_{1i}^-)\) of discounts to the like and dislike
+rates.
 
@@
 \subsubsection{Demand Parameters}\label{demand-parameters-1}}
+
+An ideal set of covariates \(x_{it}\) that I would like to use in
+estimating (\ref{arrivalReg}), given by \[
+A_{it} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
+\] \noindent would be price, the review label, log reviews, age (plus a
+dummy for being at most 14 days old), and a set of day of the week and
+sample week time effects. However, this proved to be computationally
+infeasible. Even though I manage to concentrate out \$2n=\$1812
+game-specific parameters \((\lambda_i, \psi_i)\) from the numerical
+optimization routine, estimation of \(\beta\) still relies on minimizing
+the sum of squared residuals in a \(\dim(\beta)\)-dimensional space. The
+routine would fail to converge to a solution within reasonable
+boundaries, so I had to eliminate some regressors.
+
+\begin{table}
+\caption{Estimates of the Demand Parameters}
+\begin{center}
+\begin{tabular}{l c c c}
+\hline
+ & NLLS & Reg & Full Reg \\
+\hline
+Log Price     & $-0.118^{***}$ & $-0.100^{***}$ & $-0.114^{***}$ \\
+              & $(0.027)$      & $(0.004)$      & $(0.004)$      \\
+Seasonal Sale & $-0.004$       & $0.063^{***}$  &                \\
+              & $(0.012)$      & $(0.003)$      &                \\
+Age           & $-0.137$       & $-0.000^{***}$ & $0.001^{***}$  \\
+              & $(0.458)$      & $(0.000)$      & $(0.000)$      \\
+Age $\le 14$  & $0.081^{**}$   & $0.147^{***}$  & $0.172^{***}$  \\
+              & $(0.041)$      & $(0.006)$      & $(0.006)$      \\
+Log Reviews   & $-0.120^{***}$ & $0.025^{***}$  & $0.024^{***}$  \\
+              & $(0.006)$      & $(0.005)$      & $(0.006)$      \\
+Lag Players   &                & $0.795^{***}$  & $0.790^{***}$  \\
+              &                & $(0.002)$      & $(0.002)$      \\
+No Score      & $0.565^{***}$  & $0.085^{***}$  & $0.090^{***}$  \\
+              & $(0.098)$      & $(0.011)$      & $(0.011)$      \\
+Negative      & $0.053$        & $-0.088^{***}$ & $-0.088^{***}$ \\
+              & $(0.047)$      & $(0.017)$      & $(0.017)$      \\
+M. Positive   & $0.064^{***}$  & $0.058^{***}$  & $0.066^{***}$  \\
+              & $(0.023)$      & $(0.007)$      & $(0.007)$      \\
+Positive      & $0.078^{**}$   & $0.099^{***}$  & $0.095^{***}$  \\
+              & $(0.031)$      & $(0.009)$      & $(0.009)$      \\
+V. Positive   &                &                & $0.118^{***}$  \\
+              &                &                & $(0.009)$      \\
+Ov. Positive  &                &                & $0.142^{***}$  \\
+              &                &                & $(0.011)$      \\
+\hline
+Weekdays      & $\checkmark$        & $\checkmark$        & $\checkmark$        \\
+Week          & $\times$        & $\times$        & $\checkmark$        \\
+Observations  & $355983$   & $355586$   & $355669$   \\
+R$^2$         & $0.930$        & $0.706$        & $0.707$        \\
+\hline
+\multicolumn{4}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\label{demandEstimates}
+\end{center}
+\end{table}
+
+The week effects contribute the most to the dimensionality of the
+problem, as there are 105 weeks in the sample. The reason to include
+these week effects is to account for platform-wide shocks. The biggest
+shocks shared by games on Steam are Seasonal Sales. These sales take
+place around major holidays, and, thus, blend together the increased
+platform-wide demand with the higher quantity demanded caused by the
+plethora of price promotions (depicted in Figure \ref{seasonalSales}).
+To capture these periods in a parsimonious way, I calculated the average
+daily discount in the sample, and labeled the days when the average
+discount exceeded 20\%. Figure \ref{seasonalSalesPeriods} in the
+Appendix shows that my definition tracks closely the spikes in the
+aggregate discounting behavior. I also tried using the raw value of the
+average discount in the sample, but the results remained the same.
+
+Another exclusion I have to make is that of the ``Very Positive'' and
+``Overwhelmingly Positive'' review lables. While the latter is not very
+prevalent in the sample, as is depicted in Figure
+\ref{reviewDescriptivePlots}, the former is by far the most common
+review label. In order to avoid dropping out these observations, I pool
+the ``Very Positive'' and ``Overwhelmingly Positive'' labels together
+with the ``Positive'' label. Recall that the only difference between
+``Positive'' and ``Very Positive'' is whether the game has less or more
+than 50 reviews, so this pooling averages between two similar and
+adjacent review labels.
+
+Thus, the final set of covariates that I use in estimating
+(\ref{arrivalReg}) are: price, review label, log reviews, two age
+variables, and a set of day of the week time effects, and a Seasonal
+Sale dummy. I mentioned in the Identification section that a more
+simplistic, yet more tractable, alternative to estimating the non-linear
+model (\ref{arrivalReg}) is given by equation (\ref{logReg}) \[
+\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}
+\] \noindent To check whether the omitted covariates could be playing a
+crucial role, I will report the results of estimaing (\ref{logReg}) both
+with the ideal set of covariates, and with the covariates used to
+estimate (\ref{arrivalReg}). The results are presented in Table
+\ref{demandEstimates}.
 
@@
 Positive & 0.004 \\    & (0.013) \\    Log Reviews & $-$0.011$^{***}$ \\    & (0.002) \\    Age & 0.0003$^{***}$ \\    & (0.00001) \\    Const & 0.872$^{***}$ \\    & (0.014) \\   \hline \\[-1.8ex]  Time Effects & Weekdays, Week \\ Game Effects & $\times$ \\ Polynomial($t$ W/O Discount) & $d = 2$ \\ Observations & 32,412 \\  R$^{2}$ & 0.397 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  \end{table}
+
 \newpage
@@
 \begin{table}[hp] \centering    \caption{Spikes in Reviews After a Discount}    \label{reviewLag}  \begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & New Reviews \\  \hline \\[-1.8ex]   Discount 0 Days Ago & 1.107$^{***}$ \\    & (0.123) \\    Discount 1 Day Ago & 3.308$^{***}$ \\    & (0.277) \\    Discount 2 Days Ago & 1.397$^{***}$ \\    & (0.139) \\    Discount 3 Days Ago & 0.748$^{***}$ \\    & (0.110) \\    Discount 4 Days Ago & 0.612$^{***}$ \\    & (0.096) \\    Discount 5 Days Ago & 0.397$^{***}$ \\    & (0.104) \\    Discount 6 Days Ago & 0.036 \\    & (0.086) \\    Discount 7 Days Ago & $-$0.160$^{**}$ \\    & (0.073) \\   \hline \\[-1.8ex]  Time Effects & Weekdays, Week \\ Game Effects & $\checkmark$ \\ Observations & 355,983 \\  R$^{2}$ & 0.054 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  \end{table}
+
+\newpage
+
+\hypertarget{definition-of-seasonal-sales}{%
+\subsection{Definition of Seasonal
+Sales}\label{definition-of-seasonal-sales}}
+
+\begin{figure}[h]
+
+{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/seasonal-sales-periods-1}
+
+}
+
+\caption{\label{seasonalSalesPeriods} Seasonal Sales and Discounting Activity.
+Shaded regions are my definition of Seasonal Sales periods.
+The first spike on the graph is excluded because the sample starts with just one game, and I exclude the first 2 weeks from the calculations.}\label{fig:seasonal-sales-periods}
+\end{figure}
 

### 2020-08-12 Analysis/Code/StructuralFunctions.R

@@ -222,7 +222,83 @@ dataFrameToTexreg <- function(regFrame, statsFrame){
 }
 
 
+plmJuliaToTex <- function(r1, r2, juliaFrame, juliaStats){
+  
+  # First the Julia regression
+  coef.row.indices <- seq(1, nrow(juliaFrame), 3)
+  se.row.indices <- seq(2, nrow(juliaFrame), 3)
+  pval.row.indices <- seq(3, nrow(juliaFrame), 3)
+  gofnames <- c("Weekdays", "Week", "Observations", "R$^2$")
+  texregObjects <- list()
 
+  coefs <- juliaFrame[coef.row.indices, 2]
+  coefs[2] <- coefs[2]*100 # I had normalized the age var. for Julia
+  coefnames <- c("Log Price", "Age", "Age $\\le 14$", "No Score",
+                 "Negative", "M. Positive", "Positive", "Log Reviews",
+                 "Seasonal Sale")
+  sevalues <- juliaFrame[se.row.indices, 2]
+  sevalues[2] <- sevalues[2]*100
+  pvalues <- juliaFrame[pval.row.indices, 2]
+  gofvalues <- c(1., 0., juliaStats[2:3, 2])
+  
+  # Create a Texreg object with Julia results. Note: goodnesss 
+  # of fit has to be numeric
+  tr <- createTexreg(coef = coefs, 
+                     coef.names = coefnames,
+                     se = sevalues,
+                     pvalues = pvalues,
+                     gof.names = gofnames,
+                     gof = gofvalues)
+  texregObjects[1] <- list(tr)
+  
+  # Now the first plm regression 
+  coefnames <- c("Lag Players", "Log Price", "No Score",
+                 "Negative", "M. Positive", "Positive", 
+                 "Log Reviews", "Age", "Age $\\le 14$", 
+                 "Seasonal Sale")
+  coefs <- r1$coefficients[1:10]
+  
+  # calculate the s.e. and p. values
+  cov<-vcovHC(r1, method="white1")
+  test <- coeftest(r1, vcov. = cov)
+  sevalues <- test[1:10, 2]
+  pvalues <- test[1:10, 4]
+  f <- summary(r1)
+  
+  tr <- createTexreg(coef = coefs,
+                     coef.names = coefnames,
+                     se = sevalues,
+                     pvalues = pvalues,
+                     gof.names = gofnames,
+                     gof = c(1., 0., length(f$residuals),
+                             f$r.squared[1]))
[…]

### 2020-08-12 Build/Code/CreateSample.R

@@ -235,7 +235,6 @@ panel[, price := round(price/(price[1]/(1-discount[1])), digits = 2), by=ID]
 panel[is.na(price), price := 1.0]
 
 panel <- merge(panel, info[, .(ID, id)], by = "ID")
-panel[, lrev2 := lrev^2]
 panel <- dummy_cols(panel, select_columns = "day")
 
 regressors = c("price", "discSeason", "age", "young", 

### 2020-08-14 Analysis/Code/Paper.Rmd
Added .tex to gitignore
Added all review labels to the Julia code

@@
 ```{r, include=F}
+panel[noScore==T, score := 0]
+panel[noScore==T, reviews := 0]
 reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos + 
-              + noScore + negative + mPositive + realPositive + vPositive + ovPositive +
-              log(reviews) + age + poly(tWODisc, degree = 2) + day + week, data = transPanel)
+             noScore + negative + mPositive + realPositive +
+             vPositive + ovPositive + score +
+             log(reviews+1) + age + poly(tWODisc, degree = 2) + 
+             day + week, data = transPanel)
 cov<-vcovHC(reg1)
@@
                                "Negative", "Mostly Positive", "Positive", "Very Positive",
-                               "Ov. Positive", "Log Reviews", "Age", "Const"),
+                               "Ov. Positive", "Score", "Log Reviews", "Age", "Const"),
           model.numbers = F,
@@
 reg3 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
+              log(needPosDays) + log(needNegDays) + 
+              poly(tWODisc, degree = 2) + log(reviews+1) + score + 
               mPositive + age + young + day + week,
@@
 reg1 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
+               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + 
                mPositive + realPositive + vPositive + age + young + day + week,
@@
 reg2 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) +
+               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + 
                mPositive + realPositive + vPositive + age + young + day + week,
@@
                                   "Log Days to Pos. Tr.", "Log Days to Neg Tr.",
-                                  "Log Reviews", "Mostly Positive", "Positive",
-                                  "Very Positive", "Age", "Age $\\le 14$"),
+                                  "Mostly Positive", "Positive", "Very Positive",
+                                  "Score", "Log Reviews", "Age", "Age $\\le 14$"),
              model.numbers = F,
@@
                       "Poly($t$ W/O Discount, $d=2$) & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\"),
-                    insert.after = c(33,33,33)))
+                    insert.after = c(35,35,35)))
 ```
@@
 
+The week effects contribute the most to the dimensionality of the problem, as there are `r panel[, length(unique(week))]` weeks in the sample.
+The reason to include these week effects is to account for platform-wide shocks.
+The biggest shocks shared by games on Steam are Seasonal Sales.
+These sales take place around major holidays, and, thus, blend together the increased platform-wide demand with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSales}).
+To capture these periods in a parsimonious way, I calculated the average daily discount in the sample, and labeled the days when the average discount exceeded 20\%.
+Figure \ref{seasonalSalesPeriods} in the Appendix shows that my definition tracks closely the spikes in the aggregate discounting behavior.
+I also tried using the raw value of the average discount in the sample, but the results remained the same.
+
+Another exclusion I have to make is that of the “Very Positive” and “Overwhelmingly Positive” review lables.
+While the latter is not very prevalent in the sample, as is depicted in Figure \ref{reviewDescriptivePlots}, the former is by far the most common review label.
+In order to avoid dropping out these observations, I pool the “Very Positive” and “Overwhelmingly Positive” labels together with the “Positive” label.
+Recall that the only difference between “Positive” and “Very Positive” is whether the game has less or more than 50 reviews, so this pooling averages between two similar and adjacent review labels.
+
+Thus, the final set of covariates that I use in estimating (\ref{arrivalReg}) are: price, review label, log reviews, two age variables, and a set of day of the week time effects, and a Seasonal Sale dummy.
+I mentioned in the Identification section that a more simplistic, yet more tractable, alternative to estimating the non-linear model (\ref{arrivalReg}) is given by equation (\ref{logReg})
+$$
+\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}
+$$
+\noindent To check whether the omitted covariates could be playing a crucial role, I report the results of estimaing (\ref{logReg}) both with the ideal set of covariates, and with the covariates used to estimate (\ref{arrivalReg}).
+The results are presented in Table \ref{demandEstimates}.
+
 ```{r cache = F}
@@
 ```{r results='asis'}
-reg1 <- plm(log(number) ~ log(numberLag) + log(price) + noScore +
-              negative + mPositive + positive + log(reviews+1) + 
-              age + young + discSeason + day,
+reg1 <- plm(log(number) ~ log(numberLag) + log(price) +
+            discNewLag + discSeason + noScore + negative + 
+            mPositive +
+            realPositive + vPositive + ovPositive +
+            log(reviews+1) + score + age + young + day,
                 data=panel[price!=0,],
@@
 
-reg2 <- plm(log(number) ~ log(numberLag) + log(price) + noScore + 
-              negative + mPositive + realPositive + vPositive + 
-              ovPositive + log(reviews+1) + age + young + 
-              day + week,
+reg2 <- plm(log(number) ~ log(numberLag) + log(price) +
+              discNewLag + noScore + negative + mPositive +
+              realPositive + vPositive + ovPositive +
+              log(reviews+1) + score + age + young + day + week,
                 data=panel[price!=0,],
@@
                 digits = 3,
-                custom.model.names = c("NLLS", "Reg", "Full Reg"),
-                reorder.coef = c(1, 9, 2, 3, 8, 10, 
-                                 4, 5, 6, 7, 11, 12),
+                custom.model.names = c("NLLS", "Reg", "Ideal Reg"),
+                #reorder.coef = c(1, 9, 2, 3, 8, 10, 
+                #                 4, 5, 6, 7, 11, 12),
                 caption = "Estimates of the Demand Parameters",
@@
 
-The week effects contribute the most to the dimensionality of the problem, as there are `r panel[, length(unique(week))]` weeks in the sample.
-The reason to include these week effects is to account for platform-wide shocks.
-The biggest shocks shared by games on Steam are Seasonal Sales.
-These sales take place around major holidays, and, thus, blend together the increased platform-wide demand with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSales}).
-To capture these periods in a parsimonious way, I calculated the average daily discount in the sample, and labeled the days when the average discount exceeded 20\%.
-Figure \ref{seasonalSalesPeriods} in the Appendix shows that my definition tracks closely the spikes in the aggregate discounting behavior.
-I also tried using the raw value of the average discount in the sample, but the results remained the same.
-
-Another exclusion I have to make is that of the “Very Positive” and “Overwhelmingly Positive” review lables.
-While the latter is not very prevalent in the sample, as is depicted in Figure \ref{reviewDescriptivePlots}, the former is by far the most common review label.
-In order to avoid dropping out these observations, I pool the “Very Positive” and “Overwhelmingly Positive” labels together with the “Positive” label.
-Recall that the only difference between “Positive” and “Very Positive” is whether the game has less or more than 50 reviews, so this pooling averages between two similar and adjacent review labels.
-
-Thus, the final set of covariates that I use in estimating (\ref{arrivalReg}) are: price, review label, log reviews, two age variables, and a set of day of the week time effects, and a Seasonal Sale dummy.
-I mentioned in the Identification section that a more simplistic, yet more tractable, alternative to estimating the non-linear model (\ref{arrivalReg}) is given by equation (\ref{logReg})
-$$
-\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}
-$$
-\noindent To check whether the omitted covariates could be playing a crucial role, I will report the results of estimaing (\ref{logReg}) both with the ideal set of covariates, and with the covariates used to estimate (\ref{arrivalReg}).
-The results are presented in Table \ref{demandEstimates}.
+Column “NLLS” in table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column “Reg” presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates; finally, column “Full Reg” reports the results of estimating the log-regression with the ideal set of covariates.
+The parameters that are of main interest are the price elasticity and the review labels semi-elasticities.
+
+The price coefficient estimates display a strong unanimity across all specifications.
+It is, perhaps, surprising to find the price elasticity of demand to be as low as `r -round(reg1$coefficients[2], 1)`.
+It is tempting to
 
@@
                                 "Game Effects & $\\times$ \\\\",
-                                "Polynomial($t$ W/O Discount) & $d = 2$ \\\\"), insert.after = c(34,34,34)))
+                                "Polynomial($t$ W/O Discount) & $d = 2$ \\\\"), insert.after = c(36,36,36)))
 ```
@@
                           discNewLag5 + discNewLag6 + discNewLag7 + 
-                          negative + mPositive + positive + age + young + day + week,
+                          negative + mPositive + realPositive + vPositive + ovPositive + score + age + young + day + week,
                           data = panel, model = "within")
@@
              model.numbers = F,
-             omit = c("day","week","negative","mPositive","positive","age", "young"),
+             omit = c("day","week","negative","mPositive","realPositive",
+                      "vPositive", "ovPositive", "score", "age", "young"),
              omit.stat=c("f","adj.rsq","ser"),

### 2020-08-14 Analysis/Code/NLLS.jl

@@ -26,24 +26,24 @@ include("estimation_funcs.jl");
 # print_tests(testβ(β̂ , varβ̂))
 
 
-
-panel = "/Users/Dmitry/Steam/Build/Output/AnalysisData/juliaData.csv" |>
+# load the data
+# You would need to change this path for reproduction
+panel = "/Users/Dmitry/Steam_Discounting/Build/Output/juliaData.csv" |>
         load |> DataFrame
-#panel = panel[Not(in.(panel.id, Ref([508, 678, 1270, 1297]))), :]
 
-# convert the Bools
-panel.discNew = (x -> ifelse(x=="TRUE", true, false)).(panel.discNew)
+# convert the Bools from text
 panel.discNewLag = (x -> ifelse(x=="TRUE", true, false)).(panel.discNewLag)
-#panel.exogDiscNew = (x -> ifelse(x=="TRUE", true, false)).(panel.exogDiscNew)
-#panel.exogDiscNewLag = (x -> ifelse(x=="TRUE", true, false)).(panel.exogDiscNewLag)
 panel.noScore = (x -> ifelse(x=="TRUE", true, false)).(panel.noScore)
 panel.negative = (x -> ifelse(x=="TRUE", true, false)).(panel.negative)
 panel.mPositive = (x -> ifelse(x=="TRUE", true, false)).(panel.mPositive)
 panel.positive = (x -> ifelse(x=="TRUE", true, false)).(panel.positive)
+panel.realPositive = (x -> ifelse(x=="TRUE", true, false)).(panel.realPositive)
+panel.vPositive = (x -> ifelse(x=="TRUE", true, false)).(panel.vPositive)
+panel.ovPositive = (x -> ifelse(x=="TRUE", true, false)).(panel.ovPositive)
 panel.young = (x -> ifelse(x=="TRUE", true, false)).(panel.young)
 panel.discSeason = (x -> ifelse(x=="TRUE", true, false)).(panel.discSeason)
 
-# initialize entries of the data frame that will be used later
+# initialize entries of the data frame that will be used later for estimation
 panel.z = zeros(size(panel,1))
 panel.λ = zeros(size(panel,1))
 panel.ψ = zeros(size(panel,1))
@@ -55,20 +55,25 @@ func = (F, G, H, x) -> ssr_concentrated!(F, G, H, x, panel; hessian = true)
 stats = DataFrame(regressor = ["Seasonality", "Observations", "R2"])
 
 # Model 1
-regressors = [:price, :age, :young,
[…]

### 2020-08-14 Analysis/Code/StructuralFunctions.R

@@ -232,12 +232,17 @@ plmJuliaToTex <- function(r1, r2, juliaFrame, juliaStats){
   texregObjects <- list()
 
   coefs <- juliaFrame[coef.row.indices, 2]
-  coefs[2] <- coefs[2]*100 # I had normalized the age var. for Julia
-  coefnames <- c("Log Price", "Age", "Age $\\le 14$", "No Score",
-                 "Negative", "M. Positive", "Positive", "Log Reviews",
+  # I had normalized the age and the score vars for Julia
+  coefs[3] <- coefs[3]*100 
+  coefs[5] <- coefs[5]*10 
+  coefnames <- c("Log Price", "New Discount", "Age", 
+                 "Age $\\le 14$", "Score", "No Score",
+                 "Negative", "M. Positive", "Positive", 
+                 "V. Positive", "Ov. Positive", "Log Reviews",
                  "Seasonal Sale")
   sevalues <- juliaFrame[se.row.indices, 2]
-  sevalues[2] <- sevalues[2]*100
+  sevalues[3] <- sevalues[3]*100
+  sevalues[5] <- sevalues[5]*10
   pvalues <- juliaFrame[pval.row.indices, 2]
   gofvalues <- c(1., 0., juliaStats[2:3, 2])
   
@@ -251,18 +256,20 @@ plmJuliaToTex <- function(r1, r2, juliaFrame, juliaStats){
                      gof = gofvalues)
   texregObjects[1] <- list(tr)
   
-  # Now the first plm regression 
-  coefnames <- c("Lag Players", "Log Price", "No Score",
-                 "Negative", "M. Positive", "Positive", 
-                 "Log Reviews", "Age", "Age $\\le 14$", 
-                 "Seasonal Sale")
-  coefs <- r1$coefficients[1:10]
+  
+  # The  first plm regression 
+  coefnames <- c("Lag Players", "Log Price", "New Discount",
+                 "Seasonal Sale",
+                 "No Score", "Negative", "M. Positive", "Positive", 
+                 "V. Positive", "Ov. Positive", "Log Reviews", 
+                 "Score", "Age", "Age $\\le 14$")
+  coefs <- r1$coefficients[1:14]
   
   # calculate the s.e. and p. values
   cov<-vcovHC(r1, method="white1")
   test <- coeftest(r1, vcov. = cov)
-  sevalues <- test[1:10, 2]
-  pvalues <- test[1:10, 4]
+  sevalues <- test[1:14, 2]
+  pvalues <- test[1:14, 4]
[…]

### 2020-08-14 Build/Code/CreateSample.R

@@ -230,19 +230,20 @@ panel[noScore==T, score := 0]
 panel[noScore==T, reviews := 0]
 panel[, lrev := log(reviews+1)]
 panel[, price := round(price/(price[1]/(1-discount[1])), digits = 2), by=ID]
-
+panel[, numberLag := numberLag/(max(number)), by = ID]
+panel[, number := number/(max(number)), by = ID]
 # price for the game that has a 100% discount in the data
 panel[is.na(price), price := 1.0]
 
 panel <- merge(panel, info[, .(ID, id)], by = "ID")
 panel <- dummy_cols(panel, select_columns = "day")
 
-regressors = c("price", "discSeason", "age", "young", 
+regressors = c("price", "discSeason", "discNewLag", "age", "young", 
                "noScore", "negative", "mPositive", "positive", 
+               "realPositive", "vPositive", "ovPositive", "score",
                "day_Tue", "day_Wed", "day_Thu", "day_Fri", "day_Sat",
                "day_Sun", "lrev")
 
-# for this exercise keep only the stuff that is needed
 panel <- panel[, c("id","t","number","numberLag",regressors), with=F]
 setkey(panel, "id", "t")
 fwrite(panel, file=here("Build", "Output", "juliaData.csv"))

### 2020-08-14 Analysis/Code/Paper.Rmd
Corrected the wrong renormalization of Age and Score variables.

@@
 
+# plmJuliaToTex contains a lot of manual coding, because of the 
+# difference in variable names between Julia and R codes. If you 
+# change the Julia results, or reg1/reg2 regs, you would have to
+# change plmJuliaToTex for this chunk to work properly
 res <- plmJuliaToTex(reg1, reg2, reg.results[, c(1,4)],

### 2020-08-14 Analysis/Code/StructuralFunctions.R

@@ -233,16 +233,17 @@ plmJuliaToTex <- function(r1, r2, juliaFrame, juliaStats){
 
   coefs <- juliaFrame[coef.row.indices, 2]
   # I had normalized the age and the score vars for Julia
-  coefs[3] <- coefs[3]*100 
-  coefs[5] <- coefs[5]*10 
+  coefs[3] <- coefs[3]/100 
+  coefs[5] <- coefs[5]/10 
   coefnames <- c("Log Price", "New Discount", "Age", 
                  "Age $\\le 14$", "Score", "No Score",
                  "Negative", "M. Positive", "Positive", 
                  "V. Positive", "Ov. Positive", "Log Reviews",
                  "Seasonal Sale")
   sevalues <- juliaFrame[se.row.indices, 2]
-  sevalues[3] <- sevalues[3]*100
-  sevalues[5] <- sevalues[5]*10
+  # s.e. also have to be renormalized
+  sevalues[3] <- sevalues[3]/100
+  sevalues[5] <- sevalues[5]/10
   pvalues <- juliaFrame[pval.row.indices, 2]
   gofvalues <- c(1., 0., juliaStats[2:3, 2])
   

### 2020-08-18 Analysis/Code/Paper.Rmd
Updated R to 4.0.2, and then updated the packages in packrat

@@
  output:
-  latex_document:
-    #keep_tex: true
+  pdf_document:
+    keep_tex: true
     fig_height: 2.5
@@
        setspace: ["doublespacing"] # spacing of the paper
-       caption: ["tableposition=top"]
+       caption:
        dsfont: null # indicator function 1
@@
 
-```{r cache = F}
+```{r cache = F, include = F}
+# Load libraries 
+library(here)
+library(devtools) # for installing packages through GitHub, needed for starpolishr
+library(data.table)
+library(stringr)
+library(stringi) # that is wasteful, but it happened
+library(anytime)
+library(dplyr)
+library(magrittr)
+library(fastDummies)
+library(kableExtra)
+library(ggplot2)
+library(ggthemes)
+library(ggridges)
+library(ggpubr)
+library(sandwich)
+library(lmtest)
+library(plm)
+library(stargazer)
+library(starpolishr) # install by devtools::install_github("ChandlerLutz/starpolishr")
+library(texreg)
+library(R.utils)
+
 knitr::opts_chunk$set(echo=F,eval=T,message=F,warning=F,comment=NA,cache=T)
-knitr::opts_chunk$set(fig.pos = "h", out.extra = "", fig.align = "center")
+knitr::opts_chunk$set(fig.pos = "hp", out.extra = "", fig.align = "center")
 

### 2020-08-18 Analysis/Code/StructuralFunctions.R

@@ -12,9 +12,7 @@ my.colors <- c("#1b85b8",  "#cc3399", "#007f66",  "#f27d0c", "#cc2a36")
 # the location if the graph looks better that way
 my.theme <- function(leg.x = 0.75, leg.y = 0.1){
   theme_bw() +
-    theme(panel.background = element_rect(
-      #fill = wes_palette("Moonrise1")[3]
-    ),
+    theme(panel.background = element_rect(),
     text = element_text(family="Times",size=11),
     plot.title = element_text(size=10, family="Times", face="bold",
                               #hjust=0.5,

### 2020-08-18 MakePaper.R

@@ -1,31 +1,8 @@
-# Load libraries 
 library(here)
-library(devtools) # for installing packages through GitHub, needed for starpolishr
-library(data.table)
-library(stringr)
-library(stringi) # that is wasteful, but it happened
-library(anytime)
-library(dplyr)
-library(magrittr)
-library(fastDummies)
-library(kableExtra)
-library(ggplot2)
-library(wesanderson)
-library(ggthemes)
-library(ggridges)
-library(ggpubr)
-library(sandwich)
-library(lmtest)
-library(plm)
-library(stargazer)
-library(starpolishr)
-library(texreg)
 library(R.utils)
 library(rmarkdown)
-
 # If you have obtained raw data from me, you can uncomment this in order to 
-# create the sample yourself.
-
+# create the sample yourself.r
 # source(here("Build", "Code", "CreateSample.R")) 
 
 # Output of Build is Input for Analysis, creating a symbolic link 
@@ -37,10 +14,11 @@ createLink(here("Analysis", "Input"), here("Build", "Output"), skip = T)
 createLink(here("Analysis", "Output", "reviewsBib.bib"), 
            here("Analysis", "Code", "reviewsBib.bib"), skip = T)
 
-# Create the Paper
-render(here("Analysis","Code", "Paper.Rmd"), 
-       output_dir = here("Analysis", "Output"),
-       output_format = "latex_document"
-       )
+# Create the Paper. Choose "latex_document" if there are issues with compiling
+# the final PDF, or choose "html_document", but some latex commands won't work
+# properly
 
+rmarkdown::render(here("Analysis", "Code", "Paper.Rmd"),
+                  output_dir = here("Analysis", "Output"),
+                  output_format = "pdf_document")
 

### 2020-08-20 Analysis/Code/Paper.Rmd
Julia dependency files are now on git.

@@
 library(stringr)
-library(stringi) # that is wasteful, but it happened
+library(stringi) # this is wasteful, but it happened because of collaboration
 library(anytime)
@@
 library(texreg)
-library(R.utils)
 
 knitr::opts_chunk$set(echo=F,eval=T,message=F,warning=F,comment=NA,cache=T)
-knitr::opts_chunk$set(fig.pos = "hp", out.extra = "", fig.align = "center")
-
-source(here("Analysis", "Code", "StructuralFunctions.R"))
+knitr::opts_chunk$set(fig.pos = "htp", out.extra = "", fig.align = "center")
+
+source(here("Analysis", "Code", "AnalysisFunctions.R"))
 load(here("Analysis", "Input", "info.Rda"))
@@
 setnames(transPanel, old = "time", new = "t")
-transPanel <- merge(transPanel, panel[,.(ID, t, age, discount, discNew, tWODisc, reviews, score, noScore, negative, mPositive, positive, realPositive, vPositive, ovPositive, day, week)], by = c("ID","t"))
+transPanel <- merge(transPanel, panel[,.(ID, t, age, discount, discNewLag, tWODisc, reviews, score, noScore, negative, mPositive, positive, realPositive, vPositive, ovPositive, day, week)], by = c("ID","t"))
 setkey(transPanel, "ID", "t", "trID")
@@
 ```{r transition-discount-plot, fig.cap='\\label{discountsTransitions} Discounting By Games Around The Transition.'}
-ggplot(data=transPanel[, .(x=tToTransit, y=100*(discount>0),
+ggplot(data=transPanel[, .(x=tToTransit, y=100*(discount > 0),
                            g=factor(goodTr))],
@@
    stat_summary(fun.data = mean_se,
-               #color = my.colors[1:2],
                size=0.4) +
-   geom_smooth(#color=my.colors[3],
-              size=0.6, se = F) +
+   geom_smooth(size=0.6, se = F) +
    scale_x_continuous(name = "Days After Transition",
@@
 
+```{r cache=F}
+# These are the tricks that I used in the Julia code, and I reuse them here for 
+# consistency. Now that describing the sample is done, these changes will facilitate
+# the analysis without messing up the exposition.
+
+# Score and reviews variables are now 1{score is defined} x Var. This allows to 
+# run regressions without excluding observations with < 10 reviews, for which the 
+# score variable is, technically, undefined.
+panel[noScore==T, score := 0]
+# panel[noScore==T, reviews := 0]
+
+# Instead of using log price, I normalize the price to be between 0 and 1 for 
+# each game. This allows me to include the rare observations with zero prices, unlike
+# the log price specification.
+panel[, price := round(price/(price[1]/(1-discount[1])), digits = 2), by=ID]
+# price for the game that has a 100% discount in the data
+panel[is.na(price), price := 1.0]
+```
+
 ```{r, include=F}
-panel[noScore==T, score := 0]
-panel[noScore==T, reviews := 0]
 reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos + 
@@
 $$
-\noindent would be price, the review label, log reviews, age (plus a dummy for being at most 14 days old), and a set of day of the week and sample week time effects.
+\noindent would be price, review label, score, log reviews, age, and a set of day of the week and sample week time effects.
 However, this proved to be computationally infeasible.
-Even though I manage to concentrate out $2n=$`r 2*info[, .N]` game-specific parameters $(\lambda_i, \psi_i)$ from the numerical optimization routine, estimation of $\beta$ still relies on minimizing the sum of squared residuals in a $\dim(\beta)$-dimensional space.
-The routine would fail to converge to a solution within reasonable boundaries, so I had to eliminate some regressors.
+Even though I manage to concentrate out $2n=$ `r 2*info[, .N]` game-specific parameters $(\lambda_i, \psi_i)$ from the numerical optimization routine, estimation of $\beta$ still relies on minimizing the sum of squared residuals in a $\dim(\beta)$-dimensional space.
+The routine would fail to converge to a solution within reasonable boundaries, so I had to alter the specification.
 
@@
 The biggest shocks shared by games on Steam are Seasonal Sales.
-These sales take place around major holidays, and, thus, blend together the increased platform-wide demand with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSales}).
+These sales take place around major holidays, and, thus, blend together the increased platform-wide demand due to holidays with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSales}).
 To capture these periods in a parsimonious way, I calculated the average daily discount in the sample, and labeled the days when the average discount exceeded 20\%.
@@
 
-Another exclusion I have to make is that of the “Very Positive” and “Overwhelmingly Positive” review lables.
-While the latter is not very prevalent in the sample, as is depicted in Figure \ref{reviewDescriptivePlots}, the former is by far the most common review label.
-In order to avoid dropping out these observations, I pool the “Very Positive” and “Overwhelmingly Positive” labels together with the “Positive” label.
-Recall that the only difference between “Positive” and “Very Positive” is whether the game has less or more than 50 reviews, so this pooling averages between two similar and adjacent review labels.
-
-Thus, the final set of covariates that I use in estimating (\ref{arrivalReg}) are: price, review label, log reviews, two age variables, and a set of day of the week time effects, and a Seasonal Sale dummy.
+The substitution of the week dummies with a Seasonal Sale dummy proved to be sufficient for convergence.
 I mentioned in the Identification section that a more simplistic, yet more tractable, alternative to estimating the non-linear model (\ref{arrivalReg}) is given by equation (\ref{logReg})
@@
 $$
-\noindent To check whether the omitted covariates could be playing a crucial role, I report the results of estimaing (\ref{logReg}) both with the ideal set of covariates, and with the covariates used to estimate (\ref{arrivalReg}).
+\noindent To check whether the omitted week effects could play a crucial role, I report the results of estimaing (\ref{logReg}) both with the ideal set of covariates, and with the covariates used to estimate (\ref{arrivalReg}).
 The results are presented in Table \ref{demandEstimates}.
@@
 effects<-fread(here("Analysis", "Temp", "juliaResults3.csv"))
-effects <- merge(effects, info[, .(id, ID)], by = c("id"), all.x = T)
+effects <- merge(effects, info[, .(id, ID, maxPlayers)], by = c("id"), all.x = T)
+effects[, lambda := maxPlayers * lambda]
 panel <- merge(panel, effects[, .(ID, t, lambda = lambda * z)], by = c("ID", "t"))
-effects <- effects[, .(psi=psi[1], lambda=lambda[1], mz = mean(z)), by = ID]
+effects <- effects[, .(psi=psi[1], mlambda=lambda[1]*mean(z)), by = ID]
 info <- merge(info, effects, by = c("ID"))
@@
 ```{r results='asis'}
-reg1 <- plm(log(number) ~ log(numberLag) + log(price) +
+reg1 <- plm(log(number) ~ log(numberLag) + price +
             discNewLag + discSeason + noScore + negative +
@@
             realPositive + vPositive + ovPositive +
-            log(reviews+1) + score + age + young + day,
-                data=panel[price!=0,],
+            log(reviews+1) + score + age + I(age<=7) + day,
+                data=panel,
             model="within")
 
-reg2 <- plm(log(number) ~ log(numberLag) + log(price) +
+reg2 <- plm(log(number) ~ log(numberLag) + price +
               discNewLag + noScore + negative + mPositive +
               realPositive + vPositive + ovPositive +
-              log(reviews+1) + score + age + young + day + week,
-                data=panel[price!=0,],
+              log(reviews+1) + score + age + I(age<=7) + day + week,
+                data=panel,
             model="within")
@@
                 custom.model.names = c("NLLS", "Reg", "Ideal Reg"),
-                #reorder.coef = c(1, 9, 2, 3, 8, 10,
-                #                 4, 5, 6, 7, 11, 12),
+                reorder.coef = c(1, 2, 6, 7, 8, 9, 10, 11, 5, 12, 3, 4, 13, 14),
                 caption = "Estimates of the Demand Parameters",
@@
 table.top <- str_sub(table, 1, season.location - 1)
-table.bottom <- str_replace_all(table.bottom, "0.000", "\\\\times")
+table.bottom <- str_replace_all(table.bottom, "\\$0.000\\$", "$\\\\times$")
 table.bottom <- str_replace_all(table.bottom, "1.000", "\\\\checkmark")
@@
 
-Column “NLLS” in table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column “Reg” presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates; finally, column “Full Reg” reports the results of estimating the log-regression with the ideal set of covariates.
-The parameters that are of main interest are the price elasticity and the review labels semi-elasticities.
-
-The price coefficient estimates display a strong unanimity across all specifications.
-It is, perhaps, surprising to find the price elasticity of demand to be as low as `r -round(reg1$coefficients[2], 1)`.
-It is tempting to
+Column “NLLS” in Table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column “Reg” presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates; finally, column “Full Reg” reports the results of estimating the log-regression with the ideal set of covariates (using week effects instead of the Seasonal Sale dummy).
+It is readily checked that the difference between the preferred log-regression in column 3 and its restricted analog in column 2 is very small.
+The $R^2$ statistic confirms that week effects do not contribute much to explaining the data, and I conclude that the Seasonal Sale dummy captures the main time-specific shocks well.
+Thus, it is reasonable to say that the omission of the week effects from the nonlinear Model (\ref{arrivalReg}) comes at little cost.
+Now we can concentrate on the estimates of the demand parameters in (\ref{arrivalReg}), presented in the first column, and compare them with the heuristic regression results in the second or third column.
+
+The review labels' semi-elasticities are fairly similar across the specifications.
+All specificaitons exhibit a monotonicity in the effects of different review tiers on sales.
+The "Negative" label is at most as good as "Mixed" (the reference group), with the log-regression results finding a penalty of `r round(-100*reg1$coefficients[6])`% that the "Negative" label entails; the "Mostly Positive" bin increseases sales by `r round(beta.hat[8]*100)`-`r round(100*reg2$coefficients[7])`% compared to the "Mixed" bin.
+At the top end we see that the "Overwhelmingly Positive" label increases demand by `r round(100*reg2$coefficients[10])`-`r round(beta.hat[11]*100)`%.
+These magnitudes are economically sizable and reasonable.
+These results close the gap that my analysis has exhibited so far, and confirms that good reviews are important for sales in the Steam marketplace.
+
+However, columns 1 and 2-3 differ substantially in the estimates of the effect of having no score on sales\footnote{In order to have both the score variable $\in [0,100]$ and a dummy for the "No Score" label I set the former to be equal to 0 when a game has no review label (which happens when it has less than 10 reviews).
+Thus, the score variable really measures the effect of score once the score is defined.}.
+While Model (\ref{arrivalReg}) suggests that having no score is associated with a `r -round(beta.hat[6]*100)`% slower customer arrival than having the “Mixed” review label, its simplified log-regression analogs find the opposite effect of a having `r round(reg1$coefficients[5]*100)`-`r round(reg2$coefficients[4]*100)`% bonus associated with having not enough reviews.
+The latter effect can not possibly be taken at face value, given that the most exlusive review label "Overwhelmingly Positive" only increases sales by  at most `r round(beta.hat[11]*100)`%.
+It would be possible to explain such large estimates by high levels of demand  when the game is young and is likely to have less than 10 reviews, but I control for being “young” by including the dummy for being less than 14 days of age.
+Thus, the coefficient on “No Score” is identified by games that exit this bin later than their first two weeks.
+Such games constitute `r round(100*panel[noScore==T & age>=14, length(unique(ID))]/info[,.N])`% of the sample, and could be different somehow from the rest of the games.
+In any case, it is hard to explain such a big effect.
+One explanation that works is that the log-regression simplification (\ref{logReg}) is misguided, and that one should only trust the coefficients from the structural model of the demand process (\ref{arrivalReg}).
+This latter model finds a penalty of `r -round(beta.hat[6]*100)`% associated with  having no score, which sounds much more reasonable.
+A negative effect could be attributed to customers' reluctance to purchase products of unknown quality.
+If that is the case, this finding suggests a pretty serious cost of asymetric information in this market.
+The same column,
+
+The second imprortant set of variables are the price variables.
+
+```{r fig.cap='\\label{psiLambdaDist} Distribtuions of the continuation probability $\\psi_i$ and average sales $\\bar{\\lambda}_{i}$.'}
+rm(res)
+p1 <- ggplot(data = info[, .(psi)]) +
+  geom_histogram(mapping = aes(x = psi, y = ..density..),
+                 color = "black",
+                 position = "identity",
+                 alpha = 0.9,
+                 binwidth = 0.05,
+                 boundary = 0,
+                 fill = my.colors[1]) +
+  geom_density(mapping = aes(x = psi),
+                 color = "black",
+                 position = "identity",
+                 alpha = 0.4,
+                 fill = my.colors[1]) +
+  scale_x_continuous(name = "Probability",
+                     breaks = seq(0, 10, 2)/10,
+                     minor_breaks = NULL) +
+  scale_y_continuous(name = NULL,
+                     minor_breaks = NULL) +
+  my.theme()
+
+p2 <- ggplot(data = info[, .(x = log(mlambda))]) +
+  geom_histogram(mapping = aes(x = x, y = ..density..),
+                 color = "black",
+                 position = "identity",
+                 alpha = 0.9,
+                 boundary = 0,
+                 fill = my.colors[1]) +
+  geom_density(mapping = aes(x = x),
+                 color = "black",
+                 position = "identity",
+                 alpha = 0.4,
+                 fill = my.colors[1]) +
+  scale_x_continuous(name = "Log Buyers",
+                     minor_breaks = NULL) +
+  scale_y_continuous(name = NULL,
+                     minor_breaks = NULL) +
+  my.theme()
+
+ggarrange(p1, p2, nrow=1, align = "h")
+```
+
+```{r lambda-psi-beamer, fig.width = 8, fig.height = 6, include = FALSE}
+ggarrange(p1, p2, nrow=2, align = "v")
+```
 
 ### Review Parameters
+
+```{r}
+# Notice that rhoPosD is the sum of the parameters I defined
+# in the text, rho_0i^+ and rho_1i^+, but the variance matrix is
+# calculated for the original parameters
+panel[, disc:=c(shift((discount > 0))),
+      by = ID][is.na(disc), disc := F]
+revs <- panel[, .(t, disc, lambda, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]
+revs <- revs[, .(rhoPosD = sum(disc*l) / sum(disc*lambda),
+                 rhoPosND = sum((1-disc)*l) / sum((1-disc)*lambda),
+                 rhoNegD = sum(disc*d) / sum(disc*lambda),
+                 rhoNegND = sum((1-disc)*d) / sum((1-disc)*lambda)),
+              by = ID]
+revs <- revs[!is.na(rhoPosD)]
+
+id.matrix <- matrix(c(1,0,0,1), nrow=2)
+for (id in revs[, ID]){
+   sums <- panel[ID==id, .(disc, lambda)][, sum(lambda), by = disc]
+
+   matND <- matrix(c(sums[disc==F,V1],0,0,0), nrow=2)
+   matD <- matrix(rep(sums[disc==T,V1],4), nrow=2)
+
+   Hpos <- matND/revs[ID==id, rhoPosND] + matD/revs[ID==id, rhoPosD]
+   HposInv <- solve(Hpos, id.matrix)
+
+   Hneg <- matND/revs[ID==id, rhoNegND] + matD/revs[ID==id, rhoNegD]
+   HnegInv <- solve(Hpos, id.matrix)
+
+   revs[ID==id, rhoPos0se := sqrt(HposInv[1,1])]
+   revs[ID==id, rhoPos1se := sqrt(HposInv[2,2])]
+
+   revs[ID==id, rhoNeg0se := sqrt(HnegInv[1,1])]
+   revs[ID==id, rhoNeg1se := sqrt(HnegInv[2,2])]
+}
+
+# label all games with significant rho_1^+
+revs[, posSignif := abs((rhoPosD-rhoPosND)/rhoPos1se) >= 1.96]
+revs[, negSignif := abs((rhoNegD-rhoNegND)/rhoNeg1se) >= 1.96]
+rm(Hpos, Hneg, HnegInv, HposInv)
+```
+
+The main parameters of interest in this section are $(\rho_{1i}^+, \rho_{1i}^-)$, which measure the change in the review rate during discounts that is not due to the increase in mere volume of the reviews.
+The precision with which this parameter could be estimated depends on the number of discount days we observe for game $i$.
+For some games it is impossible to estimate the parameter precisely, either due to their short presence in the sample, insufficient number of discounts, or both.
+However, out of `r info[, .N]` games in the sample, `r revs[posSignif == T, .N]` have a value of $\rho_{1i}^+$ that is statistically different from zero.
+The distributions of $\rho_{1i}^+$ and $\rho_{1i}^-$ for those games are plotted in Figure \ref{likeRatesPlot}.
+
+```{r like-rates, fig.width = 8, fig.height = 6, include = F}
+p1 <- ggplot(data = revs[posSignif==T, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) +
+  ggtitle("Discount Contribution to Likes") +
+  geom_histogram(mapping = aes(x = x, y = ..density..),
+                 color = "black",
+                 position = "identity",
+                 boundary = 0,
+                 alpha = 0.9,
+                 binwidth = 0.25,
+                 fill = my.colors[1]) +
+  geom_density(mapping = aes(x = x),
+                 color = "black",
+                 position = "identity",
+                 alpha = 0.4,
+                 fill = my.colors[1]) +
+  scale_x_continuous(name = "Change in Like Rates",
+                     minor_breaks = NULL) +
+  scale_y_continuous(name = NULL,
+                     breaks = c(0, 1, 2),
+                     minor_breaks = NULL) +
+  my.theme() +
+  coord_cartesian(xlim = c(-0.5, 2))
+
+p2 <- ggplot(data = revs[posSignif==T, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) +
+  ggtitle("Discount Contribution to Dislikes") +
+  geom_histogram(mapping = aes(x = x, y = ..density..),
+                 color = "black",
+                 position = "identity",
+                 boundary = 0,
+                 alpha = 0.9,
+                 fill = my.colors[1]) +
+  geom_density(mapping = aes(x = x),
+                 color = "black",
+                 position = "identity",
+                 alpha = 0.4,
+                 fill = my.colors[1]) +
+  scale_x_continuous(name = "Change in Dislike Rates",
+                     minor_breaks = NULL) +
+  scale_y_continuous(name = NULL,
+                     minor_breaks = NULL) +
+  my.theme() +
+  coord_cartesian(xlim = c(-0.5, 2))
+
+ggarrange(p1, p2, nrow=2, align = "v")
+```
+
+```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$', fig.width=9}
+ggarrange(p1, p2, nrow=1, align = "h")
+```
 

### 2020-08-20 Analysis/Code/AnalysisFunctions.R

@@ -1,0 +1,316 @@
+# Define some variables
+one.year <- anydate("2016-01-01") - anydate("2015-01-01")
+one.day<- anydate("2014-01-02") - anydate("2014-01-01")
+sampleStartDate <- "2017-01-01"
+sampleFinalDate <- anydate("2019-01-01")
+
+# The color scheme
+my.colors <- c("#1b85b8",  "#cc3399", "#007f66",  "#f27d0c", "#cc2a36")
+
+# The style function has two arguments that specify the location of the legend
+# in graphs that need one. The defaults are specified, but feel free to change
+# the location if the graph looks better that way
+my.theme <- function(leg.x = 0.75, leg.y = 0.1){
+  theme_bw() +
+    theme(panel.background = element_rect(),
+    text = element_text(family="Times",size=11),
+    plot.title = element_text(size=10, family="Times", face="bold",
+                              #hjust=0.5,
+                              lineheight=2),
+    axis.title.x = element_text(family="Times",size=11),  
+    axis.title.y = element_text(family="Times",size=11),  
+    legend.text  = element_text(family="Times",size=10),
+    legend.title = element_text(size=10,family="Times",
+                                face="bold"),
+    legend.position = c(leg.x, leg.y),
+    legend.direction = "horizontal",
+    legend.background = element_rect(
+      fill = "white",
+      size = 0.25,
+      linetype="solid",
+      colour = "black"))
+}
+
+splitPriceDuration <- function(x){
+  # Break the duration of the price into 7-day periods, and return the vector with
+  # the number of days (x7) that needs to be added to the date to make sure each
+  # week has a date that we can use to duplicate the price.
+  # Example: price duration is 22 days. Return a vector (7, 14, 21) (days), that
+  # could then be added to the date of the price change. This way every week
+  # will have price information.
+
+  # Add n.weeks rows
+  n.weeks <- x[, p.dur] %>% as.integer(.) %/% 7
+  switch(as.integer(x[, p.dur]) %% 7 == 0, n.weeks <- n.weeks - 1)
+  
+  # 7 day step
+  step <- anydate("1992-01-08") - anydate("1992-01-01")
+  
+  # Duplicate the input row, to create new etnries (and later change the dates)
[…]

### 2020-08-20 Analysis/Code/StructuralFunctions.R

@@ -1,316 +1,0 @@
-# Define some variables
-one.year <- anydate("2016-01-01") - anydate("2015-01-01")
-one.day<- anydate("2014-01-02") - anydate("2014-01-01")
-sampleStartDate <- "2017-01-01"
-sampleFinalDate <- anydate("2019-01-01")
-
-# The color scheme
-my.colors <- c("#1b85b8",  "#cc3399", "#007f66",  "#f27d0c", "#cc2a36")
-
-# The style function has two arguments that specify the location of the legend
-# in graphs that need one. The defaults are specified, but feel free to change
-# the location if the graph looks better that way
-my.theme <- function(leg.x = 0.75, leg.y = 0.1){
-  theme_bw() +
-    theme(panel.background = element_rect(),
-    text = element_text(family="Times",size=11),
-    plot.title = element_text(size=10, family="Times", face="bold",
-                              #hjust=0.5,
-                              lineheight=2),
-    axis.title.x = element_text(family="Times",size=11),  
-    axis.title.y = element_text(family="Times",size=11),  
-    legend.text  = element_text(family="Times",size=10),
-    legend.title = element_text(size=10,family="Times",
-                                face="bold"),
-    legend.position = c(leg.x, leg.y),
-    legend.direction = "horizontal",
-    legend.background = element_rect(
-      fill = "white",
-      size = 0.25,
-      linetype="solid",
-      colour = "black"))
-}
-
-splitPriceDuration <- function(x){
-  # Break the duration of the price into 7-day periods, and return the vector with
-  # the number of days (x7) that needs to be added to the date to make sure each
-  # week has a date that we can use to duplicate the price.
-  # Example: price duration is 22 days. Return a vector (7, 14, 21) (days), that
-  # could then be added to the date of the price change. This way every week
-  # will have price information.
-
-  # Add n.weeks rows
-  n.weeks <- x[, p.dur] %>% as.integer(.) %/% 7
-  switch(as.integer(x[, p.dur]) %% 7 == 0, n.weeks <- n.weeks - 1)
-  
-  # 7 day step
-  step <- anydate("1992-01-08") - anydate("1992-01-01")
-  
-  # Duplicate the input row, to create new etnries (and later change the dates)
[…]

### 2020-08-20 Build/Code/BrushUpCleanData.R

@@ -139,7 +139,6 @@ setkey(info, ID)
 rm(relDates)
 
 # Only keep games we have reviews for
-# load(here("Build","Output","AnalysisData","panelReviews.Rda"))
 ids <- intersect(ids, panelReviews[, unique(game_id)])
 info <- info[ID %in% ids, ]
 info <- info[, firstDayReview:=

### 2020-08-20 Build/Code/CreateSample.R

@@ -1,3 +1,12 @@
+library(here)
+library(data.table)
+library(stringr)
+library(stringi) # that is wasteful, but it happened
+library(anytime)
+library(dplyr)
+library(tidyr)
+library(fastDummies)
+
 # This organizes processed raw data and has some basic filters
 source(here("Build", "Code", "BrushUpCleanData.R"))
 # Load functions
@@ -25,44 +34,49 @@ info<-info[mult==F&multOnline ==F&crossplatform==F&mmo==F&ea==F&
           mult:=NULL][,multOnline:=NULL][,mmo:=NULL][,crossplatform:=F]
 info[,ea:=NULL][,eaExit:=NULL]
 
-# Drop the largest outlier game
-info <- info[ID != 437060, ]
 
 load(here("Build", "Temp", "pricesSample.Rda"))
+# there is an issue with class attributes of the date column, so I convert it
+# to String to be able to add some new rows
+prices[, date2 := toString(date), by = c("ID", "date")]
+prices <- prices[, .(ID = ID, date = date2, price = price, discount = discount)]
 prices[, discNew := discount > 0]
-prices[, date := anydate(date)]
-
 # some manual corrections of scraping mistakes. These mistakes seem to steamDB's,
 # not mine
-prices <- rbind(prices, list(626640, anydate("2017-10-26"), 6.99, 0.00, F))
-setkey(prices, ID, "date")
-prices <- rbind(prices, list(366870, anydate("2018-02-20"), 19.99, 0.00, F))
-prices <- rbind(prices, list(583760, anydate("2017-08-22"), 0.99, 0.00, F))
-prices <- rbind(prices, list(586090, anydate("2017-12-15"), 0.99, 0.00, F))
-prices <- rbind(prices, list(595440, anydate("2018-02-19"), 0.99, 0.00, F))
-prices <- rbind(prices, list(595440, anydate("2018-04-16"), 0.49, 0.51, T))
-prices <- rbind(prices, list(601530, anydate("2017-10-02"), 5.99, 0.00, F))
-prices <- rbind(prices, list(665090, anydate("2017-10-02"), 9.99, 0.00, F))
-prices <- rbind(prices, list(708580, anydate("2018-11-27"), 4.99, 0.00, F))
-prices <- rbind(prices, list(712840, anydate("2017-10-26"), 1.99, 0.00, F))
[…]

### 2020-08-20 MakePaper.R

@@ -2,7 +2,7 @@ library(here)
 library(R.utils)
 library(rmarkdown)
 # If you have obtained raw data from me, you can uncomment this in order to 
-# create the sample yourself.r
+# create the sample yourself
 # source(here("Build", "Code", "CreateSample.R")) 
 
 # Output of Build is Input for Analysis, creating a symbolic link 
@@ -21,4 +21,3 @@ createLink(here("Analysis", "Output", "reviewsBib.bib"),
 rmarkdown::render(here("Analysis", "Code", "Paper.Rmd"),
                   output_dir = here("Analysis", "Output"),
                   output_format = "pdf_document")
-

### 2020-08-21 Analysis/Code/Paper.Rmd
sample

@@
        setspace: ["doublespacing"] # spacing of the paper
-       caption:
+       caption: ["normal"]
        dsfont: null # indicator function 1
@@
 panel[noScore==T, score := 0]
-# panel[noScore==T, reviews := 0]
 
@@
 
+# the rates of review arrivals
 panel[, pRevRate := max(pReviews,na.rm = T)/max(age, na.rm = T), by = ID]
@@
 
+# define how many positive and negative reviews are needed to transition, manualy
+# for every threshold
 R.low <- 0.4
@@
                 digits = 3,
-                custom.model.names = c("NLLS", "Reg", "Ideal Reg"),
+                custom.model.names = c("(1)", "(2)", "(3"),
                 reorder.coef = c(1, 2, 6, 7, 8, 9, 10, 11, 5, 12, 3, 4, 13, 14),
@@
 
-Column “NLLS” in Table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column “Reg” presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates; finally, column “Full Reg” reports the results of estimating the log-regression with the ideal set of covariates (using week effects instead of the Seasonal Sale dummy).
+Column (1) in Table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column (2) presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates; finally, column (3) reports the results of estimating the log-regression with the ideal set of covariates (using week effects instead of the Seasonal Sale dummy).
 It is readily checked that the difference between the preferred log-regression in column 3 and its restricted analog in column 2 is very small.
@@
 The second imprortant set of variables are the price variables.
+First row of Table \ref{demandEstimates} suggests that the price elasticity of demand of very low, between  `r round(-reg1$coefficients[2],2)` and `r round(-beta.hat[1],2)` in absolute value.
+This magnitude is very similar to the price elasticity that @ReimersWaldfogel20 finds studying reviews for books on Amazon.com.
+That paper argues that Amazon has been known to prioritize growth over profit, charging low prices and operating on the inelastic part of the demand curve.
+However, on Steam individual firms choose which prices to charge for their product, and they should have a stronger preference for profit than an entity that is a marketplace, rather than a seller.
+The situation becomes more clear after examining the coefficient on “New Discount”, an indicator variable for the first day after the discount\footnote{I found the effect to be stronger if a one day lag is allowed}.
+On average, a discount leads to a `r round(beta.hat[2]*100)`-`r round(reg2$coefficients[3]*100)`% spike in sales upon introduction.
+An average discount in the sample is `r round(panel[discount>0, mean(discount)]*100)`%, meaning that, based on the estimates in column 1, the effective change in quantity sold upon the introduction of the discount is `r round(beta.hat[2]*100)`%$+$`r round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100))`$%=$`r round(beta.hat[2]*100) + round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100))`%, with the effective elasticity of `r round((round(beta.hat[2]*100) + round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100)))/round(panel[discount>0, mean(discount)]*100),2)`.
+This number looks more reasonable, especially given that the products I study have a zero marginal cost of production, and in a static world firms would set prices at which the demand for their products would be unit-elastic.
+As I have mentioned in the Identification section, the the durable good nature of video games means that forward-looking behavior by the customers could lead to diff
 
@@
 # calculated for the original parameters
-panel[, disc:=c(shift((discount > 0))),
-      by = ID][is.na(disc), disc := F]
-revs <- panel[, .(t, disc, lambda, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]
-revs <- revs[, .(rhoPosD = sum(disc*l) / sum(disc*lambda),
-                 rhoPosND = sum((1-disc)*l) / sum((1-disc)*lambda),
-                 rhoNegD = sum(disc*d) / sum(disc*lambda),
-                 rhoNegND = sum((1-disc)*d) / sum((1-disc)*lambda)),
+
+# Shifting the variables because I am using lag k = 1
+panel[, disc:=c(shift((discount > 0))), by = ID]
+panel[, lam:=shift(lambda), by = ID]
+
+revs <- panel[!(is.na(lam)), .(t, disc, lam, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]
+revs <- revs[, .(rhoPosD = sum(disc*l) / sum(disc*lam),
+                 rhoPosND = sum((1-disc)*l) / sum((1-disc)*lam),
+                 rhoNegD = sum(disc*d) / sum(disc*lam),
+                 rhoNegND = sum((1-disc)*d) / sum((1-disc)*lam)),
               by = ID]
@@
 for (id in revs[, ID]){
-   sums <- panel[ID==id, .(disc, lambda)][, sum(lambda), by = disc]
+   sums <- panel[ID==id, .(disc, lam)][, sum(lam), by = disc]
 
@@
 
-```{r like-rates, fig.width = 8, fig.height = 6, include = F}
-p1 <- ggplot(data = revs[posSignif==T, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) +
+```{r like-rates, include = F}
+p1 <- ggplot(data = revs[, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) +
   ggtitle("Discount Contribution to Likes") +
@@
                  alpha = 0.9,
-                 binwidth = 0.25,
+                 binwidth = 0.1,
                  fill = my.colors[1]) +
@@
 
-p2 <- ggplot(data = revs[posSignif==T, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) +
+p2 <- ggplot(data = revs[, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) +
   ggtitle("Discount Contribution to Dislikes") +
@@
                  boundary = 0,
+                 binwidth = 0.025,
                  alpha = 0.9,
@@
 
-```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$', fig.width=9}
+```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'}
 ggarrange(p1, p2, nrow=1, align = "h")
+```
+
+```{r results = 'asis', warning = FALSE}
+# remove 1% with the highest values of rho_1+ (<=2)
+# and only keep significant coefficients
+panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, rhoPosD, rhoNegD)])
+
+panel[, pos.treatment := (needPos <= 2*band)]
+panel[, neg.treatment := (needNeg <= 2*band)]
+
+reg1 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
+               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
+               mPositive + realPositive + vPositive + age + young + day + week,
+           data = panel[rho1 <= 2 & rho1 >= -0.5 
+                        # ID %in% revs[negSignif == T | posSignif == T, ID], 
+                        ],
+           model = "pooling")
+cov<-vcovHC(reg1, method="white1")
+se1 <- sqrt(diag(cov))
+
+reg2 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
+               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
+               mPositive + realPositive + vPositive + age + young + day + week,
+           data = panel[rho1 <= 2 & rho1 >= -0.5
+                        # ID %in% revs[negSignif == T | posSignif == T, ID], 
+                        ],
+           model = "within")
+cov<-vcovHC(reg2, method = "white1")
+se2 <- sqrt(diag(cov))
+
+star.out<-stargazer(reg1, reg2,
+                    label = "rhoTransDiscReg",
+                    header = FALSE,
+                    title = "Discounts Before Potential Transitions And Firm Heterogeneity",
+                    se=list(se1, se2),
+                    dep.var.labels = c("$\\mathbb{P}(Discount)$"),
+                    # column.labels=c("OLS", "Interaction", "FE", "FE: no $\\rho_{1i}^+$"),
+                    model.numbers = F,
+                    omit = c("tWODisc", "reviews", "noScore", "realPositive", 
+                             "mPositive", "vPositive", "age", "young", "Constant",
+                             "score", "day", "week", "needPosDays", "needNegDays"),
+                    #covariate.labels = ,
+                    order = c("rho1"),
+                    omit.stat=c("f","adj.rsq","ser"),
+                    no.space=T)
 ```

### 2020-08-21 Build/Code/CreateSample.R

@@ -41,8 +41,8 @@ load(here("Build", "Temp", "pricesSample.Rda"))
 prices[, date2 := toString(date), by = c("ID", "date")]
 prices <- prices[, .(ID = ID, date = date2, price = price, discount = discount)]
 prices[, discNew := discount > 0]
-# some manual corrections of scraping mistakes. These mistakes seem to steamDB's,
-# not mine
+# some manual corrections of scraping/data processing mistakes that I discovered very late. 
+# These should really be in the BrushUpCleanData.R, but it is easier to correct them here.
 prices <- rbind(prices, list(626640, ("2017-10-26"), 6.99, 0.00, F))
 prices <- rbind(prices, list(366870, ("2018-02-20"), 19.99, 0.00, F))
 prices <- rbind(prices, list(583760, ("2017-08-22"), 0.99, 0.00, F))
@@ -65,7 +65,7 @@ prices <- rbind(prices, list(543870, ("2018-11-21"), 9.99, 0.5, T))
 prices <- rbind(prices, list(588730, ("2018-11-27"), 5.99, 0.0, F))
 prices <- rbind(prices, list(618970, ("2018-11-27"), 34.99, 0.0, F))
 prices <- rbind(prices, list(634160, ("2018-11-27"), 14.99, 0.0, F))
-
+prices <- rbind(prices, list(841980, "2018-07-06", 9.99, 0.0, F))
 prices[, date := anydate(date)]
 setkey(prices, ID, "date")
 

### 2020-09-03 Analysis/Code/Paper.Rmd
Changed the colors of the graphs

@@
 
-```{r sample-size-hist-vert, include=FALSE}
+```{r sample-size-hist-vert, include=FALSE, fig_height = 5}
 # for beamer
@@
 An important type of curated discounts are the so-called “Seasonal Sales”--big platform-wide events that take place about four times a year around major holidays.
-Figure \ref{seasonalSales} shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving).
+Figure \ref{seasonalSalesPeriods} (in the Appendix) shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving).
 Around `r  round(panel[discSeason==T & discNew == T, .N]/panel[discNew==T, .N]*100)`% of discounts in the sample go live during a Seasonal Sale.
@@
 
-```{r seasonal-sales, fig.cap='\\label{seasonalSales} Fraction of Games in the Sample Running a Promotion.'}
-months1 <- c(-1, 30, 58, 89, 119, 150, 180, 211, 242, 272, 303, 333) + 1
-months2 <- c(333 + 32 + months1, 699 + 31)
-ggplot(data = panel[, .(y=sum(discount > 0)/(.N)), by = t]) +
-  # ggtitle() +
-  geom_line(aes(x = t, y = y),
-            color = my.colors[1],
-            size = 1) +
-  scale_x_continuous(name = NULL,
-                     breaks = c(months1, months2)[seq(1,25,3)], 
-                     labels = months(getDate(c(months1, months2))[seq(1,25,3)], 
-                                     abbreviate=T),
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = "Fraction of Games",
-                     minor_breaks = NULL)  +
-  my.theme(leg.x = 0.25, leg.y = 0.9)
-rm(months1, months2)
-```
-
-The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly.
-Recall that the review score is just the fraction of the positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in.
-Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release.
-On average across games, the standard deviation of the review score (out of one hundred) is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`, with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that.
-The score is only assigned once the game reaches 10 reviews, and once can see that 10 reviews is enough on average keep the score stable.
-The distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, is, then, representative of the situation at other ages.
-
-```{r review-descriptive-plots, fig.width = 6.5, fig.cap='\\label{reviewDescriptivePlots} Distribution of Games by Review Bins and the CDF\'s of Review Arrival Times by Quintiles at 180 Days.'}
+```{r review-descriptive-plots, fig.cap='\\label{reviewDescriptivePlots} Distribution of Games by Review Bins and the CDF\'s of Review Arrival Times by Quintiles at 180 Days.'}
 # Histogram of the bin distribution at the age of 180 days
@@
 ```
+
+The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly.
+Recall that the review score is just the fraction of the positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in.
+Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release.
+On average across games, the standard deviation of the review score (out of one hundred) is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`, with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that.
+The score is only assigned once the game reaches 10 reviews, and one can see that 10 reviews is enough, on average, to keep the score stable.
+The distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, is, then, representative of the situation at other ages.
 
@@
 
+```{r cache=F}
+# These are the tricks that I used in the Julia code, and I reuse them here for 
+# consistency. Now that describing the sample is done, these changes will facilitate
+# the analysis without messing up the exposition.
+
+# Score and reviews variables are now 1{score is defined} x Var. This allows to 
+# run regressions without excluding observations with < 10 reviews, for which the 
+# score variable is, technically, undefined.
+panel[noScore==T, score := 0]
+
+# Instead of using log price, I normalize the price to be between 0 and 1 for 
+# each game. This allows me to include the rare observations with zero prices, unlike
+# the log price specification.
+panel[, price := round(price/(price[1]/(1-discount[1])), digits = 2), by=ID]
+# price for the game that has a 100% discount in the data
+panel[is.na(price), price := 1.0]
+```
+
+```{r, include=F}
+reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos +
+             negative + mPositive + realPositive +
+             vPositive + ovPositive + score +
+             log(reviews+1) + age + poly(tWODisc, degree = 2) + 
+             day + week, data = transPanel)
+cov<-vcovHC(reg1)
+se1 <- sqrt(diag(cov))
+
+star.out.transitions <- stargazer(reg1,
+          label = "transitionReg",
+          table.placement = "hp",
+          header = FALSE,
+          title = "Discounts In The Days Around Transition",
+          se=list(se1),
+          #column.labels=c(),
+          dep.var.labels = c("Discount Probability"),
+          covariate.labels = c("Days to Transition", "Days After Transition",
+                               "Negative", "Mostly Positive", "Positive", "Very Positive",
+                               "Ov. Positive", "Score", "Log Reviews", "Age", "Const"),
+          model.numbers = F,
+          omit = c("day", "week", "tWODisc"),
+          omit.stat=c("f","adj.rsq","ser"),
+          no.space=T)
+```
+
+# Descriptive Evidence
+\label{descriptiveEvidence}
+
+In this section I present evidence that firms use discounting to manage their online reputation, in particular, by running price promotions when they are close to improving their review label.
+For now, let us resort to a very simplistic story of why a firm would be interested in doing that.
+Assume that discounts increase the inflow customers, and that more customers means more reviews.
+Also, take for granted, for now, that better review labels improve sales.
+Then, if a firm is one positive review away from upgrading its review label, it might be tempted to speed things up by giving a discount.
+Similarly, a product that is close to sliding into a worse review bin, could be tempted to run a price promotion, in order to avoid a slump in its reviews.
+I will address this story in more detail in the discussion part of this section, but for now I turn attention to simply establishing that this sort of behavior indeed takes place in the sample.
+
 ```{r transition-discount-plot, fig.cap='\\label{discountsTransitions} Discounting By Games Around The Transition.'}
@@
    my.theme(leg.x = 0.78, leg.y = 0.82)
-```
-
-```{r cache=F}
-# These are the tricks that I used in the Julia code, and I reuse them here for 
-# consistency. Now that describing the sample is done, these changes will facilitate
-# the analysis without messing up the exposition.
-
-# Score and reviews variables are now 1{score is defined} x Var. This allows to 
-# run regressions without excluding observations with < 10 reviews, for which the 
-# score variable is, technically, undefined.
-panel[noScore==T, score := 0]
-
-# Instead of using log price, I normalize the price to be between 0 and 1 for 
-# each game. This allows me to include the rare observations with zero prices, unlike
-# the log price specification.
-panel[, price := round(price/(price[1]/(1-discount[1])), digits = 2), by=ID]
-# price for the game that has a 100% discount in the data
-panel[is.na(price), price := 1.0]
-```
-
-```{r, include=F}
-reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos + 
-             noScore + negative + mPositive + realPositive +
-             vPositive + ovPositive + score +
-             log(reviews+1) + age + poly(tWODisc, degree = 2) + 
-             day + week, data = transPanel)
-cov<-vcovHC(reg1)
-se1 <- sqrt(diag(cov))
-
-star.out.transitions <- stargazer(reg1,
-          label = "transitionReg",
-          table.placement = "hp",
-          header = FALSE,
-          title = "Discounts In The Days Around Transition",
-          se=list(se1),
-          #column.labels=c(),
-          dep.var.labels = c("Discount Probability"),
-          covariate.labels = c("Days to Transition", "Days After Transition", "No Score", 
-                               "Negative", "Mostly Positive", "Positive", "Very Positive",
-                               "Ov. Positive", "Score", "Log Reviews", "Age", "Const"),
-          model.numbers = F,
-          omit = c("day", "week", "tWODisc"),
-          omit.stat=c("f","adj.rsq","ser"),
-          no.space=T)
-```
-
-# Descriptive Evidence
-
-In this section I present evidence that firms use discounting to manage their online reputation, in particular, by running price promotions when they are close to improving their review label.
-For now, let us resort to a very simplistic story of why a firm would be interested in doing that.
-Assume that discounts increase the inflow customers, and that more customers means more reviews.
-Also, take for granted, for now, that better review labels improve sales.
-Then, if a firm is one positive review away from upgrading its review label, it might be tempted to speed things up by giving a discount.
-Similarly, a product that is close to sliding into a worse review bin, could be tempted to run a price promotion, in order to avoid a slump in its reviews.
-I will address this story in more detail in the discussion part of this section, but for now I turn attention to simply establishing that this sort of behavior indeed takes place in the sample.
+rm(transPanel, transitions)
+```
 
@@
 \noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, review bin dummies, and age; $f_i$ is a set of game-level fixed effects, and $\tau_t$ is a set of day of the week effects and sample week time effects.
-These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSales}.
+These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSalesPeriods}.
 We expect $\beta^+$ to be positive, but, when it comes to $\beta^-$, any sign could be rationalized.
@@
 # Empirical Model
+
+\textcolor{red}{Write a small introduction here.}
 
@@
 A deeper problem for identifying the price elasticity of demand lies in defining precisely the elasticity of interest.
-A video game is a durable good, and some consumers could be purchasing it strategically, thinking about the probability and depth of discounts that they could get in the near future.
-A discount that is announced a week in advance will appear to have a strong effect on sales, but only because consumers would abstain from purchasing the game throughout that week.
+A video game is a durable good, and some consumers could be purchasing it strategically, thinking about the probability and depth of discounts that they could get in the near future.In particular, Steam allows users to add any game to their wishlist, which means that they would be notified about promotions affecting that game.
+Later in the results section we will see that the lion's share of sales on a discount take place on the first day of the discount, which is consistent with users waiting for a discount and buying the game when the discount goes live.
 For studying counterfactual price policies one would need to specify a more complicated model of forward-looking consumers, and estimate the fundamentals of their behavior.
@@
 The biggest shocks shared by games on Steam are Seasonal Sales.
-These sales take place around major holidays, and, thus, blend together the increased platform-wide demand due to holidays with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSales}).
+These sales take place around major holidays, and, thus, blend together the increased platform-wide demand due to holidays with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSalesPeriods}).
 To capture these periods in a parsimonious way, I calculated the average daily discount in the sample, and labeled the days when the average discount exceeded 20\%.
@@
 Column (1) in Table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column (2) presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates; finally, column (3) reports the results of estimating the log-regression with the ideal set of covariates (using week effects instead of the Seasonal Sale dummy).
-It is readily checked that the difference between the preferred log-regression in column 3 and its restricted analog in column 2 is very small.
+It is readily checked that the difference between the preferred log-regression in column (3) and its restricted analog in column (2) is very small.
 The $R^2$ statistic confirms that week effects do not contribute much to explaining the data, and I conclude that the Seasonal Sale dummy captures the main time-specific shocks well.
@@
 
-However, columns 1 and 2-3 differ substantially in the estimates of the effect of having no score on sales\footnote{In order to have both the score variable $\in [0,100]$ and a dummy for the "No Score" label I set the former to be equal to 0 when a game has no review label (which happens when it has less than 10 reviews).
+However, columns (1) and (2)-(3) differ substantially in the estimates of the effect of having no score on sales\footnote{In order to have both the score variable $\in [0,100]$ and a dummy for the "No Score" label I set the former to be equal to 0 when a game has no review label (which happens when it has less than 10 reviews).
 Thus, the score variable really measures the effect of score once the score is defined.}.
 While Model (\ref{arrivalReg}) suggests that having no score is associated with a `r -round(beta.hat[6]*100)`% slower customer arrival than having the “Mixed” review label, its simplified log-regression analogs find the opposite effect of a having `r round(reg1$coefficients[5]*100)`-`r round(reg2$coefficients[4]*100)`% bonus associated with having not enough reviews.
-The latter effect can not possibly be taken at face value, given that the most exlusive review label "Overwhelmingly Positive" only increases sales by  at most `r round(beta.hat[11]*100)`%.
+The latter effect can not possibly be taken at face value, given that the most exlusive review label "Overwhelmingly Positive" only increases sales by at most `r round(beta.hat[11]*100)`% compared to the baseline.
 It would be possible to explain such large estimates by high levels of demand  when the game is young and is likely to have less than 10 reviews, but I control for being “young” by including the dummy for being less than 14 days of age.
 Thus, the coefficient on “No Score” is identified by games that exit this bin later than their first two weeks.
-Such games constitute `r round(100*panel[noScore==T & age>=14, length(unique(ID))]/info[,.N])`% of the sample, and could be different somehow from the rest of the games.
-In any case, it is hard to explain such a big effect.
-One explanation that works is that the log-regression simplification (\ref{logReg}) is misguided, and that one should only trust the coefficients from the structural model of the demand process (\ref{arrivalReg}).
+Such games constitute `r round(100*panel[noScore==T & age>=14, length(unique(ID))]/info[,.N])`% of the sample, and are probably different from the rest of the games.
+However, it is still hard to come up with omitted factors that would explain the positive effect of “No Score” on sales found in columns (2)-(3).
+One explanation that works is that the log-regression simplification (\ref{logReg}) is simply misguided, and that one should only trust the coefficients from the structural model of the demand process (\ref{arrivalReg}).
 This latter model finds a penalty of `r -round(beta.hat[6]*100)`% associated with  having no score, which sounds much more reasonable.
@@
 If that is the case, this finding suggests a pretty serious cost of asymetric information in this market.
-The same column,
 
@@
 On average, a discount leads to a `r round(beta.hat[2]*100)`-`r round(reg2$coefficients[3]*100)`% spike in sales upon introduction.
-An average discount in the sample is `r round(panel[discount>0, mean(discount)]*100)`%, meaning that, based on the estimates in column 1, the effective change in quantity sold upon the introduction of the discount is `r round(beta.hat[2]*100)`%$+$`r round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100))`$%=$`r round(beta.hat[2]*100) + round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100))`%, with the effective elasticity of `r round((round(beta.hat[2]*100) + round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100)))/round(panel[discount>0, mean(discount)]*100),2)`.
+An average discount in the sample is `r round(panel[discount>0, mean(discount)]*100)`%, meaning that, based on the estimates in column 1, the effective change in quantity sold upon the introduction of the discount is `r round(beta.hat[2]*100)`% $+$ `r round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100))`% $=$ `r round(beta.hat[2]*100) + round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100))`%, with the implied elasticity of `r round((round(beta.hat[2]*100) + round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100)))/round(panel[discount>0, mean(discount)]*100),2)`.
 This number looks more reasonable, especially given that the products I study have a zero marginal cost of production, and in a static world firms would set prices at which the demand for their products would be unit-elastic.
-As I have mentioned in the Identification section, the the durable good nature of video games means that forward-looking behavior by the customers could lead to diff
+As I have mentioned in the Identification section, the durable good nature of video games means that forward-looking behavior by consumers could lead to different price elasticities for short-lived promotions and long-term price changes.
 
@@
                      minor_breaks = NULL) +
-  my.theme()
+  my.theme() +
+  coord_cartesian(xlim = c(-2, 6))
 
@@
 ```
+
+The second set of demand parameters that I estimate are the game-specific customer arrival 
+rates $\lambda_i$ and the probabilities $\psi_i$ with which active players of game $i$
+continue playing the game. For the ease of interpretation, I present the estimates of 
+$\bar \lambda_{i} := \lambda_i(1+\mathbb{E}[x_{it}]'\beta)$, the average number of sales
+for game $i$ (recall that I can only estimate the part of sales that contributes to the gaming
+activity during peak times). Estimated distributions of these parameters are presented in 
+Figure \ref{psiLambdaDist}. The model produces very well-behaved estimates without any constraints
+imposed in the estimation: there are just
+`r info[psi > 1 | psi <0, .N]` games with estimated values of $\psi_i$ outside of the $[0,1]$
+interval, and only `r round(panel[lambda < 0, .N]/panel[, .N]*100)`% of the observations in 
+the sample predict negative sales. Quite remarkably, the average continuation probability, 
+`r info[, round(mean(psi), 2)]`, is very close to the estimates of its log-regression counterpart 
+in Table \ref{demandEstimates}, line "Lag Players".
 
@@
 
+# calculate s.e.
 id.matrix <- matrix(c(1,0,0,1), nrow=2)
@@
 ```
-
-The main parameters of interest in this section are $(\rho_{1i}^+, \rho_{1i}^-)$, which measure the change in the review rate during discounts that is not due to the increase in mere volume of the reviews.
-The precision with which this parameter could be estimated depends on the number of discount days we observe for game $i$.
-For some games it is impossible to estimate the parameter precisely, either due to their short presence in the sample, insufficient number of discounts, or both.
-However, out of `r info[, .N]` games in the sample, `r revs[posSignif == T, .N]` have a value of $\rho_{1i}^+$ that is statistically different from zero.
-The distributions of $\rho_{1i}^+$ and $\rho_{1i}^-$ for those games are plotted in Figure \ref{likeRatesPlot}.
 
@@
 
+The main parameters of interest in this section are $(\rho_{1i}^+, \rho_{1i}^-)$, which measure the change in the like and dislike rates during discounts.
+The precision with which this parameter could be estimated for game $i$ depends on the number of discount days we observe for that game.
+For some products it is impossible to estimate the parameter precisely, either due to their short presence in the sample, insufficient number of discounts, or both.
+However, out of `r info[, .N]` games in the sample, `r revs[posSignif == T, .N]` have a value of $\rho_{1i}^+$ that is statistically different from zero, and `r revs[negSignif == T, .N]` have a value of $\rho_{1i}^-$ that is statistically different from zero.
+The distributions of $\rho_{1i}^+$ and $\rho_{1i}^-$ all games (excluding some outliers) are plotted in Figure \ref{likeRatesPlot}.
+These plots reveal two patterns.
+The first is that there are a lot of products whose consumers leave positive and/or negative feedback with the same probability on and off a discount, as is reflected in high density of the histograms close to zero.
+Second, the like rates appear to be way more responsive to discounts than the dislike rates.
+
+These findings require some interpretation.
+@Li16 claims “It is by now almost accepted as a stylized fact that offering deal promotion [...] deteriorates local merchants' online reputations”, while my findings seem to suggest that discounts improve review scores.
+Column (2) in Table \ref{reviewLag} in the Appendix presents the results of
+regressing review score on days after a discount (with controls).
+The results suggest that, on average, the review score goes down, not up, in the days following a discount.
+The total effect at best adds up to 1 point out of a 100, but, technically, my findings do not contradict the literature.
+Instead, I show that there is a long tail of products that receive significantly better reviews during a price promotion.
+The main hypothesis that I am developing in this paper is that firms use discounting to manage their online reputation.
+This hypothesis implies that firms that  receive better reviews during price promotions should be more likely to engage in such behavior.
+Thus, my goal in this section is not to study the heterogeneity in the response of the review sentiment to discounts for its own sake, but simply to identify games that my hypothesis predicts should exhibit stronger effects.
+However, my findings present an interesting puzzle for future investigation: how does the (average) negative response of review score to discounts coexist with the distribution of products that seem to receive better reviews during discounts, not worse.
+
+\textcolor{red}{Looks like consumers are more likely to leave reviews during a discount. That could be interesting. Calculate standard errors for that?}
+
+## Revisiting Discounting and Transitions
+
+Now that I have estimated the parameters of the demand and review processes, I am ready to use them to revisit my
+main hypothesis. In Section \ref{descriptiveEvidence} I have established that
+
 ```{r results = 'asis', warning = FALSE}
@@
 \appendix
-
 # Additional Tables and Figures
@@
 \newpage
-## Review Lag
+## Response Of Reviews and Score to Discounts
 Table \ref{reviewLag} presents the results of estimating
-$$NewReviews_{it} =\sum_{l = 0}^{7} \mathds{1}(\text{Disc. } l \text{ days ago})
-+ reviewBin_{it} + age_{it} + young_{it} +  f_i + \tau_t + u_{it}$$
+$$y_{it} \sim \sum_{l = 0}^{7} \mathds{1}(\text{Disc. } l \text{ days ago})
++ Controls_{it} +  f_i + \tau_t + u_{it}$$
+\noindent for $y_{it}$ being the number of new reviews for game $i$ on day $t$ and game $i$'s 
+review score. I use all the same controls as usual: review bin, score (in the first regression),
+log reviews, age, dummy for being less than 14 days old.
+
 ```{r include=F}
@@
 panel[, new.reviews := c(reviews[1], diff(reviews)), by = ID]
+#panel[, score.change := c(NA, diff(score)), by = ID]
 panel[, discNewLag2 := shift(discNewLag), by = ID][is.na(discNewLag2), discNewLag2 := F]
@@
                           discNewLag5 + discNewLag6 + discNewLag7 +
-                          negative + mPositive + realPositive + vPositive + ovPositive + score + age + young + day + week,
+                          negative + mPositive + realPositive + vPositive + ovPositive + 
+                          score + log(reviews + 1) + age + young + day + week,
                           data = panel, model = "within")
@@
 
-star.out <- stargazer(reg1,
+reg2 <- plm(score~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
+                           discNewLag5 + discNewLag6 + discNewLag7 +
+                           negative + mPositive + realPositive + vPositive + ovPositive +
+                           log(reviews + 1) + age + young + day + week,
+                           data = panel, model = "within")
+cov<-vcovHC(reg2, method="white1")
+se2 <- sqrt(diag(cov))
+
+star.out <- stargazer(reg1, reg2, 
              label = "reviewLag",
@@
              header = FALSE,
-             title = "Spikes in Reviews After a Discount",
+             title = "Changes in Review Flows and Score After a Discount",
              se=list(se1),
-             dep.var.labels = c("New Reviews"),
+             dep.var.labels = c("New Reviews", "Score (0-100)"),
              covariate.labels = c("Discount 0 Days Ago", "Discount 1 Day Ago",
@@
              omit = c("day","week","negative","mPositive","realPositive",
-                      "vPositive", "ovPositive", "score", "age", "young"),
+                      "vPositive", "ovPositive", "reviews", "score", "age", "young"),
              omit.stat=c("f","adj.rsq","ser"),
@@
 ```{r results = 'asis'}
-cat(star_insert_row(star.out, c("Time Effects & Weekdays, Week \\\\",
-                                "Game Effects & $\\checkmark$ \\\\"), insert.after = c(28,28)))
+cat(star_insert_row(star.out, c("Weekdays + Week Effects & $\\checkmark$  & $\\checkmark$  \\\\",
+                                "Game Effects & $\\checkmark$  & $\\checkmark$ \\\\"), 
+                    insert.after = c(28,28)))
 ```
@@
                      minor_breaks = NULL) +
-  scale_y_continuous(name = "Fraction of Games",
+  scale_y_continuous(name = "Fraction of Games on Discount",
                      minor_breaks = NULL)  +
@@
 # Mathematical Appendix
+## NLLS estimator of $\beta$
+
+In this appendix I  develop the estimator for the parameters of the model
+\begin{equation}\label{nonLinearLS}
+ y_{it} = \psi_i y_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
+\end{equation}
+with the moment condition $\CE{u_{it}}{y_{it-1}, x_{it}} = 0$.
+This model has \(2n\) \(i\)-specific parameters \((\lambda_i, \psi_i)\) and \(\dim(\beta)\) parameters that are shared by all entities in the panel.
+Estimation is via Non-linear Least Squares.
+The F.O.C.
+of the problem could
+be reduced so as to concentrate out all \((\lambda_i,\psi_i)\) parameters.
+Thus, estimation of \(2n + \dim(\beta)\) parameters reduces to solving a system of non-linear equations for \(\dim(\beta)\) parameters (or solving a NLLS problem of that dimension).
+
+The estimator is defined as the minimizer of the sum of \emph{weighted} squared errors:
+\begin{equation}\label{sse}
+ \hat \theta := \underset{\lambda_i, \psi_i, \beta}{\mathrm{argmin}}\;
+ \sum_{i=1}^n \sum_{t=2}^{T_i} w_i(y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))^2
+\end{equation}
+
+The reason for using weights $w_i$ comes from the large disparities in the sizes of 
+games in my sample.
+A on observation with $y_{it} = 12$, when the model predicts 10, contributes $2^2$ to the sum of squares, while an observation with $y_{it} = 120$ instead of $100$ contributes $20^2$.
+I use $w_i = 1/\max_{t} y_{it}$ as weights, forcing the dependent variable to be between 0 and 1.
+The F.O.C.
+are
+\begin{alignat}{3}
+\label{regFOC1} \psi_i:\; & \sum_{t=2}^{T_i} (y_{it} - \psi_iy_{it-1} - \lambda_i(1+x_{it}'\beta))y_{it-1} &\;=\;& 0\\
+\label{regFOC2} \lambda_i:\; &\sum_{t=2}^{T_i} (y_{it} - \psi_iy_{it-1} - \lambda_i(1+x_{it}'\beta))(1+x_{it}'\beta) &\;=\;& 0 \\
+  \beta:\; & \sum_{i=1}^n \sum_{t=2}^{T_i} w_i (y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))\lambda_ix_{it} &\;=\;& 0
+\end{alignat}
+
+\noindent Notice that the weights drop out of the first two conditions.
+As for the last condition, observe that the moment condition $\CE{u_{it}}{y_{it-1}, x_{it}} = 0$ implies $\EE{x_{it}u_{it}} = 0$, and, thus, the sum in the F.O.C.
+converges to 0 as $n \to \infty$ under any set of weights:
+$$\frac{1}{nT_i}\sum_{i=1}^n \sum_{t=2}^{T_i} w_i(y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))\lambda_ix_{it}
+=
+\frac{1}{n}\sum_{i=1}^n \lambda_i w_i\left(\frac{1}{T_i}\sum_{t=2}^{T_i} u_{it}x_{it}\right) \stackrel{p}{\to}0$$
+In other words, the true value of $\beta$ is identified by the weighted moment conditions.
+
+Conditional on \(\beta\), the F.O.C. for \((\psi_i, \lambda_i)\) are F.O.C.'s of an OLS problem of the form
+\[\min_{\psi_i, \lambda_i}\sum_{t=2}^{T_i} (y_{it} - \psi_i y_{it-1} - \lambda_iz_{it})^2,\]
+where \(z_{it} = (1+x_{it}'\beta)\).
+Defining, in the standard way, \(\tilde{\mathbf X}_i (\beta)\) to be the matrix with row \(t\) given by \([z_{it}, y_{it-1}]\), and \(y_i\) to be the vector of \(y_{it}\)
+observations, we get that the values of \(\hat \lambda_i,\hat \psi_i\) that solve (\ref{regFOC1})-(\ref{regFOC2}) are given by
+\begin{equation}\label{psilambda}
+\begin{bmatrix}
+\hat \lambda_i \\
+\hat \psi_i
+\end{bmatrix}(\beta)
+=
+(\tilde{\mathbf X}_i' (\beta)\tilde{\mathbf X}_i (\beta))^{-1}\tilde{\mathbf X}_i' (\beta)y_i
+\end{equation}
+
+\noindent The estimator \(\hat \beta\) of \(\beta\) is now obtained
+as a solution to
+\begin{equation}\label{concFOC}
+\sum_{i=1}^n \sum_{t=2}^{T_i} w_i(y_{it} - \psi_i(\beta) y_{it-1} - \lambda_i(\beta)(1+x'_{it}\beta))\lambda_i(\beta)x_{it} = 0
+\end{equation}
+In practice I solve the concentrated minimization problem using (\ref{concFOC}) as the gradient.
+
+Supplying an analytic expression for the Hessian matrix has proven to significantly expedite and improve convergence.
+The concentrated out sum of squared errors is $SSE(\beta) = SSE(\beta, \lambda(\beta), \psi(\beta))$, and while the expression for the gradient simplifies to $\partial SSE/\partial \beta$ due to the envelope theorem, the expression for the Hessian is more complex:
+\begin{equation}\label{hessianEq}
+\frac{d SSE}{d^2\beta} = \frac{\partial SSE}{\partial^2 \beta} +
+\sum_i \frac{\partial SSE}{\partial\lambda_i \partial \beta} \left(\frac{d \lambda_i}{d \beta}\right)' +
+\sum_i \frac{\partial SSE}{\partial\psi_i \partial \beta} \left(\frac{d \psi_i}{d \beta}\right)'
+\end{equation}
+
+\noindent The expressions for $\frac{d \lambda_i}{d \beta}$ and $\frac{d \psi_i}{d \beta}$ are obtained by applying the inverse function theorem to (\ref{psilambda}), and the remaining derivatives could be obtained directly.
+
+The asymptotic covariance matrix for \(\hat \theta\) in a nonlinear
+LS problem \(\sum_i (y_i - m(x_i, \theta))^2\) is estimated using the sample analog of
+\begin{equation}
+\mathbf V_\theta = \left(\mathbb{E}\left[m_{\theta i}m_{\theta i}'\right]\right)^{-1}
+                \mathbb{E}\left[m_{\theta i}m_{\theta i}'e_i^2\right]
+                \left(\mathbb{E}\left[m_{\theta i}'m_{\theta i}\right]\right)^{-1},
+\end{equation}
+where
+\(m_{\theta i} = \frac{\partial}{\partial \theta} m(x_i, \theta_0)\),
+\(e_i = y_i - m(x_i, \theta_0)\) [@Hansen20, p.751]. More details could be found in the code.
+
+\newpage
 
@@
 
-\vspace{1em}\noindent *Proof*: We start by showing that $G$ is Poisson.
+\vspace{1em}\noindent \textbf{Proof}: We start by showing that $G$ is Poisson.
 $$
@@
 
-Now the independence part. We are interested in $\PP{G=g, B=b}$, which could be written as
+\noindent Now the independence part. We are interested in $\PP{G=g, B=b}$, which could be written as
 $$\PP{G=g, B=b} = \CP{G=g, B=b}{R=g+b}\PP{R=g+b} =
@@
 =
-P(g; \pi \lambda) P(b; (1-\pi)\lambda)$$
-\begin{flushright}
-$\triangleleft$
-\end{flushright}
+P(g; \pi \lambda) P(b; (1-\pi)\lambda)\; \triangleleft$$
 
 \newpage
-## NLLS estimator of $\beta$
-
-In this appendix I  develop the estimator for the parameters of the model
-\begin{equation}\label{nonLinearLS}
- y_{it} = \psi_i y_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
-\end{equation}
-This model has \(2n\) \(i\)-specific parameters \((\lambda_i, \psi_i)\) and \(\dim(\beta)\) parameters that are shared by all entities in the panel.
-Estimation is via Non-linear Least Squares.
-The F.O.C.
-of the problem could
-be reduced so as to concentrate out all \((\lambda_i,\psi_i)\) parameters.
-Thus, estimation of \(2n + \dim(\beta)\) parameters reduces to solving a system of non-linear equations for \(\dim(\beta)\) parameters (or solving a NLLS problem of that dimension).
-
-The estimator is defined as the minimizer of the sum of squared errors:
-\begin{equation}\label{sse}
- \hat \theta := \underset{\lambda_i, \psi_i, \beta}{\mathrm{argmin}}\;
- \sum_{i=1}^n \sum_{t=2}^{T_i} (y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))^2
-\end{equation}
-The F.O.C. are
-\begin{alignat}{3}
-\label{regFOC1} \psi_i:\; & \sum_{t=2}^{T_i} (y_{it} - \psi_iy_{it-1} - \lambda_i(1+x_{it}'\beta))y_{it-1} &\;=\;& 0\\
-\label{regFOC2} \lambda_i:\; &\sum_{t=2}^{T_i} (y_{it} - \psi_iy_{it-1} - \lambda_i(1+x_{it}'\beta))(1+x_{it}'\beta) &\;=\;& 0 \\
-  \beta:\; & \sum_{i=1}^n \sum_{t=2}^{T_i} (y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))\lambda_ix_{it} &\;=\;& 0
-\end{alignat}
-Conditional on \(\beta\), the F.O.C. for \((\psi_i, \lambda_i)\) are F.O.C.'s of an OLS problem of the form
-\[\min_{\psi_i, \lambda_i}\sum_{t=2}^{T_i} (y_{it} - \psi_i y_{it-1} - \lambda_iz_{it})^2,\]
-where \(z_{it} = (1+x_{it}'\beta)\).
-Defining, in the standard way, \(\tilde{\mathbf Z}_i (\beta)\) to be the matrix with row \(t\) given by \([z_{it+1}, y_{it}]\), and \(y_i\) to be the vector of \(y_{it}\)
-observations, we get that the values of \(\hat \lambda_i,\hat \psi_i\) that solve (\ref{regFOC1})-(\ref{regFOC2}) are given by
-\begin{equation}\label{psilambda}
-\begin{bmatrix}
-\hat \lambda_i \\
-\hat \psi_i
-\end{bmatrix}(\beta)
-=
-(\tilde{\mathbf Z}_i' (\beta)\tilde{\mathbf Z}_i (\beta))^{-1}\tilde{\mathbf Z}_i' (\beta)y_i
-\end{equation}
-
-\noindent The estimator \(\hat \beta\) of \(\beta\) is now obtained
-as a solution to
-\begin{equation}\label{concFOC}
-\sum_{i=1}^n \sum_{t=2}^{T_i} (y_{it} - \psi_i(\beta) y_{it-1} - \lambda_i(\beta)(1+x'_{it}\beta))\lambda_i(\beta)x_{it} = 0
-\end{equation}
-In practice I solve the concentrated minimization problem using (\ref{concFOC}) as the gradient.
-
-Supplying an analytic expression for the Hessian matrix has proven to significantly expedite and improve convergence.
-The concentrated out sum of squared errors is $SSE(\beta) = SSE(\beta, \lambda(\beta), \psi(\beta))$, and while the expression for the gradient simplifies to $\partial SSE/\partial \beta$ due to the envelope theorem, the expression for the Hessian is more complex:
-\begin{equation}\label{hessianEq}
-\frac{d SSE}{d^2\beta} = \frac{\partial SSE}{\partial^2 \beta} +
-\sum_i \frac{\partial SSE}{\partial\lambda_i \partial \beta} \left(\frac{d \lambda_i}{d \beta}\right)' +
-\sum_i \frac{\partial SSE}{\partial\psi_i \partial \beta} \left(\frac{d \psi_i}{d \beta}\right)'
-\end{equation}
-
-\noindent The expressions for $\frac{d \lambda_i}{d \beta}$ and $\frac{d \psi_i}{d \beta}$ are obtained by applying the inverse function theorem to (\ref{psilambda}), and the remaining derivatives could be obtained directly.
-
-The asymptotic covariance matrix for \(\hat \theta\) in a nonlinear
-LS problem \(\sum_i (y_i - m(x_i, \theta))^2\) is estimated using the sample analog of
-\begin{equation}
-\mathbf V_\theta = \left(\mathbb{E}\left[m_{\theta i}m_{\theta i}'\right]\right)^{-1}
-                \mathbb{E}\left[m_{\theta i}m_{\theta i}'e_i^2\right]
-                \left(\mathbb{E}\left[m_{\theta i}'m_{\theta i}\right]\right)^{-1},
-\end{equation}
-where
-\(m_{\theta i} = \frac{\partial}{\partial \theta} m(x_i, \theta_0)\),
-\(e_i = y_i - m(x_i, \theta_0)\) [@Hansen20, p.751]. More details could be found in the code.
-
-\newpage

### 2020-09-03 Analysis/Code/AnalysisFunctions.R

@@ -5,7 +5,7 @@ sampleStartDate <- "2017-01-01"
 sampleFinalDate <- anydate("2019-01-01")
 
 # The color scheme
-my.colors <- c("#1b85b8",  "#cc3399", "#007f66",  "#f27d0c", "#cc2a36")
+my.colors <- c("#1F3D7A",  "##CC0052", "#007f66",  "#f27d0c", "#cc2a36")
 
 # The style function has two arguments that specify the location of the legend
 # in graphs that need one. The defaults are specified, but feel free to change

### 2020-09-09 Analysis/Code/Paper.Rmd
minor changes

@@
 
-\noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, review bin dummies, and age; $f_i$ is a set of game-level fixed effects, and $\tau_t$ is a set of day of the week effects and sample week time effects.
+\noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, score, review bin dummies, and age; $f_i$ is a set of game-level fixed effects, and $\tau_t$ is a set of day of the week effects and sample week time effects.
 These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSalesPeriods}.
@@
 Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg1$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
-The uncertainty about the sign and the significance of the proximity to a potential negative transition is resolved in favor of the prudent approach on the firms' side: the results suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg3$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`-`r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is only present in two out of three specifications.
+The uncertainty about the sign and the significance of the proximity to a potential negative transition is resolved in favor of the prudent approach on the firms' side: the results suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg3$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`-`r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is only significant at 1\% level in two out of three specifications.
 
@@
                 digits = 3,
-                custom.model.names = c("(1)", "(2)", "(3"),
+                custom.model.names = c("(1)", "(2)", "(3)"),
                 reorder.coef = c(1, 2, 6, 7, 8, 9, 10, 11, 5, 12, 3, 4, 13, 14),
@@
 for (id in revs[, ID]){
-   sums <- panel[ID==id, .(disc, lam)][, sum(lam), by = disc]
+   sums <- panel[ID==id, .(disc, lam)][, sum(lam), by=disc][!is.na(disc),]
 
@@
    Hpos <- matND/revs[ID==id, rhoPosND] + matD/revs[ID==id, rhoPosD]
-   HposInv <- solve(Hpos, id.matrix)
+   HposInv <- tryCatch(solve(Hpos, id.matrix),
+                       error = function(x){return(matrix(rep(NA,4), 
+                                                         nrow = 2))})
 
    Hneg <- matND/revs[ID==id, rhoNegND] + matD/revs[ID==id, rhoNegD]
-   HnegInv <- solve(Hpos, id.matrix)
+   HnegInv <- tryCatch(solve(Hneg, id.matrix),
+                       error = function(x){return(matrix(rep(NA,4), 
+                                                         nrow = 2))})
 
@@
 revs[, negSignif := abs((rhoNegD-rhoNegND)/rhoNeg1se) >= 1.96]
+
+# score off discount and score on discount
+revs[, scoreND := rhoPosND/(rhoPosND+rhoNegND)]
+revs[, scoreD := rhoPosD/(rhoPosD+rhoNegD)]
+revs[, score.dif := scoreD - scoreND]
+
 rm(Hpos, Hneg, HnegInv, HposInv)
@@
 
-```{r like-rates, include = F}
+```{r}
+# Game by game test whether reviews during a discount are more positive 
+# (in the score sense) than those off discount
+f <- panel[!is.na(disc), .(disc, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by = ID][, .(n1 = sum(l), n0 = sum(d)), keyby = c("ID", "disc")]
+
+test <- f[,  .(p.val = tryCatch(t.test(c(rep(1, n1[1]), rep(0, n0[1])),
+         c(rep(1, n1[2]), rep(0, n0[2])),
+         alternative = "less")$p.value,
+         error = function(x){-1})), by = ID]
+test[p.val ==-1, p.val := NA]
+discIDs <- test[p.val <=0.05, ID]
+panel[, scoreIsBiggerDisc := (ID %in% test[p.val <= 0.05, ID])]
+
+test <- f[,  .(p.val = tryCatch(t.test(c(rep(1, n1[1]), rep(0, n0[1])),
+         c(rep(1, n1[2]), rep(0, n0[2])),
+         alternative = "greater")$p.value,
+         error = function(x){-1})), by = ID]
+test[p.val ==-1, p.val := NA]
+discIDs <- test[p.val <=0.05, ID]
+panel[, scoreIsLessDisc := (ID %in% test[p.val <= 0.05, ID])]
+```
+
+```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'}
 p1 <- ggplot(data = revs[, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) +
-  ggtitle("Discount Contribution to Likes") +
   geom_histogram(mapping = aes(x = x, y = ..density..),
@@
 p2 <- ggplot(data = revs[, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) +
-  ggtitle("Discount Contribution to Dislikes") +
   geom_histogram(mapping = aes(x = x, y = ..density..),
@@
 
+ggarrange(p1, p2, nrow=1, align = "h")
+```
+
+```{r like-rates, fig.width = 8, fig.height = 6, include = FALSE}
 ggarrange(p1, p2, nrow=2, align = "v")
-```
-
-```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'}
-ggarrange(p1, p2, nrow=1, align = "h")
 ```
@@
 # and only keep significant coefficients
-panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, rhoPosD, rhoNegD)])
+panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, score.dif)])
 
@@
                mPositive + realPositive + vPositive + age + young + day + week,
-           data = panel[rho1 <= 2 & rho1 >= -0.5 
-                        # ID %in% revs[negSignif == T | posSignif == T, ID], 
-                        ],
+           data = panel[rho1 <= 2 & rho1 >= -0.5,],
            model = "pooling")
@@
 reg2 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
+               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
+               mPositive + realPositive + vPositive + age + young + day + week,
+           data = panel[rho1 <= 2 & rho1 >= -0.5 & 
+                        ID %in% revs[negSignif == T | posSignif == T, ID], 
+                        ],
+           model = "pooling")
+cov<-vcovHC(reg2, method="white1")
+se2 <- sqrt(diag(cov))
+
+reg3 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
@@
            model = "within")
-cov<-vcovHC(reg2, method = "white1")
-se2 <- sqrt(diag(cov))
-
-star.out<-stargazer(reg1, reg2,
+cov<-vcovHC(reg3, method = "white1")
+se3 <- sqrt(diag(cov))
+
+reg4 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
+               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
+               mPositive + realPositive + vPositive + age + young + day + week,
+           data = panel[rho1 <= 2 & rho1 >= -0.5 & 
+                        ID %in% revs[negSignif == T | posSignif == T, ID], 
+                        ],
+           model = "within")
+cov<-vcovHC(reg4, method = "white1")
+se4 <- sqrt(diag(cov))
+
+star.out<-stargazer(reg1, reg2, reg3, reg4,
                     label = "rhoTransDiscReg",
@@
                     title = "Discounts Before Potential Transitions And Firm Heterogeneity",
-                    se=list(se1, se2),
+                    se=list(se1, se2, se3, se4),
                     dep.var.labels = c("$\\mathbb{P}(Discount)$"),
-                    # column.labels=c("OLS", "Interaction", "FE", "FE: no $\\rho_{1i}^+$"),
+                    column.labels=c("OLS", "OLS:Signif", "FE", "FE:Signif"),
                     model.numbers = F,
@@
                              "score", "day", "week", "needPosDays", "needNegDays"),
-                    #covariate.labels = ,
+                    covariate.labels = c("$\\rho_1^+$",
+                                         "$\\rho_1^+ \\times$ Pos. Tr.",
+                                         "$\\rho_1^+ \\times$ Neg. Tr.",
+                                         "Pos. Tr.", "Neg. Tr."),
                     order = c("rho1"),
@@
 + Controls_{it} +  f_i + \tau_t + u_{it}$$
-\noindent for $y_{it}$ being the number of new reviews for game $i$ on day $t$ and game $i$'s 
+\noindent for $y_{it}$ being the number of new reviews for game $i$ on day $t$, the ratio of new reviews to the average speed of review arrival, and game $i$'s 
 review score. I use all the same controls as usual: review bin, score (in the first regression),
@@
 
-reg2 <- plm(score~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
+reg2 <- plm(I(new.reviews/(pRevRate+nRevRate)) ~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
+                          discNewLag5 + discNewLag6 + discNewLag7 +
+                          negative + mPositive + realPositive + vPositive + ovPositive + 
+                          score + log(reviews + 1) + age + young + day + week,
+                          data = panel, model = "within")
+cov<-vcovHC(reg2, method="white1")
+se2 <- sqrt(diag(cov))
+
+reg3 <- plm(score ~ discNew + discNewLag + discNewLag2 + discNewLag3 + discNewLag4 +
                            discNewLag5 + discNewLag6 + discNewLag7 +
@@
                            data = panel, model = "within")
-cov<-vcovHC(reg2, method="white1")
-se2 <- sqrt(diag(cov))
-
-star.out <- stargazer(reg1, reg2, 
+cov<-vcovHC(reg3, method="white1")
+se3 <- sqrt(diag(cov))
+
+star.out <- stargazer(reg1, reg2, reg3, 
              label = "reviewLag",
@@
              title = "Changes in Review Flows and Score After a Discount",
-             se=list(se1),
-             dep.var.labels = c("New Reviews", "Score (0-100)"),
+             se=list(se1, se2, se3),
+             dep.var.labels = c("New Reviews", "New Reviews \\%", "Score (0-100)"),
              covariate.labels = c("Discount 0 Days Ago", "Discount 1 Day Ago",

### 2020-09-09 Analysis/Code/AnalysisFunctions.R

@@ -5,7 +5,7 @@ sampleStartDate <- "2017-01-01"
 sampleFinalDate <- anydate("2019-01-01")
 
 # The color scheme
-my.colors <- c("#1F3D7A",  "##CC0052", "#007f66",  "#f27d0c", "#cc2a36")
+my.colors <- c("#1F3D7A",  "#CC0052", "#007f66",  "#f27d0c", "#cc2a36")
 
 # The style function has two arguments that specify the location of the legend
 # in graphs that need one. The defaults are specified, but feel free to change

### 2020-09-09 Analysis/Code/Paper.Rmd
Added no score to transitions

@@
 ```{r}
-transitions <- panel[, .(t, neg=c(NA, diff(negative)),
+transitions <- panel[, .(t, age,
+                    noscore=c(NA, diff(noScore)),
+                    neg=c(NA, diff(negative)),
                     mix=c(NA, diff(mixed)),
@@
                     ovPos=c(NA, diff(ovPositive)),
-                    negative, mixed, mPositive, realPositive,
-                    vPositive, ovPositive), by=ID]
-transitions <- transitions[neg ==-1 | mix ==-1 | 
+                    noScore, negative, mixed, mPositive, 
+                    realPositive, vPositive, ovPositive), by=ID]
+transitions <- transitions[noscore==-1 | neg ==-1 | mix ==-1 | 
                            mpos == -1 | pos == -1 | 
                            vPos == -1 | ovPos == -1, ]
+transitions[noscore==-1, origin := "No Score"]
 transitions[neg==-1, origin := "Negative"]
@@
 transitions[, origin := factor(origin, 
-                               levels = labls[-1],
-                               labels = labls[-1],
+                               levels = labls,
+                               labels = labls,
                                ordered = T)]
@@
 transitions[, goodTr := F]
-transitions[neg==-1 | (mix==-1 & neg!=1) | (mpos == -1 & mix != 1 & neg!= 1) |
-            (pos==-1 & (vPos==1 | ovPos==1)) | (vPos==-1 & ovPos == 1), goodTr := T]
+# based on the estimation of demand, classify any transition from No Score as good
+transitions[noscore==-1 | neg==-1 | (mix==-1 & neg!=1) | (mpos == -1 & mix != 1 & neg!= 1) | (pos==-1 & (vPos==1 | ovPos==1)) | (vPos==-1 & ovPos == 1), 
+            goodTr := T]
 
@@
       transitions[, .(
+         `N/S`= round(100*mean(noScore)),
          Neg = round(100*mean(negative)),
@@
       transitions[, .(
+         `N/S` = sum(noScore),
          Neg = sum(negative),
@@
       caption = "Transition Probability And Count Matrices",
-      align = c('c', "c", "c", "c", "c", "c", "c"),
+      align = c('c', 'c', "c", "c", "c", "c", "c", "c"),
       valign = 't',
@@
       booktabs = T) %>%
-add_header_above(c("Probabilities" = 6, " ","Counts" = 6)) %>%
+add_header_above(c("Probabilities" = 7, " ","Counts" = 7)) %>%
 kable_styling(latex_options = c("scale_down"))
+```
+
+```{r}
+noscore.ids <- transitions[noscore==-1 & age >=10, ID]
 ```
@@
 reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos +
-             negative + mPositive + realPositive +
+             noScore + negative + mPositive + realPositive +
              vPositive + ovPositive + score +
@@
           covariate.labels = c("Days to Transition", "Days After Transition",
-                               "Negative", "Mostly Positive", "Positive", "Very Positive",
+                               "No Score", "Negative", "Mostly Positive", "Positive", "Very Positive",
                                "Ov. Positive", "Score", "Log Reviews", "Age", "Const"),
@@
 
-# define how many positive and negative reviews are needed to transition, manualy
+# define how many positive and negative reviews are needed to transition, manually
 # for every threshold
@@
             realPositive + vPositive + ovPositive +
-            log(reviews+1) + score + age + I(age<=7) + day,
+            log(reviews+1) + score + age + young + day,
                 data=panel,
@@
               realPositive + vPositive + ovPositive +
-              log(reviews+1) + score + age + I(age<=7) + day + week,
+              log(reviews+1) + score + age + young + day + week,
                 data=panel,
@@
 ```{r}
+noscore.ids <- transitions[noscore==-1 & age >=10, ID]
+revs[ID %in% noscore.ids, summary(rhoPosND)]
+```
+
+```{r}
 # Game by game test whether reviews during a discount are more positive 

### 2020-09-10 Analysis/Code/Paper.Rmd
minor change
Added the stylized model

--- 2020-09-09 Analysis/Code/Paper.Rmd
@@
 
-# Descriptive Evidence
-\label{descriptiveEvidence}
-
-In this section I present evidence that firms use discounting to manage their online reputation, in particular, by running price promotions when they are close to improving their review label.
-For now, let us resort to a very simplistic story of why a firm would be interested in doing that.
-Assume that discounts increase the inflow customers, and that more customers means more reviews.
-Also, take for granted, for now, that better review labels improve sales.
-Then, if a firm is one positive review away from upgrading its review label, it might be tempted to speed things up by giving a discount.
-Similarly, a product that is close to sliding into a worse review bin, could be tempted to run a price promotion, in order to avoid a slump in its reviews.
-I will address this story in more detail in the discussion part of this section, but for now I turn attention to simply establishing that this sort of behavior indeed takes place in the sample.
-
-```{r transition-discount-plot, fig.cap='\\label{discountsTransitions} Discounting By Games Around The Transition.'}
-ggplot(data=transPanel[, .(x=tToTransit, y=100*(discount > 0),
-                           g=factor(goodTr))],
-       aes(x=x, y=y)) +
-   geom_vline(xintercept = 0, linetype = "longdash", size = 0.2) +
-   aes(color=g) + 
-   stat_summary(fun.data = mean_se,
-               size=0.4) +
-   geom_smooth(size=0.6, se = F) +
-   scale_x_continuous(name = "Days After Transition",
-                     breaks = seq(-14, 14, 2),
-                     minor_breaks = NULL) +
-   scale_y_continuous(name = "% Of Games Discounting", ) +
-   scale_color_manual(labels = c("Bad", "Good"),
-                      name = "Transition",
-                      values = my.colors) +
-   my.theme(leg.x = 0.78, leg.y = 0.82)
-rm(transPanel, transitions)
-```
-
-The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels are very often preceded by discounts.
-The graph shows that two weeks prior to a transition only 15% of games were on a discount, a number close to the sample average, but that this number more than doubles to around 35% one day before the label change.
-Regression analysis controlling for review label, number of reviews, age, day of the week and week time effects, as well as time since the previous discount, confirms that the association depicted in Figure \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in the Appendix).
-A game is approximately `r round(reg1$coefficients[2]*14*100)` pp more likely to be on a discount on the day of the transition than it is two weeks prior to it, and it is `r round(-reg1$coefficients[3]*14*100)` pp less likely to be on a discount two weeks following the transition.
-Given that the probability for a game to be on a discount on a random day is `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% in the sample, these effects amount to `r round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% and `r round(100*(-reg1$coefficients[3]/panel[, mean((discount > 0), na.rm=T)]))`% changes in the daily probability of a discount, which is quite sizable.
-
-Of course, this finding simply shows a correlation between firms' discounting behavior and review transitions.
-The same pattern could emerge if the causality between the two variables is reversed, i.e.
-the discounts cause transitions, and not the other way around.
-Imagine a hypothetical world in which games are only bought on discounts.
-In this world any action in the data would be preceded (and, to some extent, caused) by a discount.
-In other words, firms could be giving discounts for reasons unrelated to reviews, but transitions sometimes would follow as a result.
-As a matter of fact, suppose that the story I am after is true, and that firms try to achieve transitions  via price promotions.
-In that case, discounts *have* to be able to aid transitioning, making the reverse causality inherent in this setting.
-The analysis behind Figure \ref{discountsTransitions} remains imperfect for yet another reason.
-A discount given when a firm is close to a positive transition is not guaranteed to lead to a transition.
-Similarly, a firm trying to avoid a negative transition by giving a discount might succeed.
-In both cases, the behavior that we are interested in goes undetected if one only studies transitions that took place in the data.
-
-The solution to both problems that I suggest is to study *potential* transitional situations instead of the realized ones.
-First, it solves the reverse causality problem.
-A discount given today can cause a transition tomorrow, but a decision to give a discount can not cause the proximity to a transition that chronologically precedes it.
-Second, it clearly solves the selection issue explained above, when the analysis considers solely the firms that transitioned.
-
-With the focus now on potential transitions, the crucial question is how to define proximity to a transition.
-One approach would be to use the raw review count, and to say that a game is close to upgrading its review label when it needs five (ten, twenty ...) more positive reviews to transition.
-However, given the heterogeneity in the popularity of different games (see Figure \ref{sampleSizeHist}), five extra reviews could be nothing for a very popular game, and hard to acquire for a small game.
-For this reason I use a different approach, that measures proximity by the expected number of days that a game has to wait to accumulate the reviews necessary for a transition.
-In particular, for every game-date pair I first measure how many positive reviews that game needs at the moment to upgrade its review bin, and how many negative reviews that game needs to degrade its review bin.
-In the next step, for each game I calculate the average speed of review arrivals, by simply dividing the number of positive (negative) reviews as of the last day in the sample by the age of the game on that day.
-Knowing the speed of positive and negative review arrivals, and the  number of reviews necessary for a transition, I then define the proximity to a positive (negative) transition to be the expected number of days needed for the game to accumulate the necessary number of positive (negative) reviews, assuming that it does not receive any negative (positive) reviews during that time.
-
-To illustrate this definition, consider an example game with 19 positive reviews and 6 negative reviews at some moment in time.
-This game has a review score of 76\%, and the “Mostly Positive” review label.
-It needs 5 additional positive reviews to secure a score of 80\%, the threshold that would earn it the “Positive” label.
-Similarly, 3 new negative reviews would be sufficient for the game to slide into the “Mixed” review category, as the score would become $19/(25 + 3) \times 100\%= 67\%$, which is less than the $70\%$ required for the “Mostly Positive” bin.
-If this game ends up having 80 positive and 20 negative reviews at the age of 200 days, its last day in the sample, then, on average, it was receiving 0.4 positive and 0.1 negative reviews per day.
-Thus, for a positive transition it requires $5/0.4 = 12.5$ days of only good reviews arriving at this rate.
-Similarly, for a negative transition it requires $3 / 0.1 = 30$ days of only bad reviews arriving at this rate.
-So, for this game I set its proximity to a potential positive transition to be 12.5 days, and its proximity to a potential negative transition to be 30 days.
-
-```{r include = F, cache=F}
-band <- 7
-
-# the rates of review arrivals
-panel[, pRevRate := max(pReviews,na.rm = T)/max(age, na.rm = T), by = ID]
-panel[, nRevRate := max(nReviews,na.rm = T)/max(age, na.rm = T), by = ID]
-
-# define how many positive and negative reviews are needed to transition, manualy
-# for every threshold
-R.low <- 0.4
-R.high <- 0.7
-panel[score < R.high*100 & score >= R.low*100,
-      needPos := ceiling((R.high*reviews-pReviews)/(1-R.high))]
-panel[score < R.high*100 & score >= R.low*100,
-      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
-# corrects for the rounding error caused by machine precision division of, say, 4/10 != 0.4. If you are supposed to be brought exactly to the cutoff, your needNeg is one review more than that
-panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
-
-R.low <- 0.7
-R.high <- 0.8
-panel[score < R.high*100 & score >= R.low*100,
-      needPos := ceiling((R.high*reviews-pReviews)/(1-R.high))]
-panel[score < R.high*100 & score >= R.low*100,
-      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
-panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
-
-panel[pRevRate > 0, needPosDays:=needPos/pRevRate]
-panel[nRevRate > 0, needNegDays:=needNeg/nRevRate]
-panel[, pos.treatment := (needPos <= 2*band)]
-panel[, neg.treatment := (needNeg <= 2*band)]
-
-reg3 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
-              log(needPosDays) + log(needNegDays) +
-              poly(tWODisc, degree = 2) + log(reviews+1) + score +
-              mPositive + age + young + day + week,
-                 data=panel[],
-            model="within")
-cov<-vcovHC(reg3, method="white1")
-se3 <- sqrt(diag(cov))
-
-R.low <- 0.7
-R.high <- 0.8
-panel[score >= R.high*100 & reviews < 50,
-      needPos := 50 - reviews]
-panel[score >= R.high*100 & reviews < 50,
-      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
-panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
-
-R.high <- 0.95
-panel[vPositive == T & score >= R.high*100 & reviews < 500,
-      needPos := 500 - reviews]
-panel[vPositive == T & score >= R.high*100 & reviews < 500,
-      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
-
-panel[score < R.high*100 & vPositive == T,
-      needPos := pmax(ceiling((R.high*reviews-pReviews)/(1-R.high)), 500-reviews)]
-panel[score < R.high*100 & vPositive == T,
-      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
-
-panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
-
-panel[, needPosDays:=needPos/pRevRate]
-panel[nRevRate > 0, needNegDays:=needNeg/nRevRate]
-panel[, pos.treatment := (needPos <= 2*band)]
-panel[, neg.treatment := (needNeg <= 2*band)]
-
-reg1 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
-               mPositive + realPositive + vPositive + age + young + day + week,
-                 data=panel[],
-            model="within")
-cov<-vcovHC(reg1, method="white1")
-se1 <- sqrt(diag(cov))
-
-panel[, pos.treatment := (needPos <= band)]
-panel[, neg.treatment := (needNeg <= band)]
-
-reg2 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
-               mPositive + realPositive + vPositive + age + young + day + week,
-                 data=panel[],
-            model="within")
-cov<-vcovHC(reg2, method="white1")
-se2 <- sqrt(diag(cov))
-
-star.out <- stargazer(reg1, reg2, reg3,
-             label = "potentialTransitionsResults",
-             table.placement = "hp",
-             header = FALSE,
-             title = "Discounts Close to Potential Transitions",
-             se=list(se1, se2, se3),
-             dep.var.labels = c("Discount Probability"),
-             column.labels = c("Full", "1 W. to Tr.", "Simple Tr."),
-             covariate.labels = c("Close to Pos. Transition", "Close to Neg. Transition",
-                                  "Log Days to Pos. Tr.", "Log Days to Neg Tr.",
-                                  "Mostly Positive", "Positive", "Very Positive",
-                                  "Score", "Log Reviews", "Age", "Age $\\le 14$"),
-             model.numbers = F,
-             omit = c("day", "week", "tWODisc"),
-             omit.stat=c("f","adj.rsq","ser"),
-             no.space=T)
-
-```
-
-As the example above shows, it is impossible to consider proximity to a positive transition without taking into account the proximity to a negative transition, at least for moderately sized games.
-If firms' strategies for these types of transitions are different, then studying such transitions separately could attenuate the effect of the proximity to, say, a positive transition, on the discount probability: a firm that is close to upgrading its review bin might not give a discount not because it is a bad way to accomplish that transition, but because that firm is at the same time close to downgrading its review bin, and might prefer to exercise prudence.
-For this reason, I define two “treatment” variables of interest.
-Game $i$ at date $t$ is said to be close to a positive transition, $T_{it}^+ = 1$, if its proximity to a positive transition is less than or equal to `r 2*band` days.
-Similarly, game $i$ at date $t$ is said to be close to a negative transition, $T_{it}^- = 1$, if its proximity to a positive transition is less than or equal to `r 2*band` days.
-The `r 2*band` cutoff is inspired by the maximum duration of custom discounts on Steam, and the patterns of discounting around successful transitions, depicted in Figure \ref{discountsTransitions}.
-To estimate the effect of being close to a review transition on the discounting behavior, I then estimate the following model:
-\begin{equation}\label{potTransitionsReg}
-disc_{it} = \beta^+ T_{it}^+ + \beta^- T_{it}^- + X_{it}\beta + f_i + \tau_t + \varepsilon_{it},
-\end{equation}
-
-\noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, score, review bin dummies, and age; $f_i$ is a set of game-level fixed effects, and $\tau_t$ is a set of day of the week effects and sample week time effects.
-These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSalesPeriods}.
-We expect $\beta^+$ to be positive, but, when it comes to $\beta^-$, any sign could be rationalized.
-A positive sign on  $\beta^-$ would serve as evidence that firms use discounting in order to escape from slumps in their reviews bins, while a negative sign would indicate that, on the contrary, firms on the verge of a bad transition become more prudent with their discounts, trying to not instigate extra purchasing/reviewing activity.
-
-```{r results = 'asis'}
-cat(star_insert_row(star.out,
-                    c("Time Effects: Weekdays, Week &  $\\checkmark$ &  $\\checkmark$ & $\\checkmark$ \\\\",
-                      "Game Effects & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\",
-                      "Poly($t$ W/O Discount, $d=2$) & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\"),
-                    insert.after = c(35,35,35)))
-```
-
-Notice that the inclusion of both the distance to a potential positive, and a potential negative, transition in the regression drops all observations from the lowest ("Negative") and the highest ("Overwhelmingly Positive") review bins, as for games in those bins only one way of review transition is possible.
-However, given that the proportion of such observations in the sample is quite small, this is not a big concern.
-The analysis also excludes the observations with a “No Review Score” label, as I do not want to take a stance on what constitutes an improvement or a deterioration of the review score for such games.
-The results of estimating Equation \ref{potTransitionsReg} are presented in Table \ref{potentialTransitionsResults}.
-The first column is the full specification that uses all observations in the sample (except the omissions just mentioned).
-The second column uses a more stringent definition of proximity to a transition, requiring a game to be `r band`, rather than `r 2*band`, days away from a potential transition to be counted as being “close to a transition”.
-The third column uses only transitions between “Mixed”, “Mostly Positive”, and “Positive” labels, as these are the transitions that rely on the review score only, while “Very Positive” and “Overwhelmingly Positive” require both a certain review score, and a certain number of reviews.\footnote{Technically, a game improving its review score from 79\% to 80\% can transition to both “Positive” and “Very Positive”, so the results in the third column bundle together these types of transitions.}.
-@SorokinStevens20 exclusively uses these simple review bins in their regression discontinuity analysis, precisely in order to avoid the complications that arise from double thresholds required for “Very Positive” and “Overwhelmingly Positive”.
-
-The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion.
-Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg1$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
-The uncertainty about the sign and the significance of the proximity to a potential negative transition is resolved in favor of the prudent approach on the firms' side: the results suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg3$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`-`r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is only significant at 1\% level in two out of three specifications.
-
-## Discussion
-
-It is not unreasonable to say that model \ref{potTransitionsReg} is able to identify the causal effect of the proximity to a review transition on discounting behavior.
-As the sample was selected to include only products with the most stable quality and the lowest number of game updates, the path of the review score is relatively exogenous for the firms.
-Taking its current review score as given, a firm can decide whether to run a price promotion or not, which makes the main independent variables in my analysis exogenous.
-On top of that, model \ref{potTransitionsReg} includes a rich set of controls and fixed effects.
-Some threats to identification still remain, of course.
-One is unobserved marketing interventions preceding discounts.
-If advertisements improves the review score, then, by definition, advertisement would be correlated with the treatment variable, moving games a bit closer to transitions.
-If a discount then follows, as a part of the general marketing plan, rather than to leverage the new proximity to a transition, the positive association between discounting and positive transitions would be spurious.
-Note, however, that it would be more natural to expect firms to roll out all marketing interventions at the same time (i.e., running a price promotion while the game is advertised).
-In that case, the threat to identification vanishes.
-
-I would now like to step back and look at the story behind the behavior that I am documenting.
-Several gaps are not filled yet.
-First, I have not presented evidence that discounting meaningfully increases sales and leads to more reviews.
-Neither have I presented evidence that better review bins increase sales.
-Perhaps, more importantly, I have not discussed why firms should expect customers buying during a discount to leave better reviews than customers paying the regular price.
-If there is no difference between the two groups, then giving a discount when the game is close to a transition is, at best, a gamble.
-In fact, there is some empirical evidence that customers who choose to go to a restaurant because of a promotion tend to leave worse reviews [@ByersEtAl12; @Li16], even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19].
-Theoretically, this effect is ambiguous.
-Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews.
-At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews.
-See, for example, @AcemogluEtAl19.
-
-The results I presented in this section, therefore, lead to the following hypotheses.
-I show that firms give discounts to avoid bad transitions and to facilitate the good ones; thus, it has to be the case that the reviews left on a discount tend to be more positive than the ones left off a discount.
-Second, if that is indeed the case, then the firms that get especially positive reviews during price promotions should be more likely to try to use discounting to manipulate their reviews.
-Heterogeneity between the firms is crucial for the second hypothesis.
-In order to test these hypotheses, and to provide evidence on the effect of discounting on sales and reviewing activity, as well as the effect of reviews on sales, I now turn to formulation and estimation of a structural model demand, reviewing and gaming activity on Steam.
-
-# Empirical Model
+# Empirical Model of Demand
 
@@
 Given that the number of active players “flipping” this coin at the end of day $t-1$ is $A_{it-1}$, this process gives rise to the binomial distribution for the number of exiters.
-
-Every buyer of game $i$ is a potential reviewer.
-I assume that a buyer who buys the game at $t-k$ leaves a positive (negative) review for the game on day $t$ with probability \(r_{it}^+\)	 (\(r_{it}^-\)), and no review otherwise.
-For the reasons I will explain later, I will refer to  $r_{it}^+$ as the *like rate*, and to $r_{it}^-$ as the *dislike rate*.
-The focus of the analysis is on the difference between the reviews left on and off a discount.
-To that end, I parametrize the like and dislike rates to depend on the discounting behavior of the firm as follows.
-
-\begin{assumption}\label{likeDiscountAss}
-The like rate is a linear function of discounts:
-$r_{it}^+ = \rho_{0i}^+ + \rho_{1i}^+ disc_{it-k}$.  The dislike rate is a linear function of discounts: $r_{it}^- = \rho_{0i}^- + \rho_{1i}^- disc_{it-k}$.
-\end{assumption}
-
-\noindent Notice, that a price change affects the reviewing behavior in two ways.
-First, a lower prices increases the inflow of buyers through a higher $\lambda_{it}$.
-This leads to more reviews being left.
-My parametrization allows to further study if the reviewers who bought the game on a discount are more or less likely to leave positive and negative reviews.
-I use a dummy variable $disc_{it-k}$ to measure discounting because this will allow me to derive a closed-form estimator for the  parameters of interest.
 
@@
 However, they could hardly be used as instruments for the price, because they also bring an immense boost in visibility, by the virtue of occupying the prime store main page space.
-
-### Review Parameters
-
-The part of the model describing the reviewing behavior of the buyers is more starightforward.
-Intuitively, the propensity to leave a review on and off a discount (the like and dislike rates $r_{it}^+$, $r_{it}^-$) are identified by the differences in reviews left on and off a discount.
-In fact, this intuition becomes a rigorous proof, as wil be shown shortly.
-
-Following assumption \ref{arrivalAssumptions}, the arrival of buyers for game $i$ on day $t$ follows a Poisson distribution with arrival rate $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$.
-I also assumed that, $k$ days later, each consumer leaves a  positive review with probability $r_{it}^+$, a negative review with probability $r_{it}^-$, and no review otherwise.
-Then, the following proposition is true:
-\begin{proposition}\label{poissonReviews}
-The number of good reviews $G_{it}$ for game $i$ on day $t$ is distributed Poisson with rate $r_{it}^+\lambda_{it-k}$.
-The number of bad reviews $B_{it}$ for game $i$ on day $t$ is distributed Poisson with rate $r_{it}^-\lambda_{it-k}$.
-Moreover, $G_{it}$ and $B_{it}$ are independent.
-\end{proposition}
-
-Proposition \ref{poissonReviews} allows one to easily write down the likelihood for positive and negative reviews separately.
-I will use the positive reviews as the leading example here, but all the findings automatically translate to the negative reviews case as well.
-For every game I observe the history of the review arrivals $\{(g_{it}, b_{it})\}_{t=1}^{T_i}$.
-Since $\PP{G_{it} = g_{it}} = \frac{ (r_{it}^+\lambda_{it-k} )^{g_{it}} }{g_{it}!} e^{ -r_{it-k}^+\lambda_{it-k} }$, the log-likelihood of the history of likes is given by
-\begin{equation}\label{reviewsLikelihood}
-\ell(g_i; r_{it}^+, \lambda_{it-k}) = \sum_{t\ge k} g_{it} \log r_{it}^+\lambda_{it-k} - r_{it}^+\lambda_{it-k} - \log g_{it}!
-\end{equation}
-
-I treat $\lambda_{it}$ as known, because parameters $\lambda_{i}$ and $\beta$ that determine it can be estimated consistently for the majority of games in the sample, given the long time dimension of the panel.
-For now I also take the lag $k$ between the time when the user buys the game and leaves a review for the game to be known.
-The parameters of interest are $(\rho_{0i}^+, \rho_{1i}^+)$, which parametrize the like rate as $r_{it}^+ = \rho_{0i}^+ + \rho_{1i}^+ disc_{it-k}$.
-The likelihood is concave in the parameters, so the parameters are identified as the maximizer of the likelihood.
-Restricting attention to a binary discount variable $disc_{it}$ allows me to derive a closed-form estimator for $(\rho_{0i}^+, \rho_{1i}^+)$.
-During a discount the like rate of game $i$ is $\rho_{0i}^+ + \rho_{1i}^+$, which is consistently estimated as
-\begin{equation}\label{rhohat1}
-\hat \rho_{0i}^+ + \hat\rho_{1i}^+ = \frac{\sum_{t \ge k} disc_{it-k}g_{it}}{\sum_{t\ge k} disc_{it-k}\lambda_{it-k}},
-\end{equation}
-As we can see, the ML-estimator of the like rate during a price promotion is just the ratio of the number of good reviews left on a discount over the expected arrival on that day.
-Similarly, the like rate off a discount can be estimated by
-\begin{equation}\label{rhohat2}
-\hat \rho_{0i}^+ = \frac{\sum_{t\ge k} (1-disc_{it-k})g_{it}}{\sum_{t\ge k} (1-disc_{it-k})\lambda_{it-k}},
-\end{equation}
-with the interpretation that the like rate in the absence of a discount is just a ratio of the reviews left outside of a discount and the expected number of customers outside a discount.
-
-Note that one can use these estimators to estimate the *average review score* on and off a discount, i.e., whether users are relatively more or less likely to leave a good review during a discount.
-For example, without a price promotion, one obtains
-\begin{equation}\label{avReviewScore}
-\frac{\sum_{t\ge k} (1-disc_{it-k})g_{it}}{\sum_{t\ge k} (1-disc_{it-k})g_{it} + \sum_{t\ge k} (1-disc_{it-k})b_{it}}
-=
-\frac{\hat \rho_{0i}^+}{\hat \rho_{0i}^+  + \hat \rho_{0i}^- }
-\end{equation}
-It is intuitively clear that the relative propensity to leave a good, rather than a bad, review should be easily estimable by comparing the ratios of good to bad reviews, without any knowledge of the quantity of games sold.
-This intuition is fully reflected in Equation (\ref{avReviewScore}), where the arrival rates $\lambda_{it-k}$ have disappeared entirely.
-
-The analysis above is complicated by two facts.
-First, for each game I observe the exact review count, but my demand estimates only apply to rush hours.
-If, say, every player leaves a review, and every day there are two new players who play in the morning, and three new players who play in the evening, my data would register 3 players leaving 5 reviews on a daily basis.
-This is the reason why I refer to the values of $(r_{it}^+, r_{it}^-)$ as rates, rather than probabilities (which they are in the model).
-Propositon \ref{poissonReviews}, stating that the number of good reviews on day $t$ for game $i$ is a Poisson random variable with rate $r_{it}^+\lambda_{it-k}$, could be treated as an assumption, rather than a result.
-In that case, nothing constrains the $r_{it}^+$ parameter to be less than 1, and the identification argument goes through in the exactly the same way.
-
-Another problem stems from the fact that the purchase date behind a review is not available to the researcher.
-For that reason, the model features an additional parameter $k$, the lag between purchasing the game and leaving a review, that I assumed to be known.
-To estimate that parameter I leverage the fact that spikes in player activity on the first day of a sale represent new users, and study the review response during the following week in order to uncover the modal lag for leaving a review (see Table \ref{reviewLag} in the Appendix).
-This number turns out to be one day.
-Even though time to posting a review has a non-degenerate distribution, modelling it in a more nuanced way would significantly contribute to complexity: the likelihood of receiving a poisitive review on day 100 would depend on the entire history of buyer arrivals prior to that date.
-Therefore, I proceed using $\hat k = 1$.
 
@@
 
+# Discounting and Review Bin Transitions
+\label{descriptiveEvidence}
+
+## Stylized Model
+
+Consider a firm that has a review status $s \in (0, 1)$.
+A firm can give a discount at cost $c$ that can probabilistically change its status to exceed 1 (an upgrade), to go below 0 (a downgrade), or to remain within the $(0,1)$ band (no change).
+The result depends on whether the additional customers who buy the product on a discount happen to leave more positive or more negative reviews, and on the  weight of hte new reviews relative to the existing ones.
+Assume that with probability $p$ the firm's status becomes $s+x$, and with probability $1-p$ it becomes $s-x$.
+Firm's utility $u(s)$ from having a review status $s \in (0,1)$ is 0, while it earns a utility $u^H$ from the upgraded status and a utility $u^L < 0 < u^H$ from the downgraded status.
+The expected utility from giving a discount is
+\begin{equation}
+  \EE{U(s+X)} = p U(s + x) + (1-p) U(s-x) - c
+\end{equation}
+
+When would the firm be willing to give a discount? Consider a firm with $s > 1/2$, i.e., the one that is close to a review upgrade. For that firm the expected value of giving a discount is 
+$$
+  \EE{U(s+X)} = 
+  \begin{cases}
+  -c & x < 1-s\\
+  p u^H -c & x \in [1-s, s) \\
+  pu^H + (1-p)u^L - c & x \ge s
+  \end{cases}
+$$
+\noindent The firm would choose to give a discount if $\EE{U(s+X)}  > 0$.
+A trivial comparative statics exercise tells us that the firm is more likely to do so if the probability $p$ to get a positive shock to the review status if high, if the payoff $u^H$ of upgrading the status is high, and if the loss from downgrading the status $-u^L$ is low.
+
+What is interesting about this problem, is that the probability of improving the review status $p$ does not have to exceed $1/2$ for the firm to give a discount, i.e., the reviews it gets on a discount could be worse than the reviews it receives off a discount.
+Indeed, if the potential change to the score is moderate ($x \in [1-s, s]$), then a successful outcome leads to a transition, while an unsuccessful outcome leaves the firm with the current review status.
+In this case the firm is not risking anything, and is willing to “pull the plug” simply to gamble on the positive outcome.
+Even if the potential change to the review status is substantial $(x \ge s)$, the firm could still find  it profitable to give a discount and risk the deterioration of its review status if the benefits of having an improved status are large enough.
+Similar conclusions follow for the case of $s < 1/2$, when a firm is closer to a negative transition.
+
+The main takeaway from this stylized model is that the relationship between proximity to transitions and discounting behavior is theoretically ambiguous.
+In the data we can expect to find both firms that are more likely to give a discount when they are close to a transition (gambling to upgrade their status, or trying to escape from the downgrading threshold), and firms that are less likely to discount when close to a transition (the downside risk is too big).
+I will now investigate this relationship in the data, and will use the intuition developed here to interpret the results.
+
+## Empirical Analysis
+
+```{r transition-discount-plot, fig.cap='\\label{discountsTransitions} Discounting By Games Around The Transition.'}
+ggplot(data=transPanel[, .(x=tToTransit, y=100*(discount > 0),
+                           g=factor(goodTr))],
+       aes(x=x, y=y)) +
+   geom_vline(xintercept = 0, linetype = "longdash", size = 0.2) +
+   aes(color=g) + 
+   stat_summary(fun.data = mean_se,
+               size=0.4) +
+   geom_smooth(size=0.6, se = F) +
+   scale_x_continuous(name = "Days After Transition",
+                     breaks = seq(-14, 14, 2),
+                     minor_breaks = NULL) +
+   scale_y_continuous(name = "% Of Games Discounting", ) +
+   scale_color_manual(labels = c("Bad", "Good"),
+                      name = "Transition",
+                      values = my.colors) +
+   my.theme(leg.x = 0.78, leg.y = 0.82)
+rm(transPanel, transitions)
+```
+
+The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels are often preceded by discounts.
+The graph shows that two weeks prior to a transition only `r transPanel[x==-14, round(mean(100*(discount > 0)))]`% of games were on a discount, essentially the sample average, but that this number more than doubles to around `r transPanel[x==-1, round(mean(100*(discount > 0)))]`% one day before the label change.
+Regression analysis controlling for review label, number of reviews, age, day of the week and week time effects, as well as time since the previous discount, confirms that the association depicted in Figure \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in the Appendix).
+A game is approximately `r round(reg1$coefficients[2]*14*100)` pp more likely to be on a discount on the day of the transition than it is two weeks prior to it, and it is `r round(-reg1$coefficients[3]*14*100)` pp less likely to be on a discount two weeks following the transition.
+Given that the probability for a game to be on a discount on a random day is `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% in the sample, these effects amount to `r round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% and `r round(100*(-reg1$coefficients[3]/panel[, mean((discount > 0), na.rm=T)]))`% changes in the daily probability of a discount, which is quite sizable.
+
+Of course, this finding simply shows a correlation between firms' discounting behavior and review transitions.
+The same pattern could emerge if the causality between the two variables is reversed, i.e.
+the discounts cause transitions, and not the other way around.
+Imagine a hypothetical world in which games are only bought on discounts.
+In this world any action in the data would be preceded (and, to some extent, caused) by a discount.
+In other words, firms could be giving discounts for reasons unrelated to reviews, but transitions sometimes would follow as a result.
+As a matter of fact, suppose that the story I am after is true, and that firms try to achieve transitions  via price promotions.
+In that case, discounts *have* to be able to aid transitioning, making the reverse causality inherent in this setting.
+The analysis behind Figure \ref{discountsTransitions} remains imperfect for yet another reason.
+A discount given when a firm is close to a positive transition is not guaranteed to lead to a transition.
+Similarly, a firm trying to avoid a negative transition by giving a discount might succeed.
+In both cases, the behavior that we are interested in goes undetected if one only studies transitions that took place in the data.
+
+The solution to both problems that I suggest is to study *potential* transitional situations instead of the realized ones.
+First, it solves the reverse causality problem.
+A discount given today can cause a transition tomorrow, but a decision to give a discount can not cause the proximity to a transition that chronologically precedes it.
+Second, it clearly solves the selection issue explained above, when the analysis considers solely the firms that transitioned.
+
+With the focus now on potential transitions, the crucial question is how to define proximity to a transition.
+One approach would be to use the raw review count, and to say that a game is close to upgrading its review label when it needs five (ten, twenty ...) more positive reviews to transition.
+However, given the heterogeneity in the popularity of different games (see Figure \ref{sampleSizeHist}), five extra reviews could be nothing for a very popular game, and hard to acquire for a small game.
+For this reason I use a different approach, that measures proximity by the expected number of days that a game has to wait to accumulate the reviews necessary for a transition.
+In particular, for every game-date pair I first measure how many positive reviews that game needs at the moment to upgrade its review bin, and how many negative reviews that game needs to degrade its review bin.
+In the next step, for each game I calculate the average speed of review arrivals, by simply dividing the number of positive (negative) reviews as of the last day in the sample by the age of the game on that day.
+Knowing the speed of positive and negative review arrivals, and the  number of reviews necessary for a transition, I then define the proximity to a positive (negative) transition to be the expected number of days needed for the game to accumulate the necessary number of positive (negative) reviews, assuming that it does not receive any negative (positive) reviews during that time.
+
+To illustrate this definition, consider an example game with 19 positive reviews and 6 negative reviews at some moment in time.
+This game has a review score of 76\%, and the “Mostly Positive” review label.
+It needs 5 additional positive reviews to secure a score of 80\%, the threshold that would earn it the “Positive” label.
+Similarly, 3 new negative reviews would be sufficient for the game to slide into the “Mixed” review category, as the score would become $19/(25 + 3) \times 100\%= 67\%$, which is less than the $70\%$ required for the “Mostly Positive” bin.
+If this game ends up having 80 positive and 20 negative reviews at the age of 200 days, its last day in the sample, then, on average, it was receiving 0.4 positive and 0.1 negative reviews per day.
+Thus, for a positive transition it requires $5/0.4 = 12.5$ days of only good reviews arriving at this rate.
+Similarly, for a negative transition it requires $3 / 0.1 = 30$ days of only bad reviews arriving at this rate.
+So, for this game I set its proximity to a potential positive transition to be 12.5 days, and its proximity to a potential negative transition to be 30 days.
+
+```{r include = F, cache=F}
+band <- 7
+
+# the rates of review arrivals
+panel[, pRevRate := max(pReviews,na.rm = T)/max(age, na.rm = T), by = ID]
+panel[, nRevRate := max(nReviews,na.rm = T)/max(age, na.rm = T), by = ID]
+
+# define how many positive and negative reviews are needed to transition, manually
+# for every threshold
+R.low <- 0.4
+R.high <- 0.7
+panel[score < R.high*100 & score >= R.low*100,
+      needPos := ceiling((R.high*reviews-pReviews)/(1-R.high))]
+panel[score < R.high*100 & score >= R.low*100,
+      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
+# corrects for the rounding error caused by machine precision division of, say, 4/10 != 0.4. If you are supposed to be brought exactly to the cutoff, your needNeg is one review more than that
+panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
+
+R.low <- 0.7
+R.high <- 0.8
+panel[score < R.high*100 & score >= R.low*100,
+      needPos := ceiling((R.high*reviews-pReviews)/(1-R.high))]
+panel[score < R.high*100 & score >= R.low*100,
+      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
+panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
+
+panel[pRevRate > 0, needPosDays:=needPos/pRevRate]
+panel[nRevRate > 0, needNegDays:=needNeg/nRevRate]
+panel[, pos.treatment := (needPos <= 2*band)]
+panel[, neg.treatment := (needNeg <= 2*band)]
+
+reg3 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
+              log(needPosDays) + log(needNegDays) +
+              poly(tWODisc, degree = 2) + log(reviews+1) + score +
+              mPositive + age + young + day + week,
+                 data=panel[],
+            model="within")
+cov<-vcovHC(reg3, method="white1")
+se3 <- sqrt(diag(cov))
+
+R.low <- 0.7
+R.high <- 0.8
+panel[score >= R.high*100 & reviews < 50,
+      needPos := 50 - reviews]
+panel[score >= R.high*100 & reviews < 50,
+      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
+panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
+
+R.high <- 0.95
+panel[vPositive == T & score >= R.high*100 & reviews < 500,
+      needPos := 500 - reviews]
+panel[vPositive == T & score >= R.high*100 & reviews < 500,
+      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
+
+panel[score < R.high*100 & vPositive == T,
+      needPos := pmax(ceiling((R.high*reviews-pReviews)/(1-R.high)), 500-reviews)]
+panel[score < R.high*100 & vPositive == T,
+      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
+
+panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]
+
+panel[, needPosDays:=needPos/pRevRate]
+panel[nRevRate > 0, needNegDays:=needNeg/nRevRate]
+panel[, pos.treatment := (needPos <= 2*band)]
+panel[, neg.treatment := (needNeg <= 2*band)]
+
+reg1 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
+               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
+               mPositive + realPositive + vPositive + age + young + day + week,
+                 data=panel[],
+            model="within")
+cov<-vcovHC(reg1, method="white1")
+se1 <- sqrt(diag(cov))
+
+panel[, pos.treatment := (needPos <= band)]
+panel[, neg.treatment := (needNeg <= band)]
+
+reg2 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
+               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
+               mPositive + realPositive + vPositive + age + young + day + week,
+                 data=panel[],
+            model="within")
+cov<-vcovHC(reg2, method="white1")
+se2 <- sqrt(diag(cov))
+
+star.out <- stargazer(reg1, reg2, reg3,
+             label = "potentialTransitionsResults",
+             table.placement = "hp",
+             header = FALSE,
+             title = "Discounts Close to Potential Transitions",
+             se=list(se1, se2, se3),
+             dep.var.labels = c("Discount Probability"),
+             column.labels = c("Full", "1 W. to Tr.", "Simple Tr."),
+             covariate.labels = c("Close to Pos. Transition", "Close to Neg. Transition",
+                                  "Log Days to Pos. Tr.", "Log Days to Neg Tr.",
+                                  "Log Reviews", "Score", "Mostly Positive",
+                                  "Positive", "Very Positive",
+                                  "Age", "Age $\\le 14$"),
+             model.numbers = F,
+             omit = c("day", "week", "tWODisc"),
+             omit.stat=c("f","adj.rsq","ser"),
+             no.space=T)
+
+```
+
+As the example above shows, it is impossible to consider proximity to a positive transition without taking into account the proximity to a negative transition, at least for moderately sized games.
+If firms' strategies for these types of transitions are different, then studying such transitions separately could attenuate the effect of the proximity to, say, a positive transition, on the discount probability: a firm that is close to upgrading its review bin might not give a discount not because it is a bad way to accomplish that transition, but because that firm is at the same time close to downgrading its review bin, and might prefer to exercise prudence.
+For this reason, I define two “treatment” variables of interest.
+Game $i$ at date $t$ is said to be close to a positive transition, $T_{it}^+ = 1$, if its proximity to a positive transition is less than or equal to `r 2*band` days.
+Similarly, game $i$ at date $t$ is said to be close to a negative transition, $T_{it}^- = 1$, if its proximity to a positive transition is less than or equal to `r 2*band` days.
+The `r 2*band` cutoff is inspired by the maximum duration of custom discounts on Steam, and the patterns of discounting around successful transitions, depicted in Figure \ref{discountsTransitions}.
+To estimate the effect of being close to a review transition on the discounting behavior, I then estimate the following model:
+\begin{equation}\label{potTransitionsReg}
+disc_{it} = \beta^+ T_{it}^+ + \beta^- T_{it}^- + X_{it}\beta + f_i + \tau_t + \varepsilon_{it},
+\end{equation}
+
+\noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, score, review bin dummies, and age; $f_i$ is a set of game-level fixed effects, and $\tau_t$ is a set of day of the week effects and sample week time effects.
+These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSalesPeriods}.
+We expect $\beta^+$ to be positive, but, when it comes to $\beta^-$, any sign could be rationalized.
+A positive sign on  $\beta^-$ would serve as evidence that firms use discounting in order to escape from slumps in their reviews bins, while a negative sign would indicate that, on the contrary, firms on the verge of a bad transition become more prudent with their discounts, trying to not instigate extra purchasing/reviewing activity.
+
+```{r results = 'asis'}
+cat(star_insert_row(star.out,
+                    c("Time Effects: Weekdays, Week &  $\\checkmark$ &  $\\checkmark$ & $\\checkmark$ \\\\",
+                      "Game Effects & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\",
+                      "Poly($t$ W/O Discount, $d=2$) & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\"),
+                    insert.after = c(35,35,35)))
+```
+
+Notice that the inclusion of both the distance to a potential positive, and a potential negative, transition in the regression drops all observations from the lowest ("Negative") and the highest ("Overwhelmingly Positive") review bins, as for games in those bins only one way of review transition is possible.
+However, given that the proportion of such observations in the sample is quite small, this is not a big concern.
+The analysis also excludes the observations with a “No Review Score” label, as I do not want to take a stance on what constitutes an improvement or a deterioration of the review score for such games.
+The results of estimating Equation \ref{potTransitionsReg} are presented in Table \ref{potentialTransitionsResults}.
+The first column is the full specification that uses all observations in the sample (except the omissions just mentioned).
+The second column uses a more stringent definition of proximity to a transition, requiring a game to be `r band`, rather than `r 2*band`, days away from a potential transition to be counted as being “close to a transition”.
+The third column uses only transitions between “Mixed”, “Mostly Positive”, and “Positive” labels, as these are the transitions that rely on the review score only, while “Very Positive” and “Overwhelmingly Positive” require both a certain review score, and a certain number of reviews.\footnote{Technically, a game improving its review score from 79\% to 80\% can transition to both “Positive” and “Very Positive”, so the results in the third column bundle together these types of transitions.}.
+@SorokinStevens20 exclusively uses these simple review bins in their regression discontinuity analysis, precisely in order to avoid the complications that arise from double thresholds required for “Very Positive” and “Overwhelmingly Positive”.
+
+The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion.
+Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg1$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
+The uncertainty about the sign and the significance of the proximity to a potential negative transition is resolved in favor of the prudent approach on the firms' side: the results suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg3$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`-`r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is only significant at 1\% level in two out of three specifications.
+
+## Discussion
+
+It is not unreasonable to say that model \ref{potTransitionsReg} is able to identify the causal effect of the proximity to a review transition on discounting behavior.
+As the sample was selected to include only products with the most stable quality and the lowest number of game updates, the path of the review score is relatively exogenous for the firms.
+Taking its current review score as given, a firm can decide whether to run a price promotion or not, which makes the main independent variables in my analysis exogenous.
+On top of that, model \ref{potTransitionsReg} includes a rich set of controls and fixed effects.
+Some threats to identification still remain, of course.
+One is unobserved marketing interventions preceding discounts.
+If advertisements improves the review score, then, by definition, advertisement would be correlated with the treatment variable, moving games a bit closer to transitions.
+If a discount then follows, as a part of the general marketing plan, rather than to leverage the new proximity to a transition, the positive association between discounting and positive transitions would be spurious.
+Note, however, that it would be more natural to expect firms to roll out all marketing interventions at the same time (i.e., running a price promotion while the game is advertised).
+In that case, the threat to identification vanishes.
+
+I would now like to step back and look at the story behind the behavior that I am documenting.
+Several gaps are not filled yet.
+First, I have not presented evidence that discounting meaningfully increases sales and leads to more reviews.
+Neither have I presented evidence that better review bins increase sales.
+Perhaps, more importantly, I have not discussed why firms should expect customers buying during a discount to leave better reviews than customers paying the regular price.
+If there is no difference between the two groups, then giving a discount when the game is close to a transition is, at best, a gamble.
+In fact, there is some empirical evidence that customers who choose to go to a restaurant because of a promotion tend to leave worse reviews [@ByersEtAl12; @Li16], even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19].
+Theoretically, this effect is ambiguous.
+Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews.
+At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews.
+See, for example, @AcemogluEtAl19.
+
+The results I presented in this section, therefore, lead to the following hypotheses.
+I show that firms give discounts to avoid bad transitions and to facilitate the good ones; thus, it has to be the case that the reviews left on a discount tend to be more positive than the ones left off a discount.
+Second, if that is indeed the case, then the firms that get especially positive reviews during price promotions should be more likely to try to use discounting to manipulate their reviews.
+Heterogeneity between the firms is crucial for the second hypothesis.
+In order to test these hypotheses, and to provide evidence on the effect of discounting on sales and reviewing activity, as well as the effect of reviews on sales, I now turn to formulation and estimation of a structural model demand, reviewing and gaming activity on Steam.
+
+Every buyer of game $i$ is a potential reviewer.
+I assume that a buyer who buys the game at $t-k$ leaves a positive (negative) review for the game on day $t$ with probability \(r_{it}^+\)	 (\(r_{it}^-\)), and no review otherwise.
+For the reasons I will explain later, I will refer to  $r_{it}^+$ as the *like rate*, and to $r_{it}^-$ as the *dislike rate*.
+The focus of the analysis is on the difference between the reviews left on and off a discount.
+To that end, I parametrize the like and dislike rates to depend on the discounting behavior of the firm as follows.
+
+\begin{assumption}\label{likeDiscountAss}
+The like rate is a linear function of discounts:
+$r_{it}^+ = \rho_{0i}^+ + \rho_{1i}^+ disc_{it-k}$.  The dislike rate is a linear function of discounts: $r_{it}^- = \rho_{0i}^- + \rho_{1i}^- disc_{it-k}$.
+\end{assumption}
+
+\noindent Notice, that a price change affects the reviewing behavior in two ways.
+First, a lower prices increases the inflow of buyers through a higher $\lambda_{it}$.
+This leads to more reviews being left.
+My parametrization allows to further study if the reviewers who bought the game on a discount are more or less likely to leave positive and negative reviews.
+I use a dummy variable $disc_{it-k}$ to measure discounting because this will allow me to derive a closed-form estimator for the  parameters of interest.
+
+### Review Parameters
+
+The part of the model describing the reviewing behavior of the buyers is more starightforward.
+Intuitively, the propensity to leave a review on and off a discount (the like and dislike rates $r_{it}^+$, $r_{it}^-$) are identified by the differences in reviews left on and off a discount.
+In fact, this intuition becomes a rigorous proof, as wil be shown shortly.
+
+Following assumption \ref{arrivalAssumptions}, the arrival of buyers for game $i$ on day $t$ follows a Poisson distribution with arrival rate $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$.
+I also assumed that, $k$ days later, each consumer leaves a  positive review with probability $r_{it}^+$, a negative review with probability $r_{it}^-$, and no review otherwise.
+Then, the following proposition is true:
+\begin{proposition}\label{poissonReviews}
+The number of good reviews $G_{it}$ for game $i$ on day $t$ is distributed Poisson with rate $r_{it}^+\lambda_{it-k}$.
+The number of bad reviews $B_{it}$ for game $i$ on day $t$ is distributed Poisson with rate $r_{it}^-\lambda_{it-k}$.
+Moreover, $G_{it}$ and $B_{it}$ are independent.
+\end{proposition}
+
+Proposition \ref{poissonReviews} allows one to easily write down the likelihood for positive and negative reviews separately.
+I will use the positive reviews as the leading example here, but all the findings automatically translate to the negative reviews case as well.
+For every game I observe the history of the review arrivals $\{(g_{it}, b_{it})\}_{t=1}^{T_i}$.
+Since $\PP{G_{it} = g_{it}} = \frac{ (r_{it}^+\lambda_{it-k} )^{g_{it}} }{g_{it}!} e^{ -r_{it-k}^+\lambda_{it-k} }$, the log-likelihood of the history of likes is given by
+\begin{equation}\label{reviewsLikelihood}
+\ell(g_i; r_{it}^+, \lambda_{it-k}) = \sum_{t\ge k} g_{it} \log r_{it}^+\lambda_{it-k} - r_{it}^+\lambda_{it-k} - \log g_{it}!
+\end{equation}
+
+I treat $\lambda_{it}$ as known, because parameters $\lambda_{i}$ and $\beta$ that determine it can be estimated consistently for the majority of games in the sample, given the long time dimension of the panel.
+For now I also take the lag $k$ between the time when the user buys the game and leaves a review for the game to be known.
+The parameters of interest are $(\rho_{0i}^+, \rho_{1i}^+)$, which parametrize the like rate as $r_{it}^+ = \rho_{0i}^+ + \rho_{1i}^+ disc_{it-k}$.
+The likelihood is concave in the parameters, so the parameters are identified as the maximizer of the likelihood.
+Restricting attention to a binary discount variable $disc_{it}$ allows me to derive a closed-form estimator for $(\rho_{0i}^+, \rho_{1i}^+)$.
+During a discount the like rate of game $i$ is $\rho_{0i}^+ + \rho_{1i}^+$, which is consistently estimated as
+\begin{equation}\label{rhohat1}
+\hat \rho_{0i}^+ + \hat\rho_{1i}^+ = \frac{\sum_{t \ge k} disc_{it-k}g_{it}}{\sum_{t\ge k} disc_{it-k}\lambda_{it-k}},
+\end{equation}
+As we can see, the ML-estimator of the like rate during a price promotion is just the ratio of the number of good reviews left on a discount over the expected arrival on that day.
+Similarly, the like rate off a discount can be estimated by
+\begin{equation}\label{rhohat2}
+\hat \rho_{0i}^+ = \frac{\sum_{t\ge k} (1-disc_{it-k})g_{it}}{\sum_{t\ge k} (1-disc_{it-k})\lambda_{it-k}},
+\end{equation}
+with the interpretation that the like rate in the absence of a discount is just a ratio of the reviews left outside of a discount and the expected number of customers outside a discount.
+
+Note that one can use these estimators to estimate the *average review score* on and off a discount, i.e., whether users are relatively more or less likely to leave a good review during a discount.
+For example, without a price promotion, one obtains
+\begin{equation}\label{avReviewScore}
+\frac{\sum_{t\ge k} (1-disc_{it-k})g_{it}}{\sum_{t\ge k} (1-disc_{it-k})g_{it} + \sum_{t\ge k} (1-disc_{it-k})b_{it}}
+=
+\frac{\hat \rho_{0i}^+}{\hat \rho_{0i}^+  + \hat \rho_{0i}^- }
+\end{equation}
+It is intuitively clear that the relative propensity to leave a good, rather than a bad, review should be easily estimable by comparing the ratios of good to bad reviews, without any knowledge of the quantity of games sold.
+This intuition is fully reflected in Equation (\ref{avReviewScore}), where the arrival rates $\lambda_{it-k}$ have disappeared entirely.
+
+The analysis above is complicated by two facts.
+First, for each game I observe the exact review count, but my demand estimates only apply to rush hours.
+If, say, every player leaves a review, and every day there are two new players who play in the morning, and three new players who play in the evening, my data would register 3 players leaving 5 reviews on a daily basis.
+This is the reason why I refer to the values of $(r_{it}^+, r_{it}^-)$ as rates, rather than probabilities (which they are in the model).
+Propositon \ref{poissonReviews}, stating that the number of good reviews on day $t$ for game $i$ is a Poisson random variable with rate $r_{it}^+\lambda_{it-k}$, could be treated as an assumption, rather than a result.
+In that case, nothing constrains the $r_{it}^+$ parameter to be less than 1, and the identification argument goes through in the exactly the same way.
+
+Another problem stems from the fact that the purchase date behind a review is not available to the researcher.
+For that reason, the model features an additional parameter $k$, the lag between purchasing the game and leaving a review, that I assumed to be known.
+To estimate that parameter I leverage the fact that spikes in player activity on the first day of a sale represent new users, and study the review response during the following week in order to uncover the modal lag for leaving a review (see Table \ref{reviewLag} in the Appendix).
+This number turns out to be one day.
+Even though time to posting a review has a non-degenerate distribution, modelling it in a more nuanced way would significantly contribute to complexity: the likelihood of receiving a poisitive review on day 100 would depend on the entire history of buyer arrivals prior to that date.
+Therefore, I proceed using $\hat k = 1$.
+
 ### Review Parameters

### 2020-09-10 Analysis/Code/Paper.Rmd
Added the stylized model

@@
 Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place.
+@deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an omage to the masterfuly chosen title of \citet{deLanghe15}.}.
 Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales.
@@
 
-```{r, include=F}
-reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos +
-             negative + mPositive + realPositive +
-             vPositive + ovPositive + score +
-             log(reviews+1) + age + poly(tWODisc, degree = 2) + 
-             day + week, data = transPanel)
-cov<-vcovHC(reg1)
-se1 <- sqrt(diag(cov))
-
-star.out.transitions <- stargazer(reg1,
-          label = "transitionReg",
-          table.placement = "hp",
-          header = FALSE,
-          title = "Discounts In The Days Around Transition",
-          se=list(se1),
-          #column.labels=c(),
-          dep.var.labels = c("Discount Probability"),
-          covariate.labels = c("Days to Transition", "Days After Transition",
-                               "Negative", "Mostly Positive", "Positive", "Very Positive",
-                               "Ov. Positive", "Score", "Log Reviews", "Age", "Const"),
-          model.numbers = F,
-          omit = c("day", "week", "tWODisc"),
-          omit.stat=c("f","adj.rsq","ser"),
-          no.space=T)
-```
-
 # Empirical Model of Demand
@@
 
+```{r, include=F}
+reg1 <- lm(I(discount>0) ~  tToTransitNeg + tToTransitPos +
+             negative + mPositive + realPositive +
+             vPositive + ovPositive + score +
+             log(reviews+1) + age + poly(tWODisc, degree = 2) + 
+             day + week, data = transPanel)
+cov<-vcovHC(reg1)
+se1 <- sqrt(diag(cov))
+
+star.out.transitions <- stargazer(reg1,
+          label = "transitionReg",
+          table.placement = "hp",
+          header = FALSE,
+          title = "Discounts In The Days Around Transition",
+          se=list(se1),
+          #column.labels=c(),
+          dep.var.labels = c("Discount Probability"),
+          covariate.labels = c("Days to Transition", "Days After Transition",
+                               "Negative", "Mostly Positive", "Positive", "Very Positive",
+                               "Ov. Positive", "Score", "Log Reviews", "Age", "Const"),
+          model.numbers = F,
+          omit = c("day", "week", "tWODisc"),
+          omit.stat=c("f","adj.rsq","ser"),
+          no.space=T)
+```
+
 ```{r transition-discount-plot, fig.cap='\\label{discountsTransitions} Discounting By Games Around The Transition.'}
@@
    scale_y_continuous(name = "% Of Games Discounting", ) +
-   scale_color_manual(labels = c("Bad", "Good"),
+   scale_color_manual(labels = c("Down", "Up"),
                       name = "Transition",
@@
    my.theme(leg.x = 0.78, leg.y = 0.82)
-rm(transPanel, transitions)
 ```
@@
 The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels are often preceded by discounts.
-The graph shows that two weeks prior to a transition only `r transPanel[x==-14, round(mean(100*(discount > 0)))]`% of games were on a discount, essentially the sample average, but that this number more than doubles to around `r transPanel[x==-1, round(mean(100*(discount > 0)))]`% one day before the label change.
+The graph shows that two weeks prior to a transition only `r transPanel[tToTransit==-14, round(mean(100*(discount > 0)))]`% of games were on a discount, essentially the sample average, but that this number more than doubles to around `r transPanel[tToTransit==-1, round(mean(100*(discount > 0)))]`% one day before the label change.
 Regression analysis controlling for review label, number of reviews, age, day of the week and week time effects, as well as time since the previous discount, confirms that the association depicted in Figure \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in the Appendix).
@@
 In other words, firms could be giving discounts for reasons unrelated to reviews, but transitions sometimes would follow as a result.
-As a matter of fact, suppose that the story I am after is true, and that firms try to achieve transitions  via price promotions.
+As a matter of fact, suppose that the story I am after is true, namely that firms try to achieve transitions  via price promotions.
 In that case, discounts *have* to be able to aid transitioning, making the reverse causality inherent in this setting.
+The reverse causality would also explain why both review upgrades and downgrades are preceeded by discounts.
+
 The analysis behind Figure \ref{discountsTransitions} remains imperfect for yet another reason.
@@
 ```{r include = F, cache=F}
+rm(transPanel, transitions)
 band <- 7
@@
 
-As the example above shows, it is impossible to consider proximity to a positive transition without taking into account the proximity to a negative transition, at least for moderately sized games.
+As the example above shows, it is impossible to consider proximity to a positive transition without taking into account proximity to a negative transition, at least for moderately sized games.
 If firms' strategies for these types of transitions are different, then studying such transitions separately could attenuate the effect of the proximity to, say, a positive transition, on the discount probability: a firm that is close to upgrading its review bin might not give a discount not because it is a bad way to accomplish that transition, but because that firm is at the same time close to downgrading its review bin, and might prefer to exercise prudence.
@@
 The analysis also excludes the observations with a “No Review Score” label, as I do not want to take a stance on what constitutes an improvement or a deterioration of the review score for such games.
+My demand estimates presented in Table \ref{demandEstimates} suggest that having no reviews could be the worst review bin a game could be in, but then I would have to exclude this label as one that does not admit review deterioration.
+In any case, games that spend a lot of time in “No Score” have, by construction, very few reviews, which makes them rather unlikely to ever be one one or two weeks away from a transition according to my measure.
+
 The results of estimating Equation \ref{potTransitionsReg} are presented in Table \ref{potentialTransitionsResults}.
@@
 
-It is not unreasonable to say that model \ref{potTransitionsReg} is able to identify the causal effect of the proximity to a review transition on discounting behavior.
+It is reasonable to say that model \ref{potTransitionsReg} is able to identify the causal effect of the proximity to a review transition on discounting behavior.
 As the sample was selected to include only products with the most stable quality and the lowest number of game updates, the path of the review score is relatively exogenous for the firms.
@@
 One is unobserved marketing interventions preceding discounts.
-If advertisements improves the review score, then, by definition, advertisement would be correlated with the treatment variable, moving games a bit closer to transitions.
+If advertisements improve the review score, then, by definition, advertisement would be correlated with the treatment variable, moving games a bit closer to transitions.
 If a discount then follows, as a part of the general marketing plan, rather than to leverage the new proximity to a transition, the positive association between discounting and positive transitions would be spurious.
@@
 
-I would now like to step back and look at the story behind the behavior that I am documenting.
-Several gaps are not filled yet.
-First, I have not presented evidence that discounting meaningfully increases sales and leads to more reviews.
-Neither have I presented evidence that better review bins increase sales.
-Perhaps, more importantly, I have not discussed why firms should expect customers buying during a discount to leave better reviews than customers paying the regular price.
-If there is no difference between the two groups, then giving a discount when the game is close to a transition is, at best, a gamble.
-In fact, there is some empirical evidence that customers who choose to go to a restaurant because of a promotion tend to leave worse reviews [@ByersEtAl12; @Li16], even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19].
+It is instructive to look at the results through the lens of stylized model introduced earlier in the section.
+Take the products close to a review upgrade first.
+For such products to choose not to discount the product, the downside risk should be high, or they must have enough reviews to make changing their review score infeasible.
+Table \ref{potentialTransitionsResults} finds that games with more reviews are indeed less likely to discount, consistent with the idea that discounts are used more often when they can have an effect.
+As for the size of the downsize risk, it seems intuitive that the risk of review deterioration for a product that is close to upgrading its review label should not be too large.
+The predictions for games that are close to a review downgrade were more blurred.
+My findings suggest that reviews left on a discount are not significantly more positive than regular reviews---if it was the case, why would firms choose to stay put and not give a discount?
+
+The results I presented in this section, therefore, lead to the following hypothesis: reviews left on a discount are not more positive than the ones left off a discount.
+This hypothesis has found some support in the prior literature, albeit in a different market.
+@ByersEtAl12 and @Li16 report that customers who choose to go to a restaurant because of a price promotion tend to leave worse reviews, even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19].
 Theoretically, this effect is ambiguous.
 Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews.
-At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews.
-See, for example, @AcemogluEtAl19.
-
-The results I presented in this section, therefore, lead to the following hypotheses.
-I show that firms give discounts to avoid bad transitions and to facilitate the good ones; thus, it has to be the case that the reviews left on a discount tend to be more positive than the ones left off a discount.
-Second, if that is indeed the case, then the firms that get especially positive reviews during price promotions should be more likely to try to use discounting to manipulate their reviews.
-Heterogeneity between the firms is crucial for the second hypothesis.
-In order to test these hypotheses, and to provide evidence on the effect of discounting on sales and reviewing activity, as well as the effect of reviews on sales, I now turn to formulation and estimation of a structural model demand, reviewing and gaming activity on Steam.
+At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews [@CabralLi15; @IfrachEtAl19; @AcemogluEtAl19].
+I now turn my attention to investigating this hypothesis, as doing so would be helpful in assessing the results obtained in this section, and would contribute to the literature by providing evidence from a new market.
+
+# Selection Effect of Discounts
 

### 2020-09-11 Analysis/Code/Paper.Rmd
tracing the bug

--- 2020-09-10 Analysis/Code/Paper.Rmd
@@
 
-# Empirical Model of Demand
-
-\textcolor{red}{Write a small introduction here.}
-
-## Setup
-
-Consider game \(i\) that is observed on a daily basis. On day \(t\)
-the game sells one copy to each of the \(B_{it}\) short-lived buyers that arrive on
-that day, a number that is unobserved by the econometrician. Define
-*active players* of this game, \(A_{it}\), to be the customers who have
-already purchased the game and are still playing it, either because they have
-not yet completed it or are not bored with it yet. This number  has an empirical counterpart in
-the face of the player count variable, observable to the econometrician. The game loses \(E_{it}\) players on day \(t\), which is also not observed.
-I assume that, once a player stops playing the game, she never returns to it again. It is easy to see then that \(A_{it}\) follows the following process:
-\begin{equation}\label{activeProccess}
-  A_{it} = A_{it-1} + B_{it} - E_{it}
-\end{equation}
-
-Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about
-them in order to make progress.
-
-\begin{assumption}\label{arrivalAssumptions}
-$B_{it}$ is Poisson with arrival rate $\lambda_{it} = \lambda_i(1+x'_{it}\beta)$, where $x_{it}$ is a vector of observable characteristics of the game, and $\lambda_i$ and $\beta$ are parameters.
-$E_{it}$ follows a binomial distribution $B(A_{it-1}, 1-\psi_i)$, where $\psi_i$ is a parameter.
-\end{assumption}
-
-The rationale behind assumption (\ref{arrivalAssumptions}) is simple.
-Consumers arrive every day according to the game specific arrival rate
-\(\lambda_i\), but that rate can go up or down depending on the values
-of observable characteristics \(x_{it}\) of the game that affect demand:
-price, reviews, age of the game, or seasonal factors.
-The mapping between these variables and the number of copies sold is, of course, nothing else but the demand curve for game $i$.
-A change of $0.01$ in the index $x_{it}'\beta$ means that quantity demanded of game $i$ goes up by one percent.
-This multiplicative structure is necessary, because it will allow me to estimate the price sensitivity and the effect of reviews on sales in relative terms\footnote{See the Identification section for more details}.
-Buyers of the game become active players, and are subject to a fixed daily risk of $1-\psi_i$ of abandoning the game.
-Given that the number of active players “flipping” this coin at the end of day $t-1$ is $A_{it-1}$, this process gives rise to the binomial distribution for the number of exiters.
-
-## Identification
-
-### Demand Parameters
-The prediction of \(A_{it}\) that follows from (\ref{activeProccess}) takes the form of
-\begin{equation}
-\mathbb{E}\left[A_{it}\,|\,A_{it-1}, x_{it} \right] = A_{it-1} + \lambda_i(1+x'_{it}\beta) - (1-\psi_i)A_{it-1} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta),
-\end{equation} so the model implies the following regression equation
-\begin{equation}\label{arrivalReg}
- A_{it} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
-\end{equation}
-with
-\(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\). This model is
-non-linear in parameters, because \(\lambda_i\) is not known and enters
-the model multiplying \(\beta\), the parameters common to all games. If
-not for this commonality in $\beta$, estimation of (\ref{arrivalReg}) would be
-straightforwardly achieved by opening the parentheses and estimating
-\begin{equation}\label{arrivalRegInd}
-A_{it} = \lambda_i + \psi_i A_{it-1} + x'_{it}\beta_i + u_{it}
-\end{equation}
-using OLS on a game-by-game basis. This commonality is
-essential, however, because one game in the sample typically does not exhibit enough variation in review labels to be able to identify the effect of upgrading the review tier on sales.
-
-The fact that $x'_{it}\beta$ multiplies the game fixed effect $\lambda_i$ allows me to estimate the dependence of quantity sold on price and reviews in relative terms, i.e., to obtain the elasticities.
-Normally, a log transformation is used to achieve that.
-Indeed, @SorokinStevens20 is able to estimate these elasticities with a within-estimator, using the following model
-\begin{equation}\label{logReg}
-\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}.
-\end{equation}
-This specification “controls” for the (log) number of continuing players in order to overcome the non-availability of direct sales data; however, it is the numbers of active players and buyers that are additive, not their logs.
-Thus, the structural model I formulate confronts the estimation problem in a more “heads-up” way, and in that regard offers an improvement over @SorokinStevens20.
-I will contrast the results obtained by the two approaches in the results section, comparing a more detailed structural approach with a less precise, but a more easily implementable, log regression approach.
-
-Another important reason for insisting on estimating the relative effects stems from the limitations of my data.
-Recall that the player count variable measures only the *maximum concurrent* number of active players every day.
-This implies that the estimated values of $\lambda_{it}$ would take into account only those new buyers who contribute to gaming activity during the “rush hour”.
-An implicit assumption in my analysis is that new buyers of the game all choose their gaming time following the same game-specific distribution.
-I use this assumption to say that, if the number of new active players during rush hour goes up by 1%, then sales go up by 1% across all types of players,  not only among the "rush hour ones".
-
-Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model \ref{arrivalReg}, and guarantees identification of all parameters, as long as there is sufficient variation in the data.
-Of course, this is only true as long as equation \ref{arrivalReg} is the right model of the data generating process.
-A threat to identification would come from unobserved demand shifters $\tilde x_{it}$ that are correlated with the observed factors $x_{it}$ (omitted variable bias).
-For instance, an advertising intervention that is coupled with a price promotion would increase demand, but the entire effect would be attributed to the observed change in price.
-My approach is vulnerable to such events, as long as one is interested in getting the causal estimate of the discount elasticity of demand.
-
-However, I argue that (\ref{arrivalReg}) is an adequate specification, if the goal is to estimate the causal effect of reviews on sales, or to get a predictive model of demand.
-First and foremost, the reviews are not a choice variable of a firm, and rather serve as a state variable that a firm takes as given every day.
-Of course, there are various things that a firm can do, that can, in a non-guaranteed fashion, affect this variable.
-But, as long as the major tools that a firm has access to are controlled for in the regression, the exogenous variation in the review variables is sufficient to identify the causal effect of reviews on sales.
-
-One important way in which I control for various tools that firms have at their disposal is through sample selection.
-Sample selection rules out the possibility of an omitted variable bias stemming from a number of variables that could collectively be referred to as “changing quality”.
-The games in the sample are single player games, and thus are not subject to time-varying network externalities or frequent quality updates, that could be correlated with reviews, depths of discounts, and the player count.
-Second, game specific effect $\lambda_i$ controls for all time-invariant characteristics of game $i$ that determine average sales: initial marketing budget, extraneous popularity of the game's plot or setting, etc.
-Similarly, time effects control for important within-week seasonality in gaming patterns and for the extensive platform-wide sales.
-Third, note that Equation (\ref{arrivalReg}) allows each game to have its own continuation probability $\psi_i$, which could prove crucial in eliciting sales from the player count data.
-Two games could have the same observed median daily player count---say, ten people---but very different sales levels, if game one offers a lot of replayability and is played by the same ten people over and over again, and game two is played by new ten people every day.
-Intuitively, $\psi_i$ is identified by the rate of decay of the player count when it is far from its (slowly-changing) trend or average.
-Game release and discounts offer such events, when the player count spikes briefly due to all the new players who just bought the game; see example game in Figure \ref{exampleGame}.
-
-### Price Elasticity of Demand
-To close off the discussion of identification of the demand parameters in Equation (\ref{arrivalReg}), I would like to elaborate on the identification of the price elasticity parameter.
-As I mentioned before, at the very least, including the price in the regression controls for unobserved marketing interventions that are coupled with discounts.
-Estimating the true price elasticity of demand is not important for the questions addressed in this paper, as I am not trying to prescribe the sizes of the discounts that firms should be giving to have a meaningful chance of affecting their review labels when they are close to a review transition.
-Arguably, a 100% discount is a powerful enough option to make this strategy viable, at least in principle.
-However, should the price coefficient be of primary interest, I would like to list some further factors that have an impact on the identification of thereof.
-
-First, I believe that standard concerns about the endogeneity of prices are not directly applicable in my context.
-The reason is the high frequency nature of the data and the stickiness of posted prices.
-Using the classic notation, imagine that a discount is given on date $t$, and we observe a quantity-price pair $(Q_t, P_t)$, both of which are different from their yesterday's counterparts $(Q_{t-1}, P_{t-1})$.
-The standard endogeneity concern is that firm's demand is subject to shocks, and that the firm would change its price precisely when those shocks occur.
-The two points then, roughly speaking, would belong to different demand curves, and one can not identify the slope of the demand curve\footnote{Assuming, as is usually done, that demand shifters lead to parallel shifts in demand}.
-In my setting, however, this would require the firms to systematically give discounts *exactly on the days* of the demand shocks, which requires possessing a level of insight into one's demand condition that is unrealistic, especially for small independent studios.
-While a discount for a racing game on the day of a major F-1 race is not implausible, should the demand for the game go up with a lag of as little as one day, then both $(Q_t, P_t)$ and $(Q_{t-1}, P_{t-1})$ would belong to the same demand curve, and, therefore, identification would not be threatened.
-
-My second point is that, even though unobserved marketing interventions that are coupled with price promotions, would,  undoubtedly, be an issue, this problem could be addressed with some extra data collection.
-One way to proceed would be to study if such coupled promotions in fact do take place.
-In particular, one could collect data on YouTube queries mentioning the games in the sample, and use spikes in such queries as a proxy for unobserved marketing campaigns.
-
-A deeper problem for identifying the price elasticity of demand lies in defining precisely the elasticity of interest.
-A video game is a durable good, and some consumers could be purchasing it strategically, thinking about the probability and depth of discounts that they could get in the near future.In particular, Steam allows users to add any game to their wishlist, which means that they would be notified about promotions affecting that game.
-Later in the results section we will see that the lion's share of sales on a discount take place on the first day of the discount, which is consistent with users waiting for a discount and buying the game when the discount goes live.
-For studying counterfactual price policies one would need to specify a more complicated model of forward-looking consumers, and estimate the fundamentals of their behavior.
-A related problem is the importance of salience in a marketplace that has many thousands of products.
-Any price elasticity estimated relies on Steam keeping its algorithms unchanged.
-A game can give a 99% discount, but the quantity demanded will not change much if that promotion happens to not be reflected in Steam's system.
-This has implications, for instance, for picking good instruments for prices.
-Curated discounts created and managed by Steam are suggested to firms, and not chosen by them.
-In principle, such price changes could be exogenous to daily demand conditions.
-However, they could hardly be used as instruments for the price, because they also bring an immense boost in visibility, by the virtue of occupying the prime store main page space.
-
 ## Results
@@
 
-# Discounting and Review Bin Transitions
+# Descriptive Evidence
 \label{descriptiveEvidence}
 
-## Stylized Model
-
-Consider a firm that has a review status $s \in (0, 1)$.
-A firm can give a discount at cost $c$ that can probabilistically change its status to exceed 1 (an upgrade), to go below 0 (a downgrade), or to remain within the $(0,1)$ band (no change).
-The result depends on whether the additional customers who buy the product on a discount happen to leave more positive or more negative reviews, and on the  weight of hte new reviews relative to the existing ones.
-Assume that with probability $p$ the firm's status becomes $s+x$, and with probability $1-p$ it becomes $s-x$.
-Firm's utility $u(s)$ from having a review status $s \in (0,1)$ is 0, while it earns a utility $u^H$ from the upgraded status and a utility $u^L < 0 < u^H$ from the downgraded status.
-The expected utility from giving a discount is
-\begin{equation}
-  \EE{U(s+X)} = p U(s + x) + (1-p) U(s-x) - c
-\end{equation}
-
-When would the firm be willing to give a discount? Consider a firm with $s > 1/2$, i.e., the one that is close to a review upgrade. For that firm the expected value of giving a discount is 
-$$
-  \EE{U(s+X)} = 
-  \begin{cases}
-  -c & x < 1-s\\
-  p u^H -c & x \in [1-s, s) \\
-  pu^H + (1-p)u^L - c & x \ge s
-  \end{cases}
-$$
-\noindent The firm would choose to give a discount if $\EE{U(s+X)}  > 0$.
-A trivial comparative statics exercise tells us that the firm is more likely to do so if the probability $p$ to get a positive shock to the review status if high, if the payoff $u^H$ of upgrading the status is high, and if the loss from downgrading the status $-u^L$ is low.
-
-What is interesting about this problem, is that the probability of improving the review status $p$ does not have to exceed $1/2$ for the firm to give a discount, i.e., the reviews it gets on a discount could be worse than the reviews it receives off a discount.
-Indeed, if the potential change to the score is moderate ($x \in [1-s, s]$), then a successful outcome leads to a transition, while an unsuccessful outcome leaves the firm with the current review status.
-In this case the firm is not risking anything, and is willing to “pull the plug” simply to gamble on the positive outcome.
-Even if the potential change to the review status is substantial $(x \ge s)$, the firm could still find  it profitable to give a discount and risk the deterioration of its review status if the benefits of having an improved status are large enough.
-Similar conclusions follow for the case of $s < 1/2$, when a firm is closer to a negative transition.
-
-The main takeaway from this stylized model is that the relationship between proximity to transitions and discounting behavior is theoretically ambiguous.
-In the data we can expect to find both firms that are more likely to give a discount when they are close to a transition (gambling to upgrade their status, or trying to escape from the downgrading threshold), and firms that are less likely to discount when close to a transition (the downside risk is too big).
-I will now investigate this relationship in the data, and will use the intuition developed here to interpret the results.
-
-## Empirical Analysis
+In this section I present evidence that firms use discounting to manage their online reputation, in particular, by running price promotions when they are close to improving their review label.
+For now, let us resort to a very simplistic story of why a firm would be interested in doing that.
+Assume that discounts increase the inflow customers, and that more customers means more reviews.
+Also, take for granted, for now, that better review labels improve sales.
+Then, if a firm is one positive review away from upgrading its review label, it might be tempted to speed things up by giving a discount.
+Similarly, a product that is close to sliding into a worse review bin, could be tempted to run a price promotion, in order to avoid a slump in its reviews.
+I will address this story in more detail in the discussion part of this section, but for now I turn attention to simply establishing that this sort of behavior indeed takes place in the sample.
 
@@
 
-The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels are often preceded by discounts.
-The graph shows that two weeks prior to a transition only `r transPanel[x==-14, round(mean(100*(discount > 0)))]`% of games were on a discount, essentially the sample average, but that this number more than doubles to around `r transPanel[x==-1, round(mean(100*(discount > 0)))]`% one day before the label change.
+The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels are very often preceded by discounts.
+The graph shows that two weeks prior to a transition only 15% of games were on a discount, a number close to the sample average, but that this number more than doubles to around 35% one day before the label change.
 Regression analysis controlling for review label, number of reviews, age, day of the week and week time effects, as well as time since the previous discount, confirms that the association depicted in Figure \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in the Appendix).
@@
 
-# define how many positive and negative reviews are needed to transition, manually
+# define how many positive and negative reviews are needed to transition, manualy
 # for every threshold
@@
                                   "Log Days to Pos. Tr.", "Log Days to Neg Tr.",
-                                  "Log Reviews", "Score", "Mostly Positive",
-                                  "Positive", "Very Positive",
-                                  "Age", "Age $\\le 14$"),
+                                  "Mostly Positive", "Positive", "Very Positive",
+                                  "Score", "Log Reviews", "Age", "Age $\\le 14$"),
              model.numbers = F,
@@
 
+# Empirical Model
+
+\textcolor{red}{Write a small introduction here.}
+
+## Setup
+
+Consider game \(i\) that is observed on a daily basis. On day \(t\)
+the game sells one copy to each of the \(B_{it}\) short-lived buyers that arrive on
+that day, a number that is unobserved by the econometrician. Define
+*active players* of this game, \(A_{it}\), to be the customers who have
+already purchased the game and are still playing it, either because they have
+not yet completed it or are not bored with it yet. This number  has an empirical counterpart in
+the face of the player count variable, observable to the econometrician. The game loses \(E_{it}\) players on day \(t\), which is also not observed.
+I assume that, once a player stops playing the game, she never returns to it again. It is easy to see then that \(A_{it}\) follows the following process:
+\begin{equation}\label{activeProccess}
+  A_{it} = A_{it-1} + B_{it} - E_{it}
+\end{equation}
+
+Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about
+them in order to make progress.
+
+\begin{assumption}\label{arrivalAssumptions}
+$B_{it}$ is Poisson with arrival rate $\lambda_{it} = \lambda_i(1+x'_{it}\beta)$, where $x_{it}$ is a vector of observable characteristics of the game, and $\lambda_i$ and $\beta$ are parameters.
+$E_{it}$ follows a binomial distribution $B(A_{it-1}, 1-\psi_i)$, where $\psi_i$ is a parameter.
+\end{assumption}
+
+The rationale behind assumption (\ref{arrivalAssumptions}) is simple.
+Consumers arrive every day according to the game specific arrival rate
+\(\lambda_i\), but that rate can go up or down depending on the values
+of observable characteristics \(x_{it}\) of the game that affect demand:
+price, reviews, age of the game, or seasonal factors.
+The mapping between these variables and the number of copies sold is, of course, nothing else but the demand curve for game $i$.
+A change of $0.01$ in the index $x_{it}'\beta$ means that quantity demanded of game $i$ goes up by one percent.
+This multiplicative structure is necessary, because it will allow me to estimate the price sensitivity and the effect of reviews on sales in relative terms\footnote{See the Identification section for more details}.
+Buyers of the game become active players, and are subject to a fixed daily risk of $1-\psi_i$ of abandoning the game.
+Given that the number of active players “flipping” this coin at the end of day $t-1$ is $A_{it-1}$, this process gives rise to the binomial distribution for the number of exiters.
+
 Every buyer of game $i$ is a potential reviewer.
@@
 I use a dummy variable $disc_{it-k}$ to measure discounting because this will allow me to derive a closed-form estimator for the  parameters of interest.
+
+## Identification
+
+### Demand Parameters
+The prediction of \(A_{it}\) that follows from (\ref{activeProccess}) takes the form of
+\begin{equation}
+\mathbb{E}\left[A_{it}\,|\,A_{it-1}, x_{it} \right] = A_{it-1} + \lambda_i(1+x'_{it}\beta) - (1-\psi_i)A_{it-1} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta),
+\end{equation} so the model implies the following regression equation
+\begin{equation}\label{arrivalReg}
+ A_{it} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
+\end{equation}
+with
+\(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\). This model is
+non-linear in parameters, because \(\lambda_i\) is not known and enters
+the model multiplying \(\beta\), the parameters common to all games. If
+not for this commonality in $\beta$, estimation of (\ref{arrivalReg}) would be
+straightforwardly achieved by opening the parentheses and estimating
+\begin{equation}\label{arrivalRegInd}
+A_{it} = \lambda_i + \psi_i A_{it-1} + x'_{it}\beta_i + u_{it}
+\end{equation}
+using OLS on a game-by-game basis. This commonality is
+essential, however, because one game in the sample typically does not exhibit enough variation in review labels to be able to identify the effect of upgrading the review tier on sales.
+
+The fact that $x'_{it}\beta$ multiplies the game fixed effect $\lambda_i$ allows me to estimate the dependence of quantity sold on price and reviews in relative terms, i.e., to obtain the elasticities.
+Normally, a log transformation is used to achieve that.
+Indeed, @SorokinStevens20 is able to estimate these elasticities with a within-estimator, using the following model
+\begin{equation}\label{logReg}
+\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}.
+\end{equation}
+This specification “controls” for the (log) number of continuing players in order to overcome the non-availability of direct sales data; however, it is the numbers of active players and buyers that are additive, not their logs.
+Thus, the structural model I formulate confronts the estimation problem in a more “heads-up” way, and in that regard offers an improvement over @SorokinStevens20.
+I will contrast the results obtained by the two approaches in the results section, comparing a more detailed structural approach with a less precise, but a more easily implementable, log regression approach.
+
+Another important reason for insisting on estimating the relative effects stems from the limitations of my data.
+Recall that the player count variable measures only the *maximum concurrent* number of active players every day.
+This implies that the estimated values of $\lambda_{it}$ would take into account only those new buyers who contribute to gaming activity during the “rush hour”.
+An implicit assumption in my analysis is that new buyers of the game all choose their gaming time following the same game-specific distribution.
+I use this assumption to say that, if the number of new active players during rush hour goes up by 1%, then sales go up by 1% across all types of players,  not only among the "rush hour ones".
+
+Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model \ref{arrivalReg}, and guarantees identification of all parameters, as long as there is sufficient variation in the data.
+Of course, this is only true as long as equation \ref{arrivalReg} is the right model of the data generating process.
+A threat to identification would come from unobserved demand shifters $\tilde x_{it}$ that are correlated with the observed factors $x_{it}$ (omitted variable bias).
+For instance, an advertising intervention that is coupled with a price promotion would increase demand, but the entire effect would be attributed to the observed change in price.
+My approach is vulnerable to such events, as long as one is interested in getting the causal estimate of the discount elasticity of demand.
+
+However, I argue that (\ref{arrivalReg}) is an adequate specification, if the goal is to estimate the causal effect of reviews on sales, or to get a predictive model of demand.
+First and foremost, the reviews are not a choice variable of a firm, and rather serve as a state variable that a firm takes as given every day.
+Of course, there are various things that a firm can do, that can, in a non-guaranteed fashion, affect this variable.
+But, as long as the major tools that a firm has access to are controlled for in the regression, the exogenous variation in the review variables is sufficient to identify the causal effect of reviews on sales.
+
+One important way in which I control for various tools that firms have at their disposal is through sample selection.
+Sample selection rules out the possibility of an omitted variable bias stemming from a number of variables that could collectively be referred to as “changing quality”.
+The games in the sample are single player games, and thus are not subject to time-varying network externalities or frequent quality updates, that could be correlated with reviews, depths of discounts, and the player count.
+Second, game specific effect $\lambda_i$ controls for all time-invariant characteristics of game $i$ that determine average sales: initial marketing budget, extraneous popularity of the game's plot or setting, etc.
+Similarly, time effects control for important within-week seasonality in gaming patterns and for the extensive platform-wide sales.
+Third, note that Equation (\ref{arrivalReg}) allows each game to have its own continuation probability $\psi_i$, which could prove crucial in eliciting sales from the player count data.
+Two games could have the same observed median daily player count---say, ten people---but very different sales levels, if game one offers a lot of replayability and is played by the same ten people over and over again, and game two is played by new ten people every day.
+Intuitively, $\psi_i$ is identified by the rate of decay of the player count when it is far from its (slowly-changing) trend or average.
+Game release and discounts offer such events, when the player count spikes briefly due to all the new players who just bought the game; see example game in Figure \ref{exampleGame}.
+
+### Price Elasticity of Demand
+To close off the discussion of identification of the demand parameters in Equation (\ref{arrivalReg}), I would like to elaborate on the identification of the price elasticity parameter.
+As I mentioned before, at the very least, including the price in the regression controls for unobserved marketing interventions that are coupled with discounts.
+Estimating the true price elasticity of demand is not important for the questions addressed in this paper, as I am not trying to prescribe the sizes of the discounts that firms should be giving to have a meaningful chance of affecting their review labels when they are close to a review transition.
+Arguably, a 100% discount is a powerful enough option to make this strategy viable, at least in principle.
+However, should the price coefficient be of primary interest, I would like to list some further factors that have an impact on the identification of thereof.
+
+First, I believe that standard concerns about the endogeneity of prices are not directly applicable in my context.
+The reason is the high frequency nature of the data and the stickiness of posted prices.
+Using the classic notation, imagine that a discount is given on date $t$, and we observe a quantity-price pair $(Q_t, P_t)$, both of which are different from their yesterday's counterparts $(Q_{t-1}, P_{t-1})$.
+The standard endogeneity concern is that firm's demand is subject to shocks, and that the firm would change its price precisely when those shocks occur.
+The two points then, roughly speaking, would belong to different demand curves, and one can not identify the slope of the demand curve\footnote{Assuming, as is usually done, that demand shifters lead to parallel shifts in demand}.
+In my setting, however, this would require the firms to systematically give discounts *exactly on the days* of the demand shocks, which requires possessing a level of insight into one's demand condition that is unrealistic, especially for small independent studios.
+While a discount for a racing game on the day of a major F-1 race is not implausible, should the demand for the game go up with a lag of as little as one day, then both $(Q_t, P_t)$ and $(Q_{t-1}, P_{t-1})$ would belong to the same demand curve, and, therefore, identification would not be threatened.
+
+My second point is that, even though unobserved marketing interventions that are coupled with price promotions, would,  undoubtedly, be an issue, this problem could be addressed with some extra data collection.
+One way to proceed would be to study if such coupled promotions in fact do take place.
+In particular, one could collect data on YouTube queries mentioning the games in the sample, and use spikes in such queries as a proxy for unobserved marketing campaigns.
+
+A deeper problem for identifying the price elasticity of demand lies in defining precisely the elasticity of interest.
+A video game is a durable good, and some consumers could be purchasing it strategically, thinking about the probability and depth of discounts that they could get in the near future.In particular, Steam allows users to add any game to their wishlist, which means that they would be notified about promotions affecting that game.
+Later in the results section we will see that the lion's share of sales on a discount take place on the first day of the discount, which is consistent with users waiting for a discount and buying the game when the discount goes live.
+For studying counterfactual price policies one would need to specify a more complicated model of forward-looking consumers, and estimate the fundamentals of their behavior.
+A related problem is the importance of salience in a marketplace that has many thousands of products.
+Any price elasticity estimated relies on Steam keeping its algorithms unchanged.
+A game can give a 99% discount, but the quantity demanded will not change much if that promotion happens to not be reflected in Steam's system.
+This has implications, for instance, for picking good instruments for prices.
+Curated discounts created and managed by Steam are suggested to firms, and not chosen by them.
+In principle, such price changes could be exogenous to daily demand conditions.
+However, they could hardly be used as instruments for the price, because they also bring an immense boost in visibility, by the virtue of occupying the prime store main page space.
 

### 2020-09-11 Analysis/Code/Paper.Rmd
Added a new ML estimator. Fixed the bug with panel regressions

--- 2020-09-10 Analysis/Code/Paper.Rmd
@@
 load(here("Analysis", "Input", "panel.Rda"))
+# make sure the order of ID and t columns is right
+merge(panel[, .(ID, t)], panel, by = c("ID", "t"))
 ```
@@
 p1 <- ggplot(data = panel[age==180, 
-                    .(`Review Bin` = factor(labls[1*noScore + 2*negative + 3*mixed + 4*mPositive + 
-                                                  5*realPositive + 6*vPositive + 7*ovPositive],
+                    .(`Review Bin` = factor(labls[1*noScore + 2*negative + 
+                                                  3*mixed + 4*mPositive + 
+                                                  5*realPositive + 6*vPositive +
+                                                  7*ovPositive],
                       levels = labls, labels = short.labls)
@@
                 data=panel,
-            model="within")
+            model="within",
+            index = c("ID", "t"))
 
@@
                  data=panel[],
-            model="within")
+            model="within",
+            index = c("ID", "t"))
 cov<-vcovHC(reg3, method="white1")
@@
                  data=panel[],
-            model="within")
+            model="within",
+            index = c("ID", "t"))
 cov<-vcovHC(reg1, method="white1")
@@
                  data=panel[],
-            model="within")
+            model="within",
+            index = c("ID", "t"))
 cov<-vcovHC(reg2, method="white1")
@@
 The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion.
-Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg1$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
-The uncertainty about the sign and the significance of the proximity to a potential negative transition is resolved in favor of the prudent approach on the firms' side: the results suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg3$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`-`r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is only significant at 1\% level in two out of three specifications.
+Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the positive treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(re23$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
+Proximity to a potential negative transition seems to have negative or no effect on the probability of discount.
+The results in the main specification suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))` less likely to go on a discount, albeit the effect is not significant in the other two specifications.
 
@@
 
-It is reasonable to say that model \ref{potTransitionsReg} is able to identify the causal effect of the proximity to a review transition on discounting behavior.
+It is reasonable to say that model (\ref{potTransitionsReg}) is able to identify the causal effect of the proximity to a review transition on discounting behavior.
 As the sample was selected to include only products with the most stable quality and the lowest number of game updates, the path of the review score is relatively exogenous for the firms.
@@
 Take the products close to a review upgrade first.
-For such products to choose not to discount the product, the downside risk should be high, or they must have enough reviews to make changing their review score infeasible.
-Table \ref{potentialTransitionsResults} finds that games with more reviews are indeed less likely to discount, consistent with the idea that discounts are used more often when they can have an effect.
-As for the size of the downsize risk, it seems intuitive that the risk of review deterioration for a product that is close to upgrading its review label should not be too large.
-The predictions for games that are close to a review downgrade were more blurred.
-My findings suggest that reviews left on a discount are not significantly more positive than regular reviews---if it was the case, why would firms choose to stay put and not give a discount?
+For such products to choose to not go on a discount, the downside risk of doing so should be high, or they must have enough reviews to make changing their review score infeasible.
+Both scenarios would appear to be relatively unrealistic ex ante, and my results for firms on the verge of a positive transition comply with that expectation.
+On the other hand, the predictions for games that are close to a review downgrade were more blurred.
+It is reasonable to expect such products to dislike variance, unless the upside risk is strong.
+That would be the case reviews left during a discount are more positive, or if better review labels increase sales by a lot.
 
 The results I presented in this section, therefore, lead to the following hypothesis: reviews left on a discount are not more positive than the ones left off a discount.
+If this hypothesis is not true, the lack of discounting by products close to a negative transition would be puzzling.
 This hypothesis has found some support in the prior literature, albeit in a different market.
 @ByersEtAl12 and @Li16 report that customers who choose to go to a restaurant because of a price promotion tend to leave worse reviews, even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19].
-Theoretically, this effect is ambiguous.
+Theoretically, this effect of buying on a discount on the valence of the review ambiguous.
 Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews.
@@
 panel[, lam:=shift(lambda), by = ID]
+panel[is.na(pReviews), pReviews := 0]
+panel[is.na(nReviews), nReviews := 0]
 
@@
 rm(Hpos, Hneg, HnegInv, HposInv)
+```
+
+```{r}
+panel[, disc:=c(shift((discount > 0))), by = ID]
+panel[, lam:=shift(lambda), by = ID]
+panel[is.na(pReviews), pReviews := 0]
+panel[is.na(nReviews), nReviews := 0]
+
+revs <- panel[!(is.na(lam)), .(t, disc, lam, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]
+
+revs.lik <- function(x){
+  revs[, r.plus := x[1] + disc*x[2], by = ID]
+  revs[, r.minus := x[3] + disc*x[4], by = ID]
+
+  return(list(
+    "objective" = -revs[, sum(l * log(r.plus) - r.plus*lam +  
+                             d * log(r.minus) - r.minus*lam)],
+    "gradient" = -c(revs[, sum(l/r.plus - lam)],
+                   revs[, sum((l/r.plus - lam)*disc)],
+                   revs[, sum(d/r.minus - lam)],
+                   revs[, sum((d/r.minus - lam)*disc)])
+  ))
+}
+
+library(nloptr)
+
+x0 <- c(0.25, 0.0, 0.05, 0.0)
+max.lik <- nloptr(x0, 
+                  revs.lik,
+                  lb = c(0, -1, 0, -1),
+                  ub = c(10, 2, 10, 2),
+                  opts = list(algorithm = "NLOPT_LD_LBFGS"))
+
+x <- max.lik$solution
 ```
@@
                         ],
-           model = "within")
+           model="within",
+           index = c("ID", "t"))
 cov<-vcovHC(reg3, method = "white1")
@@
                         ],
-           model = "within")
+           model="within",
+           index = c("ID", "t"))
 cov<-vcovHC(reg4, method = "white1")
@@
                           score + log(reviews + 1) + age + young + day + week,
-                          data = panel, model = "within")
+                          data = panel, model="within",             index = c("ID", "t"))
 cov<-vcovHC(reg1, method="white1")
@@
                           score + log(reviews + 1) + age + young + day + week,
-                          data = panel, model = "within")
+                          data = panel, model="within",             index = c("ID", "t"))
 cov<-vcovHC(reg2, method="white1")
@@
                            log(reviews + 1) + age + young + day + week,
-                           data = panel, model = "within")
+                           data = panel, model="within",             index = c("ID", "t"))
 cov<-vcovHC(reg3, method="white1")

### 2020-09-15 Analysis/Code/Paper.Rmd
Added tests for average review probabilities.

@@
 It is reasonable to expect such products to dislike variance, unless the upside risk is strong.
-That would be the case reviews left during a discount are more positive, or if better review labels increase sales by a lot.
+That would be the case if reviews left during a discount were more positive, or if better review labels increased sales by a lot.
 
@@
 ```{r}
+# In this module I estimate the average like and dislike rates on and off discount,
+# and I test whether: (a) users leave better reviews on a discount, (b) users leave
+# more reviews during discounts
 panel[, disc:=c(shift((discount > 0))), by = ID]
 panel[, lam:=shift(lambda), by = ID]
-panel[is.na(pReviews), pReviews := 0]
-panel[is.na(nReviews), nReviews := 0]
-
+panel[is.na(pReviews), pReviews := 0] # remove this, it is already in CreateSample
+panel[is.na(nReviews), nReviews := 0] # remove this, it is already in CreateSample
+
+# part of the panel that has new reviews and estimated arrivals
 revs <- panel[!(is.na(lam)), .(t, disc, lam, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]
 
+# negative of the likelihood function
 revs.lik <- function(x){
@@
 
+# maximize the likelihood to estimate the parameters
 library(nloptr)
-
 x0 <- c(0.25, 0.0, 0.05, 0.0)
@@
 
-x <- max.lik$solution
+theta <- max.lik$solution
+
+# Estimate E[score score']
+sigma.hat <- function(x){
+  revs[, r.plus := x[1] + disc*x[2]]
+  revs[, r.minus := x[3] + disc*x[4]]
+
+  dt <- revs[, .(s1 = l/r.plus - lam, s2 = (l/r.plus - lam)*disc,
+                 s3 = d/r.minus - lam, s4 = (d/r.minus - lam)*disc)]
+
+  (as.matrix(transpose(dt)) %*% as.matrix(dt))/(dim(revs)[1]) %>%
+    return()
+}
+
+# Estimate the hessian d(score)/d theta'
+H.hat <- function(x){
+  n <- dim(revs)[1]
+  revs[, r.plus := x[1] + disc*x[2]]
+  revs[, r.minus := x[3] + disc*x[4]]
+
+  H <- matrix(rep(0, length(x)*length(x)), nrow = length(x))
+
+  h <- revs[, .(h11 = -l/(r.plus)^2, h12 = -l/(r.plus)^2*disc, h13 = 0, h14 = 0,
+           h21 = -l/(r.plus)^2*disc, h22 = -l/(r.plus)^2*disc^2, h23=0, h24 = 0,
+           h31 = 0, h32 = 0, h33 = -d/(r.minus)^2, h34 = -d/(r.minus)^2*disc,
+           h41 = 0, h42 = 0, h43 = -d/(r.minus)^2*disc, h44 = -d/(r.minus)^2*disc^2)]
+
+  for (i in 1:n){
+    hi <- h[i] %>% as.matrix() %>% matrix(., nrow =  length(x))
+    H <- H + hi
+  }
+
+  return(H/n)
+}
+
+# calculate the variance-covariance matrix of theta hat (divided by n)
+sigma <- sigma.hat(theta)
+H <- H.hat(theta)
+H.inv <- solve(H, diag(1, nrow = 4))
+omega <- (H.inv %*% sigma %*% H.inv) / dim(revs)[1]
+
+# Test if the probability to leave a review goes up: 
+# a(theta) = theta2 + theta4
+# Null: a(theta_0) = 0
+A <- matrix(c(0,1,0,1), nrow = 4)
+# t stat
+(theta[2] + theta[4])/sqrt(t(A) %*% omega %*% A)
+
+# Test if the probability to leave a like conditional on review (score) goes up
+# with a discount
+# a(theta) = (theta[1] + theta[3])/(sum(theta)) - theta[1]/(theta[1] + theta[3])
+grad.a <- function(x){
+
+  sum.x <- sum(x)
+
+  A1 <- (sum.x - x[1]) / (sum.x)^2 - x[3]/(x[1] + x[3])^2
+  A2 <- (sum.x - x[2]) / (sum.x)^2
+  A3 <- (- x[1] - x[2]) / (sum.x)^2  + x[1]/(x[1] + x[3])^2
+  A4 <- (- x[1] - x[2]) / (sum.x)^2
+
+  return(c(A1, A2, A3, A4))
+}
+
+A <- grad.a(theta)
+
+score.dif <- (theta[1] + theta[2])/(sum(theta)) - (theta[1])/(theta[1] + theta[3])
+
+score.dif/sqrt(t(A) %*% omega %*% A)
 ```

### 2020-09-23 Analysis/Code/Paper.Rmd
Added the tests on average like probabilities.

--- 2020-09-11 Analysis/Code/Paper.Rmd
@@
 # Empirical Model of Demand
-
+\label{demandSection}
 \textcolor{red}{Write a small introduction here.}
@@
 The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion.
-Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the positive treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(re23$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
+Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the positive treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg2$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
 Proximity to a potential negative transition seems to have negative or no effect on the probability of discount.
@@
 Both scenarios would appear to be relatively unrealistic ex ante, and my results for firms on the verge of a positive transition comply with that expectation.
-On the other hand, the predictions for games that are close to a review downgrade were more blurred.
+On the other hand, predictions for games that are close to a review downgrade were more blurred.
 It is reasonable to expect such products to dislike variance, unless the upside risk is strong.
-That would be the case reviews left during a discount are more positive, or if better review labels increase sales by a lot.
+The upside risk would be strong if reviews left during a discount were more positive, or if better review labels increased sales by a lot.
+I find no positive, nor negative effect of proximity to a negative transition on discounting behavior, which indicates that pros and cons balance out.
 
@@
 @ByersEtAl12 and @Li16 report that customers who choose to go to a restaurant because of a price promotion tend to leave worse reviews, even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19].
-Theoretically, this effect of buying on a discount on the valence of the review ambiguous.
+Theoretically, this effect of buying during a discount on the valence of the reviews is ambiguous.
 Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews.
@@
 
-# Selection Effect of Discounts
+# Discounts and Reviewing Behavior
+
+In the previous section I established two key facts.
+First, I found that firms are more likely to go on a discount when their products are close to upgrading their review bin.
+Second, I did not find any change in the discounting behavior for products that are close to downgrading their review bins.
+My theory of disconting in the face of review transitions, applied to these findings, implies that reviews left during a discount can not be significantly better than regular reviews, as otherwise the lack of discounting by products close to a review downgrade is puzzling.
+But if reviews obtained during a discount are not very different from the regular reviews, it has to be the case that discounts fascilitate the arrival of reviews, providing firms with extra variance when they want to speed things up.
+Otherwise, discounting by firms close to a positive transition would be puzzling.
+In this section I investigate if these two hypotheses about the valence and quantity of reviews left during price promotions hold in data.
+
+To formulate and test these hypotheses, I complement my model of demand and gaming on Steam introduced in Section \ref{demandSection} by a model of reviewing behavior.
+A formal model of reviewing behavior is necessary for several reasons.
+First, a structural model allows me to explicitly introduce the parameters of interest--probabilities of leaving a good or a bad reviews on and off a discount.
+Second, more importantly, the model will allow me to use my estimates of the demand process to make statements about the absolute change in probability of leaving a review that is due to the discount.
+One does not need a model to check if more reviews are left during a price promotion--a simple comparison of means would do.
+However, since sales are unobserved, it is impossible to say if the new reviews are entirely due to the influx of new customers, or part of it could be explained by an increased willingness to leave a review during a discount.
+I use my model to estimate sales, and therefore I can make inference on the propensity to leave a review.
+Note that most studies studying reviewing behavior do not observe anything close to daily sales, and thus could not possibly have indentified the effects I am interested here.
+
+As a preview of results, I do find that customers are significantly more likely to review a product if they purchase it during a price promotion, albeit the valence of the reviews is unaffected, on average.
+In other words, I provide evidence that, in my data, the negative selection effect of lower prices on the type of customers leaving reviews that has been documented in the literature does not outweigh the direct effect of lower prices on their satisfaction and their review decision.
+I then proceed to allow firms in my sample to be heterogeneous in the probabilities of recieving positive and negative reviews on and off discount.
+I check if firms whose customers are particularly likely to leave a like during a discount are more likely to discount, and I find some support for this hypothesis.
+
+## Review Model
 
@@
 \begin{assumption}\label{likeDiscountAss}
-The like rate is a linear function of discounts:
-$r_{it}^+ = \rho_{0i}^+ + \rho_{1i}^+ disc_{it-k}$.  The dislike rate is a linear function of discounts: $r_{it}^- = \rho_{0i}^- + \rho_{1i}^- disc_{it-k}$.
+The like rate is a linear function of covariates $w_{it} = [1, disc_{it}, \ldots]'$:
+$r_{it}^+ = w_{it}'\rho_i^+$.  The dislike rate is a linear function of covariates: $r_{it}^- = w_{it}'\rho_i^-$.
 \end{assumption}
 
-\noindent Notice, that a price change affects the reviewing behavior in two ways.
-First, a lower prices increases the inflow of buyers through a higher $\lambda_{it}$.
-This leads to more reviews being left.
-My parametrization allows to further study if the reviewers who bought the game on a discount are more or less likely to leave positive and negative reviews.
-I use a dummy variable $disc_{it-k}$ to measure discounting because this will allow me to derive a closed-form estimator for the  parameters of interest.
+In the simplest specification I use $w_{it} = [1, disc_{it}]'$, $\forall i: \rho_i^+ = \rho^+$,  implying $r_{it}^+ = \rho^+_0 + disc_{it}\rho^+_1$, which simply says that buyers of all games leave a positive reviews with one of two possible probabilities: $\rho^+_0$ off a discount, and $\rho^+_0 + \rho^+_1$ on a discount.
+Similarly, a probability of a negative review could be either $\rho^-_0$, or $\rho^-_0 + \rho^-_1$.
+While the model with no heterogeneity in parameters is not very realistic (for one, it implies that all games have the same expected review score), I treat the estimates that will come out of it as estimates of average parameter values: $\rho^+ \approx \bar{\rho}_i^+$, $\rho^- \approx \bar{\rho}_i^-$.
+Thus, a model without heterogeneiry offers a simple way to do inference on the average values of parameters in the population of games.
+
+As I explained in the introduction, I want to know if consumers are more likely to leave a review if they buy on a discount.
+This amounts to testing $\rho^+_0 + \rho^+_1 + \rho^-_0 + \rho^-_1 > \rho^+_0 + \rho^-_0$, or
+\begin{equation}\label{hypProbReview}
+  \rho^+_1 + \rho^-_1 > 0
+\end{equation}
+\noindent The second hypothesis I am interested in involves the sentiment of the reviews left on and off a discount.
+Product's review score measures the fraction of positive reviews among all reviews left, reflecting the probability to get a good review conditional on having a review.
+Formally, the expected review score of a game that never discounts is
+$$\EE{Score_{it}} = $$
 
@@
 ```{r}
+# In this module I estimate the average like and dislike rates on and off discount,
+# and I test whether: (a) users leave better reviews on a discount, (b) users leave
+# more reviews during discounts
 panel[, disc:=c(shift((discount > 0))), by = ID]
 panel[, lam:=shift(lambda), by = ID]
-panel[is.na(pReviews), pReviews := 0]
-panel[is.na(nReviews), nReviews := 0]
-
-revs <- panel[!(is.na(lam)), .(t, disc, lam, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]
-
+panel[is.na(pReviews), pReviews := 0] # remove this, it is already in CreateSample
+panel[is.na(nReviews), nReviews := 0] # remove this, it is already in CreateSample
+
+# part of the panel that has new reviews and estimated arrivals
+revs <- panel[!(is.na(lam)), .(t, lam, l = c(pReviews[1], diff(pReviews)), 
+                               d = c(nReviews[1], diff(nReviews)), const = 1, 
+                               zero = 0 ), by=ID]
+
+regressors <- c("disc", "young", "age")
+revs <- merge(revs, panel[!(is.na(lam)), c("ID", "t", regressors), with = F],
+              by = c("ID", "t"))
+revs[, old := age >= 365][, age := NULL]
+# NOTE: the first two regressors have to be "const" and "disc"
+regressors <- c("const", "disc", "young", "old")
+k <- length(regressors)
+
+# negative of the likelihood function
 revs.lik <- function(x){
-  revs[, r.plus := x[1] + disc*x[2], by = ID]
-  revs[, r.minus := x[3] + disc*x[4], by = ID]
-
+
+  revs[, r.plus := as.matrix(revs[, regressors, with = F]) %*% x[1:k]]
+  revs[, r.minus := as.matrix(revs[, regressors, with = F]) %*% x[(k+1):(2*k)]]
+
+  gradient.plus <- revs[, l/r.plus - lam] %*% as.matrix(revs[, regressors, with = F])
+  gradient.minus <- revs[, d/r.minus - lam] %*% as.matrix(revs[, regressors, with = F])
   return(list(
@@
                              d * log(r.minus) - r.minus*lam)],
-    "gradient" = -c(revs[, sum(l/r.plus - lam)],
-                   revs[, sum((l/r.plus - lam)*disc)],
-                   revs[, sum(d/r.minus - lam)],
-                   revs[, sum((d/r.minus - lam)*disc)])
+    "gradient" = -rbind(t(gradient.plus), t(gradient.minus))
   ))
@@
 
+# maximize the likelihood to estimate the parameters
 library(nloptr)
-
-x0 <- c(0.25, 0.0, 0.05, 0.0)
+x0 <- c(c(0.25, rep(0, k-1)), c(0.25, rep(0, k-1)))
 max.lik <- nloptr(x0, 
                   revs.lik,
-                  lb = c(0, -1, 0, -1),
-                  ub = c(10, 2, 10, 2),
+                  lb = c(0, 0, 0, -0.1, 0, 0, 0, -0.1),
+                  ub = rep(2, length(x0)),
                   opts = list(algorithm = "NLOPT_LD_LBFGS"))
 
-x <- max.lik$solution
+theta <- max.lik$solution
+
+# Estimate E[score score']
+sigma.hat <- function(x){
+  n <- dim(revs)[1]
+  revs[, r.plus := as.matrix(revs[, regressors, with = F]) %*% x[1:k]]
+  revs[, r.minus := as.matrix(revs[, regressors, with = F]) %*% x[(k+1):(2*k)]]
+
+  ans <- matrix(rep(0, 4*k^2), nrow = (2*k))
+
+  for (i in 1:n){
+    gradient.plus <- t(revs[i, l/r.plus - lam] * as.matrix(revs[i, regressors, with = F]))
+    gradient.minus <- t(revs[i, d/r.minus - lam] * as.matrix(revs[i, regressors, with = F]))
+    score <- rbind(gradient.plus, gradient.minus)
+    ans <- ans + score %*% t(score)
+  }
+
+  return(ans/n)
+}
+
+# Estimate the hessian d(score)/d theta'
+H.hat <- function(x){
+  n <- dim(revs)[1]
+  revs[, r.plus := as.matrix(revs[, regressors, with = F]) %*% x[1:k]]
+  revs[, r.minus := as.matrix(revs[, regressors, with = F]) %*% x[(k+1):(2*k)]]
+
+  H <- matrix(rep(0, 4*k^2), nrow = (2*k))
+
+  for (i in 1:n){
+    zeros <- rep("zero", k)
+    h1 <- revs[i, c(regressors, zeros), with = F] %>% as.matrix() %>% matrix(., nrow = 1)
+    h2 <- revs[i, c(zeros, regressors), with = F] %>% as.matrix() %>% matrix(., nrow = 1)
+    dr.drho <- rbind(h1, h2)
+    dlik.dr <- revs[i, .(-l/((r.plus)^2), 0, 0, -d/((r.minus)^2))] %>%
+               as.matrix() %>% matrix(., nrow = 2)
+    H <- H + t(dr.drho) %*% dlik.dr %*% dr.drho
+  }
+
+  return(H/n)
+}
+
+# calculate the variance-covariance matrix of theta hat (asymptotic divided by n)
+sigma <- sigma.hat(theta)
+H <- H.hat(theta)
+H.inv <- solve(H, diag(1, nrow = (2*k)))
+omega <- (H.inv %*% sigma %*% H.inv) / dim(revs)[1]
+
+# Test if the probability to leave a review goes up: 
+# a(theta) = theta[2] + theta[2+k]
+# Null: a(theta_0) = 0
+A <- rep(0, 2*k)
+A[2] <- 1
+A[2+k] <- 1
+# t stat
+(theta[2] + theta[2+k])/sqrt(t(A) %*% omega %*% A)
+
+# Test if the probability to leave a like conditional on review (score) goes up
+# with a discount
+# a(theta) = (theta[1] + theta[1+k])/(sum(theta[c(1,2,1+k,2+k)])) - theta[1]/(theta[1] + theta[1+k])
+grad.a <- function(x){
+
+  ans <- rep(0, length(x))
+  sum.x <- sum(x[c(1,2,1+k,2+k)])
+
+  ans[1] <- (sum.x - x[1]) / (sum.x)^2 - x[1+k]/(x[1] + x[1+k])^2
+  ans[2] <- (sum.x - x[2]) / (sum.x)^2
+  ans[1+k] <- (- x[1] - x[2]) / (sum.x)^2  + x[1]/(x[1] + x[1+k])^2
+  ans[2+k] <- (- x[1] - x[2]) / (sum.x)^2
+
+  return(ans)
+}
+
+A <- grad.a(theta)
+
+score.dif <- (theta[1] + theta[2])/(sum(theta[c(1,2,1+k,2+k)])) - 
+             (theta[1])/(theta[1] + theta[1+k])
+
+score.dif/sqrt(t(A) %*% omega %*% A)
 ```
@@
 
-```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'}
-p1 <- ggplot(data = revs[, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) +
-  geom_histogram(mapping = aes(x = x, y = ..density..),
-                 color = "black",
-                 position = "identity",
-                 boundary = 0,
-                 alpha = 0.9,
-                 binwidth = 0.1,
-                 fill = my.colors[1]) +
-  geom_density(mapping = aes(x = x),
-                 color = "black",
-                 position = "identity",
-                 alpha = 0.4,
-                 fill = my.colors[1]) +
-  scale_x_continuous(name = "Change in Like Rates",
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = NULL,
-                     breaks = c(0, 1, 2),
-                     minor_breaks = NULL) +
-  my.theme() +
-  coord_cartesian(xlim = c(-0.5, 2))
-
-p2 <- ggplot(data = revs[, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) +
-  geom_histogram(mapping = aes(x = x, y = ..density..),
-                 color = "black",
-                 position = "identity",
-                 boundary = 0,
-                 binwidth = 0.025,
-                 alpha = 0.9,
-                 fill = my.colors[1]) +
-  geom_density(mapping = aes(x = x),
-                 color = "black",
-                 position = "identity",
-                 alpha = 0.4,
-                 fill = my.colors[1]) +
-  scale_x_continuous(name = "Change in Dislike Rates",
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = NULL,
-                     minor_breaks = NULL) +
-  my.theme() +
-  coord_cartesian(xlim = c(-0.5, 2))
-
-ggarrange(p1, p2, nrow=1, align = "h")
-```
-
-```{r like-rates, fig.width = 8, fig.height = 6, include = FALSE}
-ggarrange(p1, p2, nrow=2, align = "v")
-```
-
-The main parameters of interest in this section are $(\rho_{1i}^+, \rho_{1i}^-)$, which measure the change in the like and dislike rates during discounts.
+<!-- ```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'} -->
+<!-- p1 <- ggplot(data = revs[, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) + -->
+<!--   geom_histogram(mapping = aes(x = x, y = ..density..), -->
+<!--                  color = "black", -->
+<!--                  position = "identity", -->
+<!--                  boundary = 0, -->
+<!--                  alpha = 0.9, -->
+<!--                  binwidth = 0.1, -->
+<!--                  fill = my.colors[1]) + -->
+<!--   geom_density(mapping = aes(x = x), -->
+<!--                  color = "black", -->
+<!--                  position = "identity", -->
+<!--                  alpha = 0.4, -->
+<!--                  fill = my.colors[1]) + -->
+<!--   scale_x_continuous(name = "Change in Like Rates", -->
+<!--                      minor_breaks = NULL) + -->
+<!--   scale_y_continuous(name = NULL, -->
+<!--                      breaks = c(0, 1, 2), -->
+<!--                      minor_breaks = NULL) + -->
+<!--   my.theme() + -->
+<!--   coord_cartesian(xlim = c(-0.5, 2)) -->
+
+<!-- p2 <- ggplot(data = revs[, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) + -->
+<!--   geom_histogram(mapping = aes(x = x, y = ..density..), -->
+<!--                  color = "black", -->
+<!--                  position = "identity", -->
+<!--                  boundary = 0, -->
+<!--                  binwidth = 0.025, -->
+<!--                  alpha = 0.9, -->
+<!--                  fill = my.colors[1]) + -->
+<!--   geom_density(mapping = aes(x = x), -->
+<!--                  color = "black", -->
+<!--                  position = "identity", -->
+<!--                  alpha = 0.4, -->
+<!--                  fill = my.colors[1]) + -->
+<!--   scale_x_continuous(name = "Change in Dislike Rates", -->
+<!--                      minor_breaks = NULL) + -->
+<!--   scale_y_continuous(name = NULL, -->
+<!--                      minor_breaks = NULL) + -->
+<!--   my.theme() + -->
+<!--   coord_cartesian(xlim = c(-0.5, 2)) -->
+
+<!-- ggarrange(p1, p2, nrow=1, align = "h") -->
+<!-- ``` -->
+
+<!-- ```{r like-rates, fig.width = 8, fig.height = 6, include = FALSE} -->
+<!-- ggarrange(p1, p2, nrow=2, align = "v") -->
+<!-- ``` -->
+
+<!-- The main parameters of interest in this section are $(\rho_{1i}^+, \rho_{1i}^-)$, which measure the change in the like and dislike rates during discounts.
 The precision with which this parameter could be estimated for game $i$ depends on the number of discount days we observe for that game.
@@
 Second, the like rates appear to be way more responsive to discounts than the dislike rates.
-
-These findings require some interpretation.
+-->
+
+<!-- These findings require some interpretation.
 @Li16 claims “It is by now almost accepted as a stylized fact that offering deal promotion [...] deteriorates local merchants' online reputations”, while my findings seem to suggest that discounts improve review scores.
-Column (2) in Table \ref{reviewLag} in the Appendix presents the results of
-regressing review score on days after a discount (with controls).
+Column (2) in Table \ref{reviewLag} in the Appendix presents the results of  -->
+<!-- regressing review score on days after a discount (with controls).
 The results suggest that, on average, the review score goes down, not up, in the days following a discount.
@@
 However, my findings present an interesting puzzle for future investigation: how does the (average) negative response of review score to discounts coexist with the distribution of products that seem to receive better reviews during discounts, not worse.
-
-\textcolor{red}{Looks like consumers are more likely to leave reviews during a discount. That could be interesting. Calculate standard errors for that?}
-
-## Revisiting Discounting and Transitions
-
-Now that I have estimated the parameters of the demand and review processes, I am ready to use them to revisit my
-main hypothesis. In Section \ref{descriptiveEvidence} I have established that
-
-```{r results = 'asis', warning = FALSE}
-# remove 1% with the highest values of rho_1+ (<=2)
-# and only keep significant coefficients
-panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, score.dif)])
-
-panel[, pos.treatment := (needPos <= 2*band)]
-panel[, neg.treatment := (needNeg <= 2*band)]
-
-reg1 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
-               mPositive + realPositive + vPositive + age + young + day + week,
-           data = panel[rho1 <= 2 & rho1 >= -0.5,],
-           model = "pooling")
-cov<-vcovHC(reg1, method="white1")
-se1 <- sqrt(diag(cov))
-
-reg2 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
-               mPositive + realPositive + vPositive + age + young + day + week,
-           data = panel[rho1 <= 2 & rho1 >= -0.5 & 
-                        ID %in% revs[negSignif == T | posSignif == T, ID], 
-                        ],
-           model = "pooling")
-cov<-vcovHC(reg2, method="white1")
-se2 <- sqrt(diag(cov))
-
-reg3 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
-               mPositive + realPositive + vPositive + age + young + day + week,
-           data = panel[rho1 <= 2 & rho1 >= -0.5
-                        # ID %in% revs[negSignif == T | posSignif == T, ID], 
-                        ],
-           model="within",
-           index = c("ID", "t"))
-cov<-vcovHC(reg3, method = "white1")
-se3 <- sqrt(diag(cov))
-
-reg4 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
-               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
-               mPositive + realPositive + vPositive + age + young + day + week,
-           data = panel[rho1 <= 2 & rho1 >= -0.5 & 
-                        ID %in% revs[negSignif == T | posSignif == T, ID], 
-                        ],
-           model="within",
-           index = c("ID", "t"))
-cov<-vcovHC(reg4, method = "white1")
-se4 <- sqrt(diag(cov))
-
-star.out<-stargazer(reg1, reg2, reg3, reg4,
-                    label = "rhoTransDiscReg",
-                    header = FALSE,
-                    title = "Discounts Before Potential Transitions And Firm Heterogeneity",
-                    se=list(se1, se2, se3, se4),
-                    dep.var.labels = c("$\\mathbb{P}(Discount)$"),
-                    column.labels=c("OLS", "OLS:Signif", "FE", "FE:Signif"),
-                    model.numbers = F,
-                    omit = c("tWODisc", "reviews", "noScore", "realPositive", 
-                             "mPositive", "vPositive", "age", "young", "Constant",
-                             "score", "day", "week", "needPosDays", "needNegDays"),
-                    covariate.labels = c("$\\rho_1^+$",
-                                         "$\\rho_1^+ \\times$ Pos. Tr.",
-                                         "$\\rho_1^+ \\times$ Neg. Tr.",
-                                         "Pos. Tr.", "Neg. Tr."),
-                    order = c("rho1"),
-                    omit.stat=c("f","adj.rsq","ser"),
-                    no.space=T)
-```
+-->
+
+<!-- \textcolor{red}{Looks like consumers are more likely to leave reviews during a discount. That could be interesting. Calculate standard errors for that?} -->
+
+<!-- ## Revisiting Discounting and Transitions -->
+
+<!-- Now that I have estimated the parameters of the demand and review processes, I am ready to use them to revisit my -->
+<!-- main hypothesis. In Section \ref{descriptiveEvidence} I have established that  -->
+
+<!-- ```{r results = 'asis', warning = FALSE} -->
+<!-- # remove 1% with the highest values of rho_1+ (<=2) -->
+<!-- # and only keep significant coefficients -->
+<!-- panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, score.dif)]) -->
+
+<!-- panel[, pos.treatment := (needPos <= 2*band)] -->
+<!-- panel[, neg.treatment := (needNeg <= 2*band)] -->
+
+<!-- reg1 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
+<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
+<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
+<!--            data = panel[rho1 <= 2 & rho1 >= -0.5,], -->
+<!--            model = "pooling") -->
+<!-- cov<-vcovHC(reg1, method="white1") -->
+<!-- se1 <- sqrt(diag(cov)) -->
+
+<!-- reg2 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
+<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
+<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
+<!--            data = panel[rho1 <= 2 & rho1 >= -0.5 &  -->
+<!--                         ID %in% revs[negSignif == T | posSignif == T, ID],  -->
+<!--                         ], -->
+<!--            model = "pooling") -->
+<!-- cov<-vcovHC(reg2, method="white1") -->
+<!-- se2 <- sqrt(diag(cov)) -->
+
+<!-- reg3 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
+<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
+<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
+<!--            data = panel[rho1 <= 2 & rho1 >= -0.5 -->
+<!--                         # ID %in% revs[negSignif == T | posSignif == T, ID],  -->
+<!--                         ], -->
+<!--            model="within", -->
+<!--            index = c("ID", "t")) -->
+<!-- cov<-vcovHC(reg3, method = "white1") -->
+<!-- se3 <- sqrt(diag(cov)) -->
+
+<!-- reg4 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
+<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
+<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
+<!--            data = panel[rho1 <= 2 & rho1 >= -0.5 &  -->
+<!--                         ID %in% revs[negSignif == T | posSignif == T, ID],  -->
+<!--                         ], -->
+<!--            model="within", -->
+<!--            index = c("ID", "t")) -->
+<!-- cov<-vcovHC(reg4, method = "white1") -->
+<!-- se4 <- sqrt(diag(cov)) -->
+
+<!-- star.out<-stargazer(reg1, reg2, reg3, reg4, -->
+<!--                     label = "rhoTransDiscReg", -->
+<!--                     header = FALSE, -->
+<!--                     title = "Discounts Before Potential Transitions And Firm Heterogeneity", -->
+<!--                     se=list(se1, se2, se3, se4), -->
+<!--                     dep.var.labels = c("$\\mathbb{P}(Discount)$"), -->
+<!--                     column.labels=c("OLS", "OLS:Signif", "FE", "FE:Signif"), -->
+<!--                     model.numbers = F, -->
+<!--                     omit = c("tWODisc", "reviews", "noScore", "realPositive",  -->
+<!--                              "mPositive", "vPositive", "age", "young", "Constant", -->
+<!--                              "score", "day", "week", "needPosDays", "needNegDays"), -->
+<!--                     covariate.labels = c("$\\rho_1^+$", -->
+<!--                                          "$\\rho_1^+ \\times$ Pos. Tr.", -->
+<!--                                          "$\\rho_1^+ \\times$ Neg. Tr.", -->
+<!--                                          "Pos. Tr.", "Neg. Tr."), -->
+<!--                     order = c("rho1"), -->
+<!--                     omit.stat=c("f","adj.rsq","ser"), -->
+<!--                     no.space=T) -->
+<!-- ``` -->
 
@@
                            discNewLag5 + discNewLag6 + discNewLag7 +
-                           negative + mPositive + realPositive + vPositive + ovPositive +
+                           # negative + mPositive + realPositive + vPositive + ovPositive +
                            log(reviews + 1) + age + young + day + week,
@@
              se=list(se1, se2, se3),
-             dep.var.labels = c("New Reviews", "New Reviews \\%", "Score (0-100)"),
+             dep.var.labels = c("New Reviews", "New Reviews(\\%)", "Score (0-100)"),
              covariate.labels = c("Discount 0 Days Ago", "Discount 1 Day Ago",

### 2020-09-24 Analysis/Code/Paper.Rmd
new material

@@
 The focus of the analysis is on the difference between the reviews left on and off a discount.
-To that end, I parametrize the like and dislike rates to depend on the discounting behavior of the firm as follows.
+To that end, I parametrize the like and dislike rates to depend on the discounting behavior of the firm and other covariates as  as follows.
 
 \begin{assumption}\label{likeDiscountAss}
-The like rate is a linear function of covariates $w_{it} = [1, disc_{it}, \ldots]'$:
+The like rate is a linear function of covariates $w_{it} = [1, disc_{it-k}, \ldots]'$:
 $r_{it}^+ = w_{it}'\rho_i^+$.  The dislike rate is a linear function of covariates: $r_{it}^- = w_{it}'\rho_i^-$.
@@
 
-In the simplest specification I use $w_{it} = [1, disc_{it}]'$, $\forall i: \rho_i^+ = \rho^+$,  implying $r_{it}^+ = \rho^+_0 + disc_{it}\rho^+_1$, which simply says that buyers of all games leave a positive reviews with one of two possible probabilities: $\rho^+_0$ off a discount, and $\rho^+_0 + \rho^+_1$ on a discount.
+In the simplest specification I use $w_{it} = [1, disc_{it-k}]'$, $\forall i: \rho_i^+ = \rho^+$,  implying $r_{it}^+ = \rho^+_0 + disc_{it}\rho^+_1$, which simply says that buyers of all games leave a positive reviews with one of the two possible probabilities: $\rho^+_0$ off a discount, and $\rho^+_0 + \rho^+_1$ on a discount.
 Similarly, a probability of a negative review could be either $\rho^-_0$, or $\rho^-_0 + \rho^-_1$.
 While the model with no heterogeneity in parameters is not very realistic (for one, it implies that all games have the same expected review score), I treat the estimates that will come out of it as estimates of average parameter values: $\rho^+ \approx \bar{\rho}_i^+$, $\rho^- \approx \bar{\rho}_i^-$.
-Thus, a model without heterogeneiry offers a simple way to do inference on the average values of parameters in the population of games.
-
-As I explained in the introduction, I want to know if consumers are more likely to leave a review if they buy on a discount.
+Thus, a model without heterogeneity offers a simple way to do inference on the average values of parameters in the population of games.
+
+In the introduction to this section I outlined two hypotheses I want to test.
+First, I want to know if consumers are more likely to leave a review if they buy on a discount.
 This amounts to testing $\rho^+_0 + \rho^+_1 + \rho^-_0 + \rho^-_1 > \rho^+_0 + \rho^-_0$, or
-\begin{equation}\label{hypProbReview}
-  \rho^+_1 + \rho^-_1 > 0
+\begin{align}\label{hyp1}
+H_0: &  \rho^+_1 + \rho^-_1 > 0 \\
+H_1: &  \rho^+_1 + \rho^-_1 \le 0
+\end{align}
+
+The second hypothesis I am interested in involves the sentiment of the reviews left on and off a discount.
+Product's review score measures the fraction of positive reviews among all reviews left, reflecting the probability to get a good review conditional on having a review.
+Indeed, if $L_t \in \{0, 1\}$ is a random variable that takes the value of 1 if the $i$-th review is a like, then the review score based on $T$ reviews would simply be $Score(T) = \frac 1 T \sum_{t=1}^T L_t$, which converges to $\EE{L_t} = \PP{L_t = 1}$ as $T$ grows to infinity.
+For a user buying a game off a discount we have
+\begin{equation}
+\PP{L_t = 1} = \CP{"Like"}{"Review"} = \frac{\rho^+_{0}}{\rho^+_{0} + \rho^-_{0}}
 \end{equation}
-\noindent The second hypothesis I am interested in involves the sentiment of the reviews left on and off a discount.
-Product's review score measures the fraction of positive reviews among all reviews left, reflecting the probability to get a good review conditional on having a review.
-Formally, the expected review score of a game that never discounts is
-$$\EE{Score_{it}} = $$
-
-### Review Parameters
-
-The part of the model describing the reviewing behavior of the buyers is more starightforward.
+
+\noindent For a user buying the same game on a discount we have
+\begin{equation}
+\PP{L_t = 1} = \CP{"Like"}{"Review"} = \frac{\rho^+_{0} + \rho^+_{1}}{\rho^+_{0} + \rho^+_{1} + \rho^-_{0} + \rho^-_{1}}
+\end{equation}
+
+\noindent The second hypothesis can now be formulated as follows: the expected review score on a discount is not higher than the expected review score off a discount. Formally, we have
+\begin{align}\label{hyp2}
+H_0: &  \frac{\rho^+_{0}}{\rho^+_{0} + \rho^-_{0}} - \frac{\rho^+_{0} + \rho^+_{1}}{\rho^+_{0} + \rho^+_{1} + \rho^-_{0} + \rho^-_{1}} > 0 \\
+H_1: &  \frac{\rho^+_{0}}{\rho^+_{0} + \rho^-_{0}} - \frac{\rho^+_{0} + \rho^+_{1}}{\rho^+_{0} + \rho^+_{1} + \rho^-_{0} + \rho^-_{1}}  \le 0
+\end{align}
+
+## Identification
+
+To make my identificaiton argument I will focus on the case of just two regressors, $w_{it} = [1, disc_{it-k}]$, and heterogeneous parameters $\rho_i^+$, $\rho_i^-$.
+From this analysis it will become clear how I am able to identify $\rho$'s on a game-by-game basis, and how more regressors could be accommodated.
 Intuitively, the propensity to leave a review on and off a discount (the like and dislike rates $r_{it}^+$, $r_{it}^-$) are identified by the differences in reviews left on and off a discount.
-In fact, this intuition becomes a rigorous proof, as wil be shown shortly.
+In fact, this intuition becomes a rigorous proof, as will be shown shortly.
+The proof will also highlight the importance of having estimated the arrival rates of consumers.
 
@@
 
-I treat $\lambda_{it}$ as known, because parameters $\lambda_{i}$ and $\beta$ that determine it can be estimated consistently for the majority of games in the sample, given the long time dimension of the panel.
+For simplicity, I treat $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$ as known, rather than aknowledging the fact that I only have estimates $\hat{\lambda}_{it} = \hat \lambda_i (1 + x_{it}'\hat \beta)$.
+By the virtue of observing the majority of the games for many periods, the estimates of $\lambda_i$ should be relatively precise; estimates of $\beta$ were estimated using all the observations in the sample, and should be relatively precise as well.
 For now I also take the lag $k$ between the time when the user buys the game and leaves a review for the game to be known.
@@
 The likelihood is concave in the parameters, so the parameters are identified as the maximizer of the likelihood.
-Restricting attention to a binary discount variable $disc_{it}$ allows me to derive a closed-form estimator for $(\rho_{0i}^+, \rho_{1i}^+)$.
+Restricting attention to a binary discount variable $disc_{it}$ allows me to derive a closed-form estimator for $(\rho_{0i}^+, \rho_{1i}^+)$, which is convenient and illustrates the source of identification better.
 During a discount the like rate of game $i$ is $\rho_{0i}^+ + \rho_{1i}^+$, which is consistently estimated as
@@
 with the interpretation that the like rate in the absence of a discount is just a ratio of the reviews left outside of a discount and the expected number of customers outside a discount.
-
-Note that one can use these estimators to estimate the *average review score* on and off a discount, i.e., whether users are relatively more or less likely to leave a good review during a discount.
-For example, without a price promotion, one obtains
+Notice that identification of these parameters requires the knowledge of the demand parameters $\lambda_{it}$, highlighting the point I made earlier: seeing more good reviews arriving on a discount is not sufficient to conclude whether customers are more likely to leave positive reviews when purchasing during a discount.
+One need to know how many more customers are buying because of the aforementioned discount.
+
+My second hypothesis, formulated in (\ref{hyp2}), involves the sentiment of the reviews left on and off a price promotion.
+Intuitively, one should be able to detect a change in the valence of reviews during a price promotion by simply comparing the ratios of good to bad reviews on and off a discount.
+In particular, the answer should not depend on any information on the absolute sales.
+Indeed, if we plug  in the estimators from (\ref{rhohat1})-(\ref{rhohat2}) into the expression for the expected review score off a discount from (\ref{hyp2}), we can see that our inference here will not depend on the estimates of the demand parameters in $\lambda_{it}$:
 \begin{equation}\label{avReviewScore}
+\frac{\hat \rho_{0i}^+}{\hat \rho_{0i}^+  + \hat \rho_{0i}^- }
+=
 \frac{\sum_{t\ge k} (1-disc_{it-k})g_{it}}{\sum_{t\ge k} (1-disc_{it-k})g_{it} + \sum_{t\ge k} (1-disc_{it-k})b_{it}}
-=
-\frac{\hat \rho_{0i}^+}{\hat \rho_{0i}^+  + \hat \rho_{0i}^- }
 \end{equation}
-It is intuitively clear that the relative propensity to leave a good, rather than a bad, review should be easily estimable by comparing the ratios of good to bad reviews, without any knowledge of the quantity of games sold.
-This intuition is fully reflected in Equation (\ref{avReviewScore}), where the arrival rates $\lambda_{it-k}$ have disappeared entirely.
+The estimator off the review score off a discount simply calculates the average of the positive reviews left off a discount among all the reviews left off a discount, confirming our intuition.
 
@@
 First, for each game I observe the exact review count, but my demand estimates only apply to rush hours.
-If, say, every player leaves a review, and every day there are two new players who play in the morning, and three new players who play in the evening, my data would register 3 players leaving 5 reviews on a daily basis.
+For a sake of example, assume that every buyer leaves a review.
+Suppose also that every day there are two new buyers who play in the morning, and three new buyers who play in the evening, who abandone the game after just one day.
+My data would register 3 players leaving 5 reviews on a daily basis.
 This is the reason why I refer to the values of $(r_{it}^+, r_{it}^-)$ as rates, rather than probabilities (which they are in the model).
-Propositon \ref{poissonReviews}, stating that the number of good reviews on day $t$ for game $i$ is a Poisson random variable with rate $r_{it}^+\lambda_{it-k}$, could be treated as an assumption, rather than a result.
-In that case, nothing constrains the $r_{it}^+$ parameter to be less than 1, and the identification argument goes through in the exactly the same way.
+Proposition \ref{poissonReviews}, stating that the number of good reviews on day $t$ for game $i$ is a Poisson random variable with rate $r_{it}^+\lambda_{it-k}$, could be treated as an assumption, rather than a result.
+In that case, nothing constrains the $r_{it}^+$ parameter to be less than 1, and the identification argument goes through in exactly the same way.
 
@@
 For that reason, the model features an additional parameter $k$, the lag between purchasing the game and leaving a review, that I assumed to be known.
-To estimate that parameter I leverage the fact that spikes in player activity on the first day of a sale represent new users, and study the review response during the following week in order to uncover the modal lag for leaving a review (see Table \ref{reviewLag} in the Appendix).
+To estimate this parameter I leverage the fact that spikes in player activity on the first day of a sale represent new users, and study the review response during the following week in order to uncover the modal lag for leaving a review (see Table \ref{reviewLag} in the Appendix).
 This number turns out to be one day.
-Even though time to posting a review has a non-degenerate distribution, modelling it in a more nuanced way would significantly contribute to complexity: the likelihood of receiving a poisitive review on day 100 would depend on the entire history of buyer arrivals prior to that date.
+Even though time to posting a review has a non-degenerate distribution, modeling it in a more nuanced way would significantly contribute to complexity: the likelihood of receiving a positive review on day 100 would depend on the entire history of buyer arrivals prior to that date.
 Therefore, I proceed using $\hat k = 1$.

### 2020-09-25 Analysis/Code/Paper.Rmd
review model estimated and written down.

@@
 library(texreg)
+library(nloptr)
 
@@
 ## Stylized Model
+\label{stylizedModel}
 
@@
 I use my model to estimate sales, and therefore I can make inference on the propensity to leave a review.
-Note that most studies studying reviewing behavior do not observe anything close to daily sales, and thus could not possibly have indentified the effects I am interested here.
+Note that most studies studying reviewing behavior do not observe anything close to daily sales, and thus could not possibly have identified the effects I am interested here.
 
@@
 In other words, I provide evidence that, in my data, the negative selection effect of lower prices on the type of customers leaving reviews that has been documented in the literature does not outweigh the direct effect of lower prices on their satisfaction and their review decision.
-I then proceed to allow firms in my sample to be heterogeneous in the probabilities of recieving positive and negative reviews on and off discount.
+I then proceed to allow firms in my sample to be heterogeneous in the probabilities of receiving positive and negative reviews on and off discount.
 I check if firms whose customers are particularly likely to leave a like during a discount are more likely to discount, and I find some support for this hypothesis.
@@
 \begin{align}\label{hyp1}
-H_0: &  \rho^+_1 + \rho^-_1 > 0 \\
-H_1: &  \rho^+_1 + \rho^-_1 \le 0
+H_0: &  \rho^+_1 + \rho^-_1 \le 0 \\
+H_1: &  \rho^+_1 + \rho^-_1 > 0
 \end{align}
@@
 \begin{align}\label{hyp2}
-H_0: &  \frac{\rho^+_{0}}{\rho^+_{0} + \rho^-_{0}} - \frac{\rho^+_{0} + \rho^+_{1}}{\rho^+_{0} + \rho^+_{1} + \rho^-_{0} + \rho^-_{1}} > 0 \\
-H_1: &  \frac{\rho^+_{0}}{\rho^+_{0} + \rho^-_{0}} - \frac{\rho^+_{0} + \rho^+_{1}}{\rho^+_{0} + \rho^+_{1} + \rho^-_{0} + \rho^-_{1}}  \le 0
+H_0: &  \frac{\rho^+_{0} + \rho^+_{1}}{\rho^+_{0} + \rho^+_{1} + \rho^-_{0} + \rho^-_{1}} - \frac{\rho^+_{0}}{\rho^+_{0} + \rho^-_{0}} \le 0 \\
+H_1: & \frac{\rho^+_{0} + \rho^+_{1}}{\rho^+_{0} + \rho^+_{1} + \rho^-_{0} + \rho^-_{1}} - \frac{\rho^+_{0}}{\rho^+_{0} + \rho^-_{0}} > 0
 \end{align}
@@
 \end{equation}
-The estimator off the review score off a discount simply calculates the average of the positive reviews left off a discount among all the reviews left off a discount, confirming our intuition.
+The estimator of the review score off a discount simply calculates the average of the positive reviews left off a discount among all the reviews left off a discount, confirming our intuition.
 
@@
 
-### Review Parameters
-
-```{r}
-# Notice that rhoPosD is the sum of the parameters I defined
-# in the text, rho_0i^+ and rho_1i^+, but the variance matrix is
-# calculated for the original parameters
-
-# Shifting the variables because I am using lag k = 1
-panel[, disc:=c(shift((discount > 0))), by = ID]
-panel[, lam:=shift(lambda), by = ID]
-panel[is.na(pReviews), pReviews := 0]
-panel[is.na(nReviews), nReviews := 0]
-
-revs <- panel[!(is.na(lam)), .(t, disc, lam, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]
-revs <- revs[, .(rhoPosD = sum(disc*l) / sum(disc*lam),
-                 rhoPosND = sum((1-disc)*l) / sum((1-disc)*lam),
-                 rhoNegD = sum(disc*d) / sum(disc*lam),
-                 rhoNegND = sum((1-disc)*d) / sum((1-disc)*lam)),
-              by = ID]
-revs <- revs[!is.na(rhoPosD)]
-
-# calculate s.e.
-id.matrix <- matrix(c(1,0,0,1), nrow=2)
-for (id in revs[, ID]){
-   sums <- panel[ID==id, .(disc, lam)][, sum(lam), by=disc][!is.na(disc),]
-
-   matND <- matrix(c(sums[disc==F,V1],0,0,0), nrow=2)
-   matD <- matrix(rep(sums[disc==T,V1],4), nrow=2)
-
-   Hpos <- matND/revs[ID==id, rhoPosND] + matD/revs[ID==id, rhoPosD]
-   HposInv <- tryCatch(solve(Hpos, id.matrix),
-                       error = function(x){return(matrix(rep(NA,4), 
-                                                         nrow = 2))})
-
-   Hneg <- matND/revs[ID==id, rhoNegND] + matD/revs[ID==id, rhoNegD]
-   HnegInv <- tryCatch(solve(Hneg, id.matrix),
-                       error = function(x){return(matrix(rep(NA,4), 
-                                                         nrow = 2))})
-
-   revs[ID==id, rhoPos0se := sqrt(HposInv[1,1])]
-   revs[ID==id, rhoPos1se := sqrt(HposInv[2,2])]
-
-   revs[ID==id, rhoNeg0se := sqrt(HnegInv[1,1])]
-   revs[ID==id, rhoNeg1se := sqrt(HnegInv[2,2])]
-}
-
-# label all games with significant rho_1^+
-revs[, posSignif := abs((rhoPosD-rhoPosND)/rhoPos1se) >= 1.96]
-revs[, negSignif := abs((rhoNegD-rhoNegND)/rhoNeg1se) >= 1.96]
-
-# score off discount and score on discount
-revs[, scoreND := rhoPosND/(rhoPosND+rhoNegND)]
-revs[, scoreD := rhoPosD/(rhoPosD+rhoNegD)]
-revs[, score.dif := scoreD - scoreND]
-
-rm(Hpos, Hneg, HnegInv, HposInv)
-```
+## Estimation and Inference
 
@@
 # more reviews during discounts
-panel[, disc:=c(shift((discount > 0))), by = ID]
-panel[, lam:=shift(lambda), by = ID]
+
+# preparation for formatting the estimates in a table
+texregObjects <- list()
+gofnames <- c("Observations")
+
+review.lag <- 1
+panel[, disc:=c(shift((discount > 0), review.lag)), by = ID] # reflecting k = 1
+panel[, lam:=shift(lambda, review.lag), by = ID]
 panel[is.na(pReviews), pReviews := 0] # remove this, it is already in CreateSample
@@
 
+# part of the panel that has new reviews and estimated arrivals
+revs <- panel[!(is.na(lam)), .(t, lam, l = c(pReviews[1], diff(pReviews)), 
+                               d = c(nReviews[1], diff(nReviews)), const = 1, 
+                               zero = 0 ), by=ID]
+
+regressors <- c("disc")
+revs <- merge(revs, panel[!(is.na(lam)), c("ID", "t", regressors), with = F],
+              by = c("ID", "t"))
+
+# NOTE: the first two regressors have to be "const" and "disc"
+regressors <- c("const", regressors)
+k <- length(regressors)
+
+# maximize the likelihood to estimate the parameters
+x0 <- c(c(0.25, rep(0, k-1)), c(0.25, rep(0, k-1)))
+max.lik <- nloptr(x0, 
+                  revs.lik,
+                  lb = rep(0, 2*k),
+                  ub = rep(2, 2*k),
+                  opts = list(algorithm = "NLOPT_LD_LBFGS"))
+
+theta1 <- max.lik$solution
+
+# calculate the variance-covariance matrix of theta hat (asymptotic divided by n)
+sigma <- sigma.hat(theta1)
+H <- H.hat(theta1)
+H.inv <- solve(H, diag(1, nrow = (2*k)))
+omega1 <- (H.inv %*% sigma %*% H.inv) / dim(revs)[1]
+
+# Test if the probability to leave a review goes up: 
+# a(theta) = theta[2] + theta[2+k]
+# Null: a(theta_0) = 0
+A <- rep(0, 2*k)
+A[2] <- 1
+A[2+k] <- 1
+# t stat
+t1.1 <- (theta1[2] + theta1[2+k])/sqrt(t(A) %*% omega1 %*% A)
+
+# Test if the probability to leave a like conditional on review (score) goes up
+# with a discount
+# a(theta) = (theta[1] + theta[1+k])/(sum(theta[c(1,2,1+k,2+k)])) - theta[1]/(theta[1] + theta[1+k])
+A <- grad.a(theta1)
+score.dif <- (theta1[1] + theta1[2])/(sum(theta1[c(1,2,1+k,2+k)])) - 
+             (theta1[1])/(theta1[1] + theta1[1+k])
+t2.1 <- score.dif/sqrt(t(A) %*% omega1 %*% A)
+
+# Append to the output table
+pvalues <- 2*(1-pnorm(theta1/sqrt(diag(omega1))))
+tr <- createTexreg(coef = theta1,
+                   coef.names = c("Prob. of Like", "Discount on Like", 
+                                  "Prob. of Dislike", "Discount on Dislike"),
+                   se = sqrt(diag(omega1)),
+                   pvalues = pvalues,
+                   gof.names = gofnames,
+                   gof = c(dim(revs)[1]))
+texregObjects[1] <- list(tr)
+
+# ~ SECOND SPECIFICATION
 # part of the panel that has new reviews and estimated arrivals
@@
 
-# negative of the likelihood function
-revs.lik <- function(x){
-
-  revs[, r.plus := as.matrix(revs[, regressors, with = F]) %*% x[1:k]]
-  revs[, r.minus := as.matrix(revs[, regressors, with = F]) %*% x[(k+1):(2*k)]]
-
-  gradient.plus <- revs[, l/r.plus - lam] %*% as.matrix(revs[, regressors, with = F])
-  gradient.minus <- revs[, d/r.minus - lam] %*% as.matrix(revs[, regressors, with = F])
-  return(list(
-    "objective" = -revs[, sum(l * log(r.plus) - r.plus*lam +  
-                             d * log(r.minus) - r.minus*lam)],
-    "gradient" = -rbind(t(gradient.plus), t(gradient.minus))
-  ))
-}
-
 # maximize the likelihood to estimate the parameters
-library(nloptr)
 x0 <- c(c(0.25, rep(0, k-1)), c(0.25, rep(0, k-1)))
@@
                   lb = c(0, 0, 0, -0.1, 0, 0, 0, -0.1),
-                  ub = rep(2, length(x0)),
+                  ub = rep(2, 2*k),
                   opts = list(algorithm = "NLOPT_LD_LBFGS"))
 
-theta <- max.lik$solution
-
-# Estimate E[score score']
-sigma.hat <- function(x){
-  n <- dim(revs)[1]
-  revs[, r.plus := as.matrix(revs[, regressors, with = F]) %*% x[1:k]]
-  revs[, r.minus := as.matrix(revs[, regressors, with = F]) %*% x[(k+1):(2*k)]]
-
-  ans <- matrix(rep(0, 4*k^2), nrow = (2*k))
-
-  for (i in 1:n){
-    gradient.plus <- t(revs[i, l/r.plus - lam] * as.matrix(revs[i, regressors, with = F]))
-    gradient.minus <- t(revs[i, d/r.minus - lam] * as.matrix(revs[i, regressors, with = F]))
-    score <- rbind(gradient.plus, gradient.minus)
-    ans <- ans + score %*% t(score)
-  }
-
-  return(ans/n)
-}
-
-# Estimate the hessian d(score)/d theta'
-H.hat <- function(x){
-  n <- dim(revs)[1]
-  revs[, r.plus := as.matrix(revs[, regressors, with = F]) %*% x[1:k]]
-  revs[, r.minus := as.matrix(revs[, regressors, with = F]) %*% x[(k+1):(2*k)]]
-
-  H <- matrix(rep(0, 4*k^2), nrow = (2*k))
-
-  for (i in 1:n){
-    zeros <- rep("zero", k)
-    h1 <- revs[i, c(regressors, zeros), with = F] %>% as.matrix() %>% matrix(., nrow = 1)
-    h2 <- revs[i, c(zeros, regressors), with = F] %>% as.matrix() %>% matrix(., nrow = 1)
-    dr.drho <- rbind(h1, h2)
-    dlik.dr <- revs[i, .(-l/((r.plus)^2), 0, 0, -d/((r.minus)^2))] %>%
-               as.matrix() %>% matrix(., nrow = 2)
-    H <- H + t(dr.drho) %*% dlik.dr %*% dr.drho
-  }
-
-  return(H/n)
-}
+theta2 <- max.lik$solution
 
 # calculate the variance-covariance matrix of theta hat (asymptotic divided by n)
-sigma <- sigma.hat(theta)
-H <- H.hat(theta)
+sigma <- sigma.hat(theta2)
+H <- H.hat(theta2)
 H.inv <- solve(H, diag(1, nrow = (2*k)))
-omega <- (H.inv %*% sigma %*% H.inv) / dim(revs)[1]
+omega2 <- (H.inv %*% sigma %*% H.inv) / dim(revs)[1]
 
@@
 # t stat
-(theta[2] + theta[2+k])/sqrt(t(A) %*% omega %*% A)
+t1.2 <- (theta2[2] + theta2[2+k])/sqrt(t(A) %*% omega2 %*% A)
 
@@
 # a(theta) = (theta[1] + theta[1+k])/(sum(theta[c(1,2,1+k,2+k)])) - theta[1]/(theta[1] + theta[1+k])
-grad.a <- function(x){
-
-  ans <- rep(0, length(x))
-  sum.x <- sum(x[c(1,2,1+k,2+k)])
-
-  ans[1] <- (sum.x - x[1]) / (sum.x)^2 - x[1+k]/(x[1] + x[1+k])^2
-  ans[2] <- (sum.x - x[2]) / (sum.x)^2
-  ans[1+k] <- (- x[1] - x[2]) / (sum.x)^2  + x[1]/(x[1] + x[1+k])^2
-  ans[2+k] <- (- x[1] - x[2]) / (sum.x)^2
-
-  return(ans)
+A <- grad.a(theta2)
+score.dif <- (theta2[1] + theta2[2])/(sum(theta2[c(1,2,1+k,2+k)])) - 
+             (theta2[1])/(theta2[1] + theta2[1+k])
+t2.2 <- score.dif/sqrt(t(A) %*% omega2 %*% A)
+
+# Append to the output table
+pvalues <- 2*(1-pnorm(theta2/sqrt(diag(omega2))))
+tr <- createTexreg(coef = theta2,
+                   coef.names = c("Prob. of Like", "Discount on Like", 
+                                  "Young on Like", "Old on Like", 
+                                  "Prob. of Dislike", "Discount on Dislike",
+                                  "Young on Dislike", "Old on Dislike"),
+                   se = sqrt(diag(omega2)),
+                   pvalues = pvalues,
+                   gof.names = gofnames,
+                   gof = c(dim(revs)[1]))
+texregObjects[2] <- list(tr)
+```
+I start off by estimating the average probabilities of leaving a good and a bad review in the population, and by using the estimates to test hypotheses formulated in (\ref{hyp1}) and (\ref{hyp2}).
+I use two sets of covariates to explain these probabilites.
+The baseline set of covariates, $w_{it} = [1, disc_{it-k}]'$, only allows the probability of a like or a dislike to change if a discount is in place.
+The theory behind this choice is that reviews reflect the average perception of quality by the consumers.
+As my sample was selected to only include products with constant quality, this perception should only change if different types of consumers are buying the product.
+Consumers buying on a discount are paying a lower price, and thus could be different from consumers paying the whole price.
+This is the selection effect of discounts on reviews.
+I also acknowledge the possibility that there could be a selection over time, when early buyers are very different from the late buyers.
+Similarly, the perception of quality might be deteriorating over time as new games, with potentially better characteristics, are coming out.
+For this reason, the second set of covariates also adds two variables measuring age: $w_{it} = [1, disc_{it-k}, young_{it}, old_{it}]'$, where $young_{it}$ is a dummy indicating that the game is less than 2 weeks old, and $old_{it}$ is a dummy indicating that the game is more than a year old.
+The estimates are presented in Table \ref{reviewEstimates}.
+
+```{r}
+table <- texreg(texregObjects,
+                stars = c(0.01, 0.05, 0.1),
+                digits = 3,
+                custom.model.names = c("(1)", "(2)"),
+                caption = "Estimates of the Review Parameters",
+                caption.above = T,
+                label = "reviewEstimates")
+```
+
+Given the constraints on my data, it is hard to tell if the estimates that I obtain over- or underestimate the true probabilities of leaving a review.
+On the one hand, I can only estimate sales for a fraction of players, and thus the probability to leave a review could be severely overestimated.
+On the other hand, my model assumes that a user can only leave a review on the next day after she purchases the product, so my estimates do not reflect the possibility that a user can leave a review at a later date.
+This, potentially, can underestimate the probability with which consumers leave reviews, especially during a discount\footnote{Reviews arriving more than one day after the discount is over will not be counted towards reviews left during discount}.
+Thus, my estimates are better suited for making relative statements about the probabilities of interest.
+
+Setting aside the aforementioned issues, my results suggest that a typical user on Steam leaves a positive review with a probability around `r round(theta1[1]*100)`%, and leaves a negative review with a probability around `r theta1[3]*100`%.
+Discounts appear to increase both probabilities, implying that users seem to be more likely to leave a review during a discount.
+I formally test this hypothesis, stated in (\ref{hyp1}), and I strongly reject the null that users are less likely to leave reviews when buying on a discount in favor of the alternative that they are more likely to leave reviews when buying on a discount (the values of the $t$-stats are `r round(t1.1[1],2)` and `r round(t1.2[1],2)` in the two specifications).
+My second hypothesis, stated in (\ref{hyp2}), is that reviews are less positive during a discount than they are outside the discount.
+I fail to reject the null in favor of the alternative that reviews left during a price promotion are more positive (the $p$-values are `r round(1-pnorm(t2.1[1]),2)` and `r round(1-pnorm(t2.2[1]),2)`).
+As we can see, there is no disagreement across specifications on both hypotheses, giving me confidence that this result is robust.
+As for the age controls,  I find that users are more likely to leave reviews in the first two weeks, but, somewhat surprisingly, do not lose steam as the game becomes older.
+Both findings are in accordance with the patterns or reviewing dynamics depicted in Figure \ref{reviewDescriptivePlots}.
+
+```{r}
+# Notice that rhoPosD is the sum of the parameters I defined
+# in the text, rho_0i^+ and rho_1i^+, but the variance matrix is
+# calculated for the original parameters
+
+revs <- revs[, .(rhoPosD = sum(disc*l) / sum(disc*lam),
+                 rhoPosND = sum((1-disc)*l) / sum((1-disc)*lam),
+                 rhoNegD = sum(disc*d) / sum(disc*lam),
+                 rhoNegND = sum((1-disc)*d) / sum((1-disc)*lam)),
+              by = ID]
+revs <- revs[!is.na(rhoPosD)]
+
+# calculate s.e.
+id.matrix <- matrix(c(1,0,0,1), nrow=2)
+for (id in revs[, ID]){
+   sums <- panel[ID==id, .(disc, lam)][, sum(lam), by=disc][!is.na(disc),]
+
+   matND <- matrix(c(sums[disc==F,V1],0,0,0), nrow=2)
+   matD <- matrix(rep(sums[disc==T,V1],4), nrow=2)
+
+   Hpos <- matND/revs[ID==id, rhoPosND] + matD/revs[ID==id, rhoPosD]
+   HposInv <- tryCatch(solve(Hpos, id.matrix),
+                       error = function(x){return(matrix(rep(NA,4), 
+                                                         nrow = 2))})
+
+   Hneg <- matND/revs[ID==id, rhoNegND] + matD/revs[ID==id, rhoNegD]
+   HnegInv <- tryCatch(solve(Hneg, id.matrix),
+                       error = function(x){return(matrix(rep(NA,4), 
+                                                         nrow = 2))})
+
+   revs[ID==id, rhoPos0se := sqrt(HposInv[1,1])]
+   revs[ID==id, rhoPos1se := sqrt(HposInv[2,2])]
+
+   revs[ID==id, rhoNeg0se := sqrt(HnegInv[1,1])]
+   revs[ID==id, rhoNeg1se := sqrt(HnegInv[2,2])]
 }
 
-A <- grad.a(theta)
-
-score.dif <- (theta[1] + theta[2])/(sum(theta[c(1,2,1+k,2+k)])) - 
-             (theta[1])/(theta[1] + theta[1+k])
-
-score.dif/sqrt(t(A) %*% omega %*% A)
-```
-
-```{r}
-# Game by game test whether reviews during a discount are more positive 
-# (in the score sense) than those off discount
-f <- panel[!is.na(disc), .(disc, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by = ID][, .(n1 = sum(l), n0 = sum(d)), keyby = c("ID", "disc")]
-
-test <- f[,  .(p.val = tryCatch(t.test(c(rep(1, n1[1]), rep(0, n0[1])),
-         c(rep(1, n1[2]), rep(0, n0[2])),
-         alternative = "less")$p.value,
-         error = function(x){-1})), by = ID]
-test[p.val ==-1, p.val := NA]
-discIDs <- test[p.val <=0.05, ID]
-panel[, scoreIsBiggerDisc := (ID %in% test[p.val <= 0.05, ID])]
-
-test <- f[,  .(p.val = tryCatch(t.test(c(rep(1, n1[1]), rep(0, n0[1])),
-         c(rep(1, n1[2]), rep(0, n0[2])),
-         alternative = "greater")$p.value,
-         error = function(x){-1})), by = ID]
-test[p.val ==-1, p.val := NA]
-discIDs <- test[p.val <=0.05, ID]
-panel[, scoreIsLessDisc := (ID %in% test[p.val <= 0.05, ID])]
-```
-
-<!-- ```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'} -->
-<!-- p1 <- ggplot(data = revs[, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) + -->
-<!--   geom_histogram(mapping = aes(x = x, y = ..density..), -->
-<!--                  color = "black", -->
-<!--                  position = "identity", -->
-<!--                  boundary = 0, -->
-<!--                  alpha = 0.9, -->
-<!--                  binwidth = 0.1, -->
-<!--                  fill = my.colors[1]) + -->
-<!--   geom_density(mapping = aes(x = x), -->
-<!--                  color = "black", -->
-<!--                  position = "identity", -->
-<!--                  alpha = 0.4, -->
-<!--                  fill = my.colors[1]) + -->
-<!--   scale_x_continuous(name = "Change in Like Rates", -->
-<!--                      minor_breaks = NULL) + -->
-<!--   scale_y_continuous(name = NULL, -->
-<!--                      breaks = c(0, 1, 2), -->
-<!--                      minor_breaks = NULL) + -->
-<!--   my.theme() + -->
-<!--   coord_cartesian(xlim = c(-0.5, 2)) -->
-
-<!-- p2 <- ggplot(data = revs[, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) + -->
-<!--   geom_histogram(mapping = aes(x = x, y = ..density..), -->
-<!--                  color = "black", -->
-<!--                  position = "identity", -->
-<!--                  boundary = 0, -->
-<!--                  binwidth = 0.025, -->
-<!--                  alpha = 0.9, -->
-<!--                  fill = my.colors[1]) + -->
-<!--   geom_density(mapping = aes(x = x), -->
-<!--                  color = "black", -->
-<!--                  position = "identity", -->
-<!--                  alpha = 0.4, -->
-<!--                  fill = my.colors[1]) + -->
-<!--   scale_x_continuous(name = "Change in Dislike Rates", -->
-<!--                      minor_breaks = NULL) + -->
-<!--   scale_y_continuous(name = NULL, -->
-<!--                      minor_breaks = NULL) + -->
-<!--   my.theme() + -->
-<!--   coord_cartesian(xlim = c(-0.5, 2)) -->
-
-<!-- ggarrange(p1, p2, nrow=1, align = "h") -->
-<!-- ``` -->
-
-<!-- ```{r like-rates, fig.width = 8, fig.height = 6, include = FALSE} -->
-<!-- ggarrange(p1, p2, nrow=2, align = "v") -->
-<!-- ``` -->
-
-<!-- The main parameters of interest in this section are $(\rho_{1i}^+, \rho_{1i}^-)$, which measure the change in the like and dislike rates during discounts.
-The precision with which this parameter could be estimated for game $i$ depends on the number of discount days we observe for that game.
-For some products it is impossible to estimate the parameter precisely, either due to their short presence in the sample, insufficient number of discounts, or both.
-However, out of `r info[, .N]` games in the sample, `r revs[posSignif == T, .N]` have a value of $\rho_{1i}^+$ that is statistically different from zero, and `r revs[negSignif == T, .N]` have a value of $\rho_{1i}^-$ that is statistically different from zero.
-The distributions of $\rho_{1i}^+$ and $\rho_{1i}^-$ all games (excluding some outliers) are plotted in Figure \ref{likeRatesPlot}.
-These plots reveal two patterns.
-The first is that there are a lot of products whose consumers leave positive and/or negative feedback with the same probability on and off a discount, as is reflected in high density of the histograms close to zero.
-Second, the like rates appear to be way more responsive to discounts than the dislike rates.
--->
-
-<!-- These findings require some interpretation.
-@Li16 claims “It is by now almost accepted as a stylized fact that offering deal promotion [...] deteriorates local merchants' online reputations”, while my findings seem to suggest that discounts improve review scores.
-Column (2) in Table \ref{reviewLag} in the Appendix presents the results of  -->
-<!-- regressing review score on days after a discount (with controls).
-The results suggest that, on average, the review score goes down, not up, in the days following a discount.
-The total effect at best adds up to 1 point out of a 100, but, technically, my findings do not contradict the literature.
-Instead, I show that there is a long tail of products that receive significantly better reviews during a price promotion.
-The main hypothesis that I am developing in this paper is that firms use discounting to manage their online reputation.
-This hypothesis implies that firms that  receive better reviews during price promotions should be more likely to engage in such behavior.
-Thus, my goal in this section is not to study the heterogeneity in the response of the review sentiment to discounts for its own sake, but simply to identify games that my hypothesis predicts should exhibit stronger effects.
-However, my findings present an interesting puzzle for future investigation: how does the (average) negative response of review score to discounts coexist with the distribution of products that seem to receive better reviews during discounts, not worse.
--->
-
-<!-- \textcolor{red}{Looks like consumers are more likely to leave reviews during a discount. That could be interesting. Calculate standard errors for that?} -->
-
-<!-- ## Revisiting Discounting and Transitions -->
-
-<!-- Now that I have estimated the parameters of the demand and review processes, I am ready to use them to revisit my -->
-<!-- main hypothesis. In Section \ref{descriptiveEvidence} I have established that  -->
-
-<!-- ```{r results = 'asis', warning = FALSE} -->
-<!-- # remove 1% with the highest values of rho_1+ (<=2) -->
-<!-- # and only keep significant coefficients -->
-<!-- panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, score.dif)]) -->
-
-<!-- panel[, pos.treatment := (needPos <= 2*band)] -->
-<!-- panel[, neg.treatment := (needNeg <= 2*band)] -->
-
-<!-- reg1 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
-<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
-<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
-<!--            data = panel[rho1 <= 2 & rho1 >= -0.5,], -->
-<!--            model = "pooling") -->
-<!-- cov<-vcovHC(reg1, method="white1") -->
-<!-- se1 <- sqrt(diag(cov)) -->
-
-<!-- reg2 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
-<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
-<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
-<!--            data = panel[rho1 <= 2 & rho1 >= -0.5 &  -->
-<!--                         ID %in% revs[negSignif == T | posSignif == T, ID],  -->
-<!--                         ], -->
-<!--            model = "pooling") -->
-<!-- cov<-vcovHC(reg2, method="white1") -->
-<!-- se2 <- sqrt(diag(cov)) -->
-
-<!-- reg3 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
-<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
-<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
-<!--            data = panel[rho1 <= 2 & rho1 >= -0.5 -->
-<!--                         # ID %in% revs[negSignif == T | posSignif == T, ID],  -->
-<!--                         ], -->
-<!--            model="within", -->
-<!--            index = c("ID", "t")) -->
-<!-- cov<-vcovHC(reg3, method = "white1") -->
-<!-- se3 <- sqrt(diag(cov)) -->
-
-<!-- reg4 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment + -->
-<!--                log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score + -->
-<!--                mPositive + realPositive + vPositive + age + young + day + week, -->
-<!--            data = panel[rho1 <= 2 & rho1 >= -0.5 &  -->
-<!--                         ID %in% revs[negSignif == T | posSignif == T, ID],  -->
-<!--                         ], -->
-<!--            model="within", -->
-<!--            index = c("ID", "t")) -->
-<!-- cov<-vcovHC(reg4, method = "white1") -->
-<!-- se4 <- sqrt(diag(cov)) -->
-
-<!-- star.out<-stargazer(reg1, reg2, reg3, reg4, -->
-<!--                     label = "rhoTransDiscReg", -->
-<!--                     header = FALSE, -->
-<!--                     title = "Discounts Before Potential Transitions And Firm Heterogeneity", -->
-<!--                     se=list(se1, se2, se3, se4), -->
-<!--                     dep.var.labels = c("$\\mathbb{P}(Discount)$"), -->
-<!--                     column.labels=c("OLS", "OLS:Signif", "FE", "FE:Signif"), -->
-<!--                     model.numbers = F, -->
-<!--                     omit = c("tWODisc", "reviews", "noScore", "realPositive",  -->
-<!--                              "mPositive", "vPositive", "age", "young", "Constant", -->
-<!--                              "score", "day", "week", "needPosDays", "needNegDays"), -->
-<!--                     covariate.labels = c("$\\rho_1^+$", -->
-<!--                                          "$\\rho_1^+ \\times$ Pos. Tr.", -->
-<!--                                          "$\\rho_1^+ \\times$ Neg. Tr.", -->
-<!--                                          "Pos. Tr.", "Neg. Tr."), -->
-<!--                     order = c("rho1"), -->
-<!--                     omit.stat=c("f","adj.rsq","ser"), -->
-<!--                     no.space=T) -->
-<!-- ``` -->
+# label all games with significant rho_1^+
+revs[, posSignif := abs((rhoPosD-rhoPosND)/rhoPos1se) >= 1.96]
+revs[, negSignif := abs((rhoNegD-rhoNegND)/rhoNeg1se) >= 1.96]
+
+# score off discount and score on discount
+revs[, scoreND := rhoPosND/(rhoPosND+rhoNegND)]
+revs[, scoreD := rhoPosD/(rhoPosD+rhoNegD)]
+revs[, score.dif := scoreD - scoreND]
+
+rm(Hpos, Hneg, HnegInv, HposInv)
+```
+
+```{r fig.cap='\\label{scoreDifPlot} Distribution of the difference between estimated average score on and off a discount.'}
+p1 <- ggplot(data = revs[, .(x = score.dif)]) +
+  geom_histogram(mapping = aes(x = x, y = ..density..),
+                 color = "black",
+                 position = "identity",
+                 boundary = 0,
+                 alpha = 0.9,
+                 binwidth = 0.05,
+                 fill = my.colors[1]) +
+  geom_density(mapping = aes(x = x),
+                 color = "black",
+                 position = "identity",
+                 alpha = 0.4,
+                 fill = my.colors[1]) +
+  scale_x_continuous(name = "Difference in Review Scores",
+                     minor_breaks = NULL) +
+  scale_y_continuous(name = NULL,
+                     breaks = c(0, 1, 2),
+                     minor_breaks = NULL) +
+  my.theme()
+```
+
+Now that I have carried out the analysis of the average reviewing propensity and valence, I turn attention to heterogeneity between firm.
+In the identification section I showed how one can estimate the like and dislike rates on the product level.
+The theory of discounting close to review transitions developed in this paper suggests that products whose customers leave better reviews during a price promotions should be more likely to discount when they are close to a transition, regardless of whether it is a positive or a negative one.
+It is convenient to introduce notation for the difference between the expected review scores on and off a discount for the games in my sample:
+
+\begin{equation}
+\Delta score_{i} := \frac{\rho^+_{0i} + \rho^+_{1i}}{\rho^+_{0i} + \rho^+_{1i} + \rho^-_{0i} + \rho^-_{1i}} - \frac{\rho^+_{0i}}{\rho^+_{0i} + \rho^-_{0i}} 
+\end{equation}
+
+Figure \ref{scoreDifPlot} depicts the distribution of $\widehat{\Delta score_{i}}$, the estimated differences in the expected review scores on and off a discount for the games in my sample.
+A couple of paragraphs ago I have shown that the average difference is not statistically distinguishable from zero, and the plot complies with that finding.
+Estimates of $\Delta score_{i}$ vary in their precision from game to game, as games that spent less little time in the sample and/or on discounts would naturally have noisier estimates.
+However, the distribution appears to be well-behaved.
+
+With these estimates at hand, I can now revisit Model (\ref{potTransitionsReg}), the regression I used to establish the effect of proximity to a potential transition on the discounting probability.
+I modify the equation by including the interaction between the
+treatment variables of interest (proximities to potential transitions) and $\Delta score_{i}$, leading to
+\begin{equation}\label{potTransitionsHeteroReg}
+disc_{it} = (\beta^+_0 + \Delta score_{i}\beta^+_1)T_{it}^+ +(\beta^-_0 + \Delta score_{i}\beta^-_1)T_{it}^- + \Delta score_{i} + X_{it}\beta + f_i + \tau_t + \varepsilon_{it}
+\end{equation}
+
+\noindent As $\Delta score_{i}$ does not change over time, it can not be estimated by the within-estimator, but the interaction term could still be included.
+My theory implies that $\beta^+_1$ and $\beta^-_1$ should be positive.
+I estimate (\ref{potTransitionsHeteroReg}) by OLS (without the fixed effect term $f_i$) and by the within-estimator.
+The results are presented in Table \ref{scoreDifTransDiscReg} (the controls are omitted for brevity).
+
+```{r results = 'asis', warning = FALSE}
+# remove 1% with the highest values of rho_1+ (<=2)
+# and only keep significant coefficients
+panel <- merge(panel, revs[, .(ID, rho1=rhoPosD - rhoPosND, sdif=score.dif)])
+
+panel[, pos.treatment := (needPos <= 2*band)]
+panel[, neg.treatment := (needNeg <= 2*band)]
+
+reg1 <- plm(I(discount>0) ~ sdif*pos.treatment + sdif*neg.treatment +
+               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
+               mPositive + realPositive + vPositive + age + young + day + week,
+           data = panel[abs(score.dif) <= 0.5,],
+           model = "pooling")
+cov<-vcovHC(reg1, method="white1")
+se1 <- sqrt(diag(cov))
+
+reg3 <- plm(I(discount>0) ~ sdif*pos.treatment + sdif*neg.treatment +
+               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
+               mPositive + realPositive + vPositive + age + young + day + week,
+           data = panel[abs(score.dif) <= 0.5,],
+           model="within",
+           index = c("ID", "t"))
+cov<-vcovHC(reg3, method = "white1")
+se3 <- sqrt(diag(cov))
+
+star.out<-stargazer(reg1, reg3,
+                    label = "scoreDifTransDiscReg",
+                    header = FALSE,
+                    title = "Discounts Before Potential Transitions And Firm Heterogeneity",
+                    se=list(se1, se3),
+                    dep.var.labels = c("$\\mathbb{P}(Discount)$"),
+                    column.labels=c("OLS", "FE"),
+                    model.numbers = F,
+                    omit = c("tWODisc", "reviews", "noScore", "realPositive",
+                             "mPositive", "vPositive", "age", "young", "Constant",
+                             "score", "day", "week", "needPosDays", "needNegDays"),
+                    covariate.labels = c("Pos. Transition", "Neg. Transition",
+                                         "Score Difference",
+                                         "S. Diff $\\times$ Pos. Tr.",
+                                         "S. Diff $\\times$ Neg. Tr."),
+                    order = c("treatment","sdif"),
+                    omit.stat=c("f","adj.rsq","ser"),
+                    no.space=T)
+```
+
+The least squares estimates in column (OLS) are mainly presented to check the correlations in the data.
+Better sentiment of reviews left during a discount is not related to the frequency of discount on its own, but products close to a positive transition are more likely to discount if their customers are more lenient when buying during a price promotion.
+This effect is not present in the preferred specification (\ref{potTransitionsHeteroReg}), which is estimated in the second column.
+Quite interestingly, this specification finds $\beta^-_0 < 0$, while my earlier results, essentially, failed to find any effect of a proximity to a negative transition on discounting behavior.
+This finding makes a lot of sense.
+Notice that $\beta^-_0$ measures the effect of the aforementioned proximity on discounting probability conditional on $\Delta score_{i} = 0$.
+For a game that is close to downgrading its review score and which does not receive better reviews on a discount, initiating a price promotion is a gamble with no clear upside and a significant downside.
+This finding complies perfectly with the prediction of the stylized model of discounting behavior presented in section \ref{stylizedModel}.
 

### 2020-10-04 Analysis/Code/Paper.Rmd

@@
 
-```{r}
-table <- texreg(texregObjects,
+```{r results = 'asis'}
+texreg(texregObjects,
        stars = c(0.01, 0.05, 0.1),
@@
 ```{r fig.cap='\\label{scoreDifPlot} Distribution of the difference between estimated average score on and off a discount.'}
-p1 <- ggplot(data = revs[, .(x = score.dif)]) +
+ggplot(data = revs[, .(x = score.dif)]) +
   geom_histogram(mapping = aes(x = x, y = ..density..),

### 2020-10-04 Analysis/Code/Paper.Rmd
Added the selection and variance effects.

@@
 This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes.
-In somewhat contradictory findings, @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to, while @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity, because consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.
+@ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to.
+In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity.
+The idea is that consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.
 
@@
 @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews.
-In an experimental study on Ebay, @CabralLi15 also find that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and they provide evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.
-
-The present study contributes to this literature by providing novel evidence from a new market.
-I show that customers buying computer games are significantly more likely to leave positive reviews during discounts.
-More importantly, I go beyond the descriptive nature of the other papers in the literature, and show that firms leverage this fact to improve their reviews by giving discounts, thus providing evidence of a novel reputation management behavior.
+In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and they provide evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.
+
+My paper contributes to this literature in several ways.
+First, I present evidence from a market that was not previously studied in the literature, and confirm that reviews left on a price promotion are not favorable to businesses.
+Second, I show that, nevertheless, firms can successfully manage their online reputation through pricing, by going on a discount when they are close to upgrading their review tier.
 A study similar in spirit to mine is that of @Zegners17, who argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap".
@@
 in 2018, about the size of the U.S.
-film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD], Steam is a major player in an increasingly more important industry.
+film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD[], Steam is a major player in an increasingly more important industry.
 Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to be studied in its own right.
@@
 Based on the score, Steam assigns *review labels*, or bins, to each game.
-These labels\footnote{There are labels worse than "Negative", but they are rare, so I bin all of them into "Negative"} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}.
+These labels\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}.
 For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.
@@
 Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}.
-From that list the user can get some basic information about each game, such as its name, price, and if the game is currently on a discount.
+From that list the user can get some basic information about each title, such as its name, price, and if the game is currently on a discount.
 Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has.
-I use this feature of the Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main independent review variables, rather than, say, the review score or the review texts.
+I use this feature of Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main explanatory review variables, rather than, say, the review score or the review texts.
 Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place.
@@
 The price and the player count time series are the major “dynamic” variables used in the analysis.
-The last dynamic variable, namely the evolution of the review score for each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the path of the review score.
+The last dynamic variable, namely the review score of each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the evolution of the review score.
 
@@
 @SorokinStevens20 studies the causal effect of reviews on sales on Steam, and I mirror closely the sample selection procedure used in that paper.
-First, Steam has made some significant changes to its review system in late 2016, and one of the effects was the removal of the a big number of reviews from the review score calculation.
+First, Steam has made some significant changes to its review system in late 2016, and one of the effects was the removal of a big number of reviews from the review score calculation.
 While it could be an intervention that is worthy of an independent study, in practice combining the data from before and after the intervention led to unsound results, so I focus on the two year period from January 2017 to January 2019, keeping the review system as stable as possible.
@@
 Second, online multiplayer games and games that update frequently are dropped from the sample, as these are products whose quality is changing a lot over time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience.
+I used these update announcements to measure the number of updates each game had.
+Games with more than 5 small updates in the sample were excluded.
 Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}.
-Unobserved quality would present a big obstacle to the identification of the effect of reviews on pricing decisions or sales, because, say, a game that has just issued a major update might both upgrade to a better review label (because of the positive reception of the new content) and give a big discount to rekindle the interest of the players, but the discounting decision would not be influenced by the review transition.
-For the same reasons, I also drop free games and games that are released in a beta-version (the so called “Early Access” program), as these products are likely to be adding new content, and the update history is not a perfect way to monitor the updating activity.
-Finally, I drop few games with a player count of less than four on their median day, as these games are simply very small, and the quality of their player count data is questionable.
+Unobserved dynamic quality would present a big obstacle to the identification of the effect of reviews on pricing decisions or sales.
+Consider a game that has just issued a major update.
+It is a great time for the firm to give a discount in order to rekindle the interest in the game.
+That update could also help the game transition to a better review tier, thanks to the positive reception of the new content.
+Thus, game updates could give rise to a correlation between discounting decisions and review transitions that is not causal.
+Given the fact that the update history is an imperfect way to monitor the update activity, I decided to be conservative and to eliminate as many potential updaters as I could.
+For that same reason I drop free games and games that are released in a beta-version (the so called “Early Access” program), as these products are likely to be adding new content.
+Finally, I drop games with a player count of less than four on their median day, as these games are simply very small, and the quality of their player count data is questionable.
 
@@
 The final sample includes `r info[, .N]` games which I observe for `r panel[, max(age), by = ID][, round(mean(V1))]` days each, on average.
-The main variables in the analysis are the aforementioned dynamic variables: player count, price, and review score history.
+The main variables in the analysis are the aforementioned dynamic variables: player count, price, and review score.
 An example observation from the sample is given in Figure \ref{exampleGame}.
@@
 
-As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is important.
+As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is in order.
 A representative game in the sample never changes its price, but instead occasionally goes on discounts, slowly increasing their magnitude as the game ages.
@@
 The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly.
-Recall that the review score is just the fraction of the positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in.
+Recall that the review score is just the fraction of positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in.
 Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release.
-On average across games, the standard deviation of the review score (out of one hundred) is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`, with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that.
-The score is only assigned once the game reaches 10 reviews, and one can see that 10 reviews is enough, on average, to keep the score stable.
-The distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, is, then, representative of the situation at other ages.
+On average across games, the standard deviation of the review score is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`  (out of one hundred), with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that.
+Given how little the review score changes after the first month, the distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, should be representative of the situation at other ages.
 
@@
 
-Despite the relative rigidity of the review score, there is enough transitions between the review bins to make the analysis of pricing decisions by firms around such transitions possible.
+Despite the relative rigidity of the review score, there is enough transitions between review bins to make the analysis of pricing decisions by firms around such transitions possible.
 Table \ref{tab:transitionMatrix} describes the transitions between review bins in the sample.
@@
 The number of transitions that led to the game spending at least 7 days in the new bin is `r transitions[(is.na(dur) | dur >= 7), .N]`.
-Table \ref{mDiscountTable} describes the state of the games in the two weeks before their transitions.
-Discounting  does take place before the transitions, games transition at very different ages, but tend to have only a limited number of reviews by the time their review bin changes.
+Table \ref{mDiscountTable} describes the state of the games in the two weeks before such transitions.
+Discounting  does take place before the transitions, games transition at very different ages, but tend to have accumulated only a limited number of reviews by the time their review tier changes.
 
@@
 not yet completed it or are not bored with it yet. This number  has an empirical counterpart in
-the face of the player count variable, observable to the econometrician. The game loses \(E_{it}\) players on day \(t\), which is also not observed.
+the face of the player count variable, observable to the econometrician. The game loses \(E_{it}\) active players on day \(t\), which is also not observed.
 I assume that, once a player stops playing the game, she never returns to it again. It is easy to see then that \(A_{it}\) follows the following process:
@@
 
-Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about
-them in order to make progress.
+Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about these variables in order to make progress.
 
@@
 
-### Demand Parameters
 The prediction of \(A_{it}\) that follows from (\ref{activeProccess}) takes the form of
@@
 \end{equation}
-This specification “controls” for the (log) number of continuing players in order to overcome the non-availability of direct sales data; however, it is the numbers of active players and buyers that are additive, not their logs.
+This specification “controls” for the (log) number of continuing players in order to overcome the non-availability of direct sales data; however, it is the numbers of active players and buyers that are additive, not their logs, as (\ref{activeProccess}) and (\ref{arrivalReg}) highlight.
 Thus, the structural model I formulate confronts the estimation problem in a more “heads-up” way, and in that regard offers an improvement over @SorokinStevens20.
@@
 This implies that the estimated values of $\lambda_{it}$ would take into account only those new buyers who contribute to gaming activity during the “rush hour”.
-An implicit assumption in my analysis is that new buyers of the game all choose their gaming time following the same game-specific distribution.
+An implicit assumption in my analysis is that new buyers of the game choose their gaming time following some fixed game-specific distribution.
 I use this assumption to say that, if the number of new active players during rush hour goes up by 1%, then sales go up by 1% across all types of players,  not only among the "rush hour ones".
 
-Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model \ref{arrivalReg}, and guarantees identification of all parameters, as long as there is sufficient variation in the data.
-Of course, this is only true as long as equation \ref{arrivalReg} is the right model of the data generating process.
+Another advantage of using equation (\ref{arrivalReg}) to estimate demand parameters from player count data comes from the fact that it allows each game to have its own continuation probability $\psi_i$.
+Two games could have the same observed median daily player count---say, ten people---but very different sales levels, if game one offers a lot of replayability and is played by the same ten people over and over again, and game two is played by new ten people every day.
+Intuitively, $\psi_i$ is identified by the rate of decay of the player count when it is far from its (slowly-changing) trend or average.
+Game release and discounts offer such events, when the player count spikes briefly due to all the new players who just bought the game; see example game in Figure \ref{exampleGame}.
+
+Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model (\ref{arrivalReg}), and guarantees identification of all parameters, as long as there is sufficient variation in the data.
+Of course, this is only true as long as equation (\ref{arrivalReg}) is the right model of the data generating process.
 A threat to identification would come from unobserved demand shifters $\tilde x_{it}$ that are correlated with the observed factors $x_{it}$ (omitted variable bias).
-For instance, an advertising intervention that is coupled with a price promotion would increase demand, but the entire effect would be attributed to the observed change in price.
+For instance, an unobserved advertising intervention that is coupled with a price promotion would increase demand, but the entire effect would be attributed to the observed change in price.
 My approach is vulnerable to such events, as long as one is interested in getting the causal estimate of the discount elasticity of demand.
 
-However, I argue that (\ref{arrivalReg}) is an adequate specification, if the goal is to estimate the causal effect of reviews on sales, or to get a predictive model of demand.
+However, I argue that (\ref{arrivalReg}) is an adequate specification if the goal is to estimate the causal effect of reviews on sales, or to get a predictive model of demand.
 First and foremost, the reviews are not a choice variable of a firm, and rather serve as a state variable that a firm takes as given every day.
@@
 
-One important way in which I control for various tools that firms have at their disposal is through sample selection.
+The most direct way in which I control for firm behavior is by including the price in the set of explanatory variables.
+Any intervention that is correlated with discounts will be attributed to the price variable.
+The second important way in which I control for various tools that firms have at their disposal is through sample selection.
 Sample selection rules out the possibility of an omitted variable bias stemming from a number of variables that could collectively be referred to as “changing quality”.
-The games in the sample are single player games, and thus are not subject to time-varying network externalities or frequent quality updates, that could be correlated with reviews, depths of discounts, and the player count.
-Second, game specific effect $\lambda_i$ controls for all time-invariant characteristics of game $i$ that determine average sales: initial marketing budget, extraneous popularity of the game's plot or setting, etc.
-Similarly, time effects control for important within-week seasonality in gaming patterns and for the extensive platform-wide sales.
-Third, note that Equation (\ref{arrivalReg}) allows each game to have its own continuation probability $\psi_i$, which could prove crucial in eliciting sales from the player count data.
-Two games could have the same observed median daily player count---say, ten people---but very different sales levels, if game one offers a lot of replayability and is played by the same ten people over and over again, and game two is played by new ten people every day.
-Intuitively, $\psi_i$ is identified by the rate of decay of the player count when it is far from its (slowly-changing) trend or average.
-Game release and discounts offer such events, when the player count spikes briefly due to all the new players who just bought the game; see example game in Figure \ref{exampleGame}.
+The games in the sample are single player games, and thus are not subject to time-varying network externalities or frequent quality updates that could be correlated with reviews, depths of discounts, or the player count.
+Third, game specific effect $\lambda_i$ controls for all time-invariant characteristics of game $i$ that determine average sales: initial marketing budget, extraneous popularity of the game's plot or setting, etc.
+Similarly, I employ a set of time effects to control for important within-week seasonality in gaming patterns and for the extensive platform-wide sales.
 
@@
 First, I believe that standard concerns about the endogeneity of prices are not directly applicable in my context.
-The reason is the high frequency nature of the data and the stickiness of posted prices.
+The reason for that is the high frequency nature of the data and the stickiness of posted prices.
 Using the classic notation, imagine that a discount is given on date $t$, and we observe a quantity-price pair $(Q_t, P_t)$, both of which are different from their yesterday's counterparts $(Q_{t-1}, P_{t-1})$.
 The standard endogeneity concern is that firm's demand is subject to shocks, and that the firm would change its price precisely when those shocks occur.
-The two points then, roughly speaking, would belong to different demand curves, and one can not identify the slope of the demand curve\footnote{Assuming, as is usually done, that demand shifters lead to parallel shifts in demand}.
+The two points then, roughly speaking, would belong to different demand curves, and one can not identify the slope of the demand curve.
 In my setting, however, this would require the firms to systematically give discounts *exactly on the days* of the demand shocks, which requires possessing a level of insight into one's demand condition that is unrealistic, especially for small independent studios.
-While a discount for a racing game on the day of a major F-1 race is not implausible, should the demand for the game go up with a lag of as little as one day, then both $(Q_t, P_t)$ and $(Q_{t-1}, P_{t-1})$ would belong to the same demand curve, and, therefore, identification would not be threatened.
-
-My second point is that, even though unobserved marketing interventions that are coupled with price promotions, would,  undoubtedly, be an issue, this problem could be addressed with some extra data collection.
+While a discount for a racing game on the day of a major F-1 race is not implausible, should the demand for the game go up with a lag of as little as one day, then both $(Q_t, P_t)$ and $(Q_{t-1}, P_{t-1})$ would belong to the same demand curve, and, therefore, identification would not be threatened\footnote{Assuming, as is usually done, that demand shifters lead to parallel shifts in demand}.
+
+My second point is that, even though unobserved marketing interventions that are coupled with price promotions, would,  undoubtedly, be an issue for identifying the causal price elasticity, this problem could be addressed with some extra data collection.
 One way to proceed would be to study if such coupled promotions in fact do take place.
@@
 A deeper problem for identifying the price elasticity of demand lies in defining precisely the elasticity of interest.
-A video game is a durable good, and some consumers could be purchasing it strategically, thinking about the probability and depth of discounts that they could get in the near future.In particular, Steam allows users to add any game to their wishlist, which means that they would be notified about promotions affecting that game.
+A video game is a durable good, and some consumers could be purchasing it strategically, thinking about the probability and depth of discounts that they could get in the near future.
+In particular, Steam allows users to add any game to their wishlist, which means that they would be notified about promotions affecting that game.
 Later in the results section we will see that the lion's share of sales on a discount take place on the first day of the discount, which is consistent with users waiting for a discount and buying the game when the discount goes live.
 For studying counterfactual price policies one would need to specify a more complicated model of forward-looking consumers, and estimate the fundamentals of their behavior.
+
 A related problem is the importance of salience in a marketplace that has many thousands of products.
@@
 
-In this section I present the estimates of the model parameters.
-I start with the demand parameters $(\lambda_i, \psi_i, \beta)$ in (\ref{arrivalReg}), and contrast these estimates with the ones delivered by running a regression (\ref{logReg}).
-Then I proceed to the parameters of the review process, where the focus will be on the contributions $(\rho_{1i}^+, \rho_{1i}^-)$ of discounts to the like and dislike rates.
-
-### Demand Parameters
+In this section I present the estimates of the parameters of my demand model.
+I contrast these estimates with the ones obtained from estimating a simple log-regression (\ref{logReg}).
+I find that the results are fairly similar, albeit there are some important differences that I discuss in detail.
+The main takeaway from this section is that review tiers above “Mixed” increase sales by 2-10% compared to “Mixed”, and that discounts are important drivers of sales in this market.
 
@@
 These sales take place around major holidays, and, thus, blend together the increased platform-wide demand due to holidays with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSalesPeriods}).
-To capture these periods in a parsimonious way, I calculated the average daily discount in the sample, and labeled the days when the average discount exceeded 20\%.
+To capture these periods in a parsimonious way, I calculated the average daily discount in the sample, and labeled the days when the average discount exceeded 20\% as days of the Seasonal Sale.
 Figure \ref{seasonalSalesPeriods} in the Appendix shows that my definition tracks closely the spikes in the aggregate discounting behavior.
-I also tried using the raw value of the average discount in the sample, but the results remained the same.
+I also tried using the raw value of the average discount in the sample instead of a dummy variable indicating the Seasonal Sale, but the results remained the same.
 
@@
 
-The review labels' semi-elasticities are fairly similar across the specifications.
-All specificaitons exhibit a monotonicity in the effects of different review tiers on sales.
-The "Negative" label is at most as good as "Mixed" (the reference group), with the log-regression results finding a penalty of `r round(-100*reg1$coefficients[6])`% that the "Negative" label entails; the "Mostly Positive" bin increseases sales by `r round(beta.hat[8]*100)`-`r round(100*reg2$coefficients[7])`% compared to the "Mixed" bin.
-At the top end we see that the "Overwhelmingly Positive" label increases demand by `r round(100*reg2$coefficients[10])`-`r round(beta.hat[11]*100)`%.
+The semi-elasticities sales with respect to review labels are fairly similar across the specifications.
+All specifications exhibit monotonicity in the effects of different review tiers on sales.
+The "Negative" label is at most as good as "Mixed" (the reference group), with the log-regression results finding a penalty of `r round(-100*reg1$coefficients[6])`% that the "Negative" label entails; the "Mostly Positive" bin increases sales by `r round(beta.hat[8]*100)`-`r round(100*reg2$coefficients[6])`% compared to the "Mixed" bin.
+At the top end we see that the "Overwhelmingly Positive" label increases demand by `r round(100*reg1$coefficients[10])`-`r round(beta.hat[11]*100)`%.
 These magnitudes are economically sizable and reasonable.
-These results close the gap that my analysis has exhibited so far, and confirms that good reviews are important for sales in the Steam marketplace.
-
-However, columns (1) and (2)-(3) differ substantially in the estimates of the effect of having no score on sales\footnote{In order to have both the score variable $\in [0,100]$ and a dummy for the "No Score" label I set the former to be equal to 0 when a game has no review label (which happens when it has less than 10 reviews).
+These results confirm that good reviews are important for sales in the Steam marketplace.
+
+However, columns (1) and (2)-(3) differ substantially in the estimates of the effect of having no score on sales\footnote{In order to have both the score variable $\in [0,100]$ and a dummy for the “No Score” label I set the former to be equal to 0 when a game has no review label (which happens when it has less than 10 reviews).
 Thus, the score variable really measures the effect of score once the score is defined.}.
 While Model (\ref{arrivalReg}) suggests that having no score is associated with a `r -round(beta.hat[6]*100)`% slower customer arrival than having the “Mixed” review label, its simplified log-regression analogs find the opposite effect of a having `r round(reg1$coefficients[5]*100)`-`r round(reg2$coefficients[4]*100)`% bonus associated with having not enough reviews.
-The latter effect can not possibly be taken at face value, given that the most exlusive review label "Overwhelmingly Positive" only increases sales by at most `r round(beta.hat[11]*100)`% compared to the baseline.
+The latter effect can not possibly be taken at face value, given that the most exclusive review label, "Overwhelmingly Positive",  increases sales by at most `r round(beta.hat[11]*100)`% compared to the baseline.
 It would be possible to explain such large estimates by high levels of demand  when the game is young and is likely to have less than 10 reviews, but I control for being “young” by including the dummy for being less than 14 days of age.
@@
 The second imprortant set of variables are the price variables.
-First row of Table \ref{demandEstimates} suggests that the price elasticity of demand of very low, between  `r round(-reg1$coefficients[2],2)` and `r round(-beta.hat[1],2)` in absolute value.
+The first row of Table \ref{demandEstimates} suggests that the price elasticity of demand of very low, between  `r round(-reg1$coefficients[2],2)` and `r round(-beta.hat[1],2)` in absolute value.
 This magnitude is very similar to the price elasticity that @ReimersWaldfogel20 finds studying reviews for books on Amazon.com.
-That paper argues that Amazon has been known to prioritize growth over profit, charging low prices and operating on the inelastic part of the demand curve.
+That paper argues that Amazon has been known to prioritize growth over profit, thus charging low prices and operating on the inelastic part of the demand curve.
 However, on Steam individual firms choose which prices to charge for their product, and they should have a stronger preference for profit than an entity that is a marketplace, rather than a seller.
-The situation becomes more clear after examining the coefficient on “New Discount”, an indicator variable for the first day after the discount\footnote{I found the effect to be stronger if a one day lag is allowed}.
-On average, a discount leads to a `r round(beta.hat[2]*100)`-`r round(reg2$coefficients[3]*100)`% spike in sales upon introduction.
+The situation becomes more clear after examining the coefficient on “New Discount”, an indicator variable for the first day after the introduction of the discount\footnote{I found the effect to be stronger if a one day lag is allowed}.
+As I have mentioned in the Identification section, the durable good nature of video games means that forward-looking behavior by consumers could lead to different price elasticities for short-lived promotions and long-term price changes, and the difference between the price coefficient and the indicator for the start of a discount could capture precisely that distinction.
+I find that, on average, a discount leads to a `r round(beta.hat[2]*100)`-`r round(reg2$coefficients[3]*100)`% spike in sales upon introduction.
 An average discount in the sample is `r round(panel[discount>0, mean(discount)]*100)`%, meaning that, based on the estimates in column 1, the effective change in quantity sold upon the introduction of the discount is `r round(beta.hat[2]*100)`% $+$ `r round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100))`% $=$ `r round(beta.hat[2]*100) + round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100))`%, with the implied elasticity of `r round((round(beta.hat[2]*100) + round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100)))/round(panel[discount>0, mean(discount)]*100),2)`.
 This number looks more reasonable, especially given that the products I study have a zero marginal cost of production, and in a static world firms would set prices at which the demand for their products would be unit-elastic.
-As I have mentioned in the Identification section, the durable good nature of video games means that forward-looking behavior by consumers could lead to different price elasticities for short-lived promotions and long-term price changes.
 
@@
 
-The second set of demand parameters that I estimate are the game-specific customer arrival 
-rates $\lambda_i$ and the probabilities $\psi_i$ with which active players of game $i$
-continue playing the game. For the ease of interpretation, I present the estimates of 
-$\bar \lambda_{i} := \lambda_i(1+\mathbb{E}[x_{it}]'\beta)$, the average number of sales
-for game $i$ (recall that I can only estimate the part of sales that contributes to the gaming
-activity during peak times). Estimated distributions of these parameters are presented in 
-Figure \ref{psiLambdaDist}. The model produces very well-behaved estimates without any constraints
-imposed in the estimation: there are just
-`r info[psi > 1 | psi <0, .N]` games with estimated values of $\psi_i$ outside of the $[0,1]$
-interval, and only `r round(panel[lambda < 0, .N]/panel[, .N]*100)`% of the observations in 
-the sample predict negative sales. Quite remarkably, the average continuation probability, 
-`r info[, round(mean(psi), 2)]`, is very close to the estimates of its log-regression counterpart 
-in Table \ref{demandEstimates}, line "Lag Players".
+The second set of demand parameters that I estimate are the game-specific customer arrival rates $\lambda_i$ and the probabilities $\psi_i$ with which active players of game $i$ continue playing the game.
+For the ease of interpretation, I present the estimates of  $\bar \lambda_{i} := \lambda_i(1+\mathbb{E}[x_{it}]'\beta)$, the average sales for game $i$ (recall that I can only estimate the part of sales that contributes to the gaming activity during peak times).
+Estimated distributions of these parameters are presented in  Figure \ref{psiLambdaDist}.
+The model produces very well-behaved estimates without any constraints imposed on the estimation: there are just
+`r info[psi > 1 | psi <0, .N]` games with estimated values of $\psi_i$ outside of the $[0,1]$ interval, and only `r round(panel[lambda < 0, .N]/panel[, .N]*100)`% of the observations in  the sample predict negative sales.
+The average continuation probability,  `r info[, round(mean(psi), 2)]`, is quite close to the estimates of its log-regression counterpart in Table \ref{demandEstimates}, line "Lag Players", equal to `r round(reg2$coefficients[1],2)`.
 
@@
 
+\textcolor{red}{Add an introduction}
+
+I this section I present the main findings of the paper.
+I start by presenting a stylized model of discounting close to a transition to a different review bin.
+The model predicts that, whether a firm would find discounting a worthwhile option to facilitate  a transition or not, depends on the balance between two forces: the selection effect and the variance effect.
+I then show that products are significantly more likely to go on a discount when they are close to improving their review tier, while no effect is found for products that are close to sliding down a tier.
+The two effects are then further investigated in the next section.
+
 ## Stylized Model
@@
 A firm can give a discount at cost $c$ that can probabilistically change its status to exceed 1 (an upgrade), to go below 0 (a downgrade), or to remain within the $(0,1)$ band (no change).
-The result depends on whether the additional customers who buy the product on a discount happen to leave more positive or more negative reviews, and on the  weight of hte new reviews relative to the existing ones.
-Assume that with probability $p$ the firm's status becomes $s+x$, and with probability $1-p$ it becomes $s-x$.
+The result depends on whether the additional customers who buy the product on a discount happen to leave more positive or more negative reviews, and on the volume of the new reviews relative to the existing ones.
+To reflect that, assume that with probability $p$ firm's status becomes $s+x$, and with probability $1-p$ it becomes $s-x$.
+The symmetry is purely for expositional purposes.
 Firm's utility $u(s)$ from having a review status $s \in (0,1)$ is 0, while it earns a utility $u^H$ from the upgraded status and a utility $u^L < 0 < u^H$ from the downgraded status.
@@
 
-When would the firm be willing to give a discount? Consider a firm with $s > 1/2$, i.e., the one that is close to a review upgrade. For that firm the expected value of giving a discount is 
-$$
+When would the firm be willing to give a discount?
+Consider a firm with $s > 1/2$.
+Such a firm could be regarded as one that is close to a review upgrade.
+The expected value of giving a discount to this firm is is
+\begin{equation}\label{discTradeoff}
   \EE{U(s+X)} = 
@@
   \end{cases}
-$$
+\end{equation}
 \noindent The firm would choose to give a discount if $\EE{U(s+X)}  > 0$.
-A trivial comparative statics exercise tells us that the firm is more likely to do so if the probability $p$ to get a positive shock to the review status if high, if the payoff $u^H$ of upgrading the status is high, and if the loss from downgrading the status $-u^L$ is low.
-
-What is interesting about this problem, is that the probability of improving the review status $p$ does not have to exceed $1/2$ for the firm to give a discount, i.e., the reviews it gets on a discount could be worse than the reviews it receives off a discount.
-Indeed, if the potential change to the score is moderate ($x \in [1-s, s]$), then a successful outcome leads to a transition, while an unsuccessful outcome leaves the firm with the current review status.
-In this case the firm is not risking anything, and is willing to “pull the plug” simply to gamble on the positive outcome.
-Even if the potential change to the review status is substantial $(x \ge s)$, the firm could still find  it profitable to give a discount and risk the deterioration of its review status if the benefits of having an improved status are large enough.
-Similar conclusions follow for the case of $s < 1/2$, when a firm is closer to a negative transition.
-
-The main takeaway from this stylized model is that the relationship between proximity to transitions and discounting behavior is theoretically ambiguous.
-In the data we can expect to find both firms that are more likely to give a discount when they are close to a transition (gambling to upgrade their status, or trying to escape from the downgrading threshold), and firms that are less likely to discount when close to a transition (the downside risk is too big).
-I will now investigate this relationship in the data, and will use the intuition developed here to interpret the results.
+If $x < 1-s$, the firm simply can not induce enough change, and would not give a discount, unless $c < 0$ (i.e, other factors make giving a discount attractive).
+This would be the case for products with many reviews and an established review score.
+My interested is mostly in the other type of products, the ones that potentially can transition.
+In those cases the decision to discount or not depends on the comparison between the value of the positive transition, $u^H$, the cost of giving a discount ($c$, or $c$ and $(1-p)^L$), and the probability that the transition is successful.
+If the probability of success is high, the firm is more likely to give a discount.
+This is what I refer to as the (positive) \emph{selection} effect.
+In the literature the selection effect of discounts refers to the idea that consumers buying during a price promotion could be different from regular consumers, and could therefore leave different reviews.
+A positive selection effect means that these reviews tend to be more favorable, while a negative selection effect implies the opposite.
+In the language of my stylized model, a positive selection effect means that $p > 0.5$, implying that the review score is more likely to improve from a promotion.
+The selection effect is negative if $p < 0.5$.
+Clearly, a positive selection effect improves the attractiveness of running a price promotion, and is thus an important factor to study.
+
+Theoretically, the sign of the selection effect of buying during a discount on the valence of reviews is ambiguous.
+Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews.
+At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews [@CabralLi15; @IfrachEtAl19; @AcemogluEtAl19].
+Limited empirical evidence on the sign of the selection effect is limited.
+@ByersEtAl12 and @Li16 report that customers who choose to go to a restaurant because of a price promotion tend to leave worse reviews, while  a positive effect was documented by @Li16 and @ZhuEtAl19.
+
+An interesting observation about the problem of the firm (\ref{discTradeoff}) is that the selection effect does not need to be positive for the firm to decide to go on a discount.
+Indeed, consider the case when  the potential change to the score is moderate ($x \in [1-s, s]$).
+The successful outcome of the discount leads to a transition and the prize of $u^H$, while the unsuccessful one leaves the firm with the current review status, which is not that costly.
+If the upside payoff $u^H$ is high enough, then even if selection is negative ($p < 0.5$), the firm could still be willing to “pull the plug” and give a discount, with the sole purpose of gambling on the positive outcome.
+I refer to  this idea as the “variance effect”.
+Even if the firm does not expect the new reviews to be favorable in expectation, they could still turn out to be positive, and if the reward is high enough, it could be worth the risk.
+
+Note that variance could also be bad for the firm.
+First, if $x \ge s$, then a negative realization could push the product down one review tier.
+A more important case is the one of a firm that is closer to a review downgrade rather than an upgrade, i.e.
+when $s < 0.5$.
+Following the logic of (\ref{discTradeoff}), we can see that for intermediate values of $x \in [1-s, s)$ such a firm is only risking sliding one review tier down if the reviews left during a discount turn out to be negative, while if they turn out to be positive the firm simply remains in its current review bin.
+The selection effect should be strongly positive for such a firm to find discounting profitable.
+
+To summarize, it appears that firms close to a positive transition could be more likely to benefit from the variance effect than the ones close to a negative transition.
+This makes them more likely to run price promotions.
+Both types benefit from a positive selection effect, but whether the selection effect is positive or negative is an empirical question.
+A strong negative selection effect could overturn the appeal of discounting that is coming from the variance effect, ultimately meaning that the relationship between proximity to transitions and discounting behavior is theoretically ambiguous, and should be studied empirically.
 
@@
 
-The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels are often preceded by discounts.
-The graph shows that two weeks prior to a transition only `r transPanel[tToTransit==-14, round(mean(100*(discount > 0)))]`% of games were on a discount, essentially the sample average, but that this number more than doubles to around `r transPanel[tToTransit==-1, round(mean(100*(discount > 0)))]`% one day before the label change.
+Now that a simple theory of discounting close to a review threshold has been brought forward, I turn attention the The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels are often preceded by discounts.
+The graph shows that two weeks prior to a transition only `r transPanel[tToTransit==-14, round(mean(100*(discount > 0)))]`% of games are on a discount, essentially the sample average, but that this number more than doubles to around `r transPanel[tToTransit==-1, round(mean(100*(discount > 0)))]`% one day before the label change.
 Regression analysis controlling for review label, number of reviews, age, day of the week and week time effects, as well as time since the previous discount, confirms that the association depicted in Figure \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in the Appendix).
@@
 In other words, firms could be giving discounts for reasons unrelated to reviews, but transitions sometimes would follow as a result.
-As a matter of fact, suppose that the story I am after is true, namely that firms try to achieve transitions  via price promotions.
+As a matter of fact, suppose my theory is correct and firms try to achieve transitions via price promotions.
 In that case, discounts *have* to be able to aid transitioning, making the reverse causality inherent in this setting.
-The reverse causality would also explain why both review upgrades and downgrades are preceeded by discounts.
+The reverse causality would also explain why both review upgrades and downgrades are preceded by discounts.
 
@@
 
-With the focus now on potential transitions, the crucial question is how to define proximity to a transition.
+While the merits of focusing on potential transitions are clear, defining proximity to a transition is not straightforward.
 One approach would be to use the raw review count, and to say that a game is close to upgrading its review label when it needs five (ten, twenty ...) more positive reviews to transition.
 However, given the heterogeneity in the popularity of different games (see Figure \ref{sampleSizeHist}), five extra reviews could be nothing for a very popular game, and hard to acquire for a small game.
-For this reason I use a different approach, that measures proximity by the expected number of days that a game has to wait to accumulate the reviews necessary for a transition.
+For this reason I use a different approach, and measure proximity by the expected number of \emph{days} that a game has to wait to accumulate the reviews necessary for a transition.
 In particular, for every game-date pair I first measure how many positive reviews that game needs at the moment to upgrade its review bin, and how many negative reviews that game needs to degrade its review bin.
-In the next step, for each game I calculate the average speed of review arrivals, by simply dividing the number of positive (negative) reviews as of the last day in the sample by the age of the game on that day.
-Knowing the speed of positive and negative review arrivals, and the  number of reviews necessary for a transition, I then define the proximity to a positive (negative) transition to be the expected number of days needed for the game to accumulate the necessary number of positive (negative) reviews, assuming that it does not receive any negative (positive) reviews during that time.
-
-To illustrate this definition, consider an example game with 19 positive reviews and 6 negative reviews at some moment in time.
+In the next step, for each game I calculate the average speeds of review arrival, by simply dividing the number of positive (negative) reviews as of the last day in the sample by the age of the game on that day.
+Knowing the speeds of positive and negative review arrivals, and the  number of reviews necessary for a transition, I then define the proximity to a positive (negative) transition to be the expected number of days needed for the game to accumulate the necessary number of positive (negative) reviews, assuming that it does not receive any negative (positive) reviews during that time.
+
+To illustrate this definition, consider an example game with 19 positive and 6 negative reviews at some moment in time.
 This game has a review score of 76\%, and the “Mostly Positive” review label.
@@
 As the example above shows, it is impossible to consider proximity to a positive transition without taking into account proximity to a negative transition, at least for moderately sized games.
-If firms' strategies for these types of transitions are different, then studying such transitions separately could attenuate the effect of the proximity to, say, a positive transition, on the discount probability: a firm that is close to upgrading its review bin might not give a discount not because it is a bad way to accomplish that transition, but because that firm is at the same time close to downgrading its review bin, and might prefer to exercise prudence.
+My model of discounting had a similar message: while variance could be good for a game that does not risk a deterioration of its review tier, it could be bad for a game that does risk one.
 For this reason, I define two “treatment” variables of interest.
@@
 These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSalesPeriods}.
-We expect $\beta^+$ to be positive, but, when it comes to $\beta^-$, any sign could be rationalized.
-A positive sign on  $\beta^-$ would serve as evidence that firms use discounting in order to escape from slumps in their reviews bins, while a negative sign would indicate that, on the contrary, firms on the verge of a bad transition become more prudent with their discounts, trying to not instigate extra purchasing/reviewing activity.
+My model of discounting behavior highlighted that any sign of $\beta^+$ and $\beta^-$ is possible, albeit suggesting that $\beta^+ > \beta^-$, as the variance effect is more likely to benefit a firm close to a review upgrade.
 
@@
 
-Notice that the inclusion of both the distance to a potential positive, and a potential negative, transition in the regression drops all observations from the lowest ("Negative") and the highest ("Overwhelmingly Positive") review bins, as for games in those bins only one way of review transition is possible.
+Notice that the inclusion of both the distance to a potential positive and a potential negative transition in the regression forces me to drop all observations from the lowest ("Negative") and the highest ("Overwhelmingly Positive") review bins, as for games in those bins only one direction of review transition is possible.
 However, given that the proportion of such observations in the sample is quite small, this is not a big concern.
 The analysis also excludes the observations with a “No Review Score” label, as I do not want to take a stance on what constitutes an improvement or a deterioration of the review score for such games.
-My demand estimates presented in Table \ref{demandEstimates} suggest that having no reviews could be the worst review bin a game could be in, but then I would have to exclude this label as one that does not admit review deterioration.
+My demand estimates presented in Table \ref{demandEstimates} suggest that having no reviews could be the worst review bin a game could be in, but then I would again have to exclude this label as one that does not admit review deterioration.
 In any case, games that spend a lot of time in “No Score” have, by construction, very few reviews, which makes them rather unlikely to ever be one one or two weeks away from a transition according to my measure.
@@
 The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion.
-Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to have a discount\footnote{The corresponding number for the games in the positive treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg2$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
-Proximity to a potential negative transition seems to have negative or no effect on the probability of discount.
-The results in the main specification suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))` less likely to go on a discount, albeit the effect is not significant in the other two specifications.
-
-## Discussion
-
-It is reasonable to say that model (\ref{potTransitionsReg}) is able to identify the causal effect of the proximity to a review transition on discounting behavior.
-As the sample was selected to include only products with the most stable quality and the lowest number of game updates, the path of the review score is relatively exogenous for the firms.
-Taking its current review score as given, a firm can decide whether to run a price promotion or not, which makes the main independent variables in my analysis exogenous.
-On top of that, model \ref{potTransitionsReg} includes a rich set of controls and fixed effects.
-Some threats to identification still remain, of course.
-One is unobserved marketing interventions preceding discounts.
-If advertisements improve the review score, then, by definition, advertisement would be correlated with the treatment variable, moving games a bit closer to transitions.
-If a discount then follows, as a part of the general marketing plan, rather than to leverage the new proximity to a transition, the positive association between discounting and positive transitions would be spurious.
-Note, however, that it would be more natural to expect firms to roll out all marketing interventions at the same time (i.e., running a price promotion while the game is advertised).
-In that case, the threat to identification vanishes.
+Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to feature a discount\footnote{The corresponding number for the games in the positive treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg2$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
+Proximity to a potential negative transition seems to have a negative or no effect on the probability of discount.
+The results in the main specification suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is not significant in the other two specifications.
 
 It is instructive to look at the results through the lens of stylized model introduced earlier in the section.
-Take the products close to a review upgrade first.
-For such products to choose to not go on a discount, the downside risk of doing so should be high, or they must have enough reviews to make changing their review score infeasible.
-Both scenarios would appear to be relatively unrealistic ex ante, and my results for firms on the verge of a positive transition comply with that expectation.
-On the other hand, predictions for games that are close to a review downgrade were more blurred.
-It is reasonable to expect such products to dislike variance, unless the upside risk is strong.
-The upside risk would be strong if reviews left during a discount were more positive, or if better review labels increased sales by a lot.
-I find no positive, nor negative effect of proximity to a negative transition on discounting behavior, which indicates that pros and cons balance out.
-
-The results I presented in this section, therefore, lead to the following hypothesis: reviews left on a discount are not more positive than the ones left off a discount.
-If this hypothesis is not true, the lack of discounting by products close to a negative transition would be puzzling.
-This hypothesis has found some support in the prior literature, albeit in a different market.
-@ByersEtAl12 and @Li16 report that customers who choose to go to a restaurant because of a price promotion tend to leave worse reviews, even though the effect could be positive in certain cases [@Li16; @ZhuEtAl19].
-Theoretically, this effect of buying during a discount on the valence of the reviews is ambiguous.
-Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews.
-At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews [@CabralLi15; @IfrachEtAl19; @AcemogluEtAl19].
-I now turn my attention to investigating this hypothesis, as doing so would be helpful in assessing the results obtained in this section, and would contribute to the literature by providing evidence from a new market.
+Both the variance and the positive selection effects could explain why products close to a review upgrade are more likely to run a price promotion.
+The lack of significance of the effect for products close to a review slump could be explained by the clash of the variance effect and the selection effect.
+As we see, even though my empirical investigation has resolved the theoretical ambiguity of the signs and the significance of the effects, it did not shed much light on the balance of the underlying forces behind these effects.
+I proceed to investigating the two effects in greater detail now.
 
@@
 Second, I did not find any change in the discounting behavior for products that are close to downgrading their review bins.
-My theory of disconting in the face of review transitions, applied to these findings, implies that reviews left during a discount can not be significantly better than regular reviews, as otherwise the lack of discounting by products close to a review downgrade is puzzling.
-But if reviews obtained during a discount are not very different from the regular reviews, it has to be the case that discounts fascilitate the arrival of reviews, providing firms with extra variance when they want to speed things up.
-Otherwise, discounting by firms close to a positive transition would be puzzling.
-In this section I investigate if these two hypotheses about the valence and quantity of reviews left during price promotions hold in data.
+The first finding implies that the selection effect and the variance effect can not be both negative for games close to a review upgrade.
+This is a weak finding, as it does not reveal if the selection effect is negative or positive.
+The second finding suggests that the selection effect should be positive, as it is balanced by the variance effect that we expect to be negative for the games in question.
+Alternatively, the variance effect is not strong either.
+In this section I investigate the signs of the selection and variance effects directly.
+
+The selection effect is easy to test directly.
+For example, we can compare the fractions of positive and negative reviews left on and off a discount.
+The variance effect is harder to strip down to a similar test.
+I will show that there in my data there is no evidence of the positive selection effect...
 

### 2020-10-07 Analysis/Code/Paper.Rmd
The body is ready.

@@
  title: |
-   | Consumer Reviews and Product Discounts:
-   | Evidence From Video Games
+   | Reaching for The Stars: Discounts and Review Tier 
+   | Transitions in the Video Games Market
 
@@
 
-reg3 <- plm(I(discount>0) ~ pos.treatment + neg.treatment +
-              log(needPosDays) + log(needNegDays) +
-              poly(tWODisc, degree = 2) + log(reviews+1) + score +
-              mPositive + age + young + day + week,
-                 data=panel[],
-            model="within",
-            index = c("ID", "t"))
-cov<-vcovHC(reg3, method="white1")
-se3 <- sqrt(diag(cov))
-
 R.low <- 0.7
@@
 
-star.out <- stargazer(reg1, reg2, reg3,
+panel[, pos.treatment := (needPos <= 2*band)]
+panel[, neg.treatment := (needNeg <= 2*band)]
+
+star.out <- stargazer(reg1, reg2,
              label = "potentialTransitionsResults",
@@
              title = "Discounts Close to Potential Transitions",
-             se=list(se1, se2, se3),
+             se=list(se1, se2),
              dep.var.labels = c("Discount Probability"),
-             column.labels = c("Full", "1 W. to Tr.", "Simple Tr."),
+             column.labels = c("Full", "1 W. to Tr."),
              covariate.labels = c("Close to Pos. Transition", "Close to Neg. Transition",
@@
 cat(star_insert_row(star.out,
-                    c("Time Effects: Weekdays, Week &  $\\checkmark$ &  $\\checkmark$ & $\\checkmark$ \\\\",
-                      "Game Effects & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\",
-                      "Poly($t$ W/O Discount, $d=2$) & $\\checkmark$ & $\\checkmark$ & $\\checkmark$ \\\\"),
+                    c("Time Effects: Weekdays, Week &  $\\checkmark$ &  $\\checkmark$\\\\",
+                      "Game Effects & $\\checkmark$ & $\\checkmark$  \\\\",
+                      "Poly($t$ W/O Discount, $d=2$) & $\\checkmark$ & $\\checkmark$\\\\"),
                     insert.after = c(35,35,35)))
@@
 The second column uses a more stringent definition of proximity to a transition, requiring a game to be `r band`, rather than `r 2*band`, days away from a potential transition to be counted as being “close to a transition”.
-The third column uses only transitions between “Mixed”, “Mostly Positive”, and “Positive” labels, as these are the transitions that rely on the review score only, while “Very Positive” and “Overwhelmingly Positive” require both a certain review score, and a certain number of reviews.\footnote{Technically, a game improving its review score from 79\% to 80\% can transition to both “Positive” and “Very Positive”, so the results in the third column bundle together these types of transitions.}.
-@SorokinStevens20 exclusively uses these simple review bins in their regression discontinuity analysis, precisely in order to avoid the complications that arise from double thresholds required for “Very Positive” and “Overwhelmingly Positive”.
-
 The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion.
-Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to feature a discount\footnote{The corresponding number for the games in the positive treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg2$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg3$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
-Proximity to a potential negative transition seems to have a negative or no effect on the probability of discount.
-The results in the main specification suggest that firms under a risk of deteriorating their review label are `r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount, albeit the effect is not significant in the other two specifications.
-
-It is instructive to look at the results through the lens of stylized model introduced earlier in the section.
+Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to feature a discount\footnote{The corresponding number for the games in the positive treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg2$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg1$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
+Proximity to a potential negative transition seems to have a negative effect on the probability of discount, albeit the effect is not very strong.
+I find that firms under a risk of deteriorating their review label are `r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount.
+
+It is instructive to look at the results through the lens of the stylized model introduced earlier in the section.
 Both the variance and the positive selection effects could explain why products close to a review upgrade are more likely to run a price promotion.
-The lack of significance of the effect for products close to a review slump could be explained by the clash of the variance effect and the selection effect.
+Weak significance of the effect for products close to a review slump could be explained by the clash between the variance effect and the selection effect.
 As we see, even though my empirical investigation has resolved the theoretical ambiguity of the signs and the significance of the effects, it did not shed much light on the balance of the underlying forces behind these effects.
@@
 
-# Discounts and Reviewing Behavior
+# Selection and Variance Effects
 
@@
 First, I found that firms are more likely to go on a discount when their products are close to upgrading their review bin.
-Second, I did not find any change in the discounting behavior for products that are close to downgrading their review bins.
+Second, I found only limited change in the discounting behavior for products that are close to downgrading their review bins.
 The first finding implies that the selection effect and the variance effect can not be both negative for games close to a review upgrade.
-This is a weak finding, as it does not reveal if the selection effect is negative or positive.
-The second finding suggests that the selection effect should be positive, as it is balanced by the variance effect that we expect to be negative for the games in question.
-Alternatively, the variance effect is not strong either.
+This is a weak finding, as finding the opposite would be really surprising.
+Moreover, it does not reveal if the selection effect is negative or positive.
+The second finding suggests that the variance effect should be at least somewhat important.
+Given that the variance and the selection effect could go in different directions for the products close to the negative transition, the separate contributions of the two effects also remain unclear.
 In this section I investigate the signs of the selection and variance effects directly.
@@
 The selection effect is easy to test directly.
-For example, we can compare the fractions of positive and negative reviews left on and off a discount.
+We would simply need to compare the fractions of positive and negative reviews left on and off a discount.
 The variance effect is harder to strip down to a similar test.
-I will show that there in my data there is no evidence of the positive selection effect...
-
-To formulate and test these hypotheses, I complement my model of demand and gaming on Steam introduced in Section \ref{demandSection} by a model of reviewing behavior.
+First, if one is willing to take my stylized model seriously, then the absence of the selection effect in the data would indicate that all the effects are driven by the variance effect.
+This idea could be further developed.
+Even if the selection effect is not zero, if we could quantify it, then “controlling” for the magnitude of the selection effect could shed light on the importance of the variance effect.
+Another way to evaluate the importance of the variance effect is to look at the extent to which a discount speeds up the arrival of reviews.
+For the variance effect to be relevant, a discount should be able to bring a significant number of new reviews.
+
+I implement these ideas as follows.
+I complement my model of demand and gaming on Steam introduced in Section \ref{demandSection} with a model of reviewing behavior.
 A formal model of reviewing behavior is necessary for several reasons.
 First, a structural model allows me to explicitly introduce the parameters of interest--probabilities of leaving a good or a bad reviews on and off a discount.
-Second, more importantly, the model will allow me to use my estimates of the demand process to make statements about the absolute change in probability of leaving a review that is due to the discount.
-One does not need a model to check if more reviews are left during a price promotion--a simple comparison of means would do.
-However, since sales are unobserved, it is impossible to say if the new reviews are entirely due to the influx of new customers, or part of it could be explained by an increased willingness to leave a review during a discount.
+With the estimates of these parameters I will be  able to directly assess the importance of the selection effect.
+Having developed a measure of the valence of the reviews left during a discount, I will be able to control for the selection effect in the regression of discounting behavior on proximities to transition (\ref{potTransitionsReg}).
+Second, the model will allow me to use my estimates of the demand process to make statements about the absolute change in probability of leaving a review that is due to the discount.
+Since sales are unobserved, it is impossible to say if the surge in reviews during a discount is entirely due to the influx of new customers, or if part of it could be explained by an increased willingness to leave a review during a discount.
 I use my model to estimate sales, and therefore I can make inference on the propensity to leave a review.
-Note that most studies studying reviewing behavior do not observe anything close to daily sales, and thus could not possibly have identified the effects I am interested here.
-
-As a preview of results, I do find that customers are significantly more likely to review a product if they purchase it during a price promotion, albeit the valence of the reviews is unaffected, on average.
-In other words, I provide evidence that, in my data, the negative selection effect of lower prices on the type of customers leaving reviews that has been documented in the literature does not outweigh the direct effect of lower prices on their satisfaction and their review decision.
-I then proceed to allow firms in my sample to be heterogeneous in the probabilities of receiving positive and negative reviews on and off discount.
-I check if firms whose customers are particularly likely to leave a like during a discount are more likely to discount, and I find some support for this hypothesis.
+Such inference can not be made without a model of demand and review activity or sales data, neither of which are common in the literature.
+
+In my data I find no evidence of positive selection effect.
+Table \ref{reviewLag} in the Appendix shows that, following a discount, the review score goes down by half a point (out of 100), and does not recover in the week following the discount.
+With my estimates from the structural model I fail to reject the hypothesis that the selection effect is negative.
+When I control for the size of the selection effect at a game level, I find that the negative effect of the proximity to a negative transition on discounting increases substantially, and becomes more significant.
+This serves as evidence of the importance of the variance effect.
+Speaking of the effect of a discount on the review arrival,  Table \ref{reviewLag} shows that a discount is followed by around 7 extra reviews, on average, in the week after its introduction, or at least doubles the speed of review arrival.
+My structural estimates show that consumers are significantly more likely to leave reviews during discounts, further highlighting the role of the variance effect.
 
@@
 
-In the simplest specification I use $w_{it} = [1, disc_{it-k}]'$, $\forall i: \rho_i^+ = \rho^+$,  implying $r_{it}^+ = \rho^+_0 + disc_{it}\rho^+_1$, which simply says that buyers of all games leave a positive reviews with one of the two possible probabilities: $\rho^+_0$ off a discount, and $\rho^+_0 + \rho^+_1$ on a discount.
+In the simplest specification I use $w_{it} = [1, disc_{it-k}]'$,  $\rho_i^+ = \rho^+$ for all $i$,  implying $r_{it}^+ = \rho^+_0 + disc_{it}\rho^+_1$.
+This simply says that buyers of all games leave a positive reviews with one of the two possible probabilities: $\rho^+_0$ off a discount, and $\rho^+_0 + \rho^+_1$ on a discount.
 Similarly, a probability of a negative review could be either $\rho^-_0$, or $\rho^-_0 + \rho^-_1$.
@@
 
-In the introduction to this section I outlined two hypotheses I want to test.
+In the introduction I implicitly defined two hypotheses I want to test.
 First, I want to know if consumers are more likely to leave a review if they buy on a discount.
@@
 
-The second hypothesis I am interested in involves the sentiment of the reviews left on and off a discount.
+The second hypothesis I am interested in is whether the selection effect is positive or not.
 Product's review score measures the fraction of positive reviews among all reviews left, reflecting the probability to get a good review conditional on having a review.
@@
 \begin{equation}
-\PP{L_t = 1} = \CP{"Like"}{"Review"} = \frac{\rho^+_{0}}{\rho^+_{0} + \rho^-_{0}}
+\PP{L_t = 1} = \CP{\text{“Like”}}{\text{“Review”}} = \frac{\rho^+_{0}}{\rho^+_{0} + \rho^-_{0}}
 \end{equation}
@@
 \begin{equation}
-\PP{L_t = 1} = \CP{"Like"}{"Review"} = \frac{\rho^+_{0} + \rho^+_{1}}{\rho^+_{0} + \rho^+_{1} + \rho^-_{0} + \rho^-_{1}}
-\end{equation}
-
-\noindent The second hypothesis can now be formulated as follows: the expected review score on a discount is not higher than the expected review score off a discount. Formally, we have
+\PP{L_t = 1} = \CP{\text{“Like”}}{\text{“Review”}} = \frac{\rho^+_{0} + \rho^+_{1}}{\rho^+_{0} + \rho^+_{1} + \rho^-_{0} + \rho^-_{1}}
+\end{equation}
+
+\noindent I can then test the sign of the selection effect by testing the following hypothesis: the expected review score on a discount is not higher than the expected review score off a discount.
+Formally, we have
 \begin{align}\label{hyp2}
@@
 
-To make my identificaiton argument I will focus on the case of just two regressors, $w_{it} = [1, disc_{it-k}]$, and heterogeneous parameters $\rho_i^+$, $\rho_i^-$.
-From this analysis it will become clear how I am able to identify $\rho$'s on a game-by-game basis, and how more regressors could be accommodated.
+To make my identification argument I will focus on the case of two regressors, $w_{it} = [1, disc_{it-k}]$, and heterogeneous parameters $\rho_i^+$, $\rho_i^-$.
+From this analysis it will become clear how I am able to identify $\rho_i$'s on a game-by-game basis, and how more regressors could be accommodated.
 Intuitively, the propensity to leave a review on and off a discount (the like and dislike rates $r_{it}^+$, $r_{it}^-$) are identified by the differences in reviews left on and off a discount.
@@
 Following assumption \ref{arrivalAssumptions}, the arrival of buyers for game $i$ on day $t$ follows a Poisson distribution with arrival rate $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$.
-I also assumed that, $k$ days later, each consumer leaves a  positive review with probability $r_{it}^+$, a negative review with probability $r_{it}^-$, and no review otherwise.
+I assumed that, $k$ days after the purchase is made, each consumer leaves a  positive review with probability $r_{it}^+$, a negative review with probability $r_{it}^-$, and no review otherwise.
 Then, the following proposition is true:
@@
 Proposition \ref{poissonReviews} allows one to easily write down the likelihood for positive and negative reviews separately.
-I will use the positive reviews as the leading example here, but all the findings automatically translate to the negative reviews case as well.
+I will use the positive reviews as the leading example here, but all the findings automatically translate to the case of negative reviews as well.
 For every game I observe the history of the review arrivals $\{(g_{it}, b_{it})\}_{t=1}^{T_i}$.
@@
 
-For simplicity, I treat $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$ as known, rather than aknowledging the fact that I only have estimates $\hat{\lambda}_{it} = \hat \lambda_i (1 + x_{it}'\hat \beta)$.
+For simplicity, I treat $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$ as known, rather than acknowledging the fact that I only have estimates $\hat{\lambda}_{it} = \hat \lambda_i (1 + x_{it}'\hat \beta)$.
 By the virtue of observing the majority of the games for many periods, the estimates of $\lambda_i$ should be relatively precise; estimates of $\beta$ were estimated using all the observations in the sample, and should be relatively precise as well.
@@
 \end{equation}
-As we can see, the ML-estimator of the like rate during a price promotion is just the ratio of the number of good reviews left on a discount over the expected arrival on that day.
+As we can see, the ML-estimator of the like rate during a price promotion is just the ratio of the number of good reviews left on a discount over the expected sales on that day.
 Similarly, the like rate off a discount can be estimated by
@@
 Notice that identification of these parameters requires the knowledge of the demand parameters $\lambda_{it}$, highlighting the point I made earlier: seeing more good reviews arriving on a discount is not sufficient to conclude whether customers are more likely to leave positive reviews when purchasing during a discount.
-One need to know how many more customers are buying because of the aforementioned discount.
+One needs to know how many more customers are buying because of the aforementioned discount.
 
@@
 The analysis above is complicated by two facts.
-First, for each game I observe the exact review count, but my demand estimates only apply to rush hours.
-For a sake of example, assume that every buyer leaves a review.
-Suppose also that every day there are two new buyers who play in the morning, and three new buyers who play in the evening, who abandone the game after just one day.
-My data would register 3 players leaving 5 reviews on a daily basis.
+First, for each game I observe all reviews ever left, but I only have information on a fraction of buyers, as my measure of the number of buyers is based on the peak-time data only.
+To see what the problem is, consider the following example.
+Assume that every buyer of the game leaves a review.
+Suppose also that every day there are two new buyers who play in the morning, and three new buyers who play in the evening.
+Both types abandon the game after just one day of playing.
+In such a world my data would register 3 players leaving 5 reviews on a daily basis, implying that one user leaves more than one review.
 This is the reason why I refer to the values of $(r_{it}^+, r_{it}^-)$ as rates, rather than probabilities (which they are in the model).
@@
 # preparation for formatting the estimates in a table
-texregObjects <- list()
+table <- list()
 gofnames <- c("Observations")
@@
 tr <- createTexreg(coef = theta1,
-                   coef.names = c("Prob. of Like", "Discount on Like", 
-                                  "Prob. of Dislike", "Discount on Dislike"),
+                   coef.names = c("Constant (Like)", "Discount (Like)",
+                                  "Constant (Dislike)", "Discount (Dislike)"),
                    se = sqrt(diag(omega1)),
@@
                    gof = c(dim(revs)[1]))
-texregObjects[1] <- list(tr)
+table[1] <- list(tr)
 
@@
 tr <- createTexreg(coef = theta2,
-                   coef.names = c("Prob. of Like", "Discount on Like", 
-                                  "Young on Like", "Old on Like", 
-                                  "Prob. of Dislike", "Discount on Dislike",
-                                  "Young on Dislike", "Old on Dislike"),
+                   coef.names = c("Constant (Like)", "Discount (Like)", 
+                                  "Young (Like)", "Old (Like)", 
+                                  "Constant (Dislike)", "Discount (Dislike)",
+                                  "Young (Dislike)", "Old (Dislike)"),
                    se = sqrt(diag(omega2)),
@@
                    gof = c(dim(revs)[1]))
-texregObjects[2] <- list(tr)
-```
+table[2] <- list(tr)
+```
+
 I start off by estimating the average probabilities of leaving a good and a bad review in the population, and by using the estimates to test hypotheses formulated in (\ref{hyp1}) and (\ref{hyp2}).
@@
 This is the selection effect of discounts on reviews.
-I also acknowledge the possibility that there could be a selection over time, when early buyers are very different from the late buyers.
+I also acknowledge the possibility that there could be a selection over time, when early buyers are very different from late buyers.
 Similarly, the perception of quality might be deteriorating over time as new games, with potentially better characteristics, are coming out.
@@
 ```{r results = 'asis'}
-texreg(texregObjects,
+table <- texreg(table,
        stars = c(0.01, 0.05, 0.1),
@@
        custom.model.names = c("(1)", "(2)"),
-       caption = "Estimates of the Review Parameters",
+       caption = "Estimates of the Review Rates",
        caption.above = T,
        label = "reviewEstimates")
+
+gof.location <- str_locate(table, c("Observations"))[1]
+table.bottom <- str_sub(table, gof.location, str_length(table))
+table.top <- str_sub(table, 1, gof.location - 1)
+table.bottom <- str_replace_all(table.bottom, ".000", "")
+table <- paste(table.top, table.bottom, sep = "")
+class(table) <- c("character", "texregTable")
+table
 ```
@@
 
-Setting aside the aforementioned issues, my results suggest that a typical user on Steam leaves a positive review with a probability around `r round(theta1[1]*100)`%, and leaves a negative review with a probability around `r theta1[3]*100`%.
+Setting aside the aforementioned issues, my results suggest that a typical user on Steam leaves a positive review with a probability around `r round(theta1[1]*100, 1)`%, and leaves a negative review with a probability around `r round(theta1[3]*100, 1)`%.
 Discounts appear to increase both probabilities, implying that users seem to be more likely to leave a review during a discount.
 I formally test this hypothesis, stated in (\ref{hyp1}), and I strongly reject the null that users are less likely to leave reviews when buying on a discount in favor of the alternative that they are more likely to leave reviews when buying on a discount (the values of the $t$-stats are `r round(t1.1[1],2)` and `r round(t1.2[1],2)` in the two specifications).
-My second hypothesis, stated in (\ref{hyp2}), is that reviews are less positive during a discount than they are outside the discount.
+The estimated change in the probability of leaving a review due to a discount is between `r round((theta2[2]+theta2[4])/(theta2[1]+theta2[3])*100)`% and `r round((theta1[2]+theta1[4])/(theta1[1]+theta1[3])*100)`%, where the smaller estimate is probably more reliable, as it takes into account the effects of age on discounting.
+These results indirectly confirm that the variance effect could be playing a big role in the discounting decision of firms on Steam, as discounts are really effective at bringing new reviews.
+
+My second hypothesis, stated in (\ref{hyp2}), is that reviews are less positive during a discount than they are outside of a discount.
 I fail to reject the null in favor of the alternative that reviews left during a price promotion are more positive (the $p$-values are `r round(1-pnorm(t2.1[1]),2)` and `r round(1-pnorm(t2.2[1]),2)`).
 As we can see, there is no disagreement across specifications on both hypotheses, giving me confidence that this result is robust.
-As for the age controls,  I find that users are more likely to leave reviews in the first two weeks, but, somewhat surprisingly, do not lose steam as the game becomes older.
-Both findings are in accordance with the patterns or reviewing dynamics depicted in Figure \ref{reviewDescriptivePlots}.
+This is also in accord with the results from the regression of the score on the lags of discounts and controls, presented in Table \ref{reviewLag}, which finds a small negative effect of discounts on the review score.
+Together these findings suggest that the selection effect of discounts is not big, and can not be the decisive force driving the discounting behavior close to review transitions.
 
@@
   scale_y_continuous(name = NULL,
-                     breaks = c(0, 1, 2),
                      minor_breaks = NULL) +
@@
 
-Now that I have carried out the analysis of the average reviewing propensity and valence, I turn attention to heterogeneity between firm.
+To strengthen this point, I use the difference in the valence of reviews on and off a discount to measure the selection effect at the game level.
+With such estimates at hand, I can revisit my regression of discounts on proximities to transitions (\ref{potTransitionsReg}) controlling for the selection effect.
 In the identification section I showed how one can estimate the like and dislike rates on the product level.
-The theory of discounting close to review transitions developed in this paper suggests that products whose customers leave better reviews during a price promotions should be more likely to discount when they are close to a transition, regardless of whether it is a positive or a negative one.
-It is convenient to introduce notation for the difference between the expected review scores on and off a discount for the games in my sample:
+Using these estimates, the selection effect can be measures as the difference between the expected review scores on and off a discount:
 
@@
 
-Figure \ref{scoreDifPlot} depicts the distribution of $\widehat{\Delta score_{i}}$, the estimated differences in the expected review scores on and off a discount for the games in my sample.
-A couple of paragraphs ago I have shown that the average difference is not statistically distinguishable from zero, and the plot complies with that finding.
+Figure \ref{scoreDifPlot} depicts the distribution of $\widehat{\Delta score_{i}}$, the sample counterpart of this measure.
+In line with the hypothesis test of the sign of the selection effect in the sample, the histogram is centered around zero.
 Estimates of $\Delta score_{i}$ vary in their precision from game to game, as games that spent less little time in the sample and/or on discounts would naturally have noisier estimates.
@@
 
-With these estimates at hand, I can now revisit Model (\ref{potTransitionsReg}), the regression I used to establish the effect of proximity to a potential transition on the discounting probability.
-I modify the equation by including the interaction between the
-treatment variables of interest (proximities to potential transitions) and $\Delta score_{i}$, leading to
+I  use these estimates to modify (\ref{potTransitionsReg})  by including the interaction between the treatment variables of interest (proximities to potential transitions) and $\Delta score_{i}$, leading to
 \begin{equation}\label{potTransitionsHeteroReg}
-disc_{it} = (\beta^+_0 + \Delta score_{i}\beta^+_1)T_{it}^+ +(\beta^-_0 + \Delta score_{i}\beta^-_1)T_{it}^- + \Delta score_{i} + X_{it}\beta + f_i + \tau_t + \varepsilon_{it}
-\end{equation}
-
-\noindent As $\Delta score_{i}$ does not change over time, it can not be estimated by the within-estimator, but the interaction term could still be included.
-My theory implies that $\beta^+_1$ and $\beta^-_1$ should be positive.
-I estimate (\ref{potTransitionsHeteroReg}) by OLS (without the fixed effect term $f_i$) and by the within-estimator.
-The results are presented in Table \ref{scoreDifTransDiscReg} (the controls are omitted for brevity).
+disc_{it} = (\beta^+_0 + \Delta score_{i}\beta^+_1)T_{it}^+ +(\beta^-_0 + \Delta score_{i}\beta^-_1)T_{it}^- +  X_{it}\beta + \Delta score_{i} + f_i + \tau_t + \varepsilon_{it}
+\end{equation}
+
+\noindent As $\Delta score_{i}$ does not change over time, its effect on discounting probability can not be estimated by the within-estimator, but the interaction term could still be included.
+Notice that $\beta^+_0$ and $\beta^-_0$ measure the effect of proximity to a transition on discounting probability if $\Delta score_{i} = 0$, i.e.
+\emph{if there is no selection effect}.
+The signs and significance of these coefficients offers another test of the importance of the variance effect.
+In the absence of the selection effect, a moderate amount of variance is good for a game close to a review upgrade, and is bad for a game close to a review downgrade.
+Thus, we expect to find $\beta^+_0 >0$ and $\beta^-_0 < 0$.
+The remaining coefficients $\beta^+_1$ and $\beta^-_1$ measure how the selection effect changes the probability of running a price promotion close to a transition.
+Selection effect is good for the firms, and the prediction of my stylized model is $\beta^+_1 > 0$ and $\beta^-_1 > 0$.
 
@@
 
+I estimate (\ref{potTransitionsHeteroReg}) by OLS (without the fixed effect term $f_i$) and by the within-estimator.
+The results are presented in Table \ref{scoreDifTransDiscReg} (the controls are omitted for brevity).
 The least squares estimates in column (OLS) are mainly presented to check the correlations in the data.
-Better sentiment of reviews left during a discount is not related to the frequency of discount on its own, but products close to a positive transition are more likely to discount if their customers are more lenient when buying during a price promotion.
-This effect is not present in the preferred specification (\ref{potTransitionsHeteroReg}), which is estimated in the second column.
-Quite interestingly, this specification finds $\beta^-_0 < 0$, while my earlier results, essentially, failed to find any effect of a proximity to a negative transition on discounting behavior.
-This finding makes a lot of sense.
-Notice that $\beta^-_0$ measures the effect of the aforementioned proximity on discounting probability conditional on $\Delta score_{i} = 0$.
-For a game that is close to downgrading its review score and which does not receive better reviews on a discount, initiating a price promotion is a gamble with no clear upside and a significant downside.
-This finding complies perfectly with the prediction of the stylized model of discounting behavior presented in section \ref{stylizedModel}.
+Games that tend to receive better reviews on discounts discount more.
+However, the selection effect is not significant in both specifications.
+Crucially, in the preferred specification (FE) I find that $\beta^-_0 < 0$, and $\beta^+_0 > 0$.
+Once the variation in the selection effect is controlled for, I obtain the coefficients measuring the impact of the variance effect on discounting decisions, and the signs align with the theory.
+Their sizes are also quite economically meaningful, suggesting that, in the absence of the selection effect, games close to a positive transition are \textcolor{red}{number}% more likely to go on a discount, and games close to a negative transition are \textcolor{red}{number}% less likely to go on a discount.
 

### 2020-10-09 Analysis/Code/Paper.Rmd
Draft 1.0

@@
 
-# Literature Review
-
-This paper contributes to several closely related literatures in economics and marketing.
+In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17].
+A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfactory without guidance.
+Such guidance is provided by different types of recommendation systems.
+Many marketplaces or third party websites allow consumers to review products and services that they purchased, and aggregate these reviews into a rating, greatly facilitating the comparison between the alternatives.
+These ratings are often given a simple graphical representation; for example, a number of stars between 0 and 5 is a common way to split the alternatives into *review tiers*.
+Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services.
+Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews are at the very least important for the success of the business.
+Not surprisingly, firms assume an active approach to managing their reviews.
+Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors.
+
+In this paper I study a novel form of review management.
+I show that firms can use discounting in order to facilitate *transitions* between review tiers.
+Imagine a product that is several good reviews short of obtaining an additional star.
+I ask: would it be profitable for such a product to run a price promotion?
+With a help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect.
+Customers who purchase the good on a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews.
+If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount.
+Whether the selection effect is positive or negative is an empirical question, and I answer this question with my data.
+The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier.
+Extra positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews would not affect its review status and sales much.
+While extra variance is good for products that are on the verge of a tier upgrade, it could be harmful for products that are close to sliding one review tier down.
+Fearing to lose that precious star, such products would prefer to delay running a price promotion, unless the selection effect is positive and strong.
+
+To quantify all these effects, I analyze data from Steam, a major marketplace for computer video games.
+I build and estimate a simple structural model of demand and reviewing behavior on Steam.
+The demand part of the model lays the groundwork for my analysis.
+I confirm the importance of better review tiers for sales on Steam, finding a premium of as high as 10% of being in the best bin, and a penalty of up to 13% for not having reviews, compared to a mediocre review tier.
+My estimates also highlight how impactful discounts are in this market, with an average discount being accompanied by a 25% spike in sales.
+Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given the differential contribution of various tiers on sales.
+I further document that these incentives translate into action.
+I find that products that are close to upgrading their review tier are 4-9% more likely to be on a discount, and I find some evidence that proximity to a downward transition decreases the probability to be on a discount by up to 4%.
+
+To learn more about the relative contributions of the variance and the selection effects to the observed behavior, I estimate the review part of my structural model.
+I estimate the effect of discounts on the probabilities to leave positive and negative reviews.
+I find no evidence that the selection effect is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion.
+Thus, I attribute firms' behavior to the variance effect.
+While this effect is hard to test directly, I provide some further indirect tests of its impact on the discounting behavior around review tier transitions.
+I estimate the size of the selection effect at the product level, and “control” for it in my regressions of discounts on proximities to transition.
+I find that, in the absence of the selection effect, products that are close to a review downgrade are significantly less likely to discount, which is consistent with the idea that the variance effect is negative for such products.
+I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.
+
+## Literature Review
+
+While some of my findings are new and interesting on their own, others are best measured against the literatures in economics and marketing that I contribute to.
 The oldest of these is the literature investigating the impact of online consumer reviews on sales.
@@
 @AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue.
-@SorokinStevens20 applies a similar approach to the video games market and also finds that better review labels increase sales, albeit raising some concerns about the validity of the approach.
+In studies relying on a discontinuity for identification, it is crucial that assignment around thresholds is as good as random.
+Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes the test once, and either earns an “A” or a “B”), products carry their review scores from day to day.
+If one product is slightly below the cutoff and has 4 stars, and another product is slightly above the cutoff, why would the former not try to do something to cross the cutoff, especially if better review bins are more lucrative?
+My paper asks precisely that question, and shows that such concerns are well-founded.
+However, I do not study the implications of such behavior for a regression discontinuity approach used in the aforementioned papers.
+
+@SorokinStevens20 raises other concerns about the validity of the regression discontinuity approach in studying the causal effect of reviews on outcomes.
+To my knowledge, it was the first paper to use Steam as the object of its analysis.
 In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from the video games' usage data.
-The present paper supplements the panel methods in @SorokinStevens20 by offering a structural way to estimate the effect of reviews on sales in the absence of direct sales data.
+I inherit the data from that paper, but confront the absence of sales data in a more hands-on way.
+I make assumptions about the gaming patterns of the users of the games in my sample, and formulate a structural model of the data generating process.
+With the help of that model, I manage to extract information on product sales from usage data only.
+I also compare the estimates of the structural model with the ones obtained by its simpler regression analog, which happen to be quite similar.
+The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.
 
@@
 @LucaZervas16 provide similar evidence for restaurants on Yelp.
-A more honest way for a firm to influence reviews is by assuming an active approach to review management, and to publicly respond to reviews published online.
+A more scrupulous way for a firm to influence reviews is by assuming an active approach to review management---for instance, by publicly responding to the reviews it receives.
 @GuYe14 provide evidence that consumers who had left a negative review about their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management.
@@
 Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle.
-Another strand of literature is studying whether different kinds of promotions have an effect on firms' online reputation.
-In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a Groupon price promotion.
-They present evidence that customers attracted by the promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher, which can explain the reasons behind their dissatisfaction.
-Thus, the paper cautions against running price promotions in an attempt to poach new customers and improve the online reputation.
+Another strand of literature is studying whether price promotions have an effect on firms' online reputation.
+In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a price promotion through Groupon, a promotion service.
+In other words, @ByersEtAl12 documents a negative selection effect on Yelp.
+It presents evidence that customers attracted by a promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher.
+This difference can explain the reasons behind the dissatisfaction of the Groupon customers.
 @Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion.
+There are a couple of other studies that dispute the negativity of the selection effect.
 @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews.
-In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and they provide evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.
-
-My paper contributes to this literature in several ways.
-First, I present evidence from a market that was not previously studied in the literature, and confirm that reviews left on a price promotion are not favorable to businesses.
-Second, I show that, nevertheless, firms can successfully manage their online reputation through pricing, by going on a discount when they are close to upgrading their review tier.
-A study similar in spirit to mine is that of @Zegners17, who argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap".
-However, this study also finds that books are more likely to solicit negative feedback when sold for free, which somewhat undermines the strategy.
-Similar to @ByersEtAl12, @Zegners17 argues that purchasers of free books differ from the purchasers of regular books in their observable characteristics, and explains the negativity of the reviews by the selection effect.
+In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and it provides evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.
+My study contributes to this debate by documenting the absence of a positive selection effect in a new market.
+Additionally, my paper is the first to focus on discrete changes in review tiers that follow the discounts, instead of studying the continuous effect of a discount on the review score.
+
+Based on its findings, @ByersEtAl12 cautions businesses against running price promotions in an attempt to poach new customers and improve their online reputation.
+To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, this finding presents a puzzle.
+A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap".
+While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which somewhat undermines the strategy.
+I provide a novel mechanism--- the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative.
+The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it would find it profitable to sell for free even if the probability to solicit favorable reviews is small.
+After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial.
+
+The rest of this paper is organized as follows.
+Section \ref{dataSection} describes the institutional setting and the data I use.
+Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam.
+The technical nature of the material in this section contributes greatly to its size, but goal of this section is simply to quantify the importance of different review tiers on sales, and to show that discounts are effective in attracting new customers.
+The main findings are described in  Section \ref{descriptiveEvidence}.
+It opens with a stylized model of discounting for a product close to a review tier transition, and introduces the selection and the variance effects.
+The section proceeds by establishing that such discounting behavior takes place in the data.
+Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} by a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effect to the observed patterns of discounting around review transitions.
+Section \ref{conclusion} concludes.
 
 # Institutional Setting and Data 
+\label{dataSection}
 
@@
 \label{demandSection}
-\textcolor{red}{Write a small introduction here.}
+
+In this section I develop and estimate a simple structural model of demand an gaming activity on Steam.
+I discuss at length the assumptions and the interpretation of the parameter estimates.
+However, the main takeaway from this section is simple: better review labels improve sales, and discounts are important drivers of sales on Steam.
+These two facts form the foundation of my main analysis that will be carried out in Section \ref{descriptiveEvidence}, where I will show that firms use discounts to attract new reviews and to transition to more lucrative review tiers.
+I will further extend the model from this section in Section \ref{selectionEffect}.
 
@@
 
-\textcolor{red}{Add an introduction}
-
 I this section I present the main findings of the paper.
@@
 # Selection and Variance Effects
+\label{selectionEffect}
 
@@
 I start off by estimating the average probabilities of leaving a good and a bad review in the population, and by using the estimates to test hypotheses formulated in (\ref{hyp1}) and (\ref{hyp2}).
-I use two sets of covariates to explain these probabilites.
+I use two sets of covariates to explain these probabilities.
 The baseline set of covariates, $w_{it} = [1, disc_{it-k}]'$, only allows the probability of a like or a dislike to change if a discount is in place.
@@
 In the identification section I showed how one can estimate the like and dislike rates on the product level.
-Using these estimates, the selection effect can be measures as the difference between the expected review scores on and off a discount:
+Using these estimates, the selection effect can be measured as the difference between the expected review scores on and off a discount:
 
@@
 In line with the hypothesis test of the sign of the selection effect in the sample, the histogram is centered around zero.
-Estimates of $\Delta score_{i}$ vary in their precision from game to game, as games that spent less little time in the sample and/or on discounts would naturally have noisier estimates.
+Estimates of $\Delta score_{i}$ vary in their precision from game to game, as games that spent less time in the sample and/or on discounts would naturally have noisier estimates.
 However, the distribution appears to be well-behaved.
@@
 Once the variation in the selection effect is controlled for, I obtain the coefficients measuring the impact of the variance effect on discounting decisions, and the signs align with the theory.
-Their sizes are also quite economically meaningful, suggesting that, in the absence of the selection effect, games close to a positive transition are \textcolor{red}{number}% more likely to go on a discount, and games close to a negative transition are \textcolor{red}{number}% less likely to go on a discount.
+Their sizes are also quite economically meaningful, suggesting that, in the absence of the selection effect, games close to a positive transition are \textcolor{red}{number} `r round(100*reg3$coefficients["pos.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% more likely to go on a discount, and games close to a negative transition are \textcolor{red}{number}  `r -round(100*reg3$coefficients["neg.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% less likely to go on a discount.
+
+# Conclusion
+\label{conclusion}
+
+In this paper I document a novel mechanism through which firms use pricing to manage their online reviews.
+Using data from Steam, a major digital marketplace for computer video games, I show that firms discount their products in order to facilitate transitions between review tiers.
+Products that are close to upgrading their review tier are 4-9% more likely to be on a discount, while products close to deteriorating their review tier are up to 4% less likely to discount, albeit this effect is less significant.
+
+I identify two channels that can make such behavior profitable: the *selection* effect and the *variance* effect.
+Customers who purchase the good on a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews.
+If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount, regardless of whether the product is about to upgrade or downgrade its review tier.
+There is some disagreement in the literature about the sign of the selection effect.
+I contribute by showing that on Steam the effect is not positive.
+
+The variance effect reflects the asymmetry between the successful and the unsuccessful discounting campaign, as measured by the valence of the new reviews.
+A product close to moving one review tier up benefits greatly from a good realization, while a bad one does not change its review tier much.
+On the other hand, a product that is close to sliding into a worse tier, if averse to a bad outcome, and would benefit less in absolute value from a good outcome.
+While I manage to test the selection effect directly, I have to test the variance effect by trying to falsify the predictions that follow from it.
+My strongest test is given by the prediction that, in the absence of a positive selection effect, the variance effect has to make a product on the verge of deteriorating its reviews less likely to discount.
+When I control for the size of the selection effect, I find that the aforementioned decline in probability of discounting goes from being 4% and weakly significant to 6% and highly significant.
+I also leverage my unique data and  structural model to document that consumers are more likely to leave reviews when they buy on a discount, which indirectly supports the importance of the variance effect.
+
+I develop a structural model of demand and product usage, that allows me to make statements about sales using data on usage.
+This model extends the approach of @SorokinStevens20.
+Using this model, I provide new estimates of the causal effect of reviews on sales on Steam.
+Being in the best review bin carries a premium of up to 10% compared to a mediocre review tier; having no reviews has a negative effect of up to 13%.
+In a methodological contribution, I compare the performance of my structural model with its simpler cousin from @SorokinStevens20.
+While there are some important differences between the two sets of estimates, I find the part concerning the effect of review bins on sales to be fairly similar.
 

### 2020-10-11 Analysis/Code/Paper.Rmd
Corrections

@@
 
-In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17].
+In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17, p.379].
 A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfactory without guidance.
-Such guidance is provided by different types of recommendation systems.
-Many marketplaces or third party websites allow consumers to review products and services that they purchased, and aggregate these reviews into a rating, greatly facilitating the comparison between the alternatives.
+Such guidance is now routinly provided by different types of recommendation systems.
+Many marketplaces or third party websites allow consumers to review products and services that they purchased, and then aggregate these reviews into a rating, greatly facilitating the comparison between alternatives.
 These ratings are often given a simple graphical representation; for example, a number of stars between 0 and 5 is a common way to split the alternatives into *review tiers*.
 Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services.
-Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews are at the very least important for the success of the business.
+Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews important, if not crucial, for the success of the business.
 Not surprisingly, firms assume an active approach to managing their reviews.
@@
 Customers who purchase the good on a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews.
-If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount.
+If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount, as new customers are likely to leave positive reviews and help the product advance to the next review tier.
 Whether the selection effect is positive or negative is an empirical question, and I answer this question with my data.
 The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier.
-Extra positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews would not affect its review status and sales much.
+Extra positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews might not affect its review status---and, therefore, sales---by much.
 While extra variance is good for products that are on the verge of a tier upgrade, it could be harmful for products that are close to sliding one review tier down.
@@
 
-To learn more about the relative contributions of the variance and the selection effects to the observed behavior, I estimate the review part of my structural model.
+My structural model provides further insight into the relative contributions of the variance and the selection effects to the observed behavior.
 I estimate the effect of discounts on the probabilities to leave positive and negative reviews.
@@
 Thus, I attribute firms' behavior to the variance effect.
-While this effect is hard to test directly, I provide some further indirect tests of its impact on the discounting behavior around review tier transitions.
+While this effect is harder to test directly, I provide some  indirect tests of its impact on the discounting behavior around review tier transitions.
 I estimate the size of the selection effect at the product level, and “control” for it in my regressions of discounts on proximities to transition.
@@
 
-## Literature Review
-
 While some of my findings are new and interesting on their own, others are best measured against the literatures in economics and marketing that I contribute to.
@@
 An extensive review of the studies focusing on this topic and their meta-analysis is provided, for example, by @Floyd14.
-<!-- Researchers have analyzed multiple online platforms, selling different products and employing different review systems, and produced, overall, conflicting evidence on whether reviews improve sales, and if so, through which channels.
-The major identification challenge stems from the fact that better reviews might simply be manifestations of consumer preferences for certain products, or reflect higher quality of the underlying products.
-As preferences and quality are unobserved and, in general, fluid, researchers have struggled to come up with convincing identification strategies.
--->
-In a seminal contribution in this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales.
+In a seminal contribution to this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales.
 A similar approach applied to the same market was recently used by @ReimersWaldfogel20, who reaffirm the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews.
@@
 In studies relying on a discontinuity for identification, it is crucial that assignment around thresholds is as good as random.
-Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes the test once, and either earns an “A” or a “B”), products carry their review scores from day to day.
-If one product is slightly below the cutoff and has 4 stars, and another product is slightly above the cutoff, why would the former not try to do something to cross the cutoff, especially if better review bins are more lucrative?
+Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes the test once, and either earns an “A” or a “B”), review scores of products on review platforms are moving slowly and are tested against the threshold on a daily basis.
+If a product is slightly below the cutoff and has 4 stars, why would it not try to do something to cross the cutoff, especially if better review bins are more lucrative?
 My paper asks precisely that question, and shows that such concerns are well-founded.
-However, I do not study the implications of such behavior for a regression discontinuity approach used in the aforementioned papers.
+I do not study the implications of such behavior for a regression discontinuity approach used in the aforementioned papers, but my findings could inform further inquiry into the subject.
 
@@
 To my knowledge, it was the first paper to use Steam as the object of its analysis.
-In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from the video games' usage data.
-I inherit the data from that paper, but confront the absence of sales data in a more hands-on way.
-I make assumptions about the gaming patterns of the users of the games in my sample, and formulate a structural model of the data generating process.
-With the help of that model, I manage to extract information on product sales from usage data only.
-I also compare the estimates of the structural model with the ones obtained by its simpler regression analog, which happen to be quite similar.
+In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from video games' usage data.
+I inherit the data from that paper, but confront the absence of sales data in a new way.
+I make assumptions about the gaming patterns for the games in my sample, and formulate a structural model of the data generating process.
+With the help of this model, I manage to extract information on product sales from usage data.
+I compare the estimates of the structural model with the ones obtained by its simpler regression analog, and find important similartities and dissimilarities.
 The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.
@@
 @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews.
-In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and it provides evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.
+In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreases the likelihood of negative feedback.
+The effect is explained by clients reciprocating to the rebate, rather than byt the differences between customers buying with a rebate and without it.
 My study contributes to this debate by documenting the absence of a positive selection effect in a new market.
@@
 After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial.
+If this reasoning is commonplace, then the researcher would observe free pricing to deteriorate review scores, on average, but the average effect on sales would be positive.
 
@@
 Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam.
-The technical nature of the material in this section contributes greatly to its size, but goal of this section is simply to quantify the importance of different review tiers on sales, and to show that discounts are effective in attracting new customers.
+The technical nature of the material in this section contributes greatly to its size, but the goal of this section is simply to quantify the importance of different review tiers on sales, and to show that discounts are effective in attracting new customers.
 The main findings are described in  Section \ref{descriptiveEvidence}.
@@
 The section proceeds by establishing that such discounting behavior takes place in the data.
-Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} by a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effect to the observed patterns of discounting around review transitions.
+Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} by a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effects to the observed patterns of discounting around review transitions.
 Section \ref{conclusion} concludes.
@@
 Steam is arguably the largest online marketplace for selling computer games in the world.
-Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it has earned around US\$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames].
+Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it has earned around \$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames].
 Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion
@@
 
-Any user who has a copy of a game on Steam can leave a review for that game.
-Starting from late 2016, by default, Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer).
+Any user who owns a game on Steam can leave a review for that game.
+Starting from late 2016 Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer).
 This distinguishes Steam from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews).
 This gives me confidence in the authenticity of most reviews.
-This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors.
+This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors [@steamPurge].
 With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave scrupulously.
@@
 A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews.
-Based on the score, Steam assigns *review labels*, or bins, to each game.
+Based on the score, Steam assigns *review tiers* to each game\footnote{I use words “tier”, “bin”, and “label” interchangebly througout the text}.
 These labels\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}.
@@
 Crucially, according to Steam's documentation, all review labels better than “Negative“ have a very similar contribution to visibility on the platform, which means, for example, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2].
-Therefore, any effect of the review labels on, say sales, should come through the perceived quality differences between different bins, rather than some mechanical visibility differences.
+Therefore, any effect of the review labels on sales should come through the perceived quality differences between different bins, rather than some mechanical visibility differences.
 As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.
@@
 Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB.
-More importantly, Steam Database offers a daily time series of prices and player activity for each game on Steam.
+More importantly, Steam Database contains time series of prices and player activity for each game on Steam on a daily level.
 In principle, the pricing information could be obtained by a repeated scraping of the store.
@@
 The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community most certainly implies that they are doing the best they can.
-The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent player for each game on a daily basis.
-In other words, if on a particular day 10 people play the game every hour, except noon, when 13 people play the game simultaneously, then the recorded player count for this game on that day will be 13.
+The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent players for each game on a daily basis.
+To clarify this definition, consider an example game that, on some day, was played by 10 people at every hour, except noon, when 13 people played the game simultaneously.
+The recorded player count for this game on that day will be 13.
 The price and the player count time series are the major “dynamic” variables used in the analysis.
@@
 The player count also jumps when a discount is given, reflecting the influx of new players.
-Games differ a lot in their sizes, as is evident from Figure \ref{sampleSizeHist}.
-
-```{r sample-size-hist, fig.cap='\\label{sampleSizeHist} Distributions of the Player Count on, and the Number of Reviews Accumulated by, the Age of 180 Days.'}
-p1 <- ggplot(data = panel[age==180, .(x = log(number))]) +
-  geom_histogram(mapping = aes(x = x, y = ..density..), 
-                 color = "black", 
-                 position = "identity", 
-                 alpha = 0.9,
-                 binwidth = 0.5,
-                 boundary = 0,
-                 fill = my.colors[1]) +
-  geom_density(mapping = aes(x = x), 
-                 color = "black", 
-                 position = "identity", 
-                 alpha = 0.4,
-                 fill = my.colors[1]) +
-  scale_x_continuous(name = "Log Players",
-                     breaks = seq(0, 8),
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = NULL, 
-                     minor_breaks = NULL) +
-  my.theme()
-
-p2 <- ggplot(data = panel[age==180, .(x = log(reviews))]) +
-  geom_histogram(mapping = aes(x = x, y = ..density..), 
-                 color = "black", 
-                 position = "identity", 
-                 alpha = 0.9,
-                 binwidth = 0.5,
-                 boundary = 0,
-                 fill = my.colors[1]) +
-  geom_density(mapping = aes(x = x), 
-                 color = "black", 
-                 position = "identity", 
-                 alpha = 0.4,
-                 fill = my.colors[1]) +
-  scale_x_continuous(name = "Log Reviews",
-                     breaks = seq(0, 8),
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = NULL, 
-                     minor_breaks = NULL) +
-  my.theme()
-
-ggarrange(p1, p2, ncol = 2, nrow = 1, align = "h")
-```
-
-```{r sample-size-hist-vert, include=FALSE, fig_height = 5}
-# for beamer
-ggarrange(p1, p2, ncol = 1, nrow = 2, align = "h")
-```
-
-As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is in order.
-A representative game in the sample never changes its price, but instead occasionally goes on discounts, slowly increasing their magnitude as the game ages.
-There are
-`r panel[discount==F, diff(price), by = ID][V1>0, .N]` incidents of price change in the data, compared to 
-`r panel[discNew==T, .N]` discounts.
-Steam has a number of rules that regulate price promotions on its platform.
-A game can have a launch discount, but, otherwise, it has to wait for two months since the release before changing its price or giving a discount.
-A game can not go on discounts too frequently, and has to wait between four to six weeks
-after a price promotion to be able to run a new one.
-The duration of a custom discount is restricted to be at least one full day, and at most two weeks.
-Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on a discount.
-As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”.
-Curated promotions are featured prominently on Steam's main page, and, arguably, lead to more visibility and sales for the participating titles than custom discounts, which also contribute to visibility, but typically do not get the front-page promotional slots.
-An important type of curated discounts are the so-called “Seasonal Sales”--big platform-wide events that take place about four times a year around major holidays.
-Figure \ref{seasonalSalesPeriods} (in the Appendix) shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving).
-Around `r  round(panel[discSeason==T & discNew == T, .N]/panel[discNew==T, .N]*100)`% of discounts in the sample go live during a Seasonal Sale.
-Thus, firms have significant agency when it comes to running price promotions, but platform regulations and platform-wide discounts are important determinants of firms' decision to discount.
+Games differ a lot in their sizes, as is evident from Figure \ref{sampleSizeHist} (in the Appendix).
 
@@
 
+As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is in order.
+A representative game in the sample never changes its price, but instead occasionally goes on discounts, slowly increasing their magnitude as the game ages.
+There are `r panel[discount==F, diff(price), by = ID][V1>0, .N]` incidents of price change in the data, compared to
+`r panel[discNew==T, .N]` discounts.
+Steam has a number of rules that regulate price promotions on its platform.
+A game can have a launch discount, but, otherwise, it has to wait for two months since the release before changing its price or giving a discount.
+A game can not go on discounts too frequently, and has to wait between four to six weeks after a price promotion to be able to run a new one.
+The duration of a custom discount is restricted to be at least one full day, and at most two weeks.
+Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on a discount.
+As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”.
+Curated promotions are featured prominently on Steam's main page, and, arguably, lead to more visibility and sales for the participating titles than custom discounts, which also contribute to visibility, but typically do not get the front-page promotional slots.
+An important type of curated discounts are the so-called “Seasonal Sales”---big platform-wide events that take place about four times a year around major holidays.
+Figure \ref{seasonalSalesPeriods} (in the Appendix) shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving).
+Around `r  round(panel[discSeason==T & discNew == T, .N]/panel[discNew==T, .N]*100)`% of discounts in the sample go live during a Seasonal Sale.
+Thus, firms have significant agency when it comes to running price promotions, but platform regulations and platform-wide discounts are important determinants of firms' decision to discount.
+
 The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly.
@@
 Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release.
-On average across games, the standard deviation of the review score is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`  (out of one hundred), with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that.
+On average across games, the standard deviation of the review score over time is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`  (out of one hundred), with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that.
 Given how little the review score changes after the first month, the distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, should be representative of the situation at other ages.
@@
 ```{r}
+# Create the transition probability and count matrix
 transitions <- panel[, .(t, neg=c(NA, diff(negative)),
@@
 transitions[, dur := shift(t,-1) - t, by = ID]
-```
-
-Despite the relative rigidity of the review score, there is enough transitions between review bins to make the analysis of pricing decisions by firms around such transitions possible.
-Table \ref{tab:transitionMatrix} describes the transitions between review bins in the sample.
-The number of unique games that have changed review labels in the data is `r transitions[, unique(ID)] %>% length`, and the number of transitions is `r transitions[, .N]`.
-Sometimes games switch their bins briefly, and go back soon after.
-The number of transitions that led to the game spending at least 7 days in the new bin is `r transitions[(is.na(dur) | dur >= 7), .N]`.
-Table \ref{mDiscountTable} describes the state of the games in the two weeks before such transitions.
-Discounting  does take place before the transitions, games transition at very different ages, but tend to have accumulated only a limited number of reviews by the time their review tier changes.
-
-```{r}
+
+# Print the resuls
 kable(
@@
 
-```{r results='asis'}
+Despite the relative rigidity of the review score, there is enough transitions between review bins to make the analysis of pricing decisions by firms around such transitions possible.
+Table \ref{tab:transitionMatrix} describes the transitions between review bins in the sample.
+The number of unique games that have changed review labels in the data is `r transitions[, unique(ID)] %>% length`, and the number of transitions is `r transitions[, .N]`.
+Sometimes games switch their bins briefly, and go back soon after.
+The number of transitions that led to the game spending at least 7 days in the new bin is `r transitions[(is.na(dur) | dur >= 7), .N]`.
+Table \ref{mDiscountTable} describes the state of the games in the two weeks before such transitions.
+Discounting  does take place before the transitions, games transition at very different ages, but tend to have accumulated only a limited number of reviews by the time their review tier changes.
+
+```{r, include=F}
 transPanel <- transitions[(is.na(dur) | dur >= 7), 
@@
 
-stargazer(
+descriptive.tabel <- stargazer(
    transPanel[tToTransit<0, .(
@@
 
-In this section I develop and estimate a simple structural model of demand an gaming activity on Steam.
-I discuss at length the assumptions and the interpretation of the parameter estimates.
-However, the main takeaway from this section is simple: better review labels improve sales, and discounts are important drivers of sales on Steam.
-These two facts form the foundation of my main analysis that will be carried out in Section \ref{descriptiveEvidence}, where I will show that firms use discounts to attract new reviews and to transition to more lucrative review tiers.
-I will further extend the model from this section in Section \ref{selectionEffect}.
+Before I start my investigation into the discounting behavior of the products close to a review transition, it is important to address two question.
+First, do discounts matter on Steam?
+Do they generate enough additional sales to be relevant?
+While the answer might be obvious for large sought-after products, the situation is less clear for an average game.
+The second question is: how big are the differences between different review tiers?
+If transitioning to a better tier does not increase sales by much, then firms would be unlikely to pursue such transitions when making on their discount decisions.
+The discussion of the assumptions behind my analysis and the interpretation of the parameter estimates contributes greatly to the size of this section.
+However, the main takeaways are simple: better review labels improve sales, and discounts are important drivers of sales on Steam.
+Having few reviews or having negative reviews depresses sales by 5-13% compared to having “Mixed” reviews; the “Overwhelmingly Positive” review tier increases sales by about 10% compared to “Mixed”.
+An average discount in the sample increases sales by 38% upon introduction, and by another 3-12% every day thereafter.
+These two facts form the foundation of my analysis of discounting behavior on a verge of a review tier transition that will be carried out in Section \ref{descriptiveEvidence}.
+I will further extend the model from this section by modelling the reviewing behavior of customers in Section \ref{selectionEffect}.
 
@@
 
-Consider game \(i\) that is observed on a daily basis. On day \(t\)
-the game sells one copy to each of the \(B_{it}\) short-lived buyers that arrive on
-that day, a number that is unobserved by the econometrician. Define
-*active players* of this game, \(A_{it}\), to be the customers who have
-already purchased the game and are still playing it, either because they have
-not yet completed it or are not bored with it yet. This number  has an empirical counterpart in
-the face of the player count variable, observable to the econometrician. The game loses \(E_{it}\) active players on day \(t\), which is also not observed.
+Consider game \(i\) that is observed on a daily basis.
+On day \(t\) the game sells one copy to each of the \(B_{it}\) short-lived buyers that arrive on that day, a number that is unobserved by the econometrician.
+Define *active players* of this game, \(A_{it}\), to be the customers who have already purchased the game and are still playing it, either because they have not yet completed it, or because they are not bored with it yet.
+This number  has an empirical counterpart in the player count variable, observable to the econometrician.
+The game loses \(E_{it}\) active players on day \(t\), which is also not observed.
 I assume that, once a player stops playing the game, she never returns to it again. It is easy to see then that \(A_{it}\) follows the following process:
@@
 
-Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about these variables in order to make progress.
+Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about these variables in order to be able to disentangle their contributions to the observed player counts.
 
@@
 
+There are two key identification challenges I need to address.
+One challenge comes from the fact that in order to tease out new purchases from the player activity data, I need to know something about player exit, which is also unobserved.
+The problem is illustrated by equation (\ref{activeProccess}), where the observed part of the data $A_{it} - A_{it-1}$ only identifies a the difference $(B_{it} - E_{it})$.
+Consider a hypothetical scenario of two games that have the same observed median daily player count---say, ten people.
+However, game one offers a lot of replayability and is played by the same ten people over and over again, while game two is played by new ten people every day.
+Clearly, such two products with identical player activity patterns would have very different sales.
+I am able to solve this problem with the help of Assumption \ref{arrivalAssumptions}.The key insight is that observed factors determine the arrival of new players (buyers) in *absolute* terms, while exit is *proportional* to the number of active players.
+Intuitively, the exit procees is identified by the rate of decay of the player count when the count is far from its (slowly-changing) trend or average.
+Player count is typically far from its average on the days following the game release or the introduction of a discount.
+Sharp spikes in player counts reflect the players who just bought the game; see example game in Figure \ref{exampleGame}.
+For a given decay parameter, the level at which the player count settles identifies the inflow of new buyers.
+Given that identifying the exit rate is crucial for teasing out the sales component, it is a great advantage of my model that it allows full heterogeneity in the exit rate $(1-\psi_i)$.
+
+The second identification challenge I tackle is obtaining estimates of the caual effect of review tiers on sales.
+In short, I achive it by minimizing the ommitted variable bias through sample selection, and by controlling for game-specific and time-specific shocks, in addition to the observable covariates that serve as important control variables on their own.
+The discussion below elaborates on the details of identifying the aforementioned effects of reviews on sales, as well as the effects of price variables that together with controls form $\beta$.
+
 The prediction of \(A_{it}\) that follows from (\ref{activeProccess}) takes the form of
@@
 
-Another advantage of using equation (\ref{arrivalReg}) to estimate demand parameters from player count data comes from the fact that it allows each game to have its own continuation probability $\psi_i$.
-Two games could have the same observed median daily player count---say, ten people---but very different sales levels, if game one offers a lot of replayability and is played by the same ten people over and over again, and game two is played by new ten people every day.
-Intuitively, $\psi_i$ is identified by the rate of decay of the player count when it is far from its (slowly-changing) trend or average.
-Game release and discounts offer such events, when the player count spikes briefly due to all the new players who just bought the game; see example game in Figure \ref{exampleGame}.
-
 Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model (\ref{arrivalReg}), and guarantees identification of all parameters, as long as there is sufficient variation in the data.
@@
 Any intervention that is correlated with discounts will be attributed to the price variable.
-The second important way in which I control for various tools that firms have at their disposal is through sample selection.
-Sample selection rules out the possibility of an omitted variable bias stemming from a number of variables that could collectively be referred to as “changing quality”.
+Second, recall that the way I constructed the  sample  rules out the possibility of an omitted variable bias stemming from a number of variables that could collectively be referred to as “changing quality”.
 The games in the sample are single player games, and thus are not subject to time-varying network externalities or frequent quality updates that could be correlated with reviews, depths of discounts, or the player count.
@@
 In my setting, however, this would require the firms to systematically give discounts *exactly on the days* of the demand shocks, which requires possessing a level of insight into one's demand condition that is unrealistic, especially for small independent studios.
-While a discount for a racing game on the day of a major F-1 race is not implausible, should the demand for the game go up with a lag of as little as one day, then both $(Q_t, P_t)$ and $(Q_{t-1}, P_{t-1})$ would belong to the same demand curve, and, therefore, identification would not be threatened\footnote{Assuming, as is usually done, that demand shifters lead to parallel shifts in demand}.
+While a discount for a racing game on the day of a major F-1 race is not implausible, should the demand for the game go up with a lag of as little as one day, then both $(Q_t, P_t)$ and $(Q_{t-1}, P_{t-1})$ would belong to the same demand curve, and, therefore, identification of the slope parameter would not be threatened\footnote{Assuming, as is usually done, that demand shifters lead to parallel shifts in demand}.
 
@@
 In particular, Steam allows users to add any game to their wishlist, which means that they would be notified about promotions affecting that game.
-Later in the results section we will see that the lion's share of sales on a discount take place on the first day of the discount, which is consistent with users waiting for a discount and buying the game when the discount goes live.
+Later in the results section we will see that the lion's share of sales on a discount takes place on the first day of the discount, which is consistent with users waiting for a discount and buying the game when the discount goes live.
 For studying counterfactual price policies one would need to specify a more complicated model of forward-looking consumers, and estimate the fundamentals of their behavior.
@@
 A game can give a 99% discount, but the quantity demanded will not change much if that promotion happens to not be reflected in Steam's system.
-This has implications, for instance, for picking good instruments for prices.
+This has implications, for instance, for picking good instruments for prices, should a researcher be interested in obtaining ones.
 Curated discounts created and managed by Steam are suggested to firms, and not chosen by them.
 In principle, such price changes could be exogenous to daily demand conditions.
-However, they could hardly be used as instruments for the price, because they also bring an immense boost in visibility, by the virtue of occupying the prime store main page space.
+However, they could hardly be used as instruments for the price, because they also bring an immense boost in visibility, by the virtue of promoting the discounted game to the front page.
 
 ## Results
-
-In this section I present the estimates of the parameters of my demand model.
-I contrast these estimates with the ones obtained from estimating a simple log-regression (\ref{logReg}).
-I find that the results are fairly similar, albeit there are some important differences that I discuss in detail.
-The main takeaway from this section is that review tiers above “Mixed” increase sales by 2-10% compared to “Mixed”, and that discounts are important drivers of sales in this market.
 
@@
 
-The semi-elasticities sales with respect to review labels are fairly similar across the specifications.
+The semi-elasticities of sales with respect to review labels are fairly similar across the specifications.
 All specifications exhibit monotonicity in the effects of different review tiers on sales.
@@
 Thus, the score variable really measures the effect of score once the score is defined.}.
-While Model (\ref{arrivalReg}) suggests that having no score is associated with a `r -round(beta.hat[6]*100)`% slower customer arrival than having the “Mixed” review label, its simplified log-regression analogs find the opposite effect of a having `r round(reg1$coefficients[5]*100)`-`r round(reg2$coefficients[4]*100)`% bonus associated with having not enough reviews.
+While the structural model (\ref{arrivalReg}) suggests that having no score is associated with a `r -round(beta.hat[6]*100)`% slower customer arrival than having the “Mixed” review label, its simplified log-regression analogs find the opposite effect of a having `r round(reg1$coefficients[5]*100)`-`r round(reg2$coefficients[4]*100)`% bonus associated with having not enough reviews.
 The latter effect can not possibly be taken at face value, given that the most exclusive review label, "Overwhelmingly Positive",  increases sales by at most `r round(beta.hat[11]*100)`% compared to the baseline.
-It would be possible to explain such large estimates by high levels of demand  when the game is young and is likely to have less than 10 reviews, but I control for being “young” by including the dummy for being less than 14 days of age.
+It would be possible to explain such large estimates by high levels of demand  when the game is young and is likely to have less than 10 reviews, but I control for being “young” by including the dummy for being less than 14 days of age\footnote{A two weeks cutoff is inspired by high speed of review arrival documented in Figure \ref{reviewDescriptivePlots}}.
 Thus, the coefficient on “No Score” is identified by games that exit this bin later than their first two weeks.
@@
 This number looks more reasonable, especially given that the products I study have a zero marginal cost of production, and in a static world firms would set prices at which the demand for their products would be unit-elastic.
+Every additional day on a discount then is associated with a  `r round(-reg1$coefficients[2],2)*round(panel[discount>0, mean(discount)]*100)`-`r round(-beta.hat[1],2)*round(panel[discount>0, mean(discount)]*100)`, where larger effect comes from the structural model.
+Discounts on Steam attract a considerable number of new users, and thus could be effective tools in generating new reviews needed for a review tier transition.
 
@@
 
-The second set of demand parameters that I estimate are the game-specific customer arrival rates $\lambda_i$ and the probabilities $\psi_i$ with which active players of game $i$ continue playing the game.
-For the ease of interpretation, I present the estimates of  $\bar \lambda_{i} := \lambda_i(1+\mathbb{E}[x_{it}]'\beta)$, the average sales for game $i$ (recall that I can only estimate the part of sales that contributes to the gaming activity during peak times).
+I conclude the overview of the results of estimating the structural model of demand  (\ref{arrivalReg}) by going over the estimates of the game-specific customer arrival rates $\lambda_i$ and the probabilities $\psi_i$ with which active players of game $i$ continue playing the game.
+For the ease of interpretation, I present the estimates of  $\bar \lambda_{i} := \lambda_i(1+\mathbb{E}[x_{it}]'\beta)$, the average sales for game $i$\footnote{This is not quite accurate, as I can only estimate the part of sales that contributes to the gaming activity during peak times}.
 Estimated distributions of these parameters are presented in  Figure \ref{psiLambdaDist}.
@@
 # Additional Tables and Figures
+## Descriptive Statistics
+
+```{r sample-size-hist, fig.cap='\\label{sampleSizeHist} Distributions of the Player Count on, and the Number of Reviews Accumulated by, the Age of 180 Days.'}
+p1 <- ggplot(data = panel[age==180, .(x = log(number))]) +
+  geom_histogram(mapping = aes(x = x, y = ..density..), 
+                 color = "black", 
+                 position = "identity", 
+                 alpha = 0.9,
+                 binwidth = 0.5,
+                 boundary = 0,
+                 fill = my.colors[1]) +
+  geom_density(mapping = aes(x = x), 
+                 color = "black", 
+                 position = "identity", 
+                 alpha = 0.4,
+                 fill = my.colors[1]) +
+  scale_x_continuous(name = "Log Players",
+                     breaks = seq(0, 8),
+                     minor_breaks = NULL) +
+  scale_y_continuous(name = NULL, 
+                     minor_breaks = NULL) +
+  my.theme()
+
+p2 <- ggplot(data = panel[age==180, .(x = log(reviews))]) +
+  geom_histogram(mapping = aes(x = x, y = ..density..), 
+                 color = "black", 
+                 position = "identity", 
+                 alpha = 0.9,
+                 binwidth = 0.5,
+                 boundary = 0,
+                 fill = my.colors[1]) +
+  geom_density(mapping = aes(x = x), 
+                 color = "black", 
+                 position = "identity", 
+                 alpha = 0.4,
+                 fill = my.colors[1]) +
+  scale_x_continuous(name = "Log Reviews",
+                     breaks = seq(0, 8),
+                     minor_breaks = NULL) +
+  scale_y_continuous(name = NULL, 
+                     minor_breaks = NULL) +
+  my.theme()
+
+ggarrange(p1, p2, ncol = 2, nrow = 1, align = "h")
+```
+
+```{r seasonal-sales-periods, fig.cap='\\label{seasonalSalesPeriods} Seasonal Sales and Discounting Activity.
+Shaded regions are my definition of Seasonal Sales periods.
+The first spike on the graph is excluded because the sample starts with just one game, and I exclude the first 2 weeks from the calculations.'}
+months1 <- c(-1, 30, 58, 89, 119, 150, 180, 211, 242, 272, 303, 333) + 1
+months2 <- c(333 + 32 + months1, 699 + 31)
+
+f<-panel[, .(disc = discSeason[1]), keyby = t][, .(t, z=c(NA, diff(disc)))]
+
+discPeriods <- data.frame(xstart = f[z==1, t], xend = c(f[z==-1, t], panel[, max(t)]))
+
+ggplot(data = panel[, .(y=sum(discount > 0)/(.N), z=avDisc[1]), by = t]) +
+  geom_rect(data = discPeriods, aes(xmin = xstart, xmax = xend, ymin = -Inf, ymax = Inf), fill = my.colors[2], alpha = 0.25) +
+  # ggtitle() +
+  geom_line(aes(x = t, y = y),
+            color = my.colors[1],
+            size = 1) +
+  scale_x_continuous(name = NULL,
+                     breaks = c(months1, months2)[seq(1,25,3)],
+                     labels = months(getDate(c(months1, months2))[seq(1,25,3)],
+                                     abbreviate=T),
+                     minor_breaks = NULL) +
+  scale_y_continuous(name = "Fraction of Games on Discount",
+                     minor_breaks = NULL)  +
+  my.theme(leg.x = 0.25, leg.y = 0.9)
+
+rm(months1, months2, f, discPeriods)
+```
+
+```{r, results='asis'}
+descriptive.tabel
+```
+
+\newpage
 ## Discounts Around Transitions
@@
 ```
-
 \newpage
-## Definition of Seasonal Sales
-```{r seasonal-sales-periods, fig.cap='\\label{seasonalSalesPeriods} Seasonal Sales and Discounting Activity.
-Shaded regions are my definition of Seasonal Sales periods.
-The first spike on the graph is excluded because the sample starts with just one game, and I exclude the first 2 weeks from the calculations.'}
-months1 <- c(-1, 30, 58, 89, 119, 150, 180, 211, 242, 272, 303, 333) + 1
-months2 <- c(333 + 32 + months1, 699 + 31)
-
-f<-panel[, .(disc = discSeason[1]), keyby = t][, .(t, z=c(NA, diff(disc)))]
-
-discPeriods <- data.frame(xstart = f[z==1, t], xend = c(f[z==-1, t], panel[, max(t)]))
-
-ggplot(data = panel[, .(y=sum(discount > 0)/(.N), z=avDisc[1]), by = t]) +
-  geom_rect(data = discPeriods, aes(xmin = xstart, xmax = xend, ymin = -Inf, ymax = Inf), fill = my.colors[2], alpha = 0.25) +
-  # ggtitle() +
-  geom_line(aes(x = t, y = y),
-            color = my.colors[1],
-            size = 1) +
-  scale_x_continuous(name = NULL,
-                     breaks = c(months1, months2)[seq(1,25,3)],
-                     labels = months(getDate(c(months1, months2))[seq(1,25,3)],
-                                     abbreviate=T),
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = "Fraction of Games on Discount",
-                     minor_breaks = NULL)  +
-  my.theme(leg.x = 0.25, leg.y = 0.9)
-
-rm(months1, months2, f, discPeriods)
-```
-
-\newpage
+
 # Mathematical Appendix

### 2020-10-12 Analysis/Code/Paper.Rmd
updated the bibliography style

@@
    | Transitions in the Video Games Market
+   | \href{https://github.com/dmsorokin/PaperRepository/blob/gh-pages/Sorokin_JMP_2020.pdf}{\large Click for the Latest Version}
 
@@
 
+ abstract: |
+  \\singlespacing I document that firms in online marketplaces use price promotions 
+  to facilitate transitions to better review tiers (similar to the number of stars on
+  Amazon.com). I find that firms close to going one tier up are 4-9% more 
+  likely to discount. I theorize that two effects could be at play. The selection effect 
+  arises because customers who buy during a discount could be different from the regular 
+  ones, and could potentially leave more positive reviews. The variance effect reflects 
+  the idea that positive reviews could help the firm move up a review tier, while 
+  negative reviews would keep the tier unchanged, minimizing the downside risk 
+  of giving a discount. To test my hypotheses, I estimate a simple structural 
+  model of demand and reviewing behavior, and develop a new approach to estimating demand 
+  from data on product usage. I do not find evidence that the selection effect is 
+  positive. I find evidence of the importance of the variance effect: when 
+  the selection effect is zero, firms close to downgrading their review tier are 6% 
+  less likely to give a discount, consistent with preferring less variance. I also 
+  find that consumers are significantly more likely to leave a review when purchasing 
+  during a discount. Additional findings include estimates of the causal effect of 
+  reviews on sales and equilibrium discount elasticities in an important market 
+  not previously studied.
+
  bibliography: reviewsBib.bib
@@
 I estimate the size of the selection effect at the product level, and “control” for it in my regressions of discounts on proximities to transition.
-I find that, in the absence of the selection effect, products that are close to a review downgrade are significantly less likely to discount, which is consistent with the idea that the variance effect is negative for such products.
+I find that, in the absence of the selection effect, products that are close to a review downgrade are 6% less likely to discount, which is consistent with the idea that the variance effect is negative for such products.
 I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.
@@
 # Conclusion
-\label{conclusion}
 

### 2020-10-12 Analysis/Code/Sorokin_JMP_2020.Rmd
updated the bibliography style

--- 2020-10-12 Analysis/Code/Paper.Rmd
@@
  title: |
-   | Reaching for The Stars: Discounts and Review Tier 
+  | \vspace{-2em} Reaching for The Stars: Discounts and Review Tier
   | Transitions in the Video Games Market
-   | \href{https://github.com/dmsorokin/PaperRepository/blob/gh-pages/Sorokin_JMP_2020.pdf}{\large Click for the Latest Version}
-
- author: "Dmitry Sorokin"
- date: "`r format(Sys.time(), '%B %d, %Y')`"
+  | \href{http://papers.dsorokin.net/Sorokin_JMP_2020.pdf}{\large [Click for the Latest Version]}
+
+ author: |
+  Dmitry Sorokin\thanks{\protect\linespread{1}\protect\selectfont New York University, dsorokin@nyu.edu.
+I am deeply grateful to Timothy Christensen, Alessandro Lizzeri, and Lu\'{i}s Cabral for their support and guidance.
+I benefited enormously from my conversations with Ryan Stevens, Jimena Galindo, Sam Kapon, Dmitry Sedov, Jonathan Elliott, and Timur Abbiasov.
+I would also like to thank Chris Conlon, Christopher Flinn, Elena Manresa, Maher Said, Mikkel Plagborg-M\o{}ller, Milena Almagro, Paula Onuchic, Sharon Traiberman, and all other great people at NYU for their helpful comments.
+All mistakes are my own.}
+
+ date: "`r format(Sys.time(), '%B %Y')`"
  classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
@@
  abstract: |
-  \\singlespacing I document that firms in online marketplaces use price promotions 
+  \onehalfspacing \noindent 
+  I document that firms in online marketplaces use price promotions 
   to facilitate transitions to better review tiers (similar to the number of stars on
@@
   reviews on sales and equilibrium discount elasticities in an important market 
-  not previously studied.
+  not previously studied. \thispagestyle{empty}
 
@@
 ```
+
+\newpage
 
@@
 
-# Print the resuls
+# Print the results
 kable(
@@
 
-descriptive.tabel <- stargazer(
-   transPanel[tToTransit<0, .(
-      `Mean Discount (%)` = mean(discount),
+descriptive.table <- transPanel[tToTransit<0, .(
+      `Discount` = round(mean(discount)),
       `Age` = round(mean(age)),
       `Reviews` = round(mean(reviews))), 
-      by = c("ID", "trID")][, -c("ID", "trID")],
-         title = "Average Discount, Age, and Review Count Two Weeks Before A Transition",
-         label = "mDiscountTable",
-         omit.summary.stat = c("min", "max"),
-         header = F,
-         digits = 0)
+      by = c("ID", "trID")][, -c("ID", "trID")]
 ```
@@
 
-I this section I present the main findings of the paper.
-I start by presenting a stylized model of discounting close to a transition to a different review bin.
-The model predicts that, whether a firm would find discounting a worthwhile option to facilitate  a transition or not, depends on the balance between two forces: the selection effect and the variance effect.
-I then show that products are significantly more likely to go on a discount when they are close to improving their review tier, while no effect is found for products that are close to sliding down a tier.
-The two effects are then further investigated in the next section.
+In the previous section I established the importance of favorable reviews for sales on Steam, and the important role that price promotions play in attracting new users.
+Now I turn attention to the main question of the paper: do firms use discounting to facilitate transitions to better review tiers, or to prevent transitions to worse review tiers?
+I start by presenting a stylized model of a firm whose product is close to a review transition.
+The model predicts that the decision to discount or not depends on the balance between two forces: the selection effect and the variance effect.
+I then turn to data, and show that products are significantly more likely to go on a discount when they are close to improving their review tier, while the effect for products that are close to sliding down a tier are much weaker.
+I use the stylized model to interpret these results, and conclude that further analysis is required in order to establish the relative contributions of the selection and the variance effects.
+This analysis is carried out in the next section.
 
@@
 Such a firm could be regarded as one that is close to a review upgrade.
-The expected value of giving a discount to this firm is is
+The expected value to the firm of giving a discount is
 \begin{equation}\label{discTradeoff}
@@
 \noindent The firm would choose to give a discount if $\EE{U(s+X)}  > 0$.
-If $x < 1-s$, the firm simply can not induce enough change, and would not give a discount, unless $c < 0$ (i.e, other factors make giving a discount attractive).
+If $x < 1-s$, the firm simply can not induce enough change to its review status, and would not give a discount, unless $c < 0$ (i.e, other factors make giving a discount attractive).
 This would be the case for products with many reviews and an established review score.
 My interested is mostly in the other type of products, the ones that potentially can transition.
-In those cases the decision to discount or not depends on the comparison between the value of the positive transition, $u^H$, the cost of giving a discount ($c$, or $c$ and $(1-p)^L$), and the probability that the transition is successful.
+In those cases the decision to discount or not depends on the comparison between the value of the positive transition, $u^H$, the cost of giving a discount ($c$, or $c$ and $(1-p)u^L$), and the probability that the transition is successful.
 If the probability of success is high, the firm is more likely to give a discount.
@@
 Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews.
-At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leave better reviews [@CabralLi15; @IfrachEtAl19; @AcemogluEtAl19].
-Limited empirical evidence on the sign of the selection effect is limited.
+At the same time, such customers get a higher utility from paying less, which, together with a desire to reciprocate, can lead them to leaving better reviews [@CabralLi15; @IfrachEtAl19; @AcemogluEtAl19].
+Empirical evidence on the sign of the selection effect is limited.
 @ByersEtAl12 and @Li16 report that customers who choose to go to a restaurant because of a price promotion tend to leave worse reviews, while  a positive effect was documented by @Li16 and @ZhuEtAl19.
@@
 I refer to  this idea as the “variance effect”.
-Even if the firm does not expect the new reviews to be favorable in expectation, they could still turn out to be positive, and if the reward is high enough, it could be worth the risk.
+Even if the firm does not expect the new reviews to be favorable in expectation, they could still turn out to be positive, and if the reward is high enough, discounting could be worth the risk.
 
@@
 when $s < 0.5$.
-Following the logic of (\ref{discTradeoff}), we can see that for intermediate values of $x \in [1-s, s)$ such a firm is only risking sliding one review tier down if the reviews left during a discount turn out to be negative, while if they turn out to be positive the firm simply remains in its current review bin.
+Following the logic of (\ref{discTradeoff}), we can see that for intermediate values of the change in review status ($x \in [s, 1-s)$) such a firm does not benefit from a discount.
+If the reviews left on discount turn out to be negative, the firm will slide one tier down, while if they turn out to be positive, the firm will merely keep its current review status.
 The selection effect should be strongly positive for such a firm to find discounting profitable.
 
-To summarize, it appears that firms close to a positive transition could be more likely to benefit from the variance effect than the ones close to a negative transition.
+To summarize, it appears that firms close to a positive transition are more likely to benefit from the variance effect than the ones close to a negative transition.
 This makes them more likely to run price promotions.
 Both types benefit from a positive selection effect, but whether the selection effect is positive or negative is an empirical question.
-A strong negative selection effect could overturn the appeal of discounting that is coming from the variance effect, ultimately meaning that the relationship between proximity to transitions and discounting behavior is theoretically ambiguous, and should be studied empirically.
+A strong negative selection effect could overturn the appeal of discounting coming from the variance effect, ultimately meaning that the relationship between proximity to transitions and discounting behavior is theoretically ambiguous and should be studied empirically.
 
@@
 
-Now that a simple theory of discounting close to a review threshold has been brought forward, I turn attention the The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels are often preceded by discounts.
+Now that a simple theory of discounting close to a review threshold has been brought forward, I turn attention the data.
+The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels on Steam are often preceded by discounts.
 The graph shows that two weeks prior to a transition only `r transPanel[tToTransit==-14, round(mean(100*(discount > 0)))]`% of games are on a discount, essentially the sample average, but that this number more than doubles to around `r transPanel[tToTransit==-1, round(mean(100*(discount > 0)))]`% one day before the label change.
@@
 While the merits of focusing on potential transitions are clear, defining proximity to a transition is not straightforward.
-One approach would be to use the raw review count, and to say that a game is close to upgrading its review label when it needs five (ten, twenty ...) more positive reviews to transition.
+One approach would be to use the raw review count, and to say that a game is close to upgrading its review label when it needs some fixed number of new positive reviews to transition.
 However, given the heterogeneity in the popularity of different games (see Figure \ref{sampleSizeHist}), five extra reviews could be nothing for a very popular game, and hard to acquire for a small game.
 For this reason I use a different approach, and measure proximity by the expected number of \emph{days} that a game has to wait to accumulate the reviews necessary for a transition.
-In particular, for every game-date pair I first measure how many positive reviews that game needs at the moment to upgrade its review bin, and how many negative reviews that game needs to degrade its review bin.
+In particular, for every game-date pair I first measure how many positive reviews that game needs at the moment to upgrade its review bin, and how many negative reviews that game needs to downgrade its review bin.
 In the next step, for each game I calculate the average speeds of review arrival, by simply dividing the number of positive (negative) reviews as of the last day in the sample by the age of the game on that day.
@@
 Similarly, for a negative transition it requires $3 / 0.1 = 30$ days of only bad reviews arriving at this rate.
-So, for this game I set its proximity to a potential positive transition to be 12.5 days, and its proximity to a potential negative transition to be 30 days.
+Therefore, for this game I set its proximity to a potential positive transition to be 12.5 days, and its proximity to a potential negative transition to be 30 days.
 
@@
 Similarly, game $i$ at date $t$ is said to be close to a negative transition, $T_{it}^- = 1$, if its proximity to a positive transition is less than or equal to `r 2*band` days.
-The `r 2*band` cutoff is inspired by the maximum duration of custom discounts on Steam, and the patterns of discounting around successful transitions, depicted in Figure \ref{discountsTransitions}.
+The `r 2*band` day cutoff is inspired by the maximum duration of custom discounts on Steam, and the patterns of discounting around successful transitions, depicted in Figure \ref{discountsTransitions}.
 To estimate the effect of being close to a review transition on the discounting behavior, I then estimate the following model:
@@
 
-\noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, score, review bin dummies, and age; $f_i$ is a set of game-level fixed effects, and $\tau_t$ is a set of day of the week effects and sample week time effects.
+\noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, score, review bin dummies, age, a set of game-level fixed effects $f_i$, and a set of day of the week and week time effects $\tau_t$.
 These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSalesPeriods}.
@@
 
-The results of estimating Equation \ref{potTransitionsReg} are presented in Table \ref{potentialTransitionsResults}.
-The first column is the full specification that uses all observations in the sample (except the omissions just mentioned).
-The second column uses a more stringent definition of proximity to a transition, requiring a game to be `r band`, rather than `r 2*band`, days away from a potential transition to be counted as being “close to a transition”.
+The results of estimating Equation (\ref{potTransitionsReg}) are presented in Table \ref{potentialTransitionsResults}.
+Column one is the preferred specification, while column tow uses a more stringent definition of proximity to a transition, requiring a game to be `r band`, rather than `r 2*band`, days away from a potential transition to be counted as being “close to a transition”.
 The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion.
 Measured against the `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% probability for a random game-day pair from the sample to feature a discount\footnote{The corresponding number for the games in the positive treatment group is `r round(100*panel[ID %in% panel[pos.treatment == 1, unique(ID)], mean((discount > 0), na.rm = T)])`.}, the effects constitute a `r round(100*(reg2$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`-`r round(100*(reg1$coefficients[1]/panel[, mean((discount > 0), na.rm=T)]))`% increase in the daily probability of a discount.
-Proximity to a potential negative transition seems to have a negative effect on the probability of discount, albeit the effect is not very strong.
+Proximity to a potential negative transition seems to have a negative effect on the probability of discount, albeit the effect is not very significant.
 I find that firms under a risk of deteriorating their review label are `r -round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% less likely to go on a discount.
@@
 Both the variance and the positive selection effects could explain why products close to a review upgrade are more likely to run a price promotion.
-Weak significance of the effect for products close to a review slump could be explained by the clash between the variance effect and the selection effect.
+Weak significance of the effect for products close to a review slump could be explained by the clash between the variance effect and the selection effect (recall that the we expect the variance effect to be negative for such products).
 As we see, even though my empirical investigation has resolved the theoretical ambiguity of the signs and the significance of the effects, it did not shed much light on the balance of the underlying forces behind these effects.
@@
 First, I found that firms are more likely to go on a discount when their products are close to upgrading their review bin.
-Second, I found only limited change in the discounting behavior for products that are close to downgrading their review bins.
+Second, I found only limited change in discounting behavior for products that are close to downgrading their review bins.
 The first finding implies that the selection effect and the variance effect can not be both negative for games close to a review upgrade.
-This is a weak finding, as finding the opposite would be really surprising.
+This is a weak conclusion, as finding the opposite would be really surprising.
 Moreover, it does not reveal if the selection effect is negative or positive.
-The second finding suggests that the variance effect should be at least somewhat important.
-Given that the variance and the selection effect could go in different directions for the products close to the negative transition, the separate contributions of the two effects also remain unclear.
-In this section I investigate the signs of the selection and variance effects directly.
+The second could be explained by either of the effects being negative, as well as them having opposite signs and contradicting each other, leading to a muted effect.
+In this section I investigate the signs of the selection and variance effects in greater detail.
 
 The selection effect is easy to test directly.
-We would simply need to compare the fractions of positive and negative reviews left on and off a discount.
+One would simply need to compare the fractions of positive and negative reviews left on and off discount.
 The variance effect is harder to strip down to a similar test.
-First, if one is willing to take my stylized model seriously, then the absence of the selection effect in the data would indicate that all the effects are driven by the variance effect.
+One way to prove the importance of the variance effect is to take my stylized model seriously, and to prove the absence of the selection effect in the data.
+In the absence of the selection effect, discounting decisions have to due to the variance effect.
 This idea could be further developed.
-Even if the selection effect is not zero, if we could quantify it, then “controlling” for the magnitude of the selection effect could shed light on the importance of the variance effect.
+Even if the selection effect is not zero, if one could quantify it, then “controlling” for the magnitude of the selection effect could shed light on the importance of the variance effect.
 Another way to evaluate the importance of the variance effect is to look at the extent to which a discount speeds up the arrival of reviews.
-For the variance effect to be relevant, a discount should be able to bring a significant number of new reviews.
+The idea here is that for the variance effect to be relevant, a discount should be able to bring in a significant number of new reviews.
 
@@
 A formal model of reviewing behavior is necessary for several reasons.
-First, a structural model allows me to explicitly introduce the parameters of interest--probabilities of leaving a good or a bad reviews on and off a discount.
-With the estimates of these parameters I will be  able to directly assess the importance of the selection effect.
-Having developed a measure of the valence of the reviews left during a discount, I will be able to control for the selection effect in the regression of discounting behavior on proximities to transition (\ref{potTransitionsReg}).
-Second, the model will allow me to use my estimates of the demand process to make statements about the absolute change in probability of leaving a review that is due to the discount.
-Since sales are unobserved, it is impossible to say if the surge in reviews during a discount is entirely due to the influx of new customers, or if part of it could be explained by an increased willingness to leave a review during a discount.
+First, a structural model allows me to explicitly introduce the parameters of interest---probabilities of leaving a good or a bad review, on and off discount.
+With the estimates of these parameters I will be  able to quantify the selection effect.
+Such a measure, in turn, will allow me to control for the selection effect in the regression of discounting behavior on proximities to transition (\ref{potTransitionsReg}), shedding light on the importance of the variance effect.
+To further understand the latter, I also use the model to estimate the effect of a price promotion on the probability to leave reviews.
+Since sales are unobserved, it is impossible to say if the surge in reviews during a discount is entirely due to the influx of new customers, or if part of it is due to an increased willingness to leave a review during a discount.
 I use my model to estimate sales, and therefore I can make inference on the propensity to leave a review.
-Such inference can not be made without a model of demand and review activity or sales data, neither of which are common in the literature.
-
-In my data I find no evidence of positive selection effect.
+Such inference can not be made without a model of demand or sales data, neither of which are common in the literature.
+
+As a preview of results, in my data I find no evidence of a positive selection effect.
 Table \ref{reviewLag} in the Appendix shows that, following a discount, the review score goes down by half a point (out of 100), and does not recover in the week following the discount.
@@
 When I control for the size of the selection effect at a game level, I find that the negative effect of the proximity to a negative transition on discounting increases substantially, and becomes more significant.
-This serves as evidence of the importance of the variance effect.
-Speaking of the effect of a discount on the review arrival,  Table \ref{reviewLag} shows that a discount is followed by around 7 extra reviews, on average, in the week after its introduction, or at least doubles the speed of review arrival.
-My structural estimates show that consumers are significantly more likely to leave reviews during discounts, further highlighting the role of the variance effect.
+This is my main evidence of the importance of the variance effect.
+Additional indirect evidence comes from analyzing the effect of discounts on the review arrival.
+My descriptive analysis finds that a discount is followed by around 7 extra reviews, on average, in the week after its introduction, or at least doubles the speed of review arrival (Table \ref{reviewLag}).
+My structural estimates show that consumers are 24-40% more likely to leave reviews during discounts.
+Both findings suggest that the variance effect could play an important role in firms' discounting decisions.
 
@@
 I formally test this hypothesis, stated in (\ref{hyp1}), and I strongly reject the null that users are less likely to leave reviews when buying on a discount in favor of the alternative that they are more likely to leave reviews when buying on a discount (the values of the $t$-stats are `r round(t1.1[1],2)` and `r round(t1.2[1],2)` in the two specifications).
-The estimated change in the probability of leaving a review due to a discount is between `r round((theta2[2]+theta2[4])/(theta2[1]+theta2[3])*100)`% and `r round((theta1[2]+theta1[4])/(theta1[1]+theta1[3])*100)`%, where the smaller estimate is probably more reliable, as it takes into account the effects of age on discounting.
+The estimated change in the probability of leaving a review due to a discount is between `r round((theta2[2]+theta2[6])/(theta2[1]+theta2[5])*100)`% and `r round((theta1[2]+theta1[4])/(theta1[1]+theta1[3])*100)`%, where the smaller estimate is probably more reliable, as it takes into account the effects of age on discounting.
 These results indirectly confirm that the variance effect could be playing a big role in the discounting decision of firms on Steam, as discounts are really effective at bringing new reviews.
@@
 
-rm(Hpos, Hneg, HnegInv, HposInv)
-```
-
-```{r fig.cap='\\label{scoreDifPlot} Distribution of the difference between estimated average score on and off a discount.'}
+rm(Hpos, Hneg, HnegInv, HposInv, table)
+```
+
+```{r fig.cap='\\label{scoreDifPlot} Distribution of the Difference Between Estimated Average Score on and off Discount.'}
 ggplot(data = revs[, .(x = score.dif)]) +
@@
 
-To strengthen this point, I use the difference in the valence of reviews on and off a discount to measure the selection effect at the game level.
+To strengthen this point, I use the difference in the valence of reviews on and off discount to measure the selection effect at the game level.
 With such estimates at hand, I can revisit my regression of discounts on proximities to transitions (\ref{potTransitionsReg}) controlling for the selection effect.
@@
 Once the variation in the selection effect is controlled for, I obtain the coefficients measuring the impact of the variance effect on discounting decisions, and the signs align with the theory.
-Their sizes are also quite economically meaningful, suggesting that, in the absence of the selection effect, games close to a positive transition are \textcolor{red}{number} `r round(100*reg3$coefficients["pos.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% more likely to go on a discount, and games close to a negative transition are \textcolor{red}{number}  `r -round(100*reg3$coefficients["neg.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% less likely to go on a discount.
+Their sizes are also quite economically meaningful, suggesting that, in the absence of the selection effect, games close to a positive transition are  `r round(100*reg3$coefficients["pos.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% more likely to go on a discount, and games close to a negative transition are `r -round(100*reg3$coefficients["neg.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% less likely to go on a discount.
 
@@
 
-I develop a structural model of demand and product usage, that allows me to make statements about sales using data on usage.
-This model extends the approach of @SorokinStevens20.
-Using this model, I provide new estimates of the causal effect of reviews on sales on Steam.
-Being in the best review bin carries a premium of up to 10% compared to a mediocre review tier; having no reviews has a negative effect of up to 13%.
-In a methodological contribution, I compare the performance of my structural model with its simpler cousin from @SorokinStevens20.
-While there are some important differences between the two sets of estimates, I find the part concerning the effect of review bins on sales to be fairly similar.
-
 \newpage
@@
 
-```{r sample-size-hist, fig.cap='\\label{sampleSizeHist} Distributions of the Player Count on, and the Number of Reviews Accumulated by, the Age of 180 Days.'}
+```{r sample-size-hist, fig.cap='\\label{sampleSizeHist} The Player Count on, and the Number of Reviews Received by, the Age of 180 Days.'}
 p1 <- ggplot(data = panel[age==180, .(x = log(number))]) +
@@
 
+```{r, results='asis'}
+stargazer(descriptive.table,
+         title = "Average Discount, Age, and Review Count Two Weeks Before A Transition",
+         label = "mDiscountTable",
+         omit.summary.stat = c("min", "max"),
+         header = F,
+         digits = 0)
+```
+\newpage
+
+## Seasonal Sales
 ```{r seasonal-sales-periods, fig.cap='\\label{seasonalSalesPeriods} Seasonal Sales and Discounting Activity.
@@
 
-```{r, results='asis'}
-descriptive.tabel
-```
-
 \newpage
 ## Discounts Around Transitions
-
 ```{r results = 'asis'}

### 2020-10-12 MakePaper.R

@@ -18,6 +18,6 @@ createLink(here("Analysis", "Output", "reviewsBib.bib"),
 # the final PDF, or choose "html_document", but some latex commands won't work
 # properly
 
-rmarkdown::render(here("Analysis", "Code", "Paper.Rmd"),
+rmarkdown::render(here("Analysis", "Code", "Sorokin_JMP_2020.Rmd"),
                   output_dir = here("Analysis", "Output"),
                   output_format = "pdf_document")

### 2020-10-13 Analysis/Code/Sorokin_JMP_2020.Rmd
Improved writing

@@
   \onehalfspacing \noindent 
-  I document that firms in online marketplaces use price promotions 
-  to facilitate transitions to better review tiers (similar to the number of stars on
-  Amazon.com). I find that firms close to going one tier up are 4-9% more 
-  likely to discount. I theorize that two effects could be at play. The selection effect 
-  arises because customers who buy during a discount could be different from the regular 
-  ones, and could potentially leave more positive reviews. The variance effect reflects 
-  the idea that positive reviews could help the firm move up a review tier, while 
-  negative reviews would keep the tier unchanged, minimizing the downside risk 
-  of giving a discount. To test my hypotheses, I estimate a simple structural 
-  model of demand and reviewing behavior, and develop a new approach to estimating demand 
-  from data on product usage. I do not find evidence that the selection effect is 
-  positive. I find evidence of the importance of the variance effect: when 
-  the selection effect is zero, firms close to downgrading their review tier are 6% 
-  less likely to give a discount, consistent with preferring less variance. I also 
-  find that consumers are significantly more likely to leave a review when purchasing 
-  during a discount. Additional findings include estimates of the causal effect of 
-  reviews on sales and equilibrium discount elasticities in an important market 
-  not previously studied. \thispagestyle{empty}
+  I document that firms in online marketplaces use price promotions to facilitate transitions to better review tiers (similar to the number of stars on Amazon.com).
+I find that firms close to going one tier up are 4-9% more likely to discount.
+I theorize that two effects could be at play.
+First, a selection effect arises because customers who buy during a discount could be different from the regular ones, and could potentially leave more positive reviews.
+Second, a variance effect reflects the idea that positive reviews could help the firm move up a review tier, while negative reviews would keep the tier unchanged, minimizing the downside risk of giving a discount.
+To test my hypotheses, I estimate a simple structural model of demand and reviewing behavior, and develop a new approach to estimating demand from data on product usage.
+I do not find evidence that the selection effect is positive.
+I find evidence of the importance of the variance effect: when the selection effect is controlled for, firms close to downgrading their review tier are 6% less likely to give a discount, consistent with preferring less variance.
+I also find that consumers are significantly more likely to leave reviews during a discount.
+Additional findings include estimates of the causal effect of reviews on sales and equilibrium discount elasticities in an important market not previously studied.
+\thispagestyle{empty}
 
  bibliography: reviewsBib.bib
+ nocite: | 
+  @stargazer, @texreg, @here, @dataframe, @plm
  fontsize: 12pt
@@
 In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17, p.379].
-A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfactory without guidance.
-Such guidance is now routinly provided by different types of recommendation systems.
+A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfyingly without guidance.
+Such guidance is now routinely provided by different types of recommendation systems.
 Many marketplaces or third party websites allow consumers to review products and services that they purchased, and then aggregate these reviews into a rating, greatly facilitating the comparison between alternatives.
@@
 Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services.
-Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews important, if not crucial, for the success of the business.
-Not surprisingly, firms assume an active approach to managing their reviews.
+Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews are important, if not crucial, for the success of the business.
+Not surprisingly, firms take an active approach to managing their reviews.
 Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors.
-
 In this paper I study a novel form of review management.
@@
 I ask: would it be profitable for such a product to run a price promotion?
+
 With a help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect.
-Customers who purchase the good on a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews.
-If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount, as new customers are likely to leave positive reviews and help the product advance to the next review tier.
-Whether the selection effect is positive or negative is an empirical question, and I answer this question with my data.
+Customers who purchase the good during a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews.
+If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on sale, as new customers are likely to leave positive reviews and help the product advance to the next review tier.
+However, these new customers could also prove to be a worse match with the product and end up leaving less favorable reviews.
+Thus, the sign of the selection effect is ultimately an empirical question.
 The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier.
-Extra positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews might not affect its review status---and, therefore, sales---by much.
+Additional positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews might not affect its review status---and, therefore, sales---by much.
 While extra variance is good for products that are on the verge of a tier upgrade, it could be harmful for products that are close to sliding one review tier down.
@@
 To quantify all these effects, I analyze data from Steam, a major marketplace for computer video games.
-I build and estimate a simple structural model of demand and reviewing behavior on Steam.
-The demand part of the model lays the groundwork for my analysis.
-I confirm the importance of better review tiers for sales on Steam, finding a premium of as high as 10% of being in the best bin, and a penalty of up to 13% for not having reviews, compared to a mediocre review tier.
+I build and estimate a tractable structural model of demand and reviewing behavior on Steam.
+The demand model lays the groundwork for my analysis, as it helps me confirm the importance of better review tiers for sales on Steam.
+I find a premium of as high as 10% of being in the best bin and a penalty of up to 13% for not having reviews, compared to a mediocre review tier.
 My estimates also highlight how impactful discounts are in this market, with an average discount being accompanied by a 25% spike in sales.
-Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given the differential contribution of various tiers on sales.
+Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given the differential contribution of various tiers to sales.
+
 I further document that these incentives translate into action.
-I find that products that are close to upgrading their review tier are 4-9% more likely to be on a discount, and I find some evidence that proximity to a downward transition decreases the probability to be on a discount by up to 4%.
-
-My structural model provides further insight into the relative contributions of the variance and the selection effects to the observed behavior.
-I estimate the effect of discounts on the probabilities to leave positive and negative reviews.
+I find that products that are close to upgrading their review tier are 4-9% more likely to sell at a discount, and I find some evidence that proximity to a downward transition decreases the probability to sell at a discount by up to 4%.
+I then employ my structural model to disentangle the relative contributions of the variance and the selection effects to the observed discounting patterns.
+To that end, I estimate the effect of discounts on the probabilities to leave positive and negative reviews.
 I find no evidence that the selection effect is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion.
@@
 While this effect is harder to test directly, I provide some  indirect tests of its impact on the discounting behavior around review tier transitions.
-I estimate the size of the selection effect at the product level, and “control” for it in my regressions of discounts on proximities to transition.
-I find that, in the absence of the selection effect, products that are close to a review downgrade are 6% less likely to discount, which is consistent with the idea that the variance effect is negative for such products.
+I estimate the size of the selection effect at the product level, and control for it in my regressions of discounts on proximities to transition.
+I find that, in the absence of the selection effect, products that are close to a review downgrade are 6% less likely to discount---an increase in both the size and the significance of the effect compared to the specification that does not control for the selection effect.
+This finding is consistent with the idea that such products are averse to variance in their review scores.
 I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.
 
-While some of my findings are new and interesting on their own, others are best measured against the literatures in economics and marketing that I contribute to.
+While some of my findings are new and interesting on their own, others are best measured against the literatures in economics and marketing to which I contribute.
 The oldest of these is the literature investigating the impact of online consumer reviews on sales.
@@
 In a seminal contribution to this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales.
-A similar approach applied to the same market was recently used by @ReimersWaldfogel20, who reaffirm the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews.
-@ZhuZhang10 exploit differences between two different video games consoles rather than websites, and find that review ratings matter only for less popular games.
+A similar approach applied to the same market was recently used by @ReimersWaldfogel20, which reaffirms the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews.
+@ZhuZhang10 exploits the differences between two video games consoles rather than websites, and finds that review ratings matter only for less popular games.
 
@@
 Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes the test once, and either earns an “A” or a “B”), review scores of products on review platforms are moving slowly and are tested against the threshold on a daily basis.
-If a product is slightly below the cutoff and has 4 stars, why would it not try to do something to cross the cutoff, especially if better review bins are more lucrative?
+If a product is slightly below the cutoff, why would it not try to do something to cross the cutoff, especially if better review bins are more lucrative?
 My paper asks precisely that question, and shows that such concerns are well-founded.
@@
 
-@SorokinStevens20 raises other concerns about the validity of the regression discontinuity approach in studying the causal effect of reviews on outcomes.
-To my knowledge, it was the first paper to use Steam as the object of its analysis.
+@SorokinStevens20 raises other concerns about the validity of the regression discontinuity approach in studying the causal effect of reviews on product outcomes.
+To my knowledge, it was the first paper to use Steam to study the causal effect of online reviews.
 In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from video games' usage data.
@@
 @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves.
-@LucaZervas16 provide similar evidence for restaurants on Yelp.
+@LucaZervas16 provides similar evidence for restaurants on Yelp.
 A more scrupulous way for a firm to influence reviews is by assuming an active approach to review management---for instance, by publicly responding to the reviews it receives.
-@GuYe14 provide evidence that consumers who had left a negative review about their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management.
+@GuYe14 provides evidence that consumers who had left a negative review of their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management.
 @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future.
@@
 Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews.
-Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle.
+Anything that could affect the satisfaction of the customers could have an effect on their reviewing behavior, at least in principle.
 Another strand of literature is studying whether price promotions have an effect on firms' online reputation.
@@
 It presents evidence that customers attracted by a promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher.
-This difference can explain the reasons behind the dissatisfaction of the Groupon customers.
-@Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion.
+Worse match quality between the restaurants and the exploring Groupon customers could explain the dip in the review score following a price promotion.
+@Li16 confirms the finding in the same market, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion.
 There are a couple of other studies that dispute the negativity of the selection effect.
@@
 In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreases the likelihood of negative feedback.
-The effect is explained by clients reciprocating to the rebate, rather than byt the differences between customers buying with a rebate and without it.
+The effect is explained by clients reciprocating to the rebate, rather than by the differences between customers buying with a rebate and without it.
 My study contributes to this debate by documenting the absence of a positive selection effect in a new market.
@@
 While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which somewhat undermines the strategy.
-I provide a novel mechanism--- the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative.
+I provide a novel mechanism---the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative.
 The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it would find it profitable to sell for free even if the probability to solicit favorable reviews is small.
@@
 Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam.
-The technical nature of the material in this section contributes greatly to its size, but the goal of this section is simply to quantify the importance of different review tiers on sales, and to show that discounts are effective in attracting new customers.
+The technical nature of the material in that section contributes greatly to its size, but the purpose of that section is to simply lay the groundwork for the main analysis by quantifying the importance of different review tiers on sales, and by showing that discounts are effective in attracting new customers.
 The main findings are described in  Section \ref{descriptiveEvidence}.
-It opens with a stylized model of discounting for a product close to a review tier transition, and introduces the selection and the variance effects.
+It opens with a stylized model of a discounting decision for a product close to a review tier transition, and introduces the selection and the variance effects.
 The section proceeds by establishing that such discounting behavior takes place in the data.
-Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} by a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effects to the observed patterns of discounting around review transitions.
+Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} with a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effects to the observed patterns of discounting around review transitions.
 Section \ref{conclusion} concludes.
@@
 Starting from late 2016 Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer).
-This distinguishes Steam from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews).
+Steam is, thus, different from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews).
 This gives me confidence in the authenticity of most reviews.
@@
 A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews.
-Based on the score, Steam assigns *review tiers* to each game\footnote{I use words “tier”, “bin”, and “label” interchangebly througout the text}.
+Based on the score, Steam assigns *review tiers* to each game\footnote{I use the words “tier”, “bin”, and “label” interchangebly througout the text}.
 These labels\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}.
@@
 Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}.
-From that list the user can get some basic information about each title, such as its name, price, and if the game is currently on a discount.
+From that list the user can get some basic information about each title, such as its price or if the game is currently sold at a discount.
 Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has.
@@
 Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place.
-@deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an omage to the masterfuly chosen title of \citet{deLanghe15}.}.
+@deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an homage to the masterfully chosen title of \citet{deLanghe15}.}.
 Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales.
-Crucially, according to Steam's documentation, all review labels better than “Negative“ have a very similar contribution to visibility on the platform, which means, for example, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2].
+Crucially, according to Steam's documentation, all review labels better than “Negative” have a very similar contribution to visibility on the platform, which implies, among other things, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2].
 Therefore, any effect of the review labels on sales should come through the perceived quality differences between different bins, rather than some mechanical visibility differences.
@@
 Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}.
-Unobserved dynamic quality would present a big obstacle to the identification of the effect of reviews on pricing decisions or sales.
+Unobserved dynamic quality would present a big obstacle to the identification of the effect of reviews on discounting decisions or sales.
 Consider a game that has just issued a major update.
@@
 The duration of a custom discount is restricted to be at least one full day, and at most two weeks.
-Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on a discount.
+Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on sale.
 As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”.
@@
 The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly.
-Recall that the review score is just the fraction of positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in.
-Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release.
+Recall that the review score is just the fraction of positive reviews among all reviews, so the law of large numbers implies that this ratio crystallizes as more reviews flow in.
+Second plot in Figure \ref{reviewDescriptivePlots} shows that out of all the reviews that games accumulate by the age of 180 days, a half arrives in the first month after the release.
 On average across games, the standard deviation of the review score over time is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`  (out of one hundred), with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that.
@@
 While the answer might be obvious for large sought-after products, the situation is less clear for an average game.
-The second question is: how big are the differences between different review tiers?
-If transitioning to a better tier does not increase sales by much, then firms would be unlikely to pursue such transitions when making on their discount decisions.
+The second question is: how big are the differences between various review tiers?
+If transitioning to a better tier does not increase sales by much, then firms would be unlikely to pursue such transitions when making their discount decisions.
 The discussion of the assumptions behind my analysis and the interpretation of the parameter estimates contributes greatly to the size of this section.
@@
 The mapping between these variables and the number of copies sold is, of course, nothing else but the demand curve for game $i$.
-A change of $0.01$ in the index $x_{it}'\beta$ means that quantity demanded of game $i$ goes up by one percent.
-This multiplicative structure is necessary, because it will allow me to estimate the price sensitivity and the effect of reviews on sales in relative terms\footnote{See the Identification section for more details}.
-Buyers of the game become active players, and are subject to a fixed daily risk of $1-\psi_i$ of abandoning the game.
+Buyers of the game then become active players, and are subject to a fixed daily risk of $1-\psi_i$ of abandoning the game.
 Given that the number of active players “flipping” this coin at the end of day $t-1$ is $A_{it-1}$, this process gives rise to the binomial distribution for the number of exiters.
+The demand model is fully parametrized by the vector $(\{\lambda_i, \psi_i\}_{i = 1}^n, \beta)$.
 
@@
 
-There are two key identification challenges I need to address.
+There are two key identification challenges I need to address in order to estimate the parameters of the demand model from my data.
 One challenge comes from the fact that in order to tease out new purchases from the player activity data, I need to know something about player exit, which is also unobserved.
-The problem is illustrated by equation (\ref{activeProccess}), where the observed part of the data $A_{it} - A_{it-1}$ only identifies a the difference $(B_{it} - E_{it})$.
-Consider a hypothetical scenario of two games that have the same observed median daily player count---say, ten people.
+The problem is illustrated by equation (\ref{activeProccess}), where the observed part of the data $(A_{it} - A_{it-1})$ only identifies the difference $(B_{it} - E_{it})$.
+Consider two  hypothetical games that have the same observed median daily player count---say, ten people.
 However, game one offers a lot of replayability and is played by the same ten people over and over again, while game two is played by new ten people every day.
 Clearly, such two products with identical player activity patterns would have very different sales.
-I am able to solve this problem with the help of Assumption \ref{arrivalAssumptions}.The key insight is that observed factors determine the arrival of new players (buyers) in *absolute* terms, while exit is *proportional* to the number of active players.
+I am able to solve this identification problem with the help of Assumption \ref{arrivalAssumptions}.
+The key insight is that observed factors determine the arrival of new players (buyers) in *absolute* terms, while exit is *proportional* to the number of active players.
 Intuitively, the exit procees is identified by the rate of decay of the player count when the count is far from its (slowly-changing) trend or average.
 Player count is typically far from its average on the days following the game release or the introduction of a discount.
-Sharp spikes in player counts reflect the players who just bought the game; see example game in Figure \ref{exampleGame}.
-For a given decay parameter, the level at which the player count settles identifies the inflow of new buyers.
+On such occasions a lot of new players buy the game simultaneously, which leads to sharp spikes in the player count variable (see example game in Figure \ref{exampleGame}).
+For a given decay parameter, the level at which the player count settles identifies the flow rate of new buyers.
 Given that identifying the exit rate is crucial for teasing out the sales component, it is a great advantage of my model that it allows full heterogeneity in the exit rate $(1-\psi_i)$.
 
-The second identification challenge I tackle is obtaining estimates of the caual effect of review tiers on sales.
-In short, I achive it by minimizing the ommitted variable bias through sample selection, and by controlling for game-specific and time-specific shocks, in addition to the observable covariates that serve as important control variables on their own.
-The discussion below elaborates on the details of identifying the aforementioned effects of reviews on sales, as well as the effects of price variables that together with controls form $\beta$.
+The second identification challenge I tackle is obtaining estimates of the causal effect of review tiers on sales.
+In short, I achieve this by minimizing the omitted variable bias through sample selection, and by controlling for game-specific and time-specific shocks, in addition to the observable covariates that serve as important control variables on their own.
+The discussion below elaborates on the details of identifying the aforementioned effects of reviews on sales, as well as the effects of price variables---the main components of the parameter vector $\beta$.
 
@@
 
-The fact that $x'_{it}\beta$ multiplies the game fixed effect $\lambda_i$ allows me to estimate the dependence of quantity sold on price and reviews in relative terms, i.e., to obtain the elasticities.
-Normally, a log transformation is used to achieve that.
-Indeed, @SorokinStevens20 is able to estimate these elasticities with a within-estimator, using the following model
+The fact that $x'_{it}\beta$ multiplies the game fixed effect $\lambda_i$ allows me to estimate the dependence of quantity sold on price and reviews in relative terms, i.e., to obtain elasticities.
+A change of $0.01$ in the index $x_{it}'\beta$ means that the quantity demanded of game $i$ goes up by one percent.
+Normally, a log transformation of the dependent variable is used to estimate elasticities.
+Indeed, @SorokinStevens20 is able to estimate these elasticities with a within-estimator, using the following model:
 \begin{equation}\label{logReg}
@@
 This number looks more reasonable, especially given that the products I study have a zero marginal cost of production, and in a static world firms would set prices at which the demand for their products would be unit-elastic.
-Every additional day on a discount then is associated with a  `r round(-reg1$coefficients[2],2)*round(panel[discount>0, mean(discount)]*100)`-`r round(-beta.hat[1],2)*round(panel[discount>0, mean(discount)]*100)`, where larger effect comes from the structural model.
+Every additional day on sale  is then associated with a `r round(round(-reg1$coefficients[2],2)*round(panel[discount>0, mean(discount)]*100))`-`r round(round(-beta.hat[1],2)*round(panel[discount>0, mean(discount)]*100))`% higher quantity demanded, where larger effect comes from the structural model.
 Discounts on Steam attract a considerable number of new users, and thus could be effective tools in generating new reviews needed for a review tier transition.
@@
 
-I conclude the overview of the results of estimating the structural model of demand  (\ref{arrivalReg}) by going over the estimates of the game-specific customer arrival rates $\lambda_i$ and the probabilities $\psi_i$ with which active players of game $i$ continue playing the game.
+I conclude the overview of the demand estimation results by going over the estimates of the game-specific customer arrival rates $\lambda_i$, and the probabilities $\psi_i$ with which active players of game $i$ continue playing the game from day to day.
 For the ease of interpretation, I present the estimates of  $\bar \lambda_{i} := \lambda_i(1+\mathbb{E}[x_{it}]'\beta)$, the average sales for game $i$\footnote{This is not quite accurate, as I can only estimate the part of sales that contributes to the gaming activity during peak times}.
@@
 Now I turn attention to the main question of the paper: do firms use discounting to facilitate transitions to better review tiers, or to prevent transitions to worse review tiers?
-I start by presenting a stylized model of a firm whose product is close to a review transition.
+I start by presenting a stylized model of a product that is close to a review transition.
 The model predicts that the decision to discount or not depends on the balance between two forces: the selection effect and the variance effect.
-I then turn to data, and show that products are significantly more likely to go on a discount when they are close to improving their review tier, while the effect for products that are close to sliding down a tier are much weaker.
+I then turn to data, and show that products are significantly more likely to sell at a discount when they are close to improving their review tier, while the effect for products that are close to sliding down a tier are much weaker.
 I use the stylized model to interpret these results, and conclude that further analysis is required in order to establish the relative contributions of the selection and the variance effects.
@@
 A firm can give a discount at cost $c$ that can probabilistically change its status to exceed 1 (an upgrade), to go below 0 (a downgrade), or to remain within the $(0,1)$ band (no change).
-The result depends on whether the additional customers who buy the product on a discount happen to leave more positive or more negative reviews, and on the volume of the new reviews relative to the existing ones.
+The outcome depends on whether the additional customers who buy the product during the discount happen to leave more positive or more negative reviews, and on the volume of the new reviews relative to the existing ones.
 To reflect that, assume that with probability $p$ firm's status becomes $s+x$, and with probability $1-p$ it becomes $s-x$.
 The symmetry is purely for expositional purposes.
-Firm's utility $u(s)$ from having a review status $s \in (0,1)$ is 0, while it earns a utility $u^H$ from the upgraded status and a utility $u^L < 0 < u^H$ from the downgraded status.
+Firm's utility $u(s)$ from having a review status $s \in (0,1)$ is 0, while it earns $u^H$ from the upgraded status and $u^L < 0 < u^H$ from the downgraded status.
 The expected utility from giving a discount is
@@
 Such a firm could be regarded as one that is close to a review upgrade.
-The expected value to the firm of giving a discount is
+The expected value to the firm of starting a price promotion is
 \begin{equation}\label{discTradeoff}
@@
 \end{equation}
-\noindent The firm would choose to give a discount if $\EE{U(s+X)}  > 0$.
+\noindent The firm would choose to start a price promotion if $\EE{U(s+X)}  > 0$.
 If $x < 1-s$, the firm simply can not induce enough change to its review status, and would not give a discount, unless $c < 0$ (i.e, other factors make giving a discount attractive).
@@
 My interested is mostly in the other type of products, the ones that potentially can transition.
-In those cases the decision to discount or not depends on the comparison between the value of the positive transition, $u^H$, the cost of giving a discount ($c$, or $c$ and $(1-p)u^L$), and the probability that the transition is successful.
-If the probability of success is high, the firm is more likely to give a discount.
+In those cases the decision to discount or not depends on the comparison between the value of the positive transition, $u^H$, the cost of giving a discount ($c$, or $c$ and $(1-p)u^L$), and the probability of a successful transition.
+If the probability of success is high, the firm is more likely to launch a discount.
 This is what I refer to as the (positive) \emph{selection} effect.
@@
 
-An interesting observation about the problem of the firm (\ref{discTradeoff}) is that the selection effect does not need to be positive for the firm to decide to go on a discount.
+An interesting observation about the problem of the firm (\ref{discTradeoff}) is that the selection effect does not need to be positive for the firm to decide to launch a discount.
 Indeed, consider the case when  the potential change to the score is moderate ($x \in [1-s, s]$).
@@
 Following the logic of (\ref{discTradeoff}), we can see that for intermediate values of the change in review status ($x \in [s, 1-s)$) such a firm does not benefit from a discount.
-If the reviews left on discount turn out to be negative, the firm will slide one tier down, while if they turn out to be positive, the firm will merely keep its current review status.
+If the reviews left during the discount turn out to be negative, the firm will slide one tier down, while if they turn out to be positive, the firm will merely keep its current review status.
 The selection effect should be strongly positive for such a firm to find discounting profitable.
@@
 ```
+
+Now that a simple theory of discounting close to a review threshold has been brought forward, I turn attention the data.
+The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels on Steam are often preceded by discounts.
+The graph shows that two weeks prior to a transition only `r transPanel[tToTransit==-14, round(mean(100*(discount > 0)))]`% of games are on a discount, essentially the sample average, but that this number more than doubles to around `r transPanel[tToTransit==-1, round(mean(100*(discount > 0)))]`% one day before the label change.
+Regression analysis controlling for review label, number of reviews, age, day of the week and week time effects, as well as time since the previous discount, confirms that the association depicted in Figure \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in the Appendix).
+A game is approximately `r round(reg1$coefficients[2]*14*100)` pp more likely to be on a discount on the day of the transition than it is two weeks prior to it, and it is `r round(-reg1$coefficients[3]*14*100)` pp less likely to be on a discount two weeks following the transition.
+Given that the probability for a game to be on a discount on a random day is `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% in the sample, these effects amount to `r round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% and `r round(100*(-reg1$coefficients[3]/panel[, mean((discount > 0), na.rm=T)]))`% changes in the daily probability of a discount, which is quite sizable.
 
@@
 
-Now that a simple theory of discounting close to a review threshold has been brought forward, I turn attention the data.
-The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels on Steam are often preceded by discounts.
-The graph shows that two weeks prior to a transition only `r transPanel[tToTransit==-14, round(mean(100*(discount > 0)))]`% of games are on a discount, essentially the sample average, but that this number more than doubles to around `r transPanel[tToTransit==-1, round(mean(100*(discount > 0)))]`% one day before the label change.
-Regression analysis controlling for review label, number of reviews, age, day of the week and week time effects, as well as time since the previous discount, confirms that the association depicted in Figure \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in the Appendix).
-A game is approximately `r round(reg1$coefficients[2]*14*100)` pp more likely to be on a discount on the day of the transition than it is two weeks prior to it, and it is `r round(-reg1$coefficients[3]*14*100)` pp less likely to be on a discount two weeks following the transition.
-Given that the probability for a game to be on a discount on a random day is `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% in the sample, these effects amount to `r round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% and `r round(100*(-reg1$coefficients[3]/panel[, mean((discount > 0), na.rm=T)]))`% changes in the daily probability of a discount, which is quite sizable.
-
 Of course, this finding simply shows a correlation between firms' discounting behavior and review transitions.
@@
 I assume that a buyer who buys the game at $t-k$ leaves a positive (negative) review for the game on day $t$ with probability \(r_{it}^+\)	 (\(r_{it}^-\)), and no review otherwise.
-For the reasons I will explain later, I will refer to  $r_{it}^+$ as the *like rate*, and to $r_{it}^-$ as the *dislike rate*.
+For the reasons I explain later, I will refer to $r_{it}^+$ as the *like rate*, and to $r_{it}^-$ as the *dislike rate*.
 The focus of the analysis is on the difference between the reviews left on and off a discount.
@@
 In the simplest specification I use $w_{it} = [1, disc_{it-k}]'$,  $\rho_i^+ = \rho^+$ for all $i$,  implying $r_{it}^+ = \rho^+_0 + disc_{it}\rho^+_1$.
-This simply says that buyers of all games leave a positive reviews with one of the two possible probabilities: $\rho^+_0$ off a discount, and $\rho^+_0 + \rho^+_1$ on a discount.
+This simply says that buyers of all games leave a positive reviews with one of the two possible probabilities: $\rho^+_0$ off discount, and $\rho^+_0 + \rho^+_1$ on discount.
 Similarly, a probability of a negative review could be either $\rho^-_0$, or $\rho^-_0 + \rho^-_1$.
-While the model with no heterogeneity in parameters is not very realistic (for one, it implies that all games have the same expected review score), I treat the estimates that will come out of it as estimates of average parameter values: $\rho^+ \approx \bar{\rho}_i^+$, $\rho^- \approx \bar{\rho}_i^-$.
-Thus, a model without heterogeneity offers a simple way to do inference on the average values of parameters in the population of games.
+While the model with no heterogeneity in parameters is not very realistic (for one, it implies that two games with the same discounting behavior will have the same expected review score), I use this model to make inference on average parameter values.
+This is econometrically easier than estimating the entire distribution of $(\rho_i^+, \rho_i^-)$, and then testing hypotheses about the functions of the means of those distributions.
+The assumption here is that the model without heterogeneity reasonably approximates the aforementioned averages: $\rho^+ \approx \bar{\rho}_i^+$, $\rho^- \approx \bar{\rho}_i^-$.
 
 In the introduction I implicitly defined two hypotheses I want to test.
-First, I want to know if consumers are more likely to leave a review if they buy on a discount.
-This amounts to testing $\rho^+_0 + \rho^+_1 + \rho^-_0 + \rho^-_1 > \rho^+_0 + \rho^-_0$, or
+First, I want to know if consumers are more likely to leave a review when they buy on discount.
+This would constitute an indirect test of the variance effect.
+In order to do so, I need to test if $\rho^+_0 + \rho^+_1 + \rho^-_0 + \rho^-_1 > \rho^+_0 + \rho^-_0$, or, more formally:
 \begin{align}\label{hyp1}
@@
 The second hypothesis I am interested in is whether the selection effect is positive or not.
-Product's review score measures the fraction of positive reviews among all reviews left, reflecting the probability to get a good review conditional on having a review.
-Indeed, if $L_t \in \{0, 1\}$ is a random variable that takes the value of 1 if the $i$-th review is a like, then the review score based on $T$ reviews would simply be $Score(T) = \frac 1 T \sum_{t=1}^T L_t$, which converges to $\EE{L_t} = \PP{L_t = 1}$ as $T$ grows to infinity.
-For a user buying a game off a discount we have
+Product's review score measures the fraction of positive reviews among all reviews left, reflecting the probability to get a good review *conditional* on having a review.
+Indeed, if $L_t \in \{0, 1\}$ is a random variable that takes the value of 1 if the $i$-th review is a like and 0 if it is a dislike, then the review score based on $T$ reviews would simply be $Score(T) = \frac 1 T \sum_{t=1}^T L_t$, which converges to $\EE{L_t} = \PP{L_t = 1}$ as $T$ grows to infinity.
+For a user buying a game off discount we have
 \begin{equation}
@@
 
-\noindent For a user buying the same game on a discount we have
+\noindent For a user buying the same game on discount we have
 \begin{equation}
@@
 
-Following assumption \ref{arrivalAssumptions}, the arrival of buyers for game $i$ on day $t$ follows a Poisson distribution with arrival rate $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$.
+Following Assumption \ref{arrivalAssumptions}, the arrival of buyers for game $i$ on day $t$ follows a Poisson distribution with arrival rate $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$.
 I assumed that, $k$ days after the purchase is made, each consumer leaves a  positive review with probability $r_{it}^+$, a negative review with probability $r_{it}^-$, and no review otherwise.
@@
 \end{equation}
-As we can see, the ML-estimator of the like rate during a price promotion is just the ratio of the number of good reviews left on a discount over the expected sales on that day.
-Similarly, the like rate off a discount can be estimated by
+As we can see, the ML-estimator of the like rate during a price promotion is just the ratio of the number of good reviews left on discount over the expected sales on those days.
+Similarly, the like rate off discount can be estimated by
 \begin{equation}\label{rhohat2}
@@
 \end{equation}
-with the interpretation that the like rate in the absence of a discount is just a ratio of the reviews left outside of a discount and the expected number of customers outside a discount.
-Notice that identification of these parameters requires the knowledge of the demand parameters $\lambda_{it}$, highlighting the point I made earlier: seeing more good reviews arriving on a discount is not sufficient to conclude whether customers are more likely to leave positive reviews when purchasing during a discount.
+with the interpretation that the like rate in the absence of a discount is just a ratio of the reviews left outside of a discount and the expected number of customers who paid the full price.
+Notice that identification of these parameters requires the knowledge of the demand parameters $\lambda_{it}$, highlighting the point I made earlier: seeing more good reviews arriving during a discount is not sufficient to infer that customers are more likely to leave positive reviews when purchasing during a discount.
 One needs to know how many more customers are buying because of the aforementioned discount.
 
-My second hypothesis, formulated in (\ref{hyp2}), involves the sentiment of the reviews left on and off a price promotion.
-Intuitively, one should be able to detect a change in the valence of reviews during a price promotion by simply comparing the ratios of good to bad reviews on and off a discount.
+My second hypothesis, formulated in (\ref{hyp2}), involves the sentiment of the reviews left on and off price promotion.
+Intuitively, one should be able to detect a change in the valence of reviews during a price promotion by simply comparing the ratios of good to bad reviews on and off discount.
 In particular, the answer should not depend on any information on the absolute sales.
-Indeed, if we plug  in the estimators from (\ref{rhohat1})-(\ref{rhohat2}) into the expression for the expected review score off a discount from (\ref{hyp2}), we can see that our inference here will not depend on the estimates of the demand parameters in $\lambda_{it}$:
+Indeed, if we plug  in the estimators from (\ref{rhohat1})-(\ref{rhohat2}) into the expression for the expected review score off discount from (\ref{hyp2}), we can see that our inference here will not depend on the estimates of the demand parameters in $\lambda_{it}$:
 \begin{equation}\label{avReviewScore}
@@
 \end{equation}
-The estimator of the review score off a discount simply calculates the average of the positive reviews left off a discount among all the reviews left off a discount, confirming our intuition.
+The estimator of the review score off discount simply calculates the average of the positive reviews left off discount among all the reviews left off discount, confirming our intuition.
 
@@
 As my sample was selected to only include products with constant quality, this perception should only change if different types of consumers are buying the product.
-Consumers buying on a discount are paying a lower price, and thus could be different from consumers paying the whole price.
+Consumers buying on a discount are paying a lower price, and thus could be different from consumers paying the full price.
 This is the selection effect of discounts on reviews.
@@
 Discounts appear to increase both probabilities, implying that users seem to be more likely to leave a review during a discount.
-I formally test this hypothesis, stated in (\ref{hyp1}), and I strongly reject the null that users are less likely to leave reviews when buying on a discount in favor of the alternative that they are more likely to leave reviews when buying on a discount (the values of the $t$-stats are `r round(t1.1[1],2)` and `r round(t1.2[1],2)` in the two specifications).
+I formally test this hypothesis, stated in (\ref{hyp1}), and I strongly reject the null that users are less likely to leave reviews when buying on discount in favor of the alternative that they are more likely to leave reviews when buying on discount (the values of the $t$-stats are `r round(t1.1[1],2)` and `r round(t1.2[1],2)` in the two specifications).
 The estimated change in the probability of leaving a review due to a discount is between `r round((theta2[2]+theta2[6])/(theta2[1]+theta2[5])*100)`% and `r round((theta1[2]+theta1[4])/(theta1[1]+theta1[3])*100)`%, where the smaller estimate is probably more reliable, as it takes into account the effects of age on discounting.
@@
 To strengthen this point, I use the difference in the valence of reviews on and off discount to measure the selection effect at the game level.
-With such estimates at hand, I can revisit my regression of discounts on proximities to transitions (\ref{potTransitionsReg}) controlling for the selection effect.
+With such estimates at hand, I can revisit my regression of discounts on proximities to transitions (\ref{potTransitionsReg}), controlling for the selection effect.
 In the identification section I showed how one can estimate the like and dislike rates on the product level.
@@
 \noindent As $\Delta score_{i}$ does not change over time, its effect on discounting probability can not be estimated by the within-estimator, but the interaction term could still be included.
-Notice that $\beta^+_0$ and $\beta^-_0$ measure the effect of proximity to a transition on discounting probability if $\Delta score_{i} = 0$, i.e.
+Notice that $\beta^+_0$ and $\beta^-_0$ measure the effect of proximity to transition on discounting probability if $\Delta score_{i} = 0$, i.e.
 \emph{if there is no selection effect}.
@@
 Crucially, in the preferred specification (FE) I find that $\beta^-_0 < 0$, and $\beta^+_0 > 0$.
-Once the variation in the selection effect is controlled for, I obtain the coefficients measuring the impact of the variance effect on discounting decisions, and the signs align with the theory.
+Once the variation in the selection effect is controlled for, I obtain the coefficients measuring the impact of the variance effect on discounting decisions, and the signs align with theory.
 Their sizes are also quite economically meaningful, suggesting that, in the absence of the selection effect, games close to a positive transition are  `r round(100*reg3$coefficients["pos.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% more likely to go on a discount, and games close to a negative transition are `r -round(100*reg3$coefficients["neg.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% less likely to go on a discount.
+Recall that my estimates of (\ref{potTransitionsReg}) that did not control for the selection effect found any effect of the proximity to a negative transition on the probability of discount.
 
@@
 Using data from Steam, a major digital marketplace for computer video games, I show that firms discount their products in order to facilitate transitions between review tiers.
-Products that are close to upgrading their review tier are 4-9% more likely to be on a discount, while products close to deteriorating their review tier are up to 4% less likely to discount, albeit this effect is less significant.
+My estimates of the demand process indicate that better review tiers substantially increase sales, and that discounts are effective at attracting new users and, therefore, reviewers.
+Therefore, using price promotions to improve the review label of a game appears to be a plausible strategy.
+I find that products that are close to upgrading their review tier are 4-9% more likely to be on a discount, while products close to deteriorating their review tier are up to 4% less likely to discount, albeit this effect is less significant.
 
 I identify two channels that can make such behavior profitable: the *selection* effect and the *variance* effect.
-Customers who purchase the good on a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews.
+Customers who purchase the good on discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews.
 If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount, regardless of whether the product is about to upgrade or downgrade its review tier.
@@
 
-The variance effect reflects the asymmetry between the successful and the unsuccessful discounting campaign, as measured by the valence of the new reviews.
-A product close to moving one review tier up benefits greatly from a good realization, while a bad one does not change its review tier much.
-On the other hand, a product that is close to sliding into a worse tier, if averse to a bad outcome, and would benefit less in absolute value from a good outcome.
+The variance effect reflects the asymmetry between a successful and an unsuccessful discounting campaign, as measured by the valence of the new reviews.
+A product close to moving one review tier up benefits greatly from a good realization, while a bad might not change its review tier.
+On the other hand, a product that is close to sliding into a worse tier is averse to a bad outcome, and would benefit less in absolute value from a good outcome.
 While I manage to test the selection effect directly, I have to test the variance effect by trying to falsify the predictions that follow from it.

### 2020-10-13 Analysis/Code/Sorokin_JMP_2020.Rmd
misc

@@
 With the help of this model, I manage to extract information on product sales from usage data.
-I compare the estimates of the structural model with the ones obtained by its simpler regression analog, and find important similartities and dissimilarities.
+I compare the estimates of the structural model with the ones obtained by its simpler regression analog, and find important similarities and dissimilarities.
 The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.
@@
 M <- panel[, max(ageGroup)]
-# Create an auxilary table that for every age (in months) takes games that have
+# Create an auxiliary table that for every age (in months) takes games that have
 # been present for that many months, and then splits those games into 10 groups,
@@
 These two facts form the foundation of my analysis of discounting behavior on a verge of a review tier transition that will be carried out in Section \ref{descriptiveEvidence}.
-I will further extend the model from this section by modelling the reviewing behavior of customers in Section \ref{selectionEffect}.
+I will further extend the model from this section by modeling the reviewing behavior of customers in Section \ref{selectionEffect}.
 
@@
 The key insight is that observed factors determine the arrival of new players (buyers) in *absolute* terms, while exit is *proportional* to the number of active players.
-Intuitively, the exit procees is identified by the rate of decay of the player count when the count is far from its (slowly-changing) trend or average.
+Intuitively, the exit process is identified by the rate of decay of the player count when the count is far from its (slowly-changing) trend or average.
 Player count is typically far from its average on the days following the game release or the introduction of a discount.
@@
 $$
-\noindent To check whether the omitted week effects could play a crucial role, I report the results of estimaing (\ref{logReg}) both with the ideal set of covariates, and with the covariates used to estimate (\ref{arrivalReg}).
+\noindent To check whether the omitted week effects could play a crucial role, I report the results of estimating (\ref{logReg}) both with the ideal set of covariates, and with the covariates used to estimate (\ref{arrivalReg}).
 The results are presented in Table \ref{demandEstimates}.
@@
 A negative effect could be attributed to customers' reluctance to purchase products of unknown quality.
-If that is the case, this finding suggests a pretty serious cost of asymetric information in this market.
-
-The second imprortant set of variables are the price variables.
+If that is the case, this finding suggests a pretty serious cost of asymmetric information in this market.
+
+The second important set of variables are the price variables.
 The first row of Table \ref{demandEstimates} suggests that the price elasticity of demand of very low, between  `r round(-reg1$coefficients[2],2)` and `r round(-beta.hat[1],2)` in absolute value.
@@
 Their sizes are also quite economically meaningful, suggesting that, in the absence of the selection effect, games close to a positive transition are  `r round(100*reg3$coefficients["pos.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% more likely to go on a discount, and games close to a negative transition are `r -round(100*reg3$coefficients["neg.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% less likely to go on a discount.
-Recall that my estimates of (\ref{potTransitionsReg}) that did not control for the selection effect found any effect of the proximity to a negative transition on the probability of discount.
+Recall that my estimates of (\ref{potTransitionsReg}) that did not control for the selection effect, found only a limited effect of the proximity to a negative transition on the probability of discount.
 
@@
 Using data from Steam, a major digital marketplace for computer video games, I show that firms discount their products in order to facilitate transitions between review tiers.
-My estimates of the demand process indicate that better review tiers substantially increase sales, and that discounts are effective at attracting new users and, therefore, reviewers.
+My estimates of the demand process indicate that better review tiers substantially increase sales, and that discounts are effective at attracting new users and, as a consequence, reviewers.
 Therefore, using price promotions to improve the review label of a game appears to be a plausible strategy.
-I find that products that are close to upgrading their review tier are 4-9% more likely to be on a discount, while products close to deteriorating their review tier are up to 4% less likely to discount, albeit this effect is less significant.
+I find that products that are close to upgrading their review tier are 4-9% more likely to be on sale, while products close to deteriorating their review tier are up to 4% less likely to discount, albeit this effect is less significant.
 
 I identify two channels that can make such behavior profitable: the *selection* effect and the *variance* effect.
-Customers who purchase the good on discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews.
+Customers who purchase the good during a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews.
 If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount, regardless of whether the product is about to upgrade or downgrade its review tier.
@@
 A product close to moving one review tier up benefits greatly from a good realization, while a bad might not change its review tier.
-On the other hand, a product that is close to sliding into a worse tier is averse to a bad outcome, and would benefit less in absolute value from a good outcome.
+On the other hand, a product that is close to sliding into a worse tier is averse to a bad outcome, and would benefit little from a good outcome.
 While I manage to test the selection effect directly, I have to test the variance effect by trying to falsify the predictions that follow from it.
@@
 When I control for the size of the selection effect, I find that the aforementioned decline in probability of discounting goes from being 4% and weakly significant to 6% and highly significant.
-I also leverage my unique data and  structural model to document that consumers are more likely to leave reviews when they buy on a discount, which indirectly supports the importance of the variance effect.
+I also leverage my data and structural model to document that consumers are more likely to leave reviews when they buy during a discount, which indirectly supports the importance of the variance effect.
 

### 2020-10-18 Analysis/Code/Sorokin_JMP_2020.Rmd
Misc

@@
                     covariate.labels = c("Pos. Transition", "Neg. Transition",
-                                         "Score Difference",
                                          "S. Diff $\\times$ Pos. Tr.",
-                                         "S. Diff $\\times$ Neg. Tr."),
+                                         "S. Diff $\\times$ Neg. Tr.",
+                                         "Score Difference"),
                     order = c("treatment","sdif"),
@@
 ```{r results = 'asis'}
-cat(star_insert_row(star.out, c("Weekdays + Week Effects & $\\checkmark$  & $\\checkmark$  \\\\",
-                                "Game Effects & $\\checkmark$  & $\\checkmark$ \\\\"), 
+cat(star_insert_row(star.out, c("Weekdays + Week Effects & $\\checkmark$  & $\\checkmark$ & $\\checkmark$  \\\\",
+                                "Game Effects & $\\checkmark$  & $\\checkmark$ & $\\checkmark$ \\\\"), 
                     insert.after = c(28,28)))

### 2020-10-18 Analysis/Code/Sorokin_JMP_2020.Rmd
misc

@@
 I benefited enormously from my conversations with Ryan Stevens, Jimena Galindo, Sam Kapon, Dmitry Sedov, Jonathan Elliott, and Timur Abbiasov.
-I would also like to thank Chris Conlon, Christopher Flinn, Elena Manresa, Maher Said, Mikkel Plagborg-M\o{}ller, Milena Almagro, Paula Onuchic, Sharon Traiberman, and all other great people at NYU for their helpful comments.
+I would also like to thank Chris Conlon, Christopher Flinn, Elena Manresa, Maher Said, Mikkel Plagborg-M\o{}ller, Milena Almagro, Paula Onuchic, Sharon Traiberman, Stefan Bucher, and all other great people at NYU for their helpful comments.
 All mistakes are my own.}

### 2020-10-22 Analysis/Code/Sorokin_JMP_2020.Rmd
Value proposition added

@@
   \onehalfspacing \noindent 
-  I document that firms in online marketplaces use price promotions to facilitate transitions to better review tiers (similar to the number of stars on Amazon.com).
+  This paper documents that firms in online marketplaces use price promotions to facilitate transitions to better review tiers (similar to the number of stars on Amazon.com).
 I find that firms close to going one tier up are 4-9% more likely to discount.
-I theorize that two effects could be at play.
+Two effects could be at play.
 First, a selection effect arises because customers who buy during a discount could be different from the regular ones, and could potentially leave more positive reviews.
 Second, a variance effect reflects the idea that positive reviews could help the firm move up a review tier, while negative reviews would keep the tier unchanged, minimizing the downside risk of giving a discount.
-To test my hypotheses, I estimate a simple structural model of demand and reviewing behavior, and develop a new approach to estimating demand from data on product usage.
-I do not find evidence that the selection effect is positive.
+In order to understand the relative contributions of these effects, I estimate a tractable structural model of demand and reviewing behavior.
 I find evidence of the importance of the variance effect: when the selection effect is controlled for, firms close to downgrading their review tier are 6% less likely to give a discount, consistent with preferring less variance.
 I also find that consumers are significantly more likely to leave reviews during a discount.
-Additional findings include estimates of the causal effect of reviews on sales and equilibrium discount elasticities in an important market not previously studied.
+The average selection effect turns out to be small.
+Additional findings include developing a new approach to estimating demand from data on product usage, estimates of the causal effect of reviews on sales and equilibrium discount elasticities in an important market not previously studied.
   \thispagestyle{empty}
@@
 Many marketplaces or third party websites allow consumers to review products and services that they purchased, and then aggregate these reviews into a rating, greatly facilitating the comparison between alternatives.
-These ratings are often given a simple graphical representation; for example, a number of stars between 0 and 5 is a common way to split the alternatives into *review tiers*.
+These ratings are often given a simple graphical representation; for example, a number of stars between 1 and 5 is a common way to split the alternatives into *review tiers*.
 Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services.
@@
 Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors.
-In this paper I study a novel form of review management.
-I show that firms can use discounting in order to facilitate *transitions* between review tiers.
+In this paper I study a novel form of review management: I show that firms can use discounting in order to facilitate *transitions* between review tiers.
 Imagine a product that is several good reviews short of obtaining an additional star.
-I ask: would it be profitable for such a product to run a price promotion?
+My question is: would it be profitable for such a product to run a price promotion?
 
 With a help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect.
-Customers who purchase the good during a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews.
+Customers who purchase the good during a discount are likely to be different from those who pay the full price, and could potentially leave different reviews.
 If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on sale, as new customers are likely to leave positive reviews and help the product advance to the next review tier.
@@
 I find a premium of as high as 10% of being in the best bin and a penalty of up to 13% for not having reviews, compared to a mediocre review tier.
-My estimates also highlight how impactful discounts are in this market, with an average discount being accompanied by a 25% spike in sales.
+My estimates also highlight how impactful discounts are in this market, with an average discount being accompanied by a 38% spike in sales.
 Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given the differential contribution of various tiers to sales.
@@
 I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.
+
+This paper contributes to the ongoing research effort to improve the design of  recommendation systems.
+Theoretical advancements have been recently made in understanding  separate components of the ideal system, such as exploration of new products vs.
+exploitation of the established options (@cheHorner18), creation of incentives for firms to invest in quality (@AperjisJohari10), promoting competition and reducing barriers to entry (@Vellodi20), to name just a few topics and contributions.
+At the heart of every such inquiry lies a particular strategic interaction between firms, users, and the platform.
+My paper provides empirical evidence on what some of these interactions result in.
+I show that firms respond to the tier structure of review systems by changing their pricing behavior around the thresholds, and that they use pricing to affect their review process.
+My estimates can inform future work that will synthesize theoretical and data-driven insights in order to make concrete design recommendations.
+For example, @Vellodi20 shows that barriers to entry resulting from the low speed of review accumulation by new firms calls for a review system that censors the reviews of the most established products; however, when firms can offer lower prices to build up the crucial review base, the need for the design intervention is diminished.
+My paper directly informs this question by quantifying two fundamental forces involved: the frequency with which firms change prices in response to their review status, and the response of the reviewing behavior to these changes in prices.
+
+## Literature Review
 

### 2020-10-24 Analysis/Code/Sorokin_JMP_2020.Rmd
Misc edits

@@
 I benefited enormously from my conversations with Ryan Stevens, Jimena Galindo, Sam Kapon, Dmitry Sedov, Jonathan Elliott, and Timur Abbiasov.
-I would also like to thank Chris Conlon, Christopher Flinn, Elena Manresa, Maher Said, Mikkel Plagborg-M\o{}ller, Milena Almagro, Paula Onuchic, Sharon Traiberman, Stefan Bucher, and all other great people at NYU for their helpful comments.
+I would also like to thank Chris Conlon, Christopher Flinn, Elena Manresa, Maher Said, Mikkel Plagborg-M\o{}ller, Milena Almagro, Paula Onuchic, Sharon Traiberman, Stefan Bucher, Vasily Rusanov, and all other great people at NYU for their helpful comments.
 All mistakes are my own.}
@@
 Such guidance is now routinely provided by different types of recommendation systems.
-Many marketplaces or third party websites allow consumers to review products and services that they purchased, and then aggregate these reviews into a rating, greatly facilitating the comparison between alternatives.
+Many marketplaces or third-party websites allow consumers to review products or services they purchase and then aggregate these reviews into a rating, greatly facilitating the comparison between alternatives.
 These ratings are often given a simple graphical representation; for example, a number of stars between 1 and 5 is a common way to split the alternatives into *review tiers*.
 Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services.
-Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews are important, if not crucial, for the success of the business.
+Both extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews are important, if not crucial, for a business's success.
 Not surprisingly, firms take an active approach to managing their reviews.
 Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors.
-In this paper I study a novel form of review management: I show that firms can use discounting in order to facilitate *transitions* between review tiers.
+In this paper I study a novel form of review management: I show that firms can use discounting to facilitate *transitions* between review tiers.
 Imagine a product that is several good reviews short of obtaining an additional star.
@@
 
-With a help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect.
-Customers who purchase the good during a discount are likely to be different from those who pay the full price, and could potentially leave different reviews.
-If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on sale, as new customers are likely to leave positive reviews and help the product advance to the next review tier.
-However, these new customers could also prove to be a worse match with the product and end up leaving less favorable reviews.
+With the help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect.
+Customers who purchase the good during a discount are likely to be different from those who pay the full price and could leave different reviews.
+If reviews left during a discount tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on sale, as new customers are likely to leave positive reviews and help the product advance to the next review tier.
+However, these new customers could also prove to be a worse match with the product and leave less favorable reviews.
 Thus, the sign of the selection effect is ultimately an empirical question.
+Previous work studying the selection effect in digital markets produced mixed findings.
+Some of the papers that documented a negative selection effect struggle to explain why firms run promotions which are unlikely to be profitable and are unlikely to attract positive reviews (see the Literature Review section).
+My variance effect provides a new and attractive explanation for this phenomenon.
+
 The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier.
-Additional positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews might not affect its review status---and, therefore, sales---by much.
-While extra variance is good for products that are on the verge of a tier upgrade, it could be harmful for products that are close to sliding one review tier down.
-Fearing to lose that precious star, such products would prefer to delay running a price promotion, unless the selection effect is positive and strong.
-
-To quantify all these effects, I analyze data from Steam, a major marketplace for computer video games.
-I build and estimate a tractable structural model of demand and reviewing behavior on Steam.
-The demand model lays the groundwork for my analysis, as it helps me confirm the importance of better review tiers for sales on Steam.
-I find a premium of as high as 10% of being in the best bin and a penalty of up to 13% for not having reviews, compared to a mediocre review tier.
-My estimates also highlight how impactful discounts are in this market, with an average discount being accompanied by a 38% spike in sales.
-Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given the differential contribution of various tiers to sales.
+Additional positive reviews can catapult it to the next review bin, which promises higher sales.
+In contrast, a few negative reviews might not affect its review tier---and, therefore, sales---by much.
+Thus, even if the expected effect of price promotion on the reviews is negative, the *expected payoff* could still be positive due to the asymmetry that arises from the tier system's discreteness.
+Similarly, while extra variance is beneficial for products on the verge of a tier upgrade, it could be harmful to products close to sliding one review tier down.
+Fearing to lose that precious star, such products would prefer to delay a price promotion, unless the selection effect is positive and strong.
+
+To quantify these effects, I analyze data from Steam, a major marketplace for computer video games.
+I build and estimate a structural model of demand and reviewing behavior on this platform.
+My model admits full heterogeneity between products in the engagement of users and the absolute effects of reviews and discounts on sales.
+Despite this richness, I show how the parameters, including nonparametric distributions of the random effects, could be estimated.
+I use this model to lay the groundwork for my analysis, as it helps me confirm the importance of better review tiers for sales on Steam.
+Compared to a mediocre review tier, the best tier comes with a premium of as high as 10% in additional sales, and the worst one entails a 13% reduction in sales.
+My estimates also highlight how impactful discounts are in this market, with an average discount accompanied by a 38% spike in sales.
+Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given their differential contribution to sales.
 
 I further document that these incentives translate into action.
-I find that products that are close to upgrading their review tier are 4-9% more likely to sell at a discount, and I find some evidence that proximity to a downward transition decreases the probability to sell at a discount by up to 4%.
+I find that products that are close to upgrading their review tier are 4-9% more likely to sell at a discount, and I find some evidence that proximity to a downward transition decreases the probability of selling at a discount by up to 4%.
 I then employ my structural model to disentangle the relative contributions of the variance and the selection effects to the observed discounting patterns.
 To that end, I estimate the effect of discounts on the probabilities to leave positive and negative reviews.
-I find no evidence that the selection effect is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion.
+I find no evidence that selection is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion.
 Thus, I attribute firms' behavior to the variance effect.
 While this effect is harder to test directly, I provide some  indirect tests of its impact on the discounting behavior around review tier transitions.
-I estimate the size of the selection effect at the product level, and control for it in my regressions of discounts on proximities to transition.
-I find that, in the absence of the selection effect, products that are close to a review downgrade are 6% less likely to discount---an increase in both the size and the significance of the effect compared to the specification that does not control for the selection effect.
+I estimate the size of the selection effect at the product level and control for it in my regressions of discounts on proximities to transition.
+I find that, in the absence of the selection effect, products close to a review downgrade are 6% less likely to discount---an increase in both the size and the significance of the effect compared to the specification that does not control for the selection effect.
 This finding is consistent with the idea that such products are averse to variance in their review scores.
-I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.
-
-This paper contributes to the ongoing research effort to improve the design of  recommendation systems.
+I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which discounts create “variance”.
+
+My paper makes an important step towards a bigger goal of studying the life cycles of products in online marketplaces.
+The flip side of my finding that a product is more likely to be sold at a discount when a review tier transition is close is that it is less likely to run a price promotion when such transition is far.
+This idea would be a natural input into a model of pricing behavior of a product that maximizes its success over the entire life span.
+Such a model would exhibit a complicated joint dynamics of review, sales, and price processes.
+A period of aggressive discounting would help a new product attract customers and transition to the best review tier it can, and would then be followed by a period of high prices that exploit the accumulated reputation.
+This study serves as a laboratory that isolates some of the effects present in such a model and foreshadows some of the findings and issues that could emerge from it.
+
+I also contribute to the ongoing research effort to improve the design of  recommendation systems.
 Theoretical advancements have been recently made in understanding separate components of the ideal system, such as exploration of new products vs.
-exploitation of the established options (@cheHorner18), creation of incentives for firms to invest in quality (@AperjisJohari10), promoting competition and reducing barriers to entry (@Vellodi20), to name just a few topics and contributions.
+exploitation of the established options [@cheHorner18], creation of incentives for firms to invest in quality [@AperjisJohari10], promotion of competition, and reduction of barriers to entry [@Vellodi20]---to name just a few topics and contributions.
 At the heart of every such inquiry lies a particular strategic interaction between firms, users, and the platform.
 My paper provides empirical evidence on what some of these interactions result in.
-I show that firms respond to the tier structure of review systems by changing their pricing behavior around the thresholds, and that they use pricing to affect their review process.
-My estimates can inform future work that will synthesize theoretical and data-driven insights in order to make concrete design recommendations.
-For example, @Vellodi20 shows that barriers to entry resulting from the low speed of review accumulation by new firms calls for a review system that censors the reviews of the most established products; however, when firms can offer lower prices to build up the crucial review base, the need for the design intervention is diminished.
-My paper directly informs this question by quantifying two fundamental forces involved: the frequency with which firms change prices in response to their review status, and the response of the reviewing behavior to these changes in prices.
+I show that firms respond to the tier structure of review systems by changing their pricing behavior around the thresholds and that they use pricing to affect their review process.
+My estimates can inform future work that will synthesize theoretical and data-driven insights to make concrete design recommendations.
+For example, @Vellodi20 shows that entry barriers resulting from the low speed of review accumulation by new firms call for a review system that censors the reviews of the most established products.
+However, when firms can offer lower prices to build up the crucial review base, the need for the design intervention is diminished.
+My paper directly informs this design question by quantifying two fundamental forces involved: the frequency with which firms change prices to influence their review status and the response of the reviewing behavior to these changes in prices.
 
@@
 
-While some of my findings are new and interesting on their own, others are best measured against the literatures in economics and marketing to which I contribute.
+While some of my findings are new and interesting on their own, others are best evaluated against the literatures in economics and marketing to which I contribute.
 The oldest of these is the literature investigating the impact of online consumer reviews on sales.
@@
 In a seminal contribution to this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales.
-A similar approach applied to the same market was recently used by @ReimersWaldfogel20, which reaffirms the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews.
-@ZhuZhang10 exploits the differences between two video games consoles rather than websites, and finds that review ratings matter only for less popular games.
-
-For identification, the difference-in-differences approach relies on the existence of several comparable platforms, and assumes that the unobserved platform-specific tastes
+A similar approach applied to the same market was recently used by @ReimersWaldfogel20, which reaffirms the importance of reviews for sales of books and quantifies the welfare implications of consumer reviews' informational content.
+@ZhuZhang10 exploits the differences between two video game consoles rather than websites and finds that review ratings matter only for less popular games.
+
+For identification, the difference-in-differences approach relies on the existence of several comparable platforms and assumes that the unobserved platform-specific tastes
 for those platforms are fixed.
 Another approach to identification exploits the rounding of the review data that platforms use to produce simple visual review labels.
-For example, Yelp.com, a popular restaurant comparison service, assigns 4 stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but 4.5 stars to restaurants with an average score between 4.25 and 4.74.
+For example, Yelp.com, a popular restaurant comparison service, assigns four stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but four and a half stars to restaurants with an average score between 4.25 and 4.74.
 @AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue.
 In studies relying on a discontinuity for identification, it is crucial that assignment around thresholds is as good as random.
-Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes the test once, and either earns an “A” or a “B”), review scores of products on review platforms are moving slowly and are tested against the threshold on a daily basis.
+Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes a test once and either earns an “A” or a “B”), review scores of products on review platforms are moving slowly and are tested against the threshold daily.
 If a product is slightly below the cutoff, why would it not try to do something to cross the cutoff, especially if better review bins are more lucrative?
-My paper asks precisely that question, and shows that such concerns are well-founded.
-I do not study the implications of such behavior for a regression discontinuity approach used in the aforementioned papers, but my findings could inform further inquiry into the subject.
+My paper asks precisely that question and shows that such concerns are well-founded.
+I do not study the implications of such behavior for a regression discontinuity approach used in the papers above, but my findings could inform further inquiry into the subject.
 
@@
 In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from video games' usage data.
-I inherit the data from that paper, but confront the absence of sales data in a new way.
-I make assumptions about the gaming patterns for the games in my sample, and formulate a structural model of the data generating process.
+I inherit the data from that paper, but confront the absence of sales data in a new way: by formulating a structural model of the data generating process.
 With the help of this model, I manage to extract information on product sales from usage data.
-I compare the estimates of the structural model with the ones obtained by its simpler regression analog, and find important similarities and dissimilarities.
+I compare the structural model estimates with the ones obtained by its simpler regression analog and find important similarities and dissimilarities.
 The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.
 
-With benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits.
-There are several ways firms can affect their online reviews.
+With the benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits.
+There are several ways for firms to affect their online reviews.
 One is review fraud.
-@Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves.
+@Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors and good reviews for themselves.
 @LucaZervas16 provides similar evidence for restaurants on Yelp.
 A more scrupulous way for a firm to influence reviews is by assuming an active approach to review management---for instance, by publicly responding to the reviews it receives.
-@GuYe14 provides evidence that consumers who had left a negative review of their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management.
+@GuYe14 provides evidence that consumers who had once left a negative review of their hotel experience were more likely to leave a positive review for the same hotel in the future if their first review was responded to by the management.
 @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future.
@@
 @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to.
-In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity.
-The idea is that consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.
-
-Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews.
-Anything that could affect the satisfaction of the customers could have an effect on their reviewing behavior, at least in principle.
+In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage unfavorable review activity.
+The idea is that consumers receive a signal that the firm is “listening” to them and are stimulated to leave negative reviews that they deem more influential.
+
+However, direct ways of managing online reputation discussed above are not the only avenues through which businesses can affect their reviews.
 Another strand of literature is studying whether price promotions have an effect on firms' online reputation.
@@
 In other words, @ByersEtAl12 documents a negative selection effect on Yelp.
-It presents evidence that customers attracted by a promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher.
+It presents evidence that customers attracted by promotion are different from regular customers and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher.
 Worse match quality between the restaurants and the exploring Groupon customers could explain the dip in the review score following a price promotion.
-@Li16 confirms the finding in the same market, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion.
+@Li16 confirms the finding in the same market but finds that restaurants with fewer and worse reviews can benefit from participating in a Groupon promotion.
 There are a couple of other studies that dispute the negativity of the selection effect.
-@ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews.
-In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreases the likelihood of negative feedback.
-The effect is explained by clients reciprocating to the rebate, rather than by the differences between customers buying with a rebate and without it.
+@ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative reviews.
+In an experimental study on eBay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreases the likelihood of negative feedback.
+The effect is explained by clients reciprocating to the rebate, and not by the differences between customers buying with a rebate and without it.
 My study contributes to this debate by documenting the absence of a positive selection effect in a new market.
-Additionally, my paper is the first to focus on discrete changes in review tiers that follow the discounts, instead of studying the continuous effect of a discount on the review score.
-
-Based on its findings, @ByersEtAl12 cautions businesses against running price promotions in an attempt to poach new customers and improve their online reputation.
-To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, this finding presents a puzzle.
-A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap".
-While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which somewhat undermines the strategy.
+Additionally, my paper is the first to focus on discrete changes in review tiers that follow discounts instead of studying the continuous effect of a price promotion on the review score.
+
+Based on its findings, @ByersEtAl12 cautions restaurants to treat Groupon customers well to avoid adverse effects on online reputation.
+To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, finding a negative selection effect in the data presents a puzzle\footnote{Direct profitability of Groupon promotions is questionable; see \citet{Dholakia11}.}.
+A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free to build a reputation and escape the "zero reviews trap".
+While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which undermines the strategy.
 I provide a novel mechanism---the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative.
-The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it would find it profitable to sell for free even if the probability to solicit favorable reviews is small.
+The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it will find it profitable to sell for free even if the probability to solicit favorable reviews is small.
 After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial.
-If this reasoning is commonplace, then the researcher would observe free pricing to deteriorate review scores, on average, but the average effect on sales would be positive.
+My variance effect conceptually echoes the “Gambling for Resurrection” effect from the political science and finance literatures [@DownsRocke94].
+If this type of reasoning is commonplace among firms, then the researcher would observe free pricing to deteriorate review scores, on average, even if the average effect on sales remains positive.
 
@@
 Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam.
-The technical nature of the material in that section contributes greatly to its size, but the purpose of that section is to simply lay the groundwork for the main analysis by quantifying the importance of different review tiers on sales, and by showing that discounts are effective in attracting new customers.
+The technical nature of the material in that section contributes greatly to its size, but the purpose is to simply lay the groundwork for the main analysis by quantifying the importance of different review tiers on sales and showing that discounts are effective in attracting new customers.
 The main findings are described in  Section \ref{descriptiveEvidence}.
-It opens with a stylized model of a discounting decision for a product close to a review tier transition, and introduces the selection and the variance effects.
-The section proceeds by establishing that such discounting behavior takes place in the data.
-Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} with a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effects to the observed patterns of discounting around review transitions.
+It opens with a stylized model of a discounting decision for a product close to a review tier transition and introduces the selection and the variance effects.
+The section proceeds by studying such decisions in the data.
+Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} with a model of reviewing activity and estimates its parameters to quantify the relative contributions of the selection and the variance effects to observed patterns of discounting around review transitions.
 Section \ref{conclusion} concludes.
@@
 Steam is arguably the largest online marketplace for selling computer games in the world.
-Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it has earned around \$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames].
+Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it  earned around \$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames].
 Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion
 in 2018, about the size of the U.S.
-film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD[], Steam is a major player in an increasingly more important industry.
-Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to be studied in its own right.
+film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD, Steam is a major player in an increasingly more important industry.
+Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to stuy in its own right.
 
@@
 
-A review consists of a binary grade, "thumbs up" or "thumbs down", and review's text.
+A review consists of a binary grade, "thumbs up" or "thumbs down", and text.
 A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews.
-Based on the score, Steam assigns *review tiers* to each game\footnote{I use the words “tier”, “bin”, and “label” interchangebly througout the text}.
-These labels\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}.
+Based on the score, Steam assigns *review tiers* to each game.
+These labels\footnote{I use the words “tier”, “bin”, and “label” interchangebly througout the text} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”}.
 For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.
@@
 From that list the user can get some basic information about each title, such as its price or if the game is currently sold at a discount.
+
 Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has.
@@
 
-Valve Corporation, the owner of Steam, is notoriously secretive about its data and algorithms.
+Valve Corporation, the owner of Steam, is notoriously secretive about its data and algorithms [@steamSecretive].
 Given the importance of the information on the performance of different games for game developers and publishers, the community has responded to this secrecy by establishing projects that monitor Steam in real time and extract  information that could be relevant for parties interested in Steam.
@@
 Thus, firms have significant agency when it comes to running price promotions, but platform regulations and platform-wide discounts are important determinants of firms' decision to discount.
+On the consumer side, it is important to note that Steam users can add games to their “wish lists” in order to be notified when the product goes on sale.
+This feature is the most likely explanation of why discounts are followed by sharp spikes in player activity: some users who add the game to their wish lists buy it immediately when it is discounted.
 
@@
 
-Before I start my investigation into the discounting behavior of the products close to a review transition, it is important to address two question.
+Before I start my investigation into the discounting behavior of the products close to a review transition, it is important to address two questions.
 First, do discounts matter on Steam?
-Do they generate enough additional sales to be relevant?
+That is, do they generate enough additional sales to be relevant?
 While the answer might be obvious for large sought-after products, the situation is less clear for an average game.
@@
 If transitioning to a better tier does not increase sales by much, then firms would be unlikely to pursue such transitions when making their discount decisions.
-The discussion of the assumptions behind my analysis and the interpretation of the parameter estimates contributes greatly to the size of this section.
-However, the main takeaways are simple: better review labels improve sales, and discounts are important drivers of sales on Steam.
+In this section I answer these questions and discuss in detail the assumptions behind my analysis, and the interpretation of the parameter estimates.
+
+The main takeaways from the section are: better review labels improve sales, and discounts are important drivers of sales on Steam.
 Having few reviews or having negative reviews depresses sales by 5-13% compared to having “Mixed” reviews; the “Overwhelmingly Positive” review tier increases sales by about 10% compared to “Mixed”.
@@
 of observable characteristics \(x_{it}\) of the game that affect demand:
-price, reviews, age of the game, or seasonal factors.
-The mapping between these variables and the number of copies sold is, of course, nothing else but the demand curve for game $i$.
+price, reviews, age of the game, or seasonal factors\footnote{I do not impose a restriction that $\lambda_{it}$ should be non-negative in estimation.
+Only 4% of day-product pairs in my data will end up having negative predicted sales, which I take as a sign of a good model fit.}.
+The mapping between these variables and the number of copies sold is the demand curve for game $i$.
 Buyers of the game then become active players, and are subject to a fixed daily risk of $1-\psi_i$ of abandoning the game.
@@
 There are two key identification challenges I need to address in order to estimate the parameters of the demand model from my data.
-One challenge comes from the fact that in order to tease out new purchases from the player activity data, I need to know something about player exit, which is also unobserved.
+One challenge comes from the fact that I need to know something about (unobserved) player exit in order to tease out new purchases from the player activity data.
 The problem is illustrated by equation (\ref{activeProccess}), where the observed part of the data $(A_{it} - A_{it-1})$ only identifies the difference $(B_{it} - E_{it})$.
@@
 The second identification challenge I tackle is obtaining estimates of the causal effect of review tiers on sales.
-In short, I achieve this by minimizing the omitted variable bias through sample selection, and by controlling for game-specific and time-specific shocks, in addition to the observable covariates that serve as important control variables on their own.
+In short, I achieve this by minimizing the omitted variable bias through sample selection, where I eliminate products that are more likely to be affected by unobserved confounding factors.
+I complement this approach by controlling for game-specific and time-specific shocks in my regressions, in addition to the observable covariates that serve as important control variables on their own.
 The discussion below elaborates on the details of identifying the aforementioned effects of reviews on sales, as well as the effects of price variables---the main components of the parameter vector $\beta$.
@@
 Arguably, a 100% discount is a powerful enough option to make this strategy viable, at least in principle.
-However, should the price coefficient be of primary interest, I would like to list some further factors that have an impact on the identification of thereof.
+However, should the price coefficient be of primary interest, I would like to list some further factors that have an impact on its identification.
 
@@
 A related problem is the importance of salience in a marketplace that has many thousands of products.
-Any price elasticity estimated relies on Steam keeping its algorithms unchanged.
+Any estimate of the price elasticity is subject to Steam keeping its algorithms unchanged.
 A game can give a 99% discount, but the quantity demanded will not change much if that promotion happens to not be reflected in Steam's system.
-This has implications, for instance, for picking good instruments for prices, should a researcher be interested in obtaining ones.
-Curated discounts created and managed by Steam are suggested to firms, and not chosen by them.
-In principle, such price changes could be exogenous to daily demand conditions.
-However, they could hardly be used as instruments for the price, because they also bring an immense boost in visibility, by the virtue of promoting the discounted game to the front page.
+This has implications for the identification of the slope of the demand curve.
+For instance, consider the problem of finding good instrumental variables for prices.
+Curated discounts, created and managed by Steam, are suggested to firms, and not chosen by them.
+In principle, such promotions could serve as valid instruments for prices, as they are likely exogenous to immediate daily demand conditions.
+However, validity would be violated because such curated discounts also bring an immense boost in visibility, by the virtue of promoting the discounted game to the front page.
 
@@
 That paper argues that Amazon has been known to prioritize growth over profit, thus charging low prices and operating on the inelastic part of the demand curve.
-However, on Steam individual firms choose which prices to charge for their product, and they should have a stronger preference for profit than an entity that is a marketplace, rather than a seller.
+However,  individual firms on Steam choose which prices to charge for their product, and they should have a stronger preference for profit than an entity that is a marketplace, rather than a seller.
 The situation becomes more clear after examining the coefficient on “New Discount”, an indicator variable for the first day after the introduction of the discount\footnote{I found the effect to be stronger if a one day lag is allowed}.
@@
 I then turn to data, and show that products are significantly more likely to sell at a discount when they are close to improving their review tier, while the effect for products that are close to sliding down a tier are much weaker.
-I use the stylized model to interpret these results, and conclude that further analysis is required in order to establish the relative contributions of the selection and the variance effects.
-This analysis is carried out in the next section.
+The extent to which the results are driven by the selection and the variance effects is then analyzed in the next section.
 
@@
 This would be the case for products with many reviews and an established review score.
-My interested is mostly in the other type of products, the ones that potentially can transition.
+My interest is mostly in the other type of products, the ones that potentially can transition.
 In those cases the decision to discount or not depends on the comparison between the value of the positive transition, $u^H$, the cost of giving a discount ($c$, or $c$ and $(1-p)u^L$), and the probability of a successful transition.
@@
 
-Theoretically, the sign of the selection effect of buying during a discount on the valence of reviews is ambiguous.
+Theoretically, the sign of the selection effect of buying during a discount on the favorability of reviews is ambiguous.
 Consumers who buy when the price is low could be a worse match for the product and, thus, leave worse reviews.
@@
 The successful outcome of the discount leads to a transition and the prize of $u^H$, while the unsuccessful one leaves the firm with the current review status, which is not that costly.
-If the upside payoff $u^H$ is high enough, then even if selection is negative ($p < 0.5$), the firm could still be willing to “pull the plug” and give a discount, with the sole purpose of gambling on the positive outcome.
+If the upside payoff $u^H$ is high enough, then even if selection is negative ($p < 0.5$), the firm could still be willing to give a discount, with the sole purpose of gambling on the positive outcome.
 I refer to  this idea as the “variance effect”.
@@
 
-Now that a simple theory of discounting close to a review threshold has been brought forward, I turn attention the data.
+Now that a simple theory of discounting close to a review threshold has been brought forward, I turn attention to the data.
 The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels on Steam are often preceded by discounts.
@@
 Regression analysis controlling for review label, number of reviews, age, day of the week and week time effects, as well as time since the previous discount, confirms that the association depicted in Figure \ref{discountsTransitions} is robust (see Table \ref{transitionReg} in the Appendix).
-A game is approximately `r round(reg1$coefficients[2]*14*100)` pp more likely to be on a discount on the day of the transition than it is two weeks prior to it, and it is `r round(-reg1$coefficients[3]*14*100)` pp less likely to be on a discount two weeks following the transition.
+A game is approximately `r round(reg1$coefficients[2]*14*100)` percentage points more likely to be on a discount on the day of the transition than it is two weeks prior to it, and it is `r round(-reg1$coefficients[3]*14*100)` pp less likely to be on a discount two weeks following the transition.
 Given that the probability for a game to be on a discount on a random day is `r round(panel[, mean((discount > 0), na.rm=T)]*100)`% in the sample, these effects amount to `r round(100*(reg1$coefficients[2]/panel[, mean((discount > 0), na.rm=T)]))`% and `r round(100*(-reg1$coefficients[3]/panel[, mean((discount > 0), na.rm=T)]))`% changes in the daily probability of a discount, which is quite sizable.
@@
 The `r 2*band` day cutoff is inspired by the maximum duration of custom discounts on Steam, and the patterns of discounting around successful transitions, depicted in Figure \ref{discountsTransitions}.
-To estimate the effect of being close to a review transition on the discounting behavior, I then estimate the following model:
+I obtain the effect of being close to a review transition on the discounting behavior by estimating the following linear probability model:
 \begin{equation}\label{potTransitionsReg}
@@
 First, I found that firms are more likely to go on a discount when their products are close to upgrading their review bin.
+This finding implies that the selection effect and the variance effect can not be both negative for games close to a review upgrade.
+While such a combination of the effects was theoretically possible, \emph{a priori} it never seemed to be the leading case.
 Second, I found only limited change in discounting behavior for products that are close to downgrading their review bins.
-The first finding implies that the selection effect and the variance effect can not be both negative for games close to a review upgrade.
-This is a weak conclusion, as finding the opposite would be really surprising.
-Moreover, it does not reveal if the selection effect is negative or positive.
-The second could be explained by either of the effects being negative, as well as them having opposite signs and contradicting each other, leading to a muted effect.
+This finding indicates that the variance effect should be important, but is still consistent with both a positive, and a negative selection effect.
 In this section I investigate the signs of the selection and variance effects in greater detail.
@@
 One would simply need to compare the fractions of positive and negative reviews left on and off discount.
-The variance effect is harder to strip down to a similar test.
-One way to prove the importance of the variance effect is to take my stylized model seriously, and to prove the absence of the selection effect in the data.
-In the absence of the selection effect, discounting decisions have to due to the variance effect.
-This idea could be further developed.
-Even if the selection effect is not zero, if one could quantify it, then “controlling” for the magnitude of the selection effect could shed light on the importance of the variance effect.
+The variance effect is harder to test.
+The strongest prediction of my stylized model regarding the variance effect is that, in the absence of the selection effect, a moderate amount of variance is welcomed by the products that are close to an upward transition, and is disliked by the products close to a downward transition.
+I develop this idea into a test, described below.
 Another way to evaluate the importance of the variance effect is to look at the extent to which a discount speeds up the arrival of reviews.
@@
 A formal model of reviewing behavior is necessary for several reasons.
-First, a structural model allows me to explicitly introduce the parameters of interest---probabilities of leaving a good or a bad review, on and off discount.
-With the estimates of these parameters I will be  able to quantify the selection effect.
-Such a measure, in turn, will allow me to control for the selection effect in the regression of discounting behavior on proximities to transition (\ref{potTransitionsReg}), shedding light on the importance of the variance effect.
-To further understand the latter, I also use the model to estimate the effect of a price promotion on the probability to leave reviews.
+First, a structural model allows me to explicitly introduce the parameters of interest---probabilities of leaving a good or a bad review, on and off a discount.
+With the estimates of these parameters at hand, I am able to quantify the selection effect.
+I then control for the selection effect in the regression of discounting behavior on proximities to transition (\ref{potTransitionsReg}).
+Using my estimates, I can consider a counterfactual in which the selection effect is absent, and check if the resulting effect is consistent with the variance effect.
+I also use the model to estimate the effect of a price promotion on the probability to leave reviews.
 Since sales are unobserved, it is impossible to say if the surge in reviews during a discount is entirely due to the influx of new customers, or if part of it is due to an increased willingness to leave a review during a discount.
-I use my model to estimate sales, and therefore I can make inference on the propensity to leave a review.
-Such inference can not be made without a model of demand or sales data, neither of which are common in the literature.
+I use my model to estimate sales, and therefore I can make inference on the propensity to leave a review, conditional on the good being discounted, gaining further insight into the origins of the variance effect.
 
@@
 The second hypothesis I am interested in is whether the selection effect is positive or not.
-Product's review score measures the fraction of positive reviews among all reviews left, reflecting the probability to get a good review *conditional* on having a review.
-Indeed, if $L_t \in \{0, 1\}$ is a random variable that takes the value of 1 if the $i$-th review is a like and 0 if it is a dislike, then the review score based on $T$ reviews would simply be $Score(T) = \frac 1 T \sum_{t=1}^T L_t$, which converges to $\EE{L_t} = \PP{L_t = 1}$ as $T$ grows to infinity.
+The review score of a product measures the fraction of positive reviews among all reviews left, reflecting the probability to get a good review *conditional* on having a review.
+Indeed, if $L_t \in \{0, 1\}$ is a random variable that takes the value of 1 if the $t$-th review is a like and 0 if it is a dislike, then the review score based on $T$ reviews would simply be $Score(T) = \frac 1 T \sum_{t=1}^T L_t$, which converges to $\EE{L_t} = \PP{L_t = 1}$ as $T$ grows to infinity.
 For a user buying a game off discount we have
@@
 Using data from Steam, a major digital marketplace for computer video games, I show that firms discount their products in order to facilitate transitions between review tiers.
-My estimates of the demand process indicate that better review tiers substantially increase sales, and that discounts are effective at attracting new users and, as a consequence, reviewers.
+My estimates of the demand process indicate that: (i) better review tiers substantially increase sales, (ii) that discounts are effective at attracting new users and, as a consequence, reviewers.
 Therefore, using price promotions to improve the review label of a game appears to be a plausible strategy.
-I find that products that are close to upgrading their review tier are 4-9% more likely to be on sale, while products close to deteriorating their review tier are up to 4% less likely to discount, albeit this effect is less significant.
+I find that products that are close to upgrading their review tier are 4-9% more likely to be on sale, while products close to deteriorating their review tier are up to 4% less likely to discount.
 
@@
 
-The variance effect reflects the asymmetry between a successful and an unsuccessful discounting campaign, as measured by the valence of the new reviews.
-A product close to moving one review tier up benefits greatly from a good realization, while a bad might not change its review tier.
+The variance effect reflects the asymmetry between a successful and an unsuccessful discounting campaign, as measured by how favorable the new reviews are.
+A product close to moving one review tier up benefits greatly from a good realization, while a bad one might not change its review tier.
 On the other hand, a product that is close to sliding into a worse tier is averse to a bad outcome, and would benefit little from a good outcome.
@@
 
-\noindent Notice that the weights drop out of the first two conditions.
-As for the last condition, observe that the moment condition $\CE{u_{it}}{y_{it-1}, x_{it}} = 0$ implies $\EE{x_{it}u_{it}} = 0$, and, thus, the sum in the F.O.C.
-converges to 0 as $n \to \infty$ under any set of weights:
-$$\frac{1}{nT_i}\sum_{i=1}^n \sum_{t=2}^{T_i} w_i(y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))\lambda_ix_{it}
+\noindent Notice that the weights drop out of the first two conditions: as I scale all observation within a product by the same weight, it has no effect on the identification of the product specific parameters $\lambda_i$ and $\psi_i$ (conditional on $\beta$).
+As for the last condition, observe that the moment condition $\CE{u_{it}}{y_{it-1}, x_{it}} = 0$ implies $\EE{x_{it}u_{it}} = 0$ under the true parameter values.
+Thus, the sum in the F.O.C.
+converges to 0 as $(\min_{i}T_i) \to \infty$ under any set of weights:
+$$\frac{1}{n}\sum_{i=1}^n \frac{1}{T_i}\sum_{t=2}^{T_i} w_i(y_{it} - \psi_i y_{it-1} - \lambda_i(1+x'_{it}\beta))\lambda_ix_{it}
 =
@@
 observations, we get that the values of \(\hat \lambda_i,\hat \psi_i\) that solve (\ref{regFOC1})-(\ref{regFOC2}) are given by
+
 \begin{equation}\label{psilambda}
@@
 
-The asymptotic covariance matrix for \(\hat \theta\) in a nonlinear
-LS problem \(\sum_i (y_i - m(x_i, \theta))^2\) is estimated using the sample analog of
-\begin{equation}
+The asymptotic covariance matrix for \(\hat \theta\) in a nonlinear cross-section
+LS problem \(\sum_i (y_i - m(x_i, \theta))^2\) is given by the sample analog of
+\begin{equation}\label{csvariance}
 \mathbf V_\theta = \left(\mathbb{E}\left[m_{\theta i}m_{\theta i}'\right]\right)^{-1}
                 \mathbb{E}\left[m_{\theta i}m_{\theta i}'e_i^2\right]
-                \left(\mathbb{E}\left[m_{\theta i}'m_{\theta i}\right]\right)^{-1},
+                \left(\mathbb{E}\left[m_{\theta i}m_{\theta i}'\right]\right)^{-1},
 \end{equation}
@@
 \(m_{\theta i} = \frac{\partial}{\partial \theta} m(x_i, \theta_0)\),
-\(e_i = y_i - m(x_i, \theta_0)\) [@Hansen20, p.751]. More details could be found in the code.
-
+\(e_i = y_i - m(x_i, \theta_0)\) [@Hansen20, p.751].
+I extend this approach to my panel setting as follows\footnote{I rescaled the data by the weights $w_i$ for estimation, so the expressions below do not feature the weights}.
+For product $i$ the concentrated conditional expectation function and its derivative are given by
+\begin{align}
+ m(y_{it-1}, x_{it}, \beta) & = \psi_i(\beta) y_{it-1} + \lambda_i(\beta)(1+x'_{it}\beta)\\
+  m_{\beta it} & := \frac{\partial}{\partial \beta} m(y_{it-1}, x_{it}, \beta) 
+ = \frac{\partial \psi_i(\beta)}{\partial \beta} y_{it-1} + \frac{\partial \lambda_i(\beta)}{\partial \beta} (1+x'_{it}\beta) + \lambda_i(\beta)x_{it}.
+\end{align}
+
+I then make the following analogy between the (sample analogs of) cross-section expressions in (\ref{csvariance}) and their panel data analogs
+$$ \frac{1}{n}\sum_{i=1}^n m_{\theta i}m_{\theta i}' \sim 
+\frac{1}{n}\sum_{i=1}^n \frac{1}{T_i}\sum_{t=2}^{T_i} m_{\beta it}m_{\beta it}'$$
+
+The resulting expression for the estimator of the variance of $\hat \beta$ is 
+\begin{equation}\label{panelvariance}
+\left(\frac{1}{n}\sum_{i=1}^n \frac{1}{T_i}\sum_{t=2}^{T_i} m_{\hat \beta it}m_{\hat \beta it}'\right)^{-1}
+\left(\frac{1}{n}\sum_{i=1}^n \frac{1}{T_i}\sum_{t=2}^{T_i} m_{\hat \beta it}m_{\hat \beta it}' \hat u_{it}^2 \right)
+\left(\frac{1}{n}\sum_{i=1}^n \frac{1}{T_i}\sum_{t=2}^{T_i} m_{\hat \beta it}m_{\hat \beta it}'\right)^{-1},
+\end{equation}
+
+\noindent where $\hat u_{it} = y_{it} - \hat \psi_i y_{it-1} - \hat \lambda_i(1+x'_{it}\hat \beta)$.
 \newpage

### 2020-11-02 Analysis/Code/Sorokin_JMP_2020.Rmd
Proofreading

@@
   This paper documents that firms in online marketplaces use price promotions to facilitate transitions to better review tiers (similar to the number of stars on Amazon.com).
-I find that firms close to going one tier up are 4-9% more likely to discount.
+I find that firms close to upgrading their tier are 4-9% more likely to discount.
 Two effects could be at play.
@@
 In order to understand the relative contributions of these effects, I estimate a tractable structural model of demand and reviewing behavior.
-I find evidence of the importance of the variance effect: when the selection effect is controlled for, firms close to downgrading their review tier are 6% less likely to give a discount, consistent with preferring less variance.
+I find evidence of the importance of the variance effect: when the selection effect is controlled for, firms close to downgrading their review tier are 6% less likely to give a discount, consistent with them preferring less variance.
 I also find that consumers are significantly more likely to leave reviews during a discount.
 The average selection effect turns out to be small.
-Additional findings include developing a new approach to estimating demand from data on product usage, estimates of the causal effect of reviews on sales and equilibrium discount elasticities in an important market not previously studied.
+Additional findings include the development of a new approach to estimating demand from data on product usage, estimates of the causal effect of reviews on sales, and equilibrium discount elasticities in an important market that has not been previously studied.
   \thispagestyle{empty}
@@
 Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services.
-Both extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews are important, if not crucial, for a business's success.
+Both extensive literature in marketing and anecdotal evidence from these markets suggest that good reviews are important, if not crucial, for a business's success.
 Not surprisingly, firms take an active approach to managing their reviews.
@@
 Customers who purchase the good during a discount are likely to be different from those who pay the full price and could leave different reviews.
-If reviews left during a discount tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on sale, as new customers are likely to leave positive reviews and help the product advance to the next review tier.
+If reviews left during a discount tend to be more favorable, then the induced positive selection effect creates an incentive for the product to go on sale, as new customers are likely to leave positive reviews and help the product advance to the next review tier.
 However, these new customers could also prove to be a worse match with the product and leave less favorable reviews.
-Thus, the sign of the selection effect is ultimately an empirical question.
-Previous work studying the selection effect in digital markets produced mixed findings.
+Therefore, the sign of the selection effect is ultimately an empirical question.
+Previous work studying the selection effect in digital markets has produced mixed findings.
 Some of the papers that documented a negative selection effect struggle to explain why firms run promotions which are unlikely to be profitable and are unlikely to attract positive reviews (see the Literature Review section).
@@
 The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier.
-Additional positive reviews can catapult it to the next review bin, which promises higher sales.
+Additional positive reviews can propel it to the next review bin, which promises higher sales.
 In contrast, a few negative reviews might not affect its review tier---and, therefore, sales---by much.
@@
 I use this model to lay the groundwork for my analysis, as it helps me confirm the importance of better review tiers for sales on Steam.
-Compared to a mediocre review tier, the best tier comes with a premium of as high as 10% in additional sales, and the worst one entails a 13% reduction in sales.
+Compared to a mediocre review tier, the best tier comes with a premium of as high as 10% in additional sales, while the worst tier entails a 13% reduction in sales.
 My estimates also highlight how impactful discounts are in this market, with an average discount accompanied by a 38% spike in sales.
@@
 I then employ my structural model to disentangle the relative contributions of the variance and the selection effects to the observed discounting patterns.
-To that end, I estimate the effect of discounts on the probabilities to leave positive and negative reviews.
+To that end, I estimate the effect of discounts on the probability of a product receiving a positive or a negative review.
 I find no evidence that selection is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion.
@@
 I estimate the size of the selection effect at the product level and control for it in my regressions of discounts on proximities to transition.
-I find that, in the absence of the selection effect, products close to a review downgrade are 6% less likely to discount---an increase in both the size and the significance of the effect compared to the specification that does not control for the selection effect.
+I find that, in the absence of the selection effect, products close to a review downgrade are 6% less likely to discount---an increase in both the size and the significance of the effect compared to the specification which does not control for the selection effect.
 This finding is consistent with the idea that such products are averse to variance in their review scores.
-I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which discounts create “variance”.
+I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which discounts create “variance.”
 
@@
 Such a model would exhibit a complicated joint dynamics of review, sales, and price processes.
-A period of aggressive discounting would help a new product attract customers and transition to the best review tier it can, and would then be followed by a period of high prices that exploit the accumulated reputation.
+A period of aggressive discounting would help a new product attract customers and transition to the best review tier attainable, and would then be followed by a period of high prices that exploit the accumulated stock of reviews.
 This study serves as a laboratory that isolates some of the effects present in such a model and foreshadows some of the findings and issues that could emerge from it.
@@
 Theoretical advancements have been recently made in understanding separate components of the ideal system, such as exploration of new products vs.
-exploitation of the established options [@cheHorner18], creation of incentives for firms to invest in quality [@AperjisJohari10], promotion of competition, and reduction of barriers to entry [@Vellodi20]---to name just a few topics and contributions.
+exploitation of the established options [@cheHorner18], creation of incentives for firms to invest in quality [@AperjisJohari10], promotion of competition, and reduction of barriers to entry [@Vellodi20], to name just a few topics and contributions.
 At the heart of every such inquiry lies a particular strategic interaction between firms, users, and the platform.
-My paper provides empirical evidence on what some of these interactions result in.
-I show that firms respond to the tier structure of review systems by changing their pricing behavior around the thresholds and that they use pricing to affect their review process.
+My paper provides empirical evidence on the results of some of these interactions.
+I show that firms respond to the tier structure of review systems by changing their pricing behavior around the review tier thresholds and that they use pricing to affect their review process.
 My estimates can inform future work that will synthesize theoretical and data-driven insights to make concrete design recommendations.
-For example, @Vellodi20 shows that entry barriers resulting from the low speed of review accumulation by new firms call for a review system that censors the reviews of the most established products.
+For example, @Vellodi20 shows that entry barriers resulting from the low speed of review accumulation by new firms necessitate a review system that censors the reviews of the most established products.
 However, when firms can offer lower prices to build up the crucial review base, the need for the design intervention is diminished.
@@
 In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from video games' usage data.
-I inherit the data from that paper, but confront the absence of sales data in a new way: by formulating a structural model of the data generating process.
+I use the data from that paper, but confront the absence of sales data in a new way: I formulate a structural model of the data generating process.
 With the help of this model, I manage to extract information on product sales from usage data.
@@
 This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes.
-@ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to.
+@ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the sentiment and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they may receive a response.
 In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage unfavorable review activity.
@@
 However, direct ways of managing online reputation discussed above are not the only avenues through which businesses can affect their reviews.
-Another strand of literature is studying whether price promotions have an effect on firms' online reputation.
+Another strand of literature is concerned with whether price promotions have an effect on firms' online reputation.
 In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a price promotion through Groupon, a promotion service.
 In other words, @ByersEtAl12 documents a negative selection effect on Yelp.
-It presents evidence that customers attracted by promotion are different from regular customers and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher.
+It presents evidence that customers attracted by a promotion are different from regular customers---and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher.
 Worse match quality between the restaurants and the exploring Groupon customers could explain the dip in the review score following a price promotion.
 @Li16 confirms the finding in the same market but finds that restaurants with fewer and worse reviews can benefit from participating in a Groupon promotion.
-There are a couple of other studies that dispute the negativity of the selection effect.
+There are a few other studies that dispute the negativity of the selection effect.
 @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative reviews.
@@
 To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, finding a negative selection effect in the data presents a puzzle\footnote{Direct profitability of Groupon promotions is questionable; see \citet{Dholakia11}.}.
-A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free to build a reputation and escape the "zero reviews trap".
-While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which undermines the strategy.
+A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free to build a reputation and escape the "zero reviews trap." While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which undermines the strategy.
 I provide a novel mechanism---the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative.
-The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it will find it profitable to sell for free even if the probability to solicit favorable reviews is small.
+The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it will find it profitable to sell for free even if the probability of soliciting favorable reviews is small.
 After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial.
@@
 Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} with a model of reviewing activity and estimates its parameters to quantify the relative contributions of the selection and the variance effects to observed patterns of discounting around review transitions.
-Section \ref{conclusion} concludes.
+Section \ref{conclusion} concludes the paper.
 
@@
 Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it  earned around \$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames].
-Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion
+Given the ongoing unprecedented growth in the size of the video games' market [\$43.4 billion
 in 2018, about the size of the U.S.
 film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD, Steam is a major player in an increasingly more important industry.
-Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to stuy in its own right.
+Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to study in its own right.
 
@@
 Steam is, thus, different from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews).
-This gives me confidence in the authenticity of most reviews.
+This lends me confidence in the authenticity of most reviews.
 This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors [@steamPurge].
-With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave scrupulously.
-
-A review consists of a binary grade, "thumbs up" or "thumbs down", and text.
+With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave ethically.
+
+A review consists of a binary grade, "thumbs up" or "thumbs down," and text.
 A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews.
@@
 These labels\footnote{I use the words “tier”, “bin”, and “label” interchangebly througout the text} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”}.
-For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.
+For example, a game with 7 positive and 2 negative reviews would not have a review score nor a label, but an extra positive review would promote it to the “Positive” bin.
 
@@
 
-Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc.
+Steam's homepage welcomes customers with a selection of featured games.
+This selection could include new games, popular games that are currently on a discount, games that have recently released a major update, etc.
 [@steamVisibility].
@@
 Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has.
-I use this feature of Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main explanatory review variables, rather than, say, the review score or the review texts.
+I use this feature of Steam's store to rationalize why I choose to focus on the review labels as my main explanatory review variables later in the analysis, rather than, say, the review score or the review texts.
 Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place.
 @deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an homage to the masterfully chosen title of \citet{deLanghe15}.}.
-Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales.
+Thus, I conjecture that games with better review labels will attract more customers and have higher sales, other things equal.
 Crucially, according to Steam's documentation, all review labels better than “Negative” have a very similar contribution to visibility on the platform, which implies, among other things, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2].
@@
 Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB.
-More importantly, Steam Database contains time series of prices and player activity for each game on Steam on a daily level.
+However, Steam Database also contains time series of prices and player activity for each game on Steam on a daily level.
 In principle, the pricing information could be obtained by a repeated scraping of the store.
-However, the player activity information is not trivial to obtain, as Steam does not directly reveal such data, let alone the data on sales of different titles.
-The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community most certainly implies that they are doing the best they can.
+However, the player activity information is not trivial to obtain, as Steam does not directly provide such data, let alone the data on sales of different titles.
+The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community certainly implies that they are doing the best they can.
 The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent players for each game on a daily basis.
@@
 @SorokinStevens20 studies the causal effect of reviews on sales on Steam, and I mirror closely the sample selection procedure used in that paper.
-First, Steam has made some significant changes to its review system in late 2016, and one of the effects was the removal of a big number of reviews from the review score calculation.
+First, Steam made some significant changes to its review system in late 2016, and one of the effects was the removal of a large number of reviews from the review score calculation.
 While it could be an intervention that is worthy of an independent study, in practice combining the data from before and after the intervention led to unsound results, so I focus on the two year period from January 2017 to January 2019, keeping the review system as stable as possible.
-In particular, only games that were released in this time period make it to the sample.
-
-Second, online multiplayer games and games that update frequently are dropped from the sample, as these are products whose quality is changing a lot over time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience.
+In particular, only games that were released in this time period are included in the sample.
+
+Second, online multiplayer games and games that update frequently are dropped from the sample, as these are products whose quality changes a lot over time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience.
 I used these update announcements to measure the number of updates each game had.
@@
 Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}.
-Unobserved dynamic quality would present a big obstacle to the identification of the effect of reviews on discounting decisions or sales.
+Unobserved dynamic quality would present a significant obstacle to the identification of the effect of reviews on discounting decisions or sales.
 Consider a game that has just issued a major update.
@@
 A game can have a launch discount, but, otherwise, it has to wait for two months since the release before changing its price or giving a discount.
-A game can not go on discounts too frequently, and has to wait between four to six weeks after a price promotion to be able to run a new one.
+A game can not have discounts too frequently; it has to wait between four to six weeks after a price promotion to be able to run a new one.
 The duration of a custom discount is restricted to be at least one full day, and at most two weeks.
-Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on sale.
+Besides these custom discounts, which are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on sale.
 As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”.
@@
 
-Despite the relative rigidity of the review score, there is enough transitions between review bins to make the analysis of pricing decisions by firms around such transitions possible.
+Despite the relative rigidity of the review score, there are enough transitions between review bins to make the analysis of pricing decisions by firms around such transitions possible.
 Table \ref{tab:transitionMatrix} describes the transitions between review bins in the sample.
@@
 While the answer might be obvious for large sought-after products, the situation is less clear for an average game.
-The second question is: how big are the differences between various review tiers?
+The second question is how big are the differences between various review tiers?
 If transitioning to a better tier does not increase sales by much, then firms would be unlikely to pursue such transitions when making their discount decisions.
@@
 An average discount in the sample increases sales by 38% upon introduction, and by another 3-12% every day thereafter.
-These two facts form the foundation of my analysis of discounting behavior on a verge of a review tier transition that will be carried out in Section \ref{descriptiveEvidence}.
+These two facts form the foundation of my analysis of discounting behavior on the verge of a review tier transition that I will carry out in Section \ref{descriptiveEvidence}.
 I will further extend the model from this section by modeling the reviewing behavior of customers in Section \ref{selectionEffect}.
@@
 Define *active players* of this game, \(A_{it}\), to be the customers who have already purchased the game and are still playing it, either because they have not yet completed it, or because they are not bored with it yet.
-This number  has an empirical counterpart in the player count variable, observable to the econometrician.
+This number  has an empirical counterpart in the player count variable, which is observable to the econometrician.
 The game loses \(E_{it}\) active players on day \(t\), which is also not observed.
@@
 
-Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about these variables in order to be able to disentangle their contributions to the observed player counts.
+Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about these variables to disentangle their contributions to the observed player counts.
 
@@
 of observable characteristics \(x_{it}\) of the game that affect demand:
-price, reviews, age of the game, or seasonal factors\footnote{I do not impose a restriction that $\lambda_{it}$ should be non-negative in estimation.
-Only 4% of day-product pairs in my data will end up having negative predicted sales, which I take as a sign of a good model fit.}.
+price, reviews, age of the game, or seasonal factors\footnote{I do not impose a restriction that \(\lambda_{it}\) should be non-negative in estimation.
+Only 4\% of day-product pairs in my data will end up having negative predicted sales, which I take as a sign of a good model fit.}.
 The mapping between these variables and the number of copies sold is the demand curve for game $i$.
 Buyers of the game then become active players, and are subject to a fixed daily risk of $1-\psi_i$ of abandoning the game.
-Given that the number of active players “flipping” this coin at the end of day $t-1$ is $A_{it-1}$, this process gives rise to the binomial distribution for the number of exiters.
+Given that the number of active players “flipping this coin” at the end of day $t-1$ is $A_{it-1}$, this process gives rise to the binomial distribution for the number of exiters.
 The demand model is fully parametrized by the vector $(\{\lambda_i, \psi_i\}_{i = 1}^n, \beta)$.
@@
 For a given decay parameter, the level at which the player count settles identifies the flow rate of new buyers.
-Given that identifying the exit rate is crucial for teasing out the sales component, it is a great advantage of my model that it allows full heterogeneity in the exit rate $(1-\psi_i)$.
+Given that identifying the exit rate is crucial for teasing out the sales component, it is a significant advantage of my model that it allows full heterogeneity in the exit rate $(1-\psi_i)$.
 
@@
 
-Another important reason for insisting on estimating the relative effects stems from the limitations of my data.
+Another important reason for estimating the relative effects stems from the limitations of my data.
 Recall that the player count variable measures only the *maximum concurrent* number of active players every day.
-This implies that the estimated values of $\lambda_{it}$ would take into account only those new buyers who contribute to gaming activity during the “rush hour”.
-An implicit assumption in my analysis is that new buyers of the game choose their gaming time following some fixed game-specific distribution.
-I use this assumption to say that, if the number of new active players during rush hour goes up by 1%, then sales go up by 1% across all types of players,  not only among the "rush hour ones".
-
-Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model (\ref{arrivalReg}), and guarantees identification of all parameters, as long as there is sufficient variation in the data.
+This implies that the estimated values of $\lambda_{it}$ would take into account only those new buyers who contribute to gaming activity during the “rush hour.” An implicit assumption in my analysis is that new buyers of the game choose their gaming time following some fixed game-specific distribution.
+I use this assumption to say that, if the number of new active players during rush hour goes up by 1%, then sales go up by 1% across all types of players,  not only among the “rush hour” ones.
+
+The condition \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model (\ref{arrivalReg}), and guarantees identification of all parameters, as long as there is sufficient variation in the data.
 Of course, this is only true as long as equation (\ref{arrivalReg}) is the right model of the data generating process.
@@
 However, I argue that (\ref{arrivalReg}) is an adequate specification if the goal is to estimate the causal effect of reviews on sales, or to get a predictive model of demand.
-First and foremost, the reviews are not a choice variable of a firm, and rather serve as a state variable that a firm takes as given every day.
+The key observation is that reviews are not a choice variable, and rather serve as a state variable that a firm takes as given every day.
 Of course, there are various things that a firm can do, that can, in a non-guaranteed fashion, affect this variable.
@@
 Any intervention that is correlated with discounts will be attributed to the price variable.
-Second, recall that the way I constructed the  sample  rules out the possibility of an omitted variable bias stemming from a number of variables that could collectively be referred to as “changing quality”.
-The games in the sample are single player games, and thus are not subject to time-varying network externalities or frequent quality updates that could be correlated with reviews, depths of discounts, or the player count.
-Third, game specific effect $\lambda_i$ controls for all time-invariant characteristics of game $i$ that determine average sales: initial marketing budget, extraneous popularity of the game's plot or setting, etc.
+On top of that, the way I constructed the  sample  rules out the possibility of an omitted variable bias stemming from a group of variables that could collectively be referred to as “changing quality”.
+The games in the sample are single player games, and thus are not subject to time-varying network externalities or frequent quality updates that could be correlated with reviews, size of discounts, or the player count.
+Finally, game specific effect $\lambda_i$ controls for all time-invariant characteristics of game $i$ that determine average sales: initial marketing budget, extraneous popularity of the game's plot or setting, etc.
 Similarly, I employ a set of time effects to control for important within-week seasonality in gaming patterns and for the extensive platform-wide sales.
@@
 First, I believe that standard concerns about the endogeneity of prices are not directly applicable in my context.
-The reason for that is the high frequency nature of the data and the stickiness of posted prices.
+The reason for this is the high frequency nature of the data and the “stickiness” of posted prices.
 Using the classic notation, imagine that a discount is given on date $t$, and we observe a quantity-price pair $(Q_t, P_t)$, both of which are different from their yesterday's counterparts $(Q_{t-1}, P_{t-1})$.
@@
 A deeper problem for identifying the price elasticity of demand lies in defining precisely the elasticity of interest.
-A video game is a durable good, and some consumers could be purchasing it strategically, thinking about the probability and depth of discounts that they could get in the near future.
+A video game is a durable good, and some consumers could be purchasing it strategically, thinking about the probability and size of discounts that they could get in the near future.
 In particular, Steam allows users to add any game to their wishlist, which means that they would be notified about promotions affecting that game.
-Later in the results section we will see that the lion's share of sales on a discount takes place on the first day of the discount, which is consistent with users waiting for a discount and buying the game when the discount goes live.
+Later in the results section we will see that the lion's share of sales on a discount take place on the first day of the discount, which is consistent with users waiting for a discount and buying the game when the discount goes live.
 For studying counterfactual price policies one would need to specify a more complicated model of forward-looking consumers, and estimate the fundamentals of their behavior.
@@
 $$
-\noindent would be price, review label, score, log reviews, age, and a set of day of the week and sample week time effects.
+\noindent would be price, review label, score, log reviews, age (days since release on Steam), and a set of day of the week and sample week time effects.
 However, this proved to be computationally infeasible.
@@
 The reason to include these week effects is to account for platform-wide shocks.
-The biggest shocks shared by games on Steam are Seasonal Sales.
-These sales take place around major holidays, and, thus, blend together the increased platform-wide demand due to holidays with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSalesPeriods}).
+The biggest shocks shared by games on Steam are seasonal sales.
+These sales take place around major holidays, and, thus, blend the increased platform-wide demand due to holidays together with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSalesPeriods}).
 To capture these periods in a parsimonious way, I calculated the average daily discount in the sample, and labeled the days when the average discount exceeded 20\% as days of the Seasonal Sale.
@@
 
-Column (1) in Table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column (2) presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates; finally, column (3) reports the results of estimating the log-regression with the ideal set of covariates (using week effects instead of the Seasonal Sale dummy).
+Column (1) in Table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column (2) presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates.
+Column (3) reports the results of estimating the log-regression with the ideal set of covariates (using week effects instead of the Seasonal Sale dummy).
 It is readily checked that the difference between the preferred log-regression in column (3) and its restricted analog in column (2) is very small.
@@
 The latter effect can not possibly be taken at face value, given that the most exclusive review label, "Overwhelmingly Positive",  increases sales by at most `r round(beta.hat[11]*100)`% compared to the baseline.
-It would be possible to explain such large estimates by high levels of demand  when the game is young and is likely to have less than 10 reviews, but I control for being “young” by including the dummy for being less than 14 days of age\footnote{A two weeks cutoff is inspired by high speed of review arrival documented in Figure \ref{reviewDescriptivePlots}}.
-Thus, the coefficient on “No Score” is identified by games that exit this bin later than their first two weeks.
+It would be possible to explain such large estimates by high levels of demand  when the game is young and is likely to have less than 10 reviews, but I control for this channel by including the dummy for being less than 14 days of age\footnote{A two weeks cutoff is inspired by high speed of review arrival documented in Figure \ref{reviewDescriptivePlots}}.
+Thus, the coefficient on “No Score” is identified by games that exit this bin after their first two weeks.
 Such games constitute `r round(100*panel[noScore==T & age>=14, length(unique(ID))]/info[,.N])`% of the sample, and are probably different from the rest of the games.
@@
 The situation becomes more clear after examining the coefficient on “New Discount”, an indicator variable for the first day after the introduction of the discount\footnote{I found the effect to be stronger if a one day lag is allowed}.
-As I have mentioned in the Identification section, the durable good nature of video games means that forward-looking behavior by consumers could lead to different price elasticities for short-lived promotions and long-term price changes, and the difference between the price coefficient and the indicator for the start of a discount could capture precisely that distinction.
+As I have mentioned in the Identification section, the durable good nature of video games means that forward-looking behavior by consumers could lead to different price elasticities for short-lived promotions and long-term price changes.
+The difference between the price coefficient and “New Discount” could capture precisely that distinction.
 I find that, on average, a discount leads to a `r round(beta.hat[2]*100)`-`r round(reg2$coefficients[3]*100)`% spike in sales upon introduction.
@@
 The outcome depends on whether the additional customers who buy the product during the discount happen to leave more positive or more negative reviews, and on the volume of the new reviews relative to the existing ones.
-To reflect that, assume that with probability $p$ firm's status becomes $s+x$, and with probability $1-p$ it becomes $s-x$.
+To reflect that, I assume that with probability $p$ firm's status goes up by $x$ to $s+x$, while with probability $1-p$ it goes down to $s-x$.
 The symmetry is purely for expositional purposes.
@@
 \noindent The firm would choose to start a price promotion if $\EE{U(s+X)}  > 0$.
-If $x < 1-s$, the firm simply can not induce enough change to its review status, and would not give a discount, unless $c < 0$ (i.e, other factors make giving a discount attractive).
+If $x < 1-s$, the firm simply can not induce enough change to its review status, and would not give a discount, unless $c < 0$ (i.e., other factors make giving a discount attractive).
 This would be the case for products with many reviews and an established review score.
-My interest is mostly in the other type of products, the ones that potentially can transition.
-In those cases the decision to discount or not depends on the comparison between the value of the positive transition, $u^H$, the cost of giving a discount ($c$, or $c$ and $(1-p)u^L$), and the probability of a successful transition.
+My interest is mostly in the other type of products---the ones that potentially can transition.
+In those cases, the decision to discount or not depends on the comparison between the value of the positive transition, $u^H$, the cost of giving a discount ($c$, or $c$ and $(1-p)u^L$), and the probability of a successful transition.
 If the probability of success is high, the firm is more likely to launch a discount.
@@
 I refer to  this idea as the “variance effect”.
-Even if the firm does not expect the new reviews to be favorable in expectation, they could still turn out to be positive, and if the reward is high enough, discounting could be worth the risk.
+Even if the firm does not expect the new reviews to be favorable, there is still potential that they may be.
+Therefore, if the reward is high enough, discounting could be worth the risk.
 
@@
 First, if $x \ge s$, then a negative realization could push the product down one review tier.
-A more important case is the one of a firm that is closer to a review downgrade rather than an upgrade, i.e.
-when $s < 0.5$.
+A more important case is one in which a firm is closer to a review downgrade rather than an upgrade, i.e., when $s < 0.5$.
 Following the logic of (\ref{discTradeoff}), we can see that for intermediate values of the change in review status ($x \in [s, 1-s)$) such a firm does not benefit from a discount.
@@
 Now that a simple theory of discounting close to a review threshold has been brought forward, I turn attention to the data.
-The departing point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels on Steam are often preceded by discounts.
+The starting point of the analysis is Figure \ref{discountsTransitions}, which shows that transitions between review labels on Steam are often preceded by discounts.
 The graph shows that two weeks prior to a transition only `r transPanel[tToTransit==-14, round(mean(100*(discount > 0)))]`% of games are on a discount, essentially the sample average, but that this number more than doubles to around `r transPanel[tToTransit==-1, round(mean(100*(discount > 0)))]`% one day before the label change.
@@
 In other words, firms could be giving discounts for reasons unrelated to reviews, but transitions sometimes would follow as a result.
-As a matter of fact, suppose my theory is correct and firms try to achieve transitions via price promotions.
-In that case, discounts *have* to be able to aid transitioning, making the reverse causality inherent in this setting.
+In fact, suppose my theory is correct and firms try to achieve transitions via price promotions.
+In that case, discounts *must* be able to aid transitioning, making the reverse causality inherent in this setting.
 The reverse causality would also explain why both review upgrades and downgrades are preceded by discounts.
@@
 One approach would be to use the raw review count, and to say that a game is close to upgrading its review label when it needs some fixed number of new positive reviews to transition.
-However, given the heterogeneity in the popularity of different games (see Figure \ref{sampleSizeHist}), five extra reviews could be nothing for a very popular game, and hard to acquire for a small game.
-For this reason I use a different approach, and measure proximity by the expected number of \emph{days} that a game has to wait to accumulate the reviews necessary for a transition.
+However, given the heterogeneity in the popularity of different games (see Figure \ref{sampleSizeHist}), five extra reviews could be negligible for a very popular game, and hard to acquire for a small game.
+For this reason, I use a different approach, and measure proximity by the expected number of \emph{days} that a game has to wait to accumulate the reviews necessary for a transition.
 In particular, for every game-date pair I first measure how many positive reviews that game needs at the moment to upgrade its review bin, and how many negative reviews that game needs to downgrade its review bin.
-In the next step, for each game I calculate the average speeds of review arrival, by simply dividing the number of positive (negative) reviews as of the last day in the sample by the age of the game on that day.
+Next, I calculate the average speeds of review arrival for each game by dividing the number of positive (negative) reviews as of the last day in the sample by the age of the game on that day.
 Knowing the speeds of positive and negative review arrivals, and the  number of reviews necessary for a transition, I then define the proximity to a positive (negative) transition to be the expected number of days needed for the game to accumulate the necessary number of positive (negative) reviews, assuming that it does not receive any negative (positive) reviews during that time.
@@
 The `r 2*band` day cutoff is inspired by the maximum duration of custom discounts on Steam, and the patterns of discounting around successful transitions, depicted in Figure \ref{discountsTransitions}.
-I obtain the effect of being close to a review transition on the discounting behavior by estimating the following linear probability model:
+I determine the effect of being close to a review transition on the discounting behavior by estimating the following linear probability model:
 \begin{equation}\label{potTransitionsReg}
@@
 \noindent $disc_{it} = \mathds{1}\{Discount_{it} > 0\}$ is a dummy measuring if the game is on a discount or not, $X_{it}$ is a set of control variables that includes log proximities to positive and negative transitions, log review count, score, review bin dummies, age, a set of game-level fixed effects $f_i$, and a set of day of the week and week time effects $\tau_t$.
-These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a big number of games at the same time, as depicted in Figure \ref{seasonalSalesPeriods}.
+These time effects are especially important to include in the regressions with discounting variables on the left hand side, because Steam's curated discounts all start on predetermined days of the week, and seasonal sales affect a large number of games at the same time, as depicted in Figure \ref{seasonalSalesPeriods}.
 My model of discounting behavior highlighted that any sign of $\beta^+$ and $\beta^-$ is possible, albeit suggesting that $\beta^+ > \beta^-$, as the variance effect is more likely to benefit a firm close to a review upgrade.
@@
 Notice that the inclusion of both the distance to a potential positive and a potential negative transition in the regression forces me to drop all observations from the lowest ("Negative") and the highest ("Overwhelmingly Positive") review bins, as for games in those bins only one direction of review transition is possible.
-However, given that the proportion of such observations in the sample is quite small, this is not a big concern.
+However, given that the proportion of such observations in the sample is quite small, this is not a significant concern.
 The analysis also excludes the observations with a “No Review Score” label, as I do not want to take a stance on what constitutes an improvement or a deterioration of the review score for such games.
 My demand estimates presented in Table \ref{demandEstimates} suggest that having no reviews could be the worst review bin a game could be in, but then I would again have to exclude this label as one that does not admit review deterioration.
-In any case, games that spend a lot of time in “No Score” have, by construction, very few reviews, which makes them rather unlikely to ever be one one or two weeks away from a transition according to my measure.
+In any case, games that have “No Score” for a long time have, by construction, very few reviews, which makes them rather unlikely to ever be one one or two weeks away from a transition according to my measure.
 
 The results of estimating Equation (\ref{potTransitionsReg}) are presented in Table \ref{potentialTransitionsResults}.
-Column one is the preferred specification, while column tow uses a more stringent definition of proximity to a transition, requiring a game to be `r band`, rather than `r 2*band`, days away from a potential transition to be counted as being “close to a transition”.
+Column one is the preferred specification, while column two uses a more stringent definition of proximity to a transition, requiring a game to be `r band`, rather than `r 2*band`, days away from a potential transition to be counted as being “close to a transition”.
 The results in Table \ref{potentialTransitionsResults} unequivocally support the hypothesis that proximity to a review bin upgrade increases firms' willingness to run a price promotion.
@@
 As we see, even though my empirical investigation has resolved the theoretical ambiguity of the signs and the significance of the effects, it did not shed much light on the balance of the underlying forces behind these effects.
-I proceed to investigating the two effects in greater detail now.
+I investigate the two effects in greater detail in the following section.
 
@@
 Using my estimates, I can consider a counterfactual in which the selection effect is absent, and check if the resulting effect is consistent with the variance effect.
-I also use the model to estimate the effect of a price promotion on the probability to leave reviews.
+I also use the model to estimate the effect of a price promotion on the probability that a review will be submitted.
 Since sales are unobserved, it is impossible to say if the surge in reviews during a discount is entirely due to the influx of new customers, or if part of it is due to an increased willingness to leave a review during a discount.
@@
 The review score of a product measures the fraction of positive reviews among all reviews left, reflecting the probability to get a good review *conditional* on having a review.
-Indeed, if $L_t \in \{0, 1\}$ is a random variable that takes the value of 1 if the $t$-th review is a like and 0 if it is a dislike, then the review score based on $T$ reviews would simply be $Score(T) = \frac 1 T \sum_{t=1}^T L_t$, which converges to $\EE{L_t} = \PP{L_t = 1}$ as $T$ grows to infinity.
+Indeed, if $L_t \in \{0, 1\}$ is a random variable that takes the value of 1 if the $t$-th review is a “like” and 0 if it is a “dislike”, then the review score based on $T$ reviews would simply be $Score(T) = \frac 1 T \sum_{t=1}^T L_t$, which converges to $\EE{L_t} = \PP{L_t = 1}$ as $T$ grows to infinity.
 For a user buying a game off discount we have
@@
 From this analysis it will become clear how I am able to identify $\rho_i$'s on a game-by-game basis, and how more regressors could be accommodated.
-Intuitively, the propensity to leave a review on and off a discount (the like and dislike rates $r_{it}^+$, $r_{it}^-$) are identified by the differences in reviews left on and off a discount.
+Intuitively, the propensities to leave a review when a discount is in place or when one is not (the like and dislike rates $r_{it}^+$, $r_{it}^-$) are identified by the differences in reviews left, respectively, during a discount and the full price.
 In fact, this intuition becomes a rigorous proof, as will be shown shortly.
@@
 For simplicity, I treat $\lambda_{it} = \lambda_i (1 + x_{it}'\beta)$ as known, rather than acknowledging the fact that I only have estimates $\hat{\lambda}_{it} = \hat \lambda_i (1 + x_{it}'\hat \beta)$.
-By the virtue of observing the majority of the games for many periods, the estimates of $\lambda_i$ should be relatively precise; estimates of $\beta$ were estimated using all the observations in the sample, and should be relatively precise as well.
+By the virtue of observing the majority of the games for many periods, the estimates of $\lambda_i$ should be relatively precise; $\beta$ was estimated using all the observations in the sample, and should be relatively precise as well.
 For now I also take the lag $k$ between the time when the user buys the game and leaves a review for the game to be known.
@@
 My second hypothesis, formulated in (\ref{hyp2}), involves the sentiment of the reviews left on and off price promotion.
-Intuitively, one should be able to detect a change in the valence of reviews during a price promotion by simply comparing the ratios of good to bad reviews on and off discount.
+Intuitively, one should be able to detect a change in the sentiment of reviews during a price promotion by simply comparing the ratios of good to bad reviews left during a discount and outside of one.
 In particular, the answer should not depend on any information on the absolute sales.
@@
 \end{equation}
-The estimator of the review score off discount simply calculates the average of the positive reviews left off discount among all the reviews left off discount, confirming our intuition.
+The estimator of the review score outside of a discount restricts attention to reviews left under the full price, and simply calculates the average of positive reviews among all reviews, which is quite intuitive.
 
@@
 First, for each game I observe all reviews ever left, but I only have information on a fraction of buyers, as my measure of the number of buyers is based on the peak-time data only.
-To see what the problem is, consider the following example.
+In order to understand the problem it presents, consider the following example.
 Assume that every buyer of the game leaves a review.
@@
 Both types abandon the game after just one day of playing.
-In such a world my data would register 3 players leaving 5 reviews on a daily basis, implying that one user leaves more than one review.
+In such a world, my data would register 3 players leaving 5 reviews on a daily basis, implying that one user leaves more than one review.
 This is the reason why I refer to the values of $(r_{it}^+, r_{it}^-)$ as rates, rather than probabilities (which they are in the model).
-Proposition \ref{poissonReviews}, stating that the number of good reviews on day $t$ for game $i$ is a Poisson random variable with rate $r_{it}^+\lambda_{it-k}$, could be treated as an assumption, rather than a result.
+Proposition \ref{poissonReviews}, which states that the number of good reviews on day $t$ for game $i$ is a Poisson random variable with rate $r_{it}^+\lambda_{it-k}$, could be treated as an assumption, rather than a result.
 In that case, nothing constrains the $r_{it}^+$ parameter to be less than 1, and the identification argument goes through in exactly the same way.
@@
 I also acknowledge the possibility that there could be a selection over time, when early buyers are very different from late buyers.
-Similarly, the perception of quality might be deteriorating over time as new games, with potentially better characteristics, are coming out.
+Similarly, the perception of quality might deteriorate over time as new games, with potentially better characteristics, come out.
 For this reason, the second set of covariates also adds two variables measuring age: $w_{it} = [1, disc_{it-k}, young_{it}, old_{it}]'$, where $young_{it}$ is a dummy indicating that the game is less than 2 weeks old, and $old_{it}$ is a dummy indicating that the game is more than a year old.
@@
 The estimated change in the probability of leaving a review due to a discount is between `r round((theta2[2]+theta2[6])/(theta2[1]+theta2[5])*100)`% and `r round((theta1[2]+theta1[4])/(theta1[1]+theta1[3])*100)`%, where the smaller estimate is probably more reliable, as it takes into account the effects of age on discounting.
-These results indirectly confirm that the variance effect could be playing a big role in the discounting decision of firms on Steam, as discounts are really effective at bringing new reviews.
+These results indirectly confirm that the variance effect could be playing a big role in the discounting decision of firms on Steam, as discounts are very effective at bringing new reviews.
 
@@
 As we can see, there is no disagreement across specifications on both hypotheses, giving me confidence that this result is robust.
-This is also in accord with the results from the regression of the score on the lags of discounts and controls, presented in Table \ref{reviewLag}, which finds a small negative effect of discounts on the review score.
-Together these findings suggest that the selection effect of discounts is not big, and can not be the decisive force driving the discounting behavior close to review transitions.
+This is also in accordance with the results from the regression of the score on the lags of discounts and controls, presented in Table \ref{reviewLag}, which finds a small negative effect of discounts on the review score.
+Together these findings suggest that the selection effect of discounts is not large, and can not be the decisive force driving the discounting behavior close to review transitions.
 
@@
 The least squares estimates in column (OLS) are mainly presented to check the correlations in the data.
-Games that tend to receive better reviews on discounts discount more.
+Games offer more discounts if they tend to receive better reviews while offering a discount.
 However, the selection effect is not significant in both specifications.
@@
 Their sizes are also quite economically meaningful, suggesting that, in the absence of the selection effect, games close to a positive transition are  `r round(100*reg3$coefficients["pos.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% more likely to go on a discount, and games close to a negative transition are `r -round(100*reg3$coefficients["neg.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% less likely to go on a discount.
-Recall that my estimates of (\ref{potTransitionsReg}) that did not control for the selection effect, found only a limited effect of the proximity to a negative transition on the probability of discount.
+Recall that my previous estimates of Model (\ref{potTransitionsReg}), where I did not control for the selection effect, exhibit only a limited effect of the proximity to a negative transition on the probability of discount.
 
@@
 On the other hand, a product that is close to sliding into a worse tier is averse to a bad outcome, and would benefit little from a good outcome.
-While I manage to test the selection effect directly, I have to test the variance effect by trying to falsify the predictions that follow from it.
-My strongest test is given by the prediction that, in the absence of a positive selection effect, the variance effect has to make a product on the verge of deteriorating its reviews less likely to discount.
+While I manage to test the selection effect directly, I can only test the variance effect by trying to falsify the predictions that follow from it.
+My strongest test is given by the prediction that, in the absence of a positive selection effect, the variance effect must make a product on the verge of deteriorating its reviews less likely to discount.
 When I control for the size of the selection effect, I find that the aforementioned decline in probability of discounting goes from being 4% and weakly significant to 6% and highly significant.
